### 2017-06-07 categorical-models.tex
Basic Category Definitions

\begin{definition}
\label{def:mc}
  A \textbf{monoidal category} $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ is a category $\cat{M}$
  consists of
  \begin{itemize}
  \item a bifunctor $\otimes:\cat{M}\times\cat{M}\rightarrow\cat{M}$, called the tensor product;
  \item an object $I$, called the unit object;
  \item three natural isomorphisms $\alpha$, $\lambda$, and $\rho$ with components
        $$\alpha_{A,B,C}:(A\otimes B)\otimes C\rightarrow A\otimes(B\otimes C)$$
        $$\lambda_A:I\otimes A\rightarrow A$$
        $$\rho_A:A\otimes I\rightarrow A$$
        where $\alpha$ is called associator, $\lambda$ is left unitor, and $\rho$ is right
        unitor,
  \end{itemize}
  such that the following diagrams commute for any objects $A$, $B$, $C$ in $\cat{M}$:
  \begin{mathpar}
  \bfig
    \square/`->`->`->/<2100,400>[
      ((A\otimes B)\otimes C)\otimes D`
      A\otimes((B\otimes C)\otimes D)`
      (A\otimes B)\otimes(C\otimes D)`
      A\otimes(B\otimes(C\otimes D));
      `
      \alpha_{A\otimes B,C,D}`
      id_A\otimes\alpha_{B,C,D}`
      \alpha_{A,B,C\otimes D}]
    \morphism(0,400)<1100,0>[
      ((A\otimes B)\otimes C)\otimes D`
      (A\otimes(B\otimes C))\otimes D;
      \alpha_{A,B,C}\otimes id_D]
    \morphism(1100,400)<1000,0>[
      (A\otimes(B\otimes C))\otimes D`
      A\otimes((B\otimes C)\otimes D);
      \alpha_{A,B\otimes C,D}]
  \efig
  \and
  \bfig
    \Vtriangle<400,400>[
      (A\otimes I)\otimes B`
      A\otimes(I\otimes B)`
      A\otimes B;
      \alpha_{A,I,B}`
      \rho_A\otimes id_B`
      id_A\otimes\lambda_B]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  A \textbf{Lambek category} (or a \textbf{biclosed monoidal category}) is a monoidal category
  $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ equipped with two bifunctors
  $\rightharpoonup:\cat{M}^{op}\times\cat{M}\rightarrow\cat{M}$ and
  $\leftharpoonup:\cat{M}\times\cat{M}^{op}\rightarrow\cat{M}$ that are both right adjoint to
  the tensor product. That is, the following natural bijections hold:
  \begin{center}
  \begin{math}
  \begin{array}{lll}
    \Hom{L}{X\otimes A}{B}\cong\Hom{L}{X}{A\lto B} & \quad\quad\quad\quad & 
    \Hom{L}{A\otimes X}{B}\cong\Hom{L}{X}{B\rto A}
  \end{array}
  \end{math}
  \end{center}
\end{definition}

\begin{definition}
  A \textbf{symmetric monoidal category} is a monoidal category
  $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ together with a natural transformation with
  components $\e{A,B}:A\otimes B\rightarrow B\otimes A$, called exchange, such that the
  following diagrams commute:
  \begin{mathpar}
  \bfig
    \Vtriangle<300,400>[A\otimes I`I\otimes A`A;\e{A,I}`\rho_A`\lambda_A]
  \efig
  \and
  \bfig
    \Vtriangle/=`->`<-/<300,400>[
      A\otimes B`A\otimes B`B\otimes A;
      id_{A\otimes B}`\e{A,B}`\e{B,A}]
  \efig
  \and
  \bfig
    \hSquares/->`->`->``->`->`->/<400>[
      (A\otimes B)\otimes C`A\otimes(B\otimes C)`(B\otimes C)\otimes A`
      (B\otimes A)\otimes C`B\otimes(A\otimes C)`B\otimes(C\otimes A);
      \alpha_{A,B,C}`\e{A,B\otimes C}`\e{A,B}\otimes id_C``
      \alpha_{B,A,C}`\alpha_{B,A,C}`id_B\otimes\e{A,C}]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  A \textbf{symmetric monoidal closed category} $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ is a
  symmetric monoidal category equipped with a bifunctor
  $\limp:\cat{M}^{op}\times\cat{M}\rightarrow\cat{M}$ that is right adjoint to the tensor
  product. That is, the following natural bijection
  $\Hom{\cat{M}}{X\otimes A}{B}\cong\Hom{\cat{M}}{X}{A\limp B}$ holds.
\end{definition}

\begin{lemma}
  \label{lemma:internal-homs-collapse}
  Let $A$ and $B$ be two objects in a Lambek category with the exchange natural transformation.
  Then $(A \lto B) \cong (B \rto A)$.
\end{lemma}
\begin{proof}
  First, notice that for any object $C$ we have
  \begin{center}
  \begin{math}
  \small
  \begin{array}{lllll}
    Hom[C,A\lto B]
    & \cong & Hom[C\otimes A,B] & \cat{L}\text{ is a Lambek category}\\
    & \cong & Hom[A\otimes C,B] & \text{By the exchange }\e{C,A}\\
    & \cong & Hom[C,B\rto A]    & \cat{L}\text{ is a Lambek category}
  \end{array}
  \end{math}
  \end{center}  
  Thus, $A\lto B\cong B\rto A$ by the Yoneda lemma.
\end{proof}
\begin{corollary}
  \label{corollary:LC-with-ex-mc}
  A Lambek category with exchange is symmetric monoidal closed.
\end{corollary}

\begin{definition}
  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories. A \textbf{monoidal
  functor} $(F,\m{})$ from $\cat{M}$ to $\cat{M'}$ is a functor $F:\cat{M}\rightarrow\cat{M'}$
  together with a morphism $\m{I}:I'\rightarrow F(I)$ and a natural transformation
  $\m{A,B}:FA'\otimes FB'\rightarrow F(A\otimes B)$, such that the following diagrams commute
  for any objects $A$, $B$, and $C$ in $\cat{M}$:
  \begin{mathpar}
  \bfig
    \hSquares/->`->`->``->`->`->/<400>[
      (FA\otimes'FB)\otimes'FC`FA\otimes'(FB\otimes'FC)`FA\otimes'F(B\otimes C)`
      F(A\otimes B)\otimes'FC`F((A\otimes B)\otimes C)`F(A\otimes(B\otimes C));
      \alpha'_{FA,FB,FC}`id_{FA}\otimes'\m{A,B}`\m{A,B}\otimes'id_{FC}``
      \m{A,B\otimes C}`\m{A\otimes B,C}`F\alpha_{A,B,C}]
  \efig
  \and
  \bfig
    \square/->`->`<-`->/<600,400>[
      I'\otimes'FA`FA`FI\otimes'FA`F(I\otimes A);
      \lambda'_{FA}`\m{I}\otimes id_{FA}`F\lambda_A`\m{I,A}]
  \efig
  \and
  \bfig
    \square/->`->`<-`->/<600,400>[
      FA\otimes'I'`FA`FA\otimes'FI`F(A\otimes I);
      \rho'_{FA}`\id_{FA}\otimes\m{I}`F\rho_A`\m{A,I}]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  An \textbf{adjunction} between categories $\cat{C}$ and $\cat{D}$ consists of
  \begin{itemize}
  \item a functor $F:\cat{D}\rightarrow\cat{C}$, called the \textbf{left adjoint}
  \item a functor $G:\cat{C}\rightarrow\cat{D}$, called the \textbf{right adjoint}
  \item a natural isomorphism $\phi:\Hom{\cat{C}}{F-}{-}\rightarrow\Hom{\cat{D}}{-}{G-}$
  \item a natural transformation $\eta:id_\cat{D}\rightarrow GF$, called the \textbf{unit}
  \item a natural transformation $\varepsilon:FG\rightarrow id_\cat{C}$, called the
        \textbf{counit}
  \end{itemize}
\end{definition}

\begin{definition}
  Let $(F,\m{})$ and $(G,\n{})$ be monoidal functors from a monoidal category $\cat{M}$ to a
  monoidal category $\cat{M'}$. A \textbf{monoidal natural transformation} from $(F,\m{})$ to 
  $(G,\n{})$ is a natural transformation $\theta:(F,\m{})\rightarrow(G,\n{})$ such that the
  following diagrams commute for any objects $A$ and $B$ in $\cat{M}$:
  \begin{mathpar}
  \bfig
    \square<700,400>[
      FA\otimes'FB`F(A\otimes B)`GA\otimes'GB`G(A\otimes B);
      \m{A,B}`\theta_A\otimes'\theta_B`\theta_{A\otimes B}`\n{A,B}]
  \efig
  \and
  \bfig
    \Vtriangle/->`<-`<-/<400,400>[fI`GI`I';\theta_I`\m{I}`\n{I}]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories,
  $F:\cat{M}\rightarrow\cat{M'}$ and $G:\cat{M}'\rightarrow\cat{M}$ be functors. The adjunction
  $F:\cat{M}\dashv\cat{M'}:G$ is a \textbf{monoidal adjunction} if $F$ and $G$ are monoidal
  functors, and the unit $\eta:id_\cat{M}\rightarrow GF$ and the counit
  $\varepsilon:FG\rightarrow id_\cat{M'}$ are monoidal natural transformations, where
  $id_\cat{M}$ and $id_\cat{M'}$ are the identity functors on $\cat{M}$ and $\cat{M'}$
  respectively.
\end{definition}

\begin{lemma}
  Let $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$ be a symmetric monoidal closed category and
  $(\cat{L},\otimes',I',\alpha',\lambda',\rho')$ be a Lambek category. Since $\cat{C}$ and
  $\cat{L}$ are both monoidal, let $F:\cat{C}\rightarrow\cat{L}$ and
  $G:\cat{L}\rightarrow\cat{C}$ be monoidal functors. Then the adjunction
  $F:\cat{M}\dashv\cat{M'}:G$ is monoidal.
\end{lemma}
\begin{proof}
  Proving the adjunction being monoidal is equivalent to proving the unit $\eta$ and the counit
  $\varepsilon$ are monoidal natural transformations. First, we show that $\eta$ and
  $\varepsilon$ are natural transformations, i.e. the following diagrams commute:
  \begin{mathpar}
  \bfig

  \efig
  \end{mathpar}
\end{proof}

\begin{lemma}
  Let $\cat{C}$ be a category. A \textbf{monad} on $\cat{C}$ consists of an endofunctor
  $T:\cat{C}\rightarrow\cat{C}$ together with two natural transformations
  $\eta:id_\cat{C}\rightarrow T$ and $\mu:T^2\rightarrow id_\cat{C}$, where $id_\cat{C}$
  is the identity functor on $\cat{C}$, such that the following diagrams commute:
  \begin{mathpar}
  \bfig
    \square<400,400>[T^3`T^2`T^2`T;T\mu`\mu_T`\mu`\mu]
  \efig
  \and
  \bfig
    \square<400,400>[T`T^2`T^2`T;\eta_T`T\eta`\mu`\mu]
    \morphism(0,400)/=/<400,-400>[T`T;]
  \efig
  \end{mathpar}
\end{lemma}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: main.tex
%%% End:

### 2017-06-13 categorical-models.tex
Proof of non-commutative monad.

@@
 \begin{definition}
-  An \textbf{adjunction} between categories $\cat{C}$ and $\cat{D}$ consists of
-  \begin{itemize}
-  \item a functor $F:\cat{D}\rightarrow\cat{C}$, called the \textbf{left adjoint}
-  \item a functor $G:\cat{C}\rightarrow\cat{D}$, called the \textbf{right adjoint}
-  \item a natural isomorphism $\phi:\Hom{\cat{C}}{F-}{-}\rightarrow\Hom{\cat{D}}{-}{G-}$
-  \item a natural transformation $\eta:id_\cat{D}\rightarrow GF$, called the \textbf{unit}
-  \item a natural transformation $\varepsilon:FG\rightarrow id_\cat{C}$, called the
-        \textbf{counit}
-  \end{itemize}
+  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
+  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories. A \textbf{symmetric
+  monoidal functor} $F:\cat{M}\rightarrow\cat{M'}$ is a monoidal functor $(F,m)$ that satisfies
+  the following coherence diagram:
+  \begin{mathpar}
+  \bfig
+    \square<700,400>[
+      FA\otimes'FB`FB\otimes'FA`F(A\otimes B)`F(B\otimes A);
+      \e{FA,FB}`\m{A,B}`\m{B,A}`F\e{A,B}]
+  \efig
+  \end{mathpar}
+\end{definition}
+
+\begin{definition}
+  An \textbf{adjunction} between categories $\cat{C}$ and $\cat{D}$ consists of two functors
+  $F:\cat{D}\rightarrow\cat{C}$, called the \textbf{left adjoint}, and
+  $G:\cat{C}\rightarrow\cat{D}$, called the \textbf{right adjoint}, and two natural
+  transformations $\eta:id_\cat{D}\rightarrow GF$, called the \textbf{unit}, and
+  $\varepsilon:FG\rightarrow id_\cat{C}$, called the \textbf{counit}, such that the following
+  diagrams commute for any object $A$ in $\cat{C}$ and $B$ in $\cat{D}$:
+  \begin{mathpar}
+  \bfig
+    \Vtriangle/->`=`->/<400,400>[FB`FGFB`FB;F\eta_B``\varepsilon_{FB}]
+  \efig
+  \and
+  \bfig
+    \Vtriangle/->`=`->/<400,400>[GA`GFGA`GA;\eta_{GA}``G\varepsilon_A]
+  \efig
+  \end{mathpar}
 \end{definition}
@@
   \bfig
-    \Vtriangle/->`<-`<-/<400,400>[fI`GI`I';\theta_I`\m{I}`\n{I}]
+    \Vtriangle/->`<-`<-/<400,400>[FI`GI`I';\theta_I`\m{I}`\n{I}]
   \efig
@@
   $F:\cat{M}\dashv\cat{M'}:G$ is a \textbf{monoidal adjunction} if $F$ and $G$ are monoidal
-  functors, and the unit $\eta:id_\cat{M}\rightarrow GF$ and the counit
-  $\varepsilon:FG\rightarrow id_\cat{M'}$ are monoidal natural transformations, where
-  $id_\cat{M}$ and $id_\cat{M'}$ are the identity functors on $\cat{M}$ and $\cat{M'}$
-  respectively.
+  functors, and the unit $\eta$ and the counit $\varepsilon$ are monoidal natural
+  transformations.
 \end{definition}
 
-\begin{lemma}
-  Let $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$ be a symmetric monoidal closed category and
-  $(\cat{L},\otimes',I',\alpha',\lambda',\rho')$ be a Lambek category. Since $\cat{C}$ and
-  $\cat{L}$ are both monoidal, let $F:\cat{C}\rightarrow\cat{L}$ and
-  $G:\cat{L}\rightarrow\cat{C}$ be monoidal functors. Then the adjunction
-  $F:\cat{M}\dashv\cat{M'}:G$ is monoidal.
-\end{lemma}
-\begin{proof}
-  Proving the adjunction being monoidal is equivalent to proving the unit $\eta$ and the counit
-  $\varepsilon$ are monoidal natural transformations. First, we show that $\eta$ and
-  $\varepsilon$ are natural transformations, i.e. the following diagrams commute:
+\begin{definition}
+  A \textbf{SMCC-Lambek model} consists of
+  \begin{itemize}
+  \item a symmetric monoidal closed category $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$;
+  \item a Lambek category $(\cat{L},\otimes',I',\alpha',\lambda',\rho')$;
+  \item a monoidal adjunction $F:\cat{C}\dashv\cat{L}:G$, where $F:\cat{C}\rightarrow\cat{L}$
+        and $G:\cat{L}\rightarrow\cat{C}$ are monoidal functors.
+  \end{itemize}
+\end{definition}
+
+Thus, in a SMCC-Lambek model, the following four diagrams commute because $\eta$ and
+$\varepsilon$ are monoidal natural transformations:
 \begin{mathpar}
 \bfig
-
+  \square/=`->`->`/<1600,400>[
+    A\otimes B`A\otimes B`GFA\otimes GFB`GF(A\otimes B);
+    id_{A\otimes B}`\eta_A\otimes\eta_B`\eta_{A\otimes B}`]
+  \morphism<800,0>[GFA\otimes GFB`G(FA\otimes FB);\n{FA,FB}]
+  \morphism(800,0)<800,0>[G(FA\otimes FB)`GF(A\otimes B);G\m{A,B}]
+\efig
+\and
+\bfig
+  \square/->`=`<-`->/<400,400>[I`GFI`I`GI';\eta_I``G\m{I}`\n{I'}]
 \efig
 \end{mathpar}
-\end{proof}
+\begin{mathpar}
+\bfig
+  \square/`->`->`=/<1600,400>[
+    FGA\otimes FGB`FG(A\otimes B)`A\otimes B`A\otimes B;
+    `
+    \varepsilon_A\otimes\varepsilon_B`\varepsilon_{A\otimes B}`]
+  \morphism(0,400)<800,0>[FGA\otimes FGB`F(GA\otimes GB);\m{GA,GB}]
+  \morphism(800,400)<800,0>[F(GA\otimes GB)`FG(A\otimes B);F\n{A,B}]
+\efig
+\and
+\bfig
+  \square/->`<-`=`<-/<400,400>[FGI'`I'`FI`I';\varepsilon_{I'}`F\n{I'}``\m{I}]
+\efig
+\end{mathpar}
+And the following two diagrams commute because of the adjunction:
+\begin{mathpar}
+\bfig
+  \Vtriangle/->`=`->/<400,400>[FA`FGFA`FA;F\eta_A``\varepsilon_{FA}]
+\efig
+\and
+\bfig
+  \Vtriangle/->`=`->/<400,400>[GB`GFGB`GB;\eta_{GX}``G\varepsilon_B]
+\efig
+\end{mathpar}
 
-\begin{lemma}
+\begin{definition}
   Let $\cat{C}$ be a category. A \textbf{monad} on $\cat{C}$ consists of an endofunctor
@@
   \end{mathpar}
+\end{definition}
+
+\begin{lemma}
+  The monad on the SMCC $\cat{C}$ in a SMCC-Lambek model is monoidal.
 \end{lemma}
+\begin{proof}
+  We define the monad $T$ on the $\cat{C}$ in the adjunction of a SMCC-Lambek model as $T=GF$,
+  and the two corresponding natural transformations $\eta:id_\cat{C}\rightarrow T$ and
+  $\mu:T^2\rightarrow T$ are defined as
+  $$\eta:id_\cat{C}\rightarrow GF$$
+  $$\mu=GF\varepsilon_A=\varepsilon_{GFA}:GFGF\rightarrow GF$$
+  where $\eta$ is the unit and $\mu$ is the counit in the adjunction $F:\cat{C}\dashv\cat{L}:G$,
+  and $(F,m)$ and $(G,n)$ are monoidal functors. \\
+  Thus, we have
+  $$\q{A,B}=G\m{A,B}\circ\n{FA,FB}:TA\otimes TB\rightarrow T(A\otimes B)$$
+  $$\q{I}=G\m{I}\circ\n{I'}:I\rightarrow TI$$
+  The monad $T$ being monoidal means
+  \begin{enumerate}
+  \item $T$ is a monoidal functor i.e. the folllowing diagrams commute:
+        \begin{mathpar}
+        \bfig
+          \hSquares/->`->`->``->`->`->/<400>[
+            (TA\otimes TB)\otimes TC`TA\otimes(TB\otimes TC)`TA\otimes T(B\otimes C)`
+            T(A\otimes B)\otimes TC`T((A\otimes B)\otimes C)`T(A\otimes(B\otimes C));
+            \alpha_{TA,TB,TC}`id_{TA}\otimes\q{B,C}`\q{A,B}\otimes id_{TC}``
+            \q{A,B\otimes C}`\q{A\otimes B,C}`T\alpha_{A,B,C}]
+        \efig
+        \and
+        \bfig
+          \square/->`->`<-`->/<600,400>[
+            I\otimes TA`TA`TI\otimes TA`T(I\otimes A);
+            \lambda_{TA}`\q{I}\otimes id_{TA}`T\lambda_A`\q{I,A}]
+        \efig
+        \and
+        \bfig
+          \square/->`->`<-`->/<600,400>[
+            TA\otimes I`TA`TA\otimes TI`T(A\otimes I);
+            \rho_{TA}`id_{TA}\otimes\q{I}`T\rho_A`\q{A,I}]
+        \efig
+        \end{mathpar}
+        We write $GF$ instead of $T$ in the diagram chasings for clarity. \\
+        By replacing $\q{}$ with its definition, the first diagram above commutes by the
+        following diagram chasing, where the two hexagons commute because $G$ and $F$ are
+        monoidal functors, and the two quadrilaterals commute by the naturality of $\n{}$.
+        \begin{mathpar}
+        \bfig
+          \iiixiii/->`->`->``->```->`<-`->``/<1400,400>[
+            (GFA\otimes GFB)\otimes GFC`GFA\otimes(GFB\otimes GFC)`GFA\otimes G(FB\otimes'FC)`
+            G(FA\otimes'FB)\otimes GFC`G(FA\otimes'(FB\otimes'FC))`GFA\otimes GF(B\otimes C)`
+            GF(A\otimes B)\otimes GFC`G((FA\otimes'FB)\otimes'FC)`G(FA\otimes'F(B\otimes C));
+            \alpha_{GFA,GFB,GFC}`id_{GFA}\otimes\n{FB,FC}`\n{FA,FB}\otimes id_{GFC}``
+            id_{GFA}\otimes G\m{B,C}```G\m{A,B}\otimes id_{GFC}`G\alpha'_{FA,FB,FC}`
+            \n{FA,F(B\otimes C)}``]
+          \morphism(2800,800)|m|<-1400,-400>[
+            GFA\otimes G(FB\otimes'FC)`G(FA\otimes'(FB\otimes'FC));\n{FA,FB\otimes'FC}]
+          \morphism(0,400)|m|<1400,-400>[
+            G(FA\otimes'FB)\otimes GFC`G((FA\otimes'FB)\otimes'FC);\n{FA\otimes'FB,FC}]
+          \morphism(1400,400)|m|<1400,-400>[
+            G(FA\otimes'(FB\otimes'FC))`G(FA\otimes'F(B\otimes C));G(id_{FA}\otimes'\m{B,C})]
+          \ptriangle(0,-400)|mlm|/`->`->/<1400,400>[
+            GF(A\otimes B)\otimes GFC`G((FA\otimes'FB)\otimes'FC)`G(F(A\otimes B)\otimes'FC);
+            `\n{F(A\otimes B),FC}`G(\m{A,B}\otimes id_{FC})]
+          \morphism(0,-400)|b|<1400,0>[
+            G(F(A\otimes B)\otimes'FC)`GF((A\otimes B)\otimes C);G\m{A\otimes B,C}]
+          \dtriangle(1400,-400)|mrb|/`->`->/<1400,400>[
+            G(FA\otimes'F(B\otimes C))`GF((A\otimes B)\otimes C)`GF(A\otimes(B\otimes C));
+            `G\m{A,B\otimes C}`GF\alpha_{A,B,C}]
+        \efig
+        \end{mathpar}
+        The first square above commutes by the following diagram chasing, in which the top
+        quadrilateral commutes because $G$ is monoidal, the right quadrilateral commutes because
+        $F$ is monoidal, and the left square commutes by the naturality of $\n{}$.
+        \begin{mathpar}
+        \bfig
+          \ptriangle/->`->`/<1600,400>[
+            I\otimes GFA`GFA`GI'\otimes GFA;\lambda_{GFA}`\n{I'}\otimes id_{GFA}`]
+          \square(0,-400)|lmmb|<800,400>[
+            GI'\otimes GFA`G(I'\otimes'FA)`GFI\otimes GFA`G(FI\otimes'FA);
+            \n{I',FA}`G\m{I}\otimes id_{GFA}`G(\m{I}\otimes'id_{FA})`\n{FI,FA}]
+          \morphism(800,0)|m|<800,400>[G(I'\otimes'FA)`GFA;G\lambda'_{FA}]
+          \dtriangle(800,-400)/`<-`->/<800,800>[
+            GFA`G(FI\otimes'FA)`GF(I\otimes A);
+            `GF\lambda_A`G\m{I,A}]
+        \efig
+        \end{mathpar}
+        Similarly, the second square above commutes by the following diagram chasing:
+        \begin{mathpar}
+        \bfig
+          \ptriangle/->`->`/<1600,400>[
+            GFA\otimes I`GFA`GFA\otimes GI';\rho_{GFA}`id_{GFA}\otimes\n{I'}`]
+          \square(0,-400)|lmmb|<800,400>[
+            GFA\otimes GI'`G(FA\otimes'I')`GFA\otimes GFI`G(FA\otimes'FI);
+            \n{FA,I'}`id_{GFA}\otimes G\m{I}`G(id_{FA}\otimes\m{I})`\n{FA,FI}]
+          \morphism(800,0)|m|<800,400>[G(FA\otimes'I')`GFA;G\rho'_{FA}]
+          \dtriangle(800,-400)/`<-`->/<800,800>[
+            GFA`G(FA\otimes'FI)`GF(A\otimes I);
+            `GF\rho_A`G\m{A,I}]
+        \efig
+        \end{mathpar}
+  \item $\eta$ is a monoidal natural transformation, i.e. the following diagrams commute. In
+        fact, since $\eta$ is the unit of the monoidal adjunction, $\eta$ is monoidal and thus
+        the following two diagrams commute.
+        \begin{mathpar}
+        \bfig
+          \square/=`->`->`->/<600,400>[
+            A\otimes B`A\otimes B`TA\otimes TB`T(A\otimes B);
+            `\eta_A\otimes\eta_B`\eta_{A\otimes B}`\q{A,B}]
+        \efig
+        \and
+        \bfig
+          \Vtriangle/->`=`<-/<400,400>[I`TI`I;\eta_I``\q{I}]
+        \efig
+        \end{mathpar}
+  \item $\mu$ is a monoidal natural transformation, i.e. the following diagrams commute. Since
+        $\mu=\varepsilon_{GFA}$, $\mu$ is obviously also monoidal since $\varepsilon$ also is.
+        Thus the following diagrams commute.
+        \begin{mathpar}
+        \bfig
+          \square/`->`->`->/<1500,400>[
+            T^2A\otimes T^2B`T^2(A\otimes B)`TA\otimes TB`T(A\otimes B);
+            `\mu_A\otimes\mu_B`\mu_{A\otimes B}`\q{A,B}]
+          \morphism(0,400)<800,0>[T^2A\otimes T^2B`T(TA\otimes TB);\q{TA,TB}]
+          \morphism(800,400)<700,0>[T(TA\otimes TB)`T^2(A\otimes B);T\q{A,B}]
+        \efig
+        \and
+        \bfig
+          \square/->`<-`<-`<-/<400,400>[T^2I`TI`TI`I;\mu_I`T\q{I}`\q{I}`\q{I}]
+        \efig
+        \end{mathpar}
+  \end{enumerate}
+\end{proof}
+
+However, the monad $T$ we get from the SMCC-Lambek model is not symmetric because the following
+diagram does not commute:
+\begin{mathpar}
+\bfig
+  \hSquares/->`->`->``->`->`->/<400>[
+    GFA\otimes GFB`GFB\otimes GFA`G(FB\otimes'FA)`G(FA\otimes'FB)`GF(A\otimes B)`GF(B\otimes A);
+    \e{GFA,GFB}`\n{FB,FA}`\n{FA,FB}``G\m{B,A}`G\m{A,B}`GF\e{A,B}]
+\efig
+\end{mathpar}
+
+Therefore, the monad is non-commutative.
 

### 2017-06-14 categorical-models.tex
Proof of strong monad.

@@
 \begin{definition}
-  A \textbf{symmetric monoidal category} is a monoidal category
+  A \textbf{symmetric monoidal category} (SMCC) is a monoidal category
   $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ together with a natural transformation with
-  components $\e{A,B}:A\otimes B\rightarrow B\otimes A$, called exchange, such that the
+  components $\e{A,B}:A\otimes B\rightarrow B\otimes A$, called \textbf{exchange}, such that the
   following diagrams commute:
@@
   $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories. A \textbf{symmetric
-  monoidal functor} $F:\cat{M}\rightarrow\cat{M'}$ is a monoidal functor $(F,m)$ that satisfies
-  the following coherence diagram:
+  monoidal functor} $F:\cat{M}\rightarrow\cat{M'}$ is a monoidal functor $(F,\m{})$ that
+  satisfies the following coherence diagram:
   \begin{mathpar}
@@
 \begin{lemma}
+  \label{lem:monoidal-monad}
   The monad on the SMCC $\cat{C}$ in a SMCC-Lambek model is monoidal.
@@
   where $\eta$ is the unit and $\mu$ is the counit in the adjunction $F:\cat{C}\dashv\cat{L}:G$,
-  and $(F,m)$ and $(G,n)$ are monoidal functors. \\
+  and $(F,\m{})$ and $(G,\n{})$ are monoidal functors. \\
   Thus, we have
@@
   \item $\mu$ is a monoidal natural transformation, i.e. the following diagrams commute. Since
-        $\mu=\varepsilon_{GFA}$, $\mu$ is obviously also monoidal since $\varepsilon$ also is.
-        Thus the following diagrams commute.
+        $\mu=\varepsilon_{GFA}$ and $\varepsilon$ is monoidal, so is $\mu$. Thus the following
+        diagrams commute.
         \begin{mathpar}
@@
 
-Therefore, the monad is non-commutative.
+\begin{definition}
+  \label{def:strong-monad}
+  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ be a monoidal category and $(T,\eta,\mu)$ be a
+  monad on $\cat{M}$. $T$ is a \textbf{strong monad} if there is natural transformation $\tau$, 
+  called the \textbf{tensorial strength}, with components
+  $\tau_{A,B}:A\otimes TB\rightarrow T(A\otimes B)$ such that the following diagrams commute:
+  \begin{mathpar}
+  \bfig
+    \Vtriangle<400,400>[I\otimes TA`T(I\otimes A)`TA;\tau_{I,A}`\lambda_{TA}`T\lambda_A]
+  \efig
+  \and
+  \bfig
+    \Vtriangle<400,400>[
+      A\otimes B`A\otimes TB`T(A\otimes B);id_A\otimes\eta_B`\eta_{A\otimes B}`\tau_{A,B}]
+  \efig
+  \and
+  \bfig
+    \square/->`->`->`/<1800,400>[
+      (A\otimes B)\otimes TC`T((A\otimes B)\otimes C)`
+      A\otimes(B\otimes TC)`T(A\otimes(B\otimes C));
+      \tau_{A\otimes B,C}`\alpha_{A,B,TC}`T\alpha_{A,B,C}`]
+    \morphism<900,0>[A\otimes(B\otimes TC)`A\otimes T(B\otimes C);id_A\otimes\tau_{B,C}]
+    \morphism(900,0)<900,0>[A\otimes T(B\otimes C)`T(A\otimes(B\otimes C));\tau_{A,B\otimes C}]
+  \efig
+  \and
+  \bfig
+    \square/`->`->`->/<1400,400>[
+      A\otimes T^2B`T^2(A\otimes B)`A\otimes TB`T(A\otimes B);
+      `id_A\otimes\mu_B`\mu_{A\otimes B}`\tau_{A,B}]
+    \morphism(0,400)<700,0>[A\otimes T^2B`T(A\otimes TB);\tau_{A,TB}]
+    \morphism(700,400)<700,0>[T(A\otimes TB)`T^2(A\otimes B);T\tau_{A,B}]
+  \efig
+  \end{mathpar}
+\end{definition}
+
+\begin{lemma}
+  \label{lem:strong-monad}
+  The monad on the SMCC in a SMCC-Lambek model is strong.
+\end{lemma}
+\begin{proof}
+  Let $F:\cat{C}\vdash\cat{L}:G$ be a SMCC-Lambek model, where
+  $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$ is an SMCC,
+  $(\cat{M},\otimes',I',\alpha',\lambda',\rho')$ is a Lambek category, and $(F,\m{})$ and
+  $(G,\n{})$ are monoidal functors. Let $(T,\eta,\mu)$ be the monad on $\cat{C}$ where
+  $T=GF$. We have proved that $T$ is monoidal with the natural transformation
+  $\q{A,B}:TA\otimes TB\rightarrow T(A\otimes B)$ and the morphism $\q{I}:I\rightarrow TI$
+  defined as in Lemma~\ref{lem:monoidal-monad}. \\
+  We define the tensorial strength $\tau_{A,B}:A\otimes TB\rightarrow T(A\otimes B)$ as
+  $\tau_{A,B}=\q{A,B}\circ\eta_A\otimes id_{TB}$. \\
+  Since $\eta$ is a monoidal natural transformation, we have $\eta_I=G\m{I}\circ\n{I'}$.
+  Therefore $\eta_I=\q{I}$. Thus the following diagram commutes because $T$ is monoidal,
+  where the composition $\q{I,A}\circ\q{I}\otimes id_{TA}$ is the definition of $\tau_{I,A}$. So
+  the first triangle in Defition~\ref{def:strong-monad} commutes.
+  \begin{mathpar}
+  \bfig
+    \square/->`->`->`<-/<600,400>[
+      I\otimes TA`TI\otimes TA`TA`T(I\otimes A);
+      \q{I}\otimes id_{TA}`\lambda_{TA}`\q{I,A}`T\lambda_A]
+  \efig
+  \end{mathpar}
+  Similarly, by using the definition of $\tau$, the the second triangle in the definition is
+  equivalent to the following diagram, which commutes because $\eta$ is a monoidal natural
+  transformation:
+  \begin{mathpar}
+  \bfig
+    \square/->`->`->`<-/<600,400>[
+      A\otimes B`A\otimes TB`T(A\otimes B)`TA\otimes TB;
+      id_A\otimes\eta_B`\eta_{A\otimes B}`\eta_A\otimes id_{TB}`\q{A,B}]
+    \morphism(0,400)|m|<600,-400>[A\otimes B`TA\otimes TB;\eta_A\otimes\eta_B]
+  \efig
+  \end{mathpar}
+  The first pentagon in the definition commutes by the following diagram chasing, because
+  $\eta$ are $\alpha$ natural transformations and $T$ is monoidal:
+  \begin{mathpar}
+  \bfig
+    \qtriangle|amm|/->`->`<-/<1000,400>[
+      (A\otimes B)\otimes TC`T(A\otimes B)\otimes TC`(TA\otimes TB)\otimes TC;
+      \eta_{A\otimes B}\otimes id_{TC}`
+      (\eta_A\otimes\eta_B)\otimes id_{TC}`
+      \q{A,B}\otimes id_{TC}]
+    \morphism(0,400)<0,-400>[(A\otimes B)\otimes TC`A\otimes(B\otimes TC);\alpha_{A,B,TC}]
+    \morphism(1000,0)|m|<0,-400>[
+      (TA\otimes TB)\otimes TC`TA\otimes(TB\otimes TC);\alpha_{TA,TB,TC}]
+    \Dtriangle(0,-800)|lmm|/->`->`<-/<1000,400>[
+      A\otimes(B\otimes TC)`TA\otimes(TB\otimes TC)`A\otimes(TB\otimes TC);
+      id_A\otimes(\eta_B\otimes id_{TC})`
+      \eta_A\otimes(\eta_B\otimes id_{TC})`
+      \eta_A\otimes id_{TB\otimes TC}]
+    \morphism(0,-800)|b|<1000,0>[
+      A\otimes(TB\otimes TC)`A\otimes T(B\otimes C);id_A\otimes\q{B,C}]
+    \qtriangle(1000,0)|amr|/->``->/<1000,400>[
+      T(A\otimes B)\otimes TC`T((A\otimes B)\otimes C)`T(A\otimes(B\otimes C));
+      \q{A\otimes B,C}``T\alpha_{A,B,C}]
+    \morphism(2000,-800)<0,800>[
+      TA\otimes T(B\otimes C)`T(A\otimes(B\otimes C));\q{A,B\otimes C}]
+    \btriangle(1000,-800)|mmb|/`->`->/<1000,400>[
+      TA\otimes(TB\otimes TC)`A\otimes T(B\otimes C)`TA\otimes T(B\otimes C);
+      `id_{TA}\otimes\q{B,C}`\eta_A\otimes id_{T(B\otimes C)}]
+  \efig
+  \end{mathpar}
+  The last diagram in the definition commtues by the following diagram chasing, because $T$ is a
+  monad, $\q{}$ is a natural transformation, and $\mu$ is a monoidal natural transformation:
+  \begin{mathpar}
+  \bfig
+    \ptriangle/->`->`/<700,400>[
+      A\otimes T^2B`TA\otimes T^2B`A\otimes TB;\eta_A\otimes id_{T^2B}`id_A\otimes\mu_B`]
+    \btriangle(0,-400)/->``->/<700,400>[
+      A\otimes TB`TA\otimes TB`T(A\otimes B);\eta_A\otimes id_{TB}``\q{A,B}]
+    \morphism(700,400)|m|<-700,-800>[TA\otimes T^2B`TA\otimes TB;id_{TA}\otimes\mu_B]
+    \morphism(700,0)|m|<-700,-400>[TA\otimes T^2B`TA\otimes TB;id_{TA}\otimes\mu_B]
+    \qtriangle(700,0)/->``->/<1800,400>[
+      TA\otimes T^2B`T(A\otimes TB)`T(TA\otimes TB);\q{A,TB}``T(\eta_A\otimes id_{TB})]
+    \btriangle(700,0)|mmm|/=`->`<-/<900,400>[
+      TA\otimes T^2B`TA\otimes T^2B`T^2A\otimes T^2B;
+      `T\eta_A\otimes id_{T^2B}`\mu_A\otimes id_{T^2B}]
+    \morphism(1600,0)|m|<900,0>[T^2A\otimes T^2B`T(TA\otimes TB);\q{TA,TB}]
+    \morphism(1600,0)|m|<-1600,-400>[T^2A\otimes T^2B`TA\otimes TB;\mu_A\otimes\mu_B]
+    \dtriangle(700,-400)/`->`<-/<1800,400>[
+      T(TA\otimes TB)`T(A\otimes B)`T^2(A\otimes B);`T\q{A,B}`\mu_{A\otimes B}]
+  \efig
+  \end{mathpar}
+\end{proof}
+
+\begin{definition}
+  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ be a symmetric monoidal category with exchange
+  $\e{}$, and $(T,\eta,\mu)$ be a strong monad on $\cat{M}$. Then there is a \textbf{``twisted''
+  tensorial strength} $\tau'_{A,B}:TA\otimes B\rightarrow T(A\otimes B)$ defined as
+  $\tau'_{A,B}=T\e{}\circ\tau_{B,A}\circ\e{}$. We can construct a pair of natural
+  transformations $\Phi$, $\Phi'$ with components
+  $\Phi_{A,B},\Phi'_{A,B}:TA\otimes TB\rightarrow T(A\otimes B)$ defined as
+  $\Phi_{A,B}=\mu_{A\otimes B}\circ T\tau'_{A,B}\circ\tau_{TA,B}$ and
+  $\Phi'_{A,B}=\mu_{A\otimes B}\circ T\tau_{A,B}\circ\tau'_{A,TB}$. If $\Phi=\Phi'$, then the
+  monad $T$ is \textbf{commutative}.
+\end{definition}
+
+\begin{lemma}
+  Let $\cat{M}$ be a symmetric monoidal category and $T$ be a strong monad on $\cat{M}$. Then
+  $T$ is a symmetric monoidal functor iff it is commutative.
+\end{lemma}
+
+\begin{theorem}
+  The monad on the SMCC in a SMCC-Lambek model is not commutative.
+\end{theorem}
 

### 2017-06-22 categorical-models.tex
categorical-models

--- 2017-06-13 categorical-models.tex
@@
-\begin{definition}
-\label{def:mc}
-  A \textbf{monoidal category} $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ is a category $\cat{M}$
-  consists of
-  \begin{itemize}
-  \item a bifunctor $\otimes:\cat{M}\times\cat{M}\rightarrow\cat{M}$, called the tensor product;
-  \item an object $I$, called the unit object;
-  \item three natural isomorphisms $\alpha$, $\lambda$, and $\rho$ with components
-        $$\alpha_{A,B,C}:(A\otimes B)\otimes C\rightarrow A\otimes(B\otimes C)$$
-        $$\lambda_A:I\otimes A\rightarrow A$$
-        $$\rho_A:A\otimes I\rightarrow A$$
-        where $\alpha$ is called associator, $\lambda$ is left unitor, and $\rho$ is right
-        unitor,
-  \end{itemize}
-  such that the following diagrams commute for any objects $A$, $B$, $C$ in $\cat{M}$:
-  \begin{mathpar}
-  \bfig
-    \square/`->`->`->/<2100,400>[
-      ((A\otimes B)\otimes C)\otimes D`
-      A\otimes((B\otimes C)\otimes D)`
-      (A\otimes B)\otimes(C\otimes D)`
-      A\otimes(B\otimes(C\otimes D));
-      `
-      \alpha_{A\otimes B,C,D}`
-      id_A\otimes\alpha_{B,C,D}`
-      \alpha_{A,B,C\otimes D}]
-    \morphism(0,400)<1100,0>[
-      ((A\otimes B)\otimes C)\otimes D`
-      (A\otimes(B\otimes C))\otimes D;
-      \alpha_{A,B,C}\otimes id_D]
-    \morphism(1100,400)<1000,0>[
-      (A\otimes(B\otimes C))\otimes D`
-      A\otimes((B\otimes C)\otimes D);
-      \alpha_{A,B\otimes C,D}]
-  \efig
-  \and
-  \bfig
-    \Vtriangle<400,400>[
-      (A\otimes I)\otimes B`
-      A\otimes(I\otimes B)`
-      A\otimes B;
-      \alpha_{A,I,B}`
-      \rho_A\otimes id_B`
-      id_A\otimes\lambda_B]
-  \efig
-  \end{mathpar}
-\end{definition}
-
-\begin{definition}
-  A \textbf{Lambek category} (or a \textbf{biclosed monoidal category}) is a monoidal category
-  $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ equipped with two bifunctors
-  $\rightharpoonup:\cat{M}^{op}\times\cat{M}\rightarrow\cat{M}$ and
-  $\leftharpoonup:\cat{M}\times\cat{M}^{op}\rightarrow\cat{M}$ that are both right adjoint to
-  the tensor product. That is, the following natural bijections hold:
-  \begin{center}
-  \begin{math}
-  \begin{array}{lll}
-    \Hom{L}{X\otimes A}{B}\cong\Hom{L}{X}{A\lto B} & \quad\quad\quad\quad & 
-    \Hom{L}{A\otimes X}{B}\cong\Hom{L}{X}{B\rto A}
-  \end{array}
-  \end{math}
-  \end{center}
-\end{definition}
-
-\begin{definition}
-  A \textbf{symmetric monoidal category} is a monoidal category
-  $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ together with a natural transformation with
-  components $\e{A,B}:A\otimes B\rightarrow B\otimes A$, called exchange, such that the
-  following diagrams commute:
-  \begin{mathpar}
-  \bfig
-    \Vtriangle<300,400>[A\otimes I`I\otimes A`A;\e{A,I}`\rho_A`\lambda_A]
-  \efig
-  \and
-  \bfig
-    \Vtriangle/=`->`<-/<300,400>[
-      A\otimes B`A\otimes B`B\otimes A;
-      id_{A\otimes B}`\e{A,B}`\e{B,A}]
-  \efig
-  \and
-  \bfig
-    \hSquares/->`->`->``->`->`->/<400>[
-      (A\otimes B)\otimes C`A\otimes(B\otimes C)`(B\otimes C)\otimes A`
-      (B\otimes A)\otimes C`B\otimes(A\otimes C)`B\otimes(C\otimes A);
-      \alpha_{A,B,C}`\e{A,B\otimes C}`\e{A,B}\otimes id_C``
-      \alpha_{B,A,C}`\alpha_{B,A,C}`id_B\otimes\e{A,C}]
-  \efig
-  \end{mathpar}
-\end{definition}
-
-\begin{definition}
-  A \textbf{symmetric monoidal closed category} $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ is a
-  symmetric monoidal category equipped with a bifunctor
-  $\limp:\cat{M}^{op}\times\cat{M}\rightarrow\cat{M}$ that is right adjoint to the tensor
-  product. That is, the following natural bijection
-  $\Hom{\cat{M}}{X\otimes A}{B}\cong\Hom{\cat{M}}{X}{A\limp B}$ holds.
-\end{definition}
-
-\begin{lemma}
-  \label{lemma:internal-homs-collapse}
-  Let $A$ and $B$ be two objects in a Lambek category with the exchange natural transformation.
-  Then $(A \lto B) \cong (B \rto A)$.
-\end{lemma}
-\begin{proof}
-  First, notice that for any object $C$ we have
-  \begin{center}
-  \begin{math}
-  \small
-  \begin{array}{lllll}
-    Hom[C,A\lto B]
-    & \cong & Hom[C\otimes A,B] & \cat{L}\text{ is a Lambek category}\\
-    & \cong & Hom[A\otimes C,B] & \text{By the exchange }\e{C,A}\\
-    & \cong & Hom[C,B\rto A]    & \cat{L}\text{ is a Lambek category}
-  \end{array}
-  \end{math}
-  \end{center}  
-  Thus, $A\lto B\cong B\rto A$ by the Yoneda lemma.
-\end{proof}
-\begin{corollary}
-  \label{corollary:LC-with-ex-mc}
-  A Lambek category with exchange is symmetric monoidal closed.
-\end{corollary}
-
-\begin{definition}
-  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
-  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories. A \textbf{monoidal
-  functor} $(F,\m{})$ from $\cat{M}$ to $\cat{M'}$ is a functor $F:\cat{M}\rightarrow\cat{M'}$
-  together with a morphism $\m{I}:I'\rightarrow F(I)$ and a natural transformation
-  $\m{A,B}:FA'\otimes FB'\rightarrow F(A\otimes B)$, such that the following diagrams commute
-  for any objects $A$, $B$, and $C$ in $\cat{M}$:
-  \begin{mathpar}
-  \bfig
-    \hSquares/->`->`->``->`->`->/<400>[
-      (FA\otimes'FB)\otimes'FC`FA\otimes'(FB\otimes'FC)`FA\otimes'F(B\otimes C)`
-      F(A\otimes B)\otimes'FC`F((A\otimes B)\otimes C)`F(A\otimes(B\otimes C));
-      \alpha'_{FA,FB,FC}`id_{FA}\otimes'\m{A,B}`\m{A,B}\otimes'id_{FC}``
-      \m{A,B\otimes C}`\m{A\otimes B,C}`F\alpha_{A,B,C}]
-  \efig
-  \and
-  \bfig
-    \square/->`->`<-`->/<600,400>[
-      I'\otimes'FA`FA`FI\otimes'FA`F(I\otimes A);
-      \lambda'_{FA}`\m{I}\otimes id_{FA}`F\lambda_A`\m{I,A}]
-  \efig
-  \and
-  \bfig
-    \square/->`->`<-`->/<600,400>[
-      FA\otimes'I'`FA`FA\otimes'FI`F(A\otimes I);
-      \rho'_{FA}`\id_{FA}\otimes\m{I}`F\rho_A`\m{A,I}]
-  \efig
-  \end{mathpar}
-\end{definition}
-
-\begin{definition}
-  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
-  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories. A \textbf{symmetric
-  monoidal functor} $F:\cat{M}\rightarrow\cat{M'}$ is a monoidal functor $(F,m)$ that satisfies
-  the following coherence diagram:
-  \begin{mathpar}
-  \bfig
-    \square<700,400>[
-      FA\otimes'FB`FB\otimes'FA`F(A\otimes B)`F(B\otimes A);
-      \e{FA,FB}`\m{A,B}`\m{B,A}`F\e{A,B}]
-  \efig
-  \end{mathpar}
-\end{definition}
-
-\begin{definition}
-  An \textbf{adjunction} between categories $\cat{C}$ and $\cat{D}$ consists of two functors
-  $F:\cat{D}\rightarrow\cat{C}$, called the \textbf{left adjoint}, and
-  $G:\cat{C}\rightarrow\cat{D}$, called the \textbf{right adjoint}, and two natural
-  transformations $\eta:id_\cat{D}\rightarrow GF$, called the \textbf{unit}, and
-  $\varepsilon:FG\rightarrow id_\cat{C}$, called the \textbf{counit}, such that the following
-  diagrams commute for any object $A$ in $\cat{C}$ and $B$ in $\cat{D}$:
-  \begin{mathpar}
-  \bfig
-    \Vtriangle/->`=`->/<400,400>[FB`FGFB`FB;F\eta_B``\varepsilon_{FB}]
-  \efig
-  \and
-  \bfig
-    \Vtriangle/->`=`->/<400,400>[GA`GFGA`GA;\eta_{GA}``G\varepsilon_A]
-  \efig
-  \end{mathpar}
-\end{definition}
-
-\begin{definition}
-  Let $(F,\m{})$ and $(G,\n{})$ be monoidal functors from a monoidal category $\cat{M}$ to a
-  monoidal category $\cat{M'}$. A \textbf{monoidal natural transformation} from $(F,\m{})$ to 
-  $(G,\n{})$ is a natural transformation $\theta:(F,\m{})\rightarrow(G,\n{})$ such that the
-  following diagrams commute for any objects $A$ and $B$ in $\cat{M}$:
-  \begin{mathpar}
-  \bfig
-    \square<700,400>[
-      FA\otimes'FB`F(A\otimes B)`GA\otimes'GB`G(A\otimes B);
-      \m{A,B}`\theta_A\otimes'\theta_B`\theta_{A\otimes B}`\n{A,B}]
-  \efig
-  \and
-  \bfig
-    \Vtriangle/->`<-`<-/<400,400>[FI`GI`I';\theta_I`\m{I}`\n{I}]
-  \efig
-  \end{mathpar}
-\end{definition}
-
-\begin{definition}
-  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
-  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories,
-  $F:\cat{M}\rightarrow\cat{M'}$ and $G:\cat{M}'\rightarrow\cat{M}$ be functors. The adjunction
-  $F:\cat{M}\dashv\cat{M'}:G$ is a \textbf{monoidal adjunction} if $F$ and $G$ are monoidal
-  functors, and the unit $\eta$ and the counit $\varepsilon$ are monoidal natural
-  transformations.
-\end{definition}
-
 \begin{definition}
@@
 
-\begin{definition}
-  Let $\cat{C}$ be a category. A \textbf{monad} on $\cat{C}$ consists of an endofunctor
-  $T:\cat{C}\rightarrow\cat{C}$ together with two natural transformations
-  $\eta:id_\cat{C}\rightarrow T$ and $\mu:T^2\rightarrow id_\cat{C}$, where $id_\cat{C}$
-  is the identity functor on $\cat{C}$, such that the following diagrams commute:
-  \begin{mathpar}
-  \bfig
-    \square<400,400>[T^3`T^2`T^2`T;T\mu`\mu_T`\mu`\mu]
-  \efig
-  \and
-  \bfig
-    \square<400,400>[T`T^2`T^2`T;\eta_T`T\eta`\mu`\mu]
-    \morphism(0,400)/=/<400,-400>[T`T;]
-  \efig
-  \end{mathpar}
-\end{definition}
-
 \begin{lemma}
+  \label{lem:monoidal-monad}
   The monad on the SMCC $\cat{C}$ in a SMCC-Lambek model is monoidal.
@@
   $\mu:T^2\rightarrow T$ are defined as
-  $$\eta:id_\cat{C}\rightarrow GF$$
-  $$\mu=GF\varepsilon_A=\varepsilon_{GFA}:GFGF\rightarrow GF$$
-  where $\eta$ is the unit and $\mu$ is the counit in the adjunction $F:\cat{C}\dashv\cat{L}:G$,
-  and $(F,m)$ and $(G,n)$ are monoidal functors. \\
+  $$\eta_A:A\rightarrow GFA$$
+  $$\mu_A=G\varepsilon_{FA}:GFGFA\rightarrow GFA$$
+  where $\eta$ is the unit and $\varepsilon:FG\rightarrow id_\cat{L}$ is the counit in the
+  adjunction $F:\cat{C}\dashv\cat{L}:G$, and $(F,\m{})$ and $(G,\n{})$ are monoidal functors. \\
   Thus, we have
-  $$\q{A,B}=G\m{A,B}\circ\n{FA,FB}:TA\otimes TB\rightarrow T(A\otimes B)$$
-  $$\q{I}=G\m{I}\circ\n{I'}:I\rightarrow TI$$
+  $$\t{A,B}=G\m{A,B}\circ\n{FA,FB}:TA\otimes TB\rightarrow T(A\otimes B)$$
+  $$\t{I}=G\m{I}\circ\n{I'}:I\rightarrow TI$$
   The monad $T$ being monoidal means
   \begin{enumerate}
-  \item $T$ is a monoidal functor i.e. the folllowing diagrams commute:
+  \item $T$ is a monoidal functor, i.e. the folllowing diagrams commute:
         \begin{mathpar}
@@
             T(A\otimes B)\otimes TC`T((A\otimes B)\otimes C)`T(A\otimes(B\otimes C));
-            \alpha_{TA,TB,TC}`id_{TA}\otimes\q{B,C}`\q{A,B}\otimes id_{TC}``
-            \q{A,B\otimes C}`\q{A\otimes B,C}`T\alpha_{A,B,C}]
+            \alpha_{TA,TB,TC}`id_{TA}\otimes\t{B,C}`\t{A,B}\otimes id_{TC}``
+            \t{A,B\otimes C}`\t{A\otimes B,C}`T\alpha_{A,B,C}]
         \efig
@@
             I\otimes TA`TA`TI\otimes TA`T(I\otimes A);
-            \lambda_{TA}`\q{I}\otimes id_{TA}`T\lambda_A`\q{I,A}]
+            \lambda_{TA}`\t{I}\otimes id_{TA}`T\lambda_A`\t{I,A}]
         \efig
@@
             TA\otimes I`TA`TA\otimes TI`T(A\otimes I);
-            \rho_{TA}`id_{TA}\otimes\q{I}`T\rho_A`\q{A,I}]
+            \rho_{TA}`id_{TA}\otimes\t{I}`T\rho_A`\t{A,I}]
         \efig
         \end{mathpar}
-        We write $GF$ instead of $T$ in the diagram chasings for clarity. \\
-        By replacing $\q{}$ with its definition, the first diagram above commutes by the
-        following diagram chasing, where the two hexagons commute because $G$ and $F$ are
+        We write $GF$ instead of $T$ in the proof for clarity. \\
+        By replacing $\t{}$ with its definition, the first diagram above commutes by the
+        following commutative diagram, where the two hexagons commute because $G$ and $F$ are
         monoidal functors, and the two quadrilaterals commute by the naturality of $\n{}$.
@@
         \end{mathpar}
-        The first square above commutes by the following diagram chasing, in which the top
+        The first square above commutes by the following commutative diagrams, in which the top
         quadrilateral commutes because $G$ is monoidal, the right quadrilateral commutes because
@@
         \end{mathpar}
-        Similarly, the second square above commutes by the following diagram chasing:
+        Similarly, the second square above commutes by the following commutative diagram:
         \begin{mathpar}
@@
         \end{mathpar}
-  \item $\eta$ is a monoidal natural transformation, i.e. the following diagrams commute. In
-        fact, since $\eta$ is the unit of the monoidal adjunction, $\eta$ is monoidal and thus
-        the following two diagrams commute.
+  \item $\eta$ is a monoidal natural transformation. In fact, since $\eta$ is the unit of the
+        monoidal adjunction, $\eta$ is monoidal and thus the following two diagrams commute.
         \begin{mathpar}
@@
             A\otimes B`A\otimes B`TA\otimes TB`T(A\otimes B);
-            `\eta_A\otimes\eta_B`\eta_{A\otimes B}`\q{A,B}]
+            `\eta_A\otimes\eta_B`\eta_{A\otimes B}`\t{A,B}]
         \efig
@@
         \bfig
-          \Vtriangle/->`=`<-/<400,400>[I`TI`I;\eta_I``\q{I}]
+          \Vtriangle/->`=`<-/<400,400>[I`TI`I;\eta_I``\t{I}]
         \efig
         \end{mathpar}
-  \item $\mu$ is a monoidal natural transformation, i.e. the following diagrams commute. Since
-        $\mu=\varepsilon_{GFA}$, $\mu$ is obviously also monoidal since $\varepsilon$ also is.
-        Thus the following diagrams commute.
+  \item $\mu$ is a monoidal natural transformation. It is obvious that since
+        $\mu=G\varepsilon_{FA}$ and $\varepsilon$ is monoidal, so is $\mu$. Thus the following
+        diagrams commute.
         \begin{mathpar}
@@
             T^2A\otimes T^2B`T^2(A\otimes B)`TA\otimes TB`T(A\otimes B);
-            `\mu_A\otimes\mu_B`\mu_{A\otimes B}`\q{A,B}]
-          \morphism(0,400)<800,0>[T^2A\otimes T^2B`T(TA\otimes TB);\q{TA,TB}]
-          \morphism(800,400)<700,0>[T(TA\otimes TB)`T^2(A\otimes B);T\q{A,B}]
+            `\mu_A\otimes\mu_B`\mu_{A\otimes B}`\t{A,B}]
+          \morphism(0,400)<800,0>[T^2A\otimes T^2B`T(TA\otimes TB);\t{TA,TB}]
+          \morphism(800,400)<700,0>[T(TA\otimes TB)`T^2(A\otimes B);T\t{A,B}]
         \efig
@@
         \bfig
-          \square/->`<-`<-`<-/<400,400>[T^2I`TI`TI`I;\mu_I`T\q{I}`\q{I}`\q{I}]
+          \square/->`<-`<-`<-/<400,400>[T^2I`TI`TI`I;\mu_I`T\t{I}`\t{I}`\t{I}]
         \efig
@@
 
-However, the monad $T$ we get from the SMCC-Lambek model is not symmetric because the following
-diagram does not commute:
+However, the monad is not symmetric becauase the following diagram does not commute, for the
+lambek category $\cat{L}$ is not symmetric.
+\begin{mathpar}
+\bfig
+  \ptriangle/->`->`/<900,400>[
+    GFA\otimes GFB`GFB\otimes GFA`G(FA\otimes'FB);\e{GFA,GFB}`\n{FA,FB}`]
+  \morphism(900,400)<900,0>[GFB\otimes GFA`G(FB\otimes' FA);\n{FB,FA}]
+  \dtriangle(900,0)/`->`->/<900,400>[
+    G(FB\otimes'FA)`GF(A\otimes B)`GF(B\otimes A);`G\m{B,A}`GF\e{A,B}]
+  \morphism|b|<900,0>[G(FA\otimes'FB)`GF(A\otimes B);G\m{A,B}]
+\efig
+\end{mathpar}
+
+\begin{lemma}
+  \label{lem:strong-monad}
+  The monad on the SMCC in a SMCC-Lambek model is strong.
+\end{lemma}
+\begin{proof}
+  Let $F:\cat{C}\vdash\cat{L}:G$ be a SMCC-Lambek model, where
+  $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$ is an SMCC,
+  $(\cat{L},\otimes',I',\alpha',\lambda',\rho')$ is a Lambek category, and $(F,\m{})$ and
+  $(G,\n{})$ are monoidal functors. Let $(T,\eta,\mu)$ be the monad on $\cat{C}$ where
+  $T=GF$. We have proved that $T$ is monoidal with the natural transformation
+  $\t{A,B}:TA\otimes TB\rightarrow T(A\otimes B)$ and the morphism $\t{I}:I\rightarrow TI$
+  defined as in Lemma~\ref{lem:monoidal-monad}. \\
+  We define the tensorial strength $\tau_{A,B}:A\otimes TB\rightarrow T(A\otimes B)$ as
+  $\tau_{A,B}=\t{A,B}\circ\eta_A\otimes id_{TB}$. \\
+  Since $\eta$ is a monoidal natural transformation, we have $\eta_I=G\m{I}\circ\n{I'}$.
+  Therefore $\eta_I=\t{I}$. Thus the following diagram commutes because $T$ is monoidal,
+  where the composition $\t{I,A}\circ\t{I}\otimes id_{TA}$ is the definition of $\tau_{I,A}$. So
+  the first triangle in Defition~\ref{def:strong-monad} commutes.
+  \begin{mathpar}
+  \bfig
+    \square/->`->`->`<-/<600,400>[
+      I\otimes TA`TI\otimes TA`TA`T(I\otimes A);
+      \t{I}\otimes id_{TA}`\lambda_{TA}`\t{I,A}`T\lambda_A]
+  \efig
+  \end{mathpar}
+  Similarly, by using the definition of $\tau$, the the second triangle in the definition is
+  equivalent to the following diagram, which commutes because $\eta$ is a monoidal natural
+  transformation:
+  \begin{mathpar}
+  \bfig
+    \square/->`->`->`<-/<600,400>[
+      A\otimes B`A\otimes TB`T(A\otimes B)`TA\otimes TB;
+      id_A\otimes\eta_B`\eta_{A\otimes B}`\eta_A\otimes id_{TB}`\t{A,B}]
+    \morphism(0,400)|m|<600,-400>[A\otimes B`TA\otimes TB;\eta_A\otimes\eta_B]
+  \efig
+  \end{mathpar}
+  The first pentagon in the definition commutes by the following commutative diagrams, because
+  $\eta$ are $\alpha$ natural transformations and $T$ is monoidal:
+  \begin{mathpar}
+  \bfig
+    \qtriangle|amm|/->`->`<-/<1000,400>[
+      (A\otimes B)\otimes TC`T(A\otimes B)\otimes TC`(TA\otimes TB)\otimes TC;
+      \eta_{A\otimes B}\otimes id_{TC}`
+      (\eta_A\otimes\eta_B)\otimes id_{TC}`
+      \t{A,B}\otimes id_{TC}]
+    \morphism(0,400)<0,-400>[(A\otimes B)\otimes TC`A\otimes(B\otimes TC);\alpha_{A,B,TC}]
+    \morphism(1000,0)|m|<0,-400>[
+      (TA\otimes TB)\otimes TC`TA\otimes(TB\otimes TC);\alpha_{TA,TB,TC}]
+    \Dtriangle(0,-800)|lmm|/->`->`<-/<1000,400>[
+      A\otimes(B\otimes TC)`TA\otimes(TB\otimes TC)`A\otimes(TB\otimes TC);
+      id_A\otimes(\eta_B\otimes id_{TC})`
+      \eta_A\otimes(\eta_B\otimes id_{TC})`
+      \eta_A\otimes id_{TB\otimes TC}]
+    \morphism(0,-800)|b|<1000,0>[
+      A\otimes(TB\otimes TC)`A\otimes T(B\otimes C);id_A\otimes\t{B,C}]
+    \qtriangle(1000,0)|amr|/->``->/<1000,400>[
+      T(A\otimes B)\otimes TC`T((A\otimes B)\otimes C)`T(A\otimes(B\otimes C));
+      \t{A\otimes B,C}``T\alpha_{A,B,C}]
+    \morphism(2000,-800)<0,800>[
+      TA\otimes T(B\otimes C)`T(A\otimes(B\otimes C));\t{A,B\otimes C}]
+    \btriangle(1000,-800)|mmb|/`->`->/<1000,400>[
+      TA\otimes(TB\otimes TC)`A\otimes T(B\otimes C)`TA\otimes T(B\otimes C);
+      `id_{TA}\otimes\t{B,C}`\eta_A\otimes id_{T(B\otimes C)}]
+  \efig
+  \end{mathpar}
+  The last diagram in the definition commtues by the following commutative diagram, because
+  $T$ is a monad, $\t{}$ is a natural transformation, and $\mu$ is a monoidal natural
+  transformation:
+  \begin{mathpar}
+  \bfig
+    \ptriangle/->`->`/<700,400>[
+      A\otimes T^2B`TA\otimes T^2B`A\otimes TB;\eta_A\otimes id_{T^2B}`id_A\otimes\mu_B`]
+    \btriangle(0,-400)/->``->/<700,400>[
+      A\otimes TB`TA\otimes TB`T(A\otimes B);\eta_A\otimes id_{TB}``\t{A,B}]
+    \morphism(700,400)|m|<-700,-800>[TA\otimes T^2B`TA\otimes TB;id_{TA}\otimes\mu_B]
+    \morphism(700,0)|m|<-700,-400>[TA\otimes T^2B`TA\otimes TB;id_{TA}\otimes\mu_B]
+    \qtriangle(700,0)/->``->/<1800,400>[
+      TA\otimes T^2B`T(A\otimes TB)`T(TA\otimes TB);\t{A,TB}``T(\eta_A\otimes id_{TB})]
+    \btriangle(700,0)|mmm|/=`->`<-/<900,400>[
+      TA\otimes T^2B`TA\otimes T^2B`T^2A\otimes T^2B;
+      `T\eta_A\otimes id_{T^2B}`\mu_A\otimes id_{T^2B}]
+    \morphism(1600,0)|m|<900,0>[T^2A\otimes T^2B`T(TA\otimes TB);\t{TA,TB}]
+    \morphism(1600,0)|m|<-1600,-400>[T^2A\otimes T^2B`TA\otimes TB;\mu_A\otimes\mu_B]
+    \dtriangle(700,-400)/`->`<-/<1800,400>[
+      T(TA\otimes TB)`T(A\otimes B)`T^2(A\otimes B);`T\t{A,B}`\mu_{A\otimes B}]
+  \efig
+  \end{mathpar}
+\end{proof}
+
+\begin{lemma}[\cite{kock1970monads}]
+  Let $\cat{M}$ be a symmetric monoidal category and $T$ be a strong monad on $\cat{M}$. Then
+  $T$ is a symmetric monoidal functor iff it is commutative.
+\end{lemma}
+
+\begin{theorem}
+  The monad on the SMCC in a SMCC-Lambek model is monoidal and non-commutative.
+\end{theorem}
+
+\begin{lemma}
+  The comonad on the Lambek category in a SMCC-Lambek model is monoidal.
+\end{lemma}
+\begin{proof}
+  We define the comonad $S$ on the Lambek category $\cat{L}$ in the adjunction
+  $F:\cat{C}\vdash\cat{L}:G$ of a SMCC-Lambek model as $S=FG$, and the two corresponding natural
+  transformations $\varepsilon:S\rightarrow id_\cat{L}$ and $\delta:S\rightarrow S^2$ are
+  defined as
+  $$\varepsilon_A:SA\rightarrow A$$
+  $$\delta_A=F\eta_{GA}:SA\rightarrow S^2A$$
+  where $\varepsilon$ is the counit and $\eta:id_\cat{L}\rightarrow GF$ is the unit in the
+  adjunction, and $(F,\m{})$ and $(G,\n{})$ are monoidal functors. Thus, we have
+  $$\s{A,B}=F\n{A,B}\circ\m{GA,GB}:SA\otimes'SB\rightarrow SA\otimes'SB$$
+  $$\s{I}=F\n{I'}\circ\m{I}:I'\rightarrow SI'$$
+  The comonad $S$ being monoidal means
+  \begin{enumerate}
+  \item $S$ is a monoidal functor, i.e. the following diagrams commute:
         \begin{mathpar}
@@
           \hSquares/->`->`->``->`->`->/<400>[
-    GFA\otimes GFB`GFB\otimes GFA`G(FB\otimes'FA)`G(FA\otimes'FB)`GF(A\otimes B)`GF(B\otimes A);
-    \e{GFA,GFB}`\n{FB,FA}`\n{FA,FB}``G\m{B,A}`G\m{A,B}`GF\e{A,B}]
+            (SA\otimes'SB)\otimes'SC`SA\otimes'(SB\otimes'SC)`SA\otimes'S(B\otimes'C)`
+            S(A\otimes'B)\otimes'SC`S((A\otimes'B)\otimes'C)`S(A\otimes'(B\otimes'C));
+            \alpha_{SA,SB,SC}'`id_{SA}\otimes'\s{B,C}`\s{A,B}\otimes'id_{SC}``
+            \s{A,B\otimes'C}`\s{A\otimes'B,C}`S\alpha_{A,B,C}']
+        \efig
+        \and
+        \bfig
+          \square/->`->`<-`->/<600,400>[
+            I'\otimes'SA`SA`SI'\otimes'SA`S(I'\otimes'A);
+            \lambda_{SA}'`\s{I'}\otimes'id_{SA}`S\lambda_A'`\s{I',A}]
+        \efig
+        \and
+        \bfig
+          \square/->`->`<-`->/<600,400>[
+            SA\otimes'I'`SA`SA\otimes'SI'`S(A\otimes'I');
+            \rho_{SA}'`id_{SA}'\otimes'\s{I'}`S\rho_A'`\s{A,I'}]
         \efig
         \end{mathpar}
-
-Therefore, the monad is non-commutative.
+  \item $\varepsilon$ is a monoidal natural transformation:
+        \begin{mathpar}
+        \bfig
+          \square/->`->`->`=/<600,400>[
+            SA\otimes'SB`S(A\otimes'B)`A\otimes'B`A\otimes'B;
+            \s{A,B}`\varepsilon_A\otimes'\varepsilon_B`\varepsilon_{A\otimes'B}`]
+        \efig
+        \and
+        \bfig
+          \Vtriangle/->`<-`=/<400,400>[SI'`I'`I';\varepsilon_{I'}`\s{I'}`]
+        \efig
+        \end{mathpar}
+  \item $\delta$ is a monoidal natural transformation:
+        \begin{mathpar}
+        \bfig
+          \square/->`->`->`/<1500,400>[
+            SA\otimes'SA`S(A\otimes'B)`S^2A\otimes'S^2B`S^2(A\otimes'B);
+            \s{A,B}`\delta_A\otimes'\delta_B`\delta_{A\otimes'B}`]
+          \morphism<800,0>[S^2A\otimes'S^2B`S(SA\otimes'SB);\s{SA,SB}]
+          \morphism(800,0)<700,0>[S(SA\otimes'SB)`S^2(A\otimes'B);S\s{A,B}]
+        \efig
+        \and
+        \bfig
+          \square/->`<-`<-`->/<400,400>[
+            SI'`S^2I'`I'`SI';\delta_{I'}`\s{I'}`S\s{I'}`\s{I'}]
+        \efig
+        \end{mathpar}
+  \end{enumerate}
+  The proof for the commutativity of the diagrams are similar as the proof in
+  Lemma~\ref{lem:monoidal-monad}. We do not include the proof here for simplicity.
+\end{proof}
 

### 2017-06-22 category-theory-basics.tex
categorical-models

\begin{definition}
\label{def:mc}
  A \textbf{monoidal category} $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ is a category $\cat{M}$
  consists of
  \begin{itemize}
  \item a bifunctor $\otimes:\cat{M}\times\cat{M}\rightarrow\cat{M}$, called the tensor product;
  \item an object $I$, called the unit object;
  \item three natural isomorphisms $\alpha$, $\lambda$, and $\rho$ with components
        $$\alpha_{A,B,C}:(A\otimes B)\otimes C\rightarrow A\otimes(B\otimes C)$$
        $$\lambda_A:I\otimes A\rightarrow A$$
        $$\rho_A:A\otimes I\rightarrow A$$
        where $\alpha$ is called associator, $\lambda$ is left unitor, and $\rho$ is right
        unitor,
  \end{itemize}
  such that the following diagrams commute for any objects $A$, $B$, $C$ in $\cat{M}$:
  \begin{mathpar}
  \bfig
    \square/`->`->`->/<2100,400>[
      ((A\otimes B)\otimes C)\otimes D`
      A\otimes((B\otimes C)\otimes D)`
      (A\otimes B)\otimes(C\otimes D)`
      A\otimes(B\otimes(C\otimes D));
      `
      \alpha_{A\otimes B,C,D}`
      id_A\otimes\alpha_{B,C,D}`
      \alpha_{A,B,C\otimes D}]
    \morphism(0,400)<1100,0>[
      ((A\otimes B)\otimes C)\otimes D`
      (A\otimes(B\otimes C))\otimes D;
      \alpha_{A,B,C}\otimes id_D]
    \morphism(1100,400)<1000,0>[
      (A\otimes(B\otimes C))\otimes D`
      A\otimes((B\otimes C)\otimes D);
      \alpha_{A,B\otimes C,D}]
  \efig
  \and
  \bfig
    \Vtriangle<400,400>[
      (A\otimes I)\otimes B`
      A\otimes(I\otimes B)`
      A\otimes B;
      \alpha_{A,I,B}`
      \rho_A\otimes id_B`
      id_A\otimes\lambda_B]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  A \textbf{Lambek category} (or a \textbf{biclosed monoidal category}) is a monoidal category
  $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ equipped with two bifunctors
  $\rightharpoonup:\cat{M}^{op}\times\cat{M}\rightarrow\cat{M}$ and
  $\leftharpoonup:\cat{M}\times\cat{M}^{op}\rightarrow\cat{M}$ that are both right adjoint to
  the tensor product. That is, the following natural bijections hold:
  \begin{center}
  \begin{math}
  \begin{array}{lll}
    \Hom{L}{X\otimes A}{B}\cong\Hom{L}{X}{A\lto B} & \quad\quad\quad\quad & 
    \Hom{L}{A\otimes X}{B}\cong\Hom{L}{X}{B\rto A}
  \end{array}
  \end{math}
  \end{center}
\end{definition}

\begin{definition}
  A \textbf{symmetric monoidal category} (SMCC) is a monoidal category
  $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ together with a natural transformation with
  components $\e{A,B}:A\otimes B\rightarrow B\otimes A$, called \textbf{exchange}, such that the
  following diagrams commute:
  \begin{mathpar}
  \bfig
    \Vtriangle<300,400>[A\otimes I`I\otimes A`A;\e{A,I}`\rho_A`\lambda_A]
  \efig
  \and
  \bfig
    \Vtriangle/=`->`<-/<300,400>[
      A\otimes B`A\otimes B`B\otimes A;
      id_{A\otimes B}`\e{A,B}`\e{B,A}]
  \efig
  \and
  \bfig
    \hSquares/->`->`->``->`->`->/<400>[
      (A\otimes B)\otimes C`A\otimes(B\otimes C)`(B\otimes C)\otimes A`
      (B\otimes A)\otimes C`B\otimes(A\otimes C)`B\otimes(C\otimes A);
      \alpha_{A,B,C}`\e{A,B\otimes C}`\e{A,B}\otimes id_C``
      \alpha_{B,A,C}`\alpha_{B,A,C}`id_B\otimes\e{A,C}]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  A \textbf{symmetric monoidal closed category} $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ is a
  symmetric monoidal category equipped with a bifunctor
  $\limp:\cat{M}^{op}\times\cat{M}\rightarrow\cat{M}$ that is right adjoint to the tensor
  product. That is, the following natural bijection
  $\Hom{\cat{M}}{X\otimes A}{B}\cong\Hom{\cat{M}}{X}{A\limp B}$ holds.
\end{definition}

\begin{lemma}
  \label{lemma:internal-homs-collapse}
  Let $A$ and $B$ be two objects in a Lambek category with the exchange natural transformation.
  Then $(A \lto B) \cong (B \rto A)$.
\end{lemma}
\begin{proof}
  First, notice that for any object $C$ we have
  \begin{center}
  \begin{math}
  \small
  \begin{array}{lllll}
    Hom[C,A\lto B]
    & \cong & Hom[C\otimes A,B] & \cat{L}\text{ is a Lambek category}\\
    & \cong & Hom[A\otimes C,B] & \text{By the exchange }\e{C,A}\\
    & \cong & Hom[C,B\rto A]    & \cat{L}\text{ is a Lambek category}
  \end{array}
  \end{math}
  \end{center}  
  Thus, $A\lto B\cong B\rto A$ by the Yoneda lemma.
\end{proof}
\begin{corollary}
  \label{corollary:LC-with-ex-mc}
  A Lambek category with exchange is symmetric monoidal closed.
\end{corollary}

\begin{definition}
  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories. A \textbf{monoidal
  functor} $(F,\m{})$ from $\cat{M}$ to $\cat{M'}$ is a functor $F:\cat{M}\rightarrow\cat{M'}$
  together with a morphism $\m{I}:I'\rightarrow F(I)$ and a natural transformation
  $\m{A,B}:FA'\otimes FB'\rightarrow F(A\otimes B)$, such that the following diagrams commute
  for any objects $A$, $B$, and $C$ in $\cat{M}$:
  \begin{mathpar}
  \bfig
    \hSquares/->`->`->``->`->`->/<400>[
      (FA\otimes'FB)\otimes'FC`FA\otimes'(FB\otimes'FC)`FA\otimes'F(B\otimes C)`
      F(A\otimes B)\otimes'FC`F((A\otimes B)\otimes C)`F(A\otimes(B\otimes C));
      \alpha'_{FA,FB,FC}`id_{FA}\otimes'\m{A,B}`\m{A,B}\otimes'id_{FC}``
      \m{A,B\otimes C}`\m{A\otimes B,C}`F\alpha_{A,B,C}]
  \efig
  \and
  \bfig
    \square/->`->`<-`->/<600,400>[
      I'\otimes'FA`FA`FI\otimes'FA`F(I\otimes A);
      \lambda'_{FA}`\m{I}\otimes id_{FA}`F\lambda_A`\m{I,A}]
  \efig
  \and
  \bfig
    \square/->`->`<-`->/<600,400>[
      FA\otimes'I'`FA`FA\otimes'FI`F(A\otimes I);
      \rho'_{FA}`\id_{FA}\otimes\m{I}`F\rho_A`\m{A,I}]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be symmetric monoidal categories. A
  \textbf{symmetric monoidal functor} $F:\cat{M}\rightarrow\cat{M'}$ is a monoidal functor
  $(F,\m{})$ that satisfies the following coherence diagram:
  \begin{mathpar}
  \bfig
    \square<700,400>[
      FA\otimes'FB`FB\otimes'FA`F(A\otimes B)`F(B\otimes A);
      \e{FA,FB}`\m{A,B}`\m{B,A}`F\e{A,B}]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  An \textbf{adjunction} between categories $\cat{C}$ and $\cat{D}$ consists of two functors
  $F:\cat{D}\rightarrow\cat{C}$, called the \textbf{left adjoint}, and
  $G:\cat{C}\rightarrow\cat{D}$, called the \textbf{right adjoint}, and two natural
  transformations $\eta:id_\cat{D}\rightarrow GF$, called the \textbf{unit}, and
  $\varepsilon:FG\rightarrow id_\cat{C}$, called the \textbf{counit}, such that the following
  diagrams commute for any object $A$ in $\cat{C}$ and $B$ in $\cat{D}$:
  \begin{mathpar}
  \bfig
    \Vtriangle/->`=`->/<400,400>[FB`FGFB`FB;F\eta_B``\varepsilon_{FB}]
  \efig
  \and
  \bfig
    \Vtriangle/->`=`->/<400,400>[GA`GFGA`GA;\eta_{GA}``G\varepsilon_A]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  Let $(F,\m{})$ and $(G,\n{})$ be monoidal functors from a monoidal category $\cat{M}$ to a
  monoidal category $\cat{M'}$. A \textbf{monoidal natural transformation} from $(F,\m{})$ to 
  $(G,\n{})$ is a natural transformation $\theta:(F,\m{})\rightarrow(G,\n{})$ such that the
  following diagrams commute for any objects $A$ and $B$ in $\cat{M}$:
  \begin{mathpar}
  \bfig
    \square<700,400>[
      FA\otimes'FB`F(A\otimes B)`GA\otimes'GB`G(A\otimes B);
      \m{A,B}`\theta_A\otimes'\theta_B`\theta_{A\otimes B}`\n{A,B}]
  \efig
  \and
  \bfig
    \Vtriangle/->`<-`<-/<400,400>[FI`GI`I';\theta_I`\m{I}`\n{I}]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories,
  $F:\cat{M}\rightarrow\cat{M'}$ and $G:\cat{M}'\rightarrow\cat{M}$ be functors. The adjunction
  $F:\cat{M}\dashv\cat{M'}:G$ is a \textbf{monoidal adjunction} if $F$ and $G$ are monoidal
  functors, and the unit $\eta$ and the counit $\varepsilon$ are monoidal natural
  transformations.
\end{definition}

\begin{definition}
  Let $\cat{C}$ be a category. A \textbf{monad} on $\cat{C}$ consists of an endofunctor
  $T:\cat{C}\rightarrow\cat{C}$ together with two natural transformations
  $\eta:id_\cat{C}\rightarrow T$ and $\mu:T^2\rightarrow T$, where $id_\cat{C}$ is the identity
  functor on $\cat{C}$, such that the following diagrams commute:
  \begin{mathpar}
  \bfig
    \square<400,400>[T^3`T^2`T^2`T;T\mu`\mu_T`\mu`\mu]
  \efig
  \and
  \bfig
    \square<400,400>[T`T^2`T^2`T;\eta_T`T\eta`\mu`\mu]
    \morphism(0,400)/=/<400,-400>[T`T;]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  \label{def:strong-monad}
  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ be a monoidal category and $(T,\eta,\mu)$ be a
  monad on $\cat{M}$. $T$ is a \textbf{strong monad} if there is natural transformation $\tau$, 
  called the \textbf{tensorial strength}, with components
  $\tau_{A,B}:A\otimes TB\rightarrow T(A\otimes B)$ such that the following diagrams commute:
  \begin{mathpar}
  \bfig
    \Vtriangle<400,400>[I\otimes TA`T(I\otimes A)`TA;\tau_{I,A}`\lambda_{TA}`T\lambda_A]
  \efig
  \and
  \bfig
    \Vtriangle<400,400>[
      A\otimes B`A\otimes TB`T(A\otimes B);id_A\otimes\eta_B`\eta_{A\otimes B}`\tau_{A,B}]
  \efig
  \and
  \bfig
    \square/->`->`->`/<1800,400>[
      (A\otimes B)\otimes TC`T((A\otimes B)\otimes C)`
      A\otimes(B\otimes TC)`T(A\otimes(B\otimes C));
      \tau_{A\otimes B,C}`\alpha_{A,B,TC}`T\alpha_{A,B,C}`]
    \morphism<900,0>[A\otimes(B\otimes TC)`A\otimes T(B\otimes C);id_A\otimes\tau_{B,C}]
    \morphism(900,0)<900,0>[A\otimes T(B\otimes C)`T(A\otimes(B\otimes C));\tau_{A,B\otimes C}]
  \efig
  \and
  \bfig
    \square/`->`->`->/<1400,400>[
      A\otimes T^2B`T^2(A\otimes B)`A\otimes TB`T(A\otimes B);
      `id_A\otimes\mu_B`\mu_{A\otimes B}`\tau_{A,B}]
    \morphism(0,400)<700,0>[A\otimes T^2B`T(A\otimes TB);\tau_{A,TB}]
    \morphism(700,400)<700,0>[T(A\otimes TB)`T^2(A\otimes B);T\tau_{A,B}]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ be a symmetric monoidal category with exchange
  $\e{}$, and $(T,\eta,\mu)$ be a strong monad on $\cat{M}$. Then there is a \textbf{``twisted''
  tensorial strength} $\tau'_{A,B}:TA\otimes B\rightarrow T(A\otimes B)$ defined as
  $\tau'_{A,B}=T\e{}\circ\tau_{B,A}\circ\e{}$. We can construct a pair of natural
  transformations $\Phi$, $\Phi'$ with components
  $\Phi_{A,B},\Phi'_{A,B}:TA\otimes TB\rightarrow T(A\otimes B)$ defined as
  $\Phi_{A,B}=\mu_{A\otimes B}\circ T\tau'_{A,B}\circ\tau_{TA,B}$ and
  $\Phi'_{A,B}=\mu_{A\otimes B}\circ T\tau_{A,B}\circ\tau'_{A,TB}$. If $\Phi=\Phi'$, then the
  monad $T$ is \textbf{commutative}.
\end{definition}

\begin{definition}
  Let $\cat{L}$ be a category. A \textbf{comonad} on $\cat{L}$ consists of an endofunctor
  $S:\cat{L}\rightarrow\cat{L}$ together with two natural transformations
  $\varepsilon:S\rightarrow id_\cat{L}$ and $\delta:S^2\rightarrow S$ such that the following
  diagrams commute:
  \begin{mathpar}
  \bfig
    \square<400,400>[S`S^2`S^2`S^3;\delta`\delta`S\delta`\delta_S]
  \efig
  \and
  \bfig
    \square<400,400>[S^2`S`S`S^2;S\varepsilon`\varepsilon_S`\delta`\delta]
  \efig
  \end{mathpar}
\end{definition}

### 2017-06-27 Elle-non-com/Elle.tex
Elle modified

\documentclass[11pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{supertabular}
\usepackage{cmll}
\usepackage{txfonts}
\usepackage{color}
\usepackage{tikz}
\usepackage{mathpartir}

\newcommand\encircle[1]{%
  \tikz[baseline=(X.base)] 
    \node (X) [draw, shape=circle, inner sep=-1.5pt] {\strut #1};}

\newcommand{\circop}[1]{\mathop{\encircle{#1}}}

\input{Elle-ott}

\begin{document}

\noindent
Should not be able to derive exchange in Elle comonadicly or monadicly.:

Deriving right contraction in Elle comonadicly:
\begin{center}
  \tiny
  \begin{math}
    $$\mprset{flushleft}
    \inferrule* [right={\tiny impR}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny tenL}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny Fl}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny Fl}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny contrR}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny tenR}] {
                $$\mprset{flushleft}
                \inferrule* [right={\tiny Fr}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny ax}] {
                    \,
                  }{[[x1 : Gf A |- x1 : Gf A]]}
                }{[[x1 : Gf A; . |- F x1 : F Gf A]]}
                \\
                \inferrule* [right={\tiny tenR}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny Fr}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny ax}] {
                      \,
                    }{[[y0 : Gf B |- y0 : Gf B]]}
                  }{[[y0 : Gf B; . |- F y0 : F Gf B]]}
                  \\
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny Fr}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny ax}] {
                      \,
                    }{[[x0 : Gf A |- x0 : Gf A]]}
                  }{[[x0 : Gf A; . |- F x0 : F Gf A]]}
                }{[[y0 : Gf B, x0 : Gf A ; . |- h(F y0) (x) F x0 : h(F Gf B) (x) F Gf A]]}
              }{[[x1 : Gf A, y0 : Gf B, x0 : Gf A ; . |- h(F x1) (x) (h(F y0) (x) F x0) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A)]]}
            }{[[y0 : Gf B, x2 : Gf A ; . |- contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0)) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A)]]}
          }{[[y0 : Gf B ; x3 : F Gf A |- let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A)]]}
        }{[[. ; y1 : F Gf B, x3 : F Gf A |- let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0)))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A)]]}
      }{[[. ; z : h(F Gf B) (x) F Gf A |- let z : h(F Gf B) (x) F Gf A be y1 (x) x3 in (let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A)]]}
    }{[[. ; . |- \l z : h(F Gf B) (x) F Gf A . let z : h(F Gf B) (x) F Gf A be y1 (x) x3 in (let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))))) : (h(F Gf B) (x) F Gf A) -> (h(F Gf A) (x) (h(F Gf B) (x) F Gf A))]]}
  \end{math}
\end{center}

Deriving left contraction in Elle comonadicly:
\begin{center}
  \tiny
  \begin{math}
    $$\mprset{flushleft}
    \inferrule* [right={\tiny impR}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny tenL}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny Fl}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny Fl}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny contrR}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny tenR}] {
                $$\mprset{flushleft}
                \inferrule* [right={\tiny tenR}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny Fr}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny ax}] {
                      \,
                    }{[[x0 : Gf A |- x0 : Gf A]]}
                  }{[[x0 : Gf A; . |- F x0 : F Gf A]]}
                  \\
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny Fr}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny ax}] {
                      \,
                    }{[[y0 : Gf B |- y0 : Gf B]]}
                  }{[[y0 : Gf B; . |- F y0 : F Gf B]]}
                }{[[x0 : Gf A, y0 : Gf B ; . |- h(F x0) (x) F y0 : h(F Gf A) (x) F Gf B]]}
                \\
                \inferrule* [right={\tiny Fr}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny ax}] {
                    \,
                  }{[[x1 : Gf A |- x1 : Gf A]]}
                }{[[x1 : Gf A; . |- F x1 : F Gf A]]}
              }{[[x0 : Gf A, y0 : Gf B, x1 : Gf A ; . |- (h(F x0) (x) F y0) (x) F x1 : (h(F Gf A) (x) F Gf B) (x) F Gf A]]}
            }{[[x2 : Gf A, y0 : Gf B ; . |- contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1) : (h(F Gf A) (x) F Gf B) (x) F Gf A]]}
          }{[[x2 : Gf A ; y1 : F Gf B |- let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1)) : (h(F Gf A) (x) F Gf B) (x) F Gf A]]}
        }{[[. ; x3 : F Gf A, y1 : F Gf B |- let x3 : F Gf A be F x2 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1))) : (h(F Gf A) (x) F Gf B) (x) F Gf A]]}
      }{[[. ; z : h(F Gf A) (x) F Gf B |- let z : h(F Gf A) (x) F Gf B be x3 (x) y1 in (let x3 : F Gf A be F x2 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1)))) : (h(F Gf A) (x) F Gf B) (x) F Gf A]]}
    }{[[. ; . |- \l z : h(F Gf A) (x) F Gf B . let z : h(F Gf A) (x) F Gf B be x3 (x) y1 in (let x3 : F Gf A be F x3 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in (h(F x0) (x) (h(F y0) (x) F x1))))) : (h(F Gf A) (x) F Gf B) -> ((h(F Gf A) (x) F Gf B) (x) F Gf A)]]}
  \end{math}
\end{center}

Deriving weakening in Elle comonadicly:
\begin{center}
  \tiny
  \begin{math}
    $$\mprset{flushleft}
    \inferrule* [right={\tiny impR}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny Fl}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny weak}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny unitR}] {
            \,
          }{[[. |- triv : Unit]]}
        }{[[x0 : Gf A ; . |- weak x0 in triv : Unit]]}
      }{[[x1 : F Gf A ; . |- let x1 : F Gf A be F x0 in weak x0 in triv : Unit]]}
    }{[[. ; . |- \l x1 : F Gf A . let x1 : F Gf A be F x0 in weak x0 in triv : (F Gf A) -> (Unit)]]}
  \end{math}
\end{center}

\appendix

\section{Full Ott Spec}
\label{sec:full_ott_spec}
\footnotesize
\ottall
% section full_ott_spec (end)

\end{document}

### 2017-06-27 Elle/Elle.tex
Elle modified

--- 2017-06-27 Elle-non-com/Elle.tex
@@
 \noindent
-Should not be able to derive exchange in Elle comonadicly or monadicly.:
+Deriving exchange in Elle comonadicly:
+
+\begin{center}
+  \tiny
+  \begin{math}
+    $$\mprset{flushleft}
+    \inferrule* [right={\tiny impR}] {
+      $$\mprset{flushleft}
+    \inferrule* [right={\tiny tenL}] {
+      $$\mprset{flushleft}
+    \inferrule* [right={\tiny Fl}] {
+      $$\mprset{flushleft}
+      \inferrule* [right={\tiny Fl}] {
+        $$\mprset{flushleft}
+        \inferrule* [right={\tiny beta}] {
+          $$\mprset{flushleft}
+          \inferrule* [right={\tiny tenR}] {
+            $$\mprset{flushleft}
+            \inferrule* [right={\tiny Fr}] {
+              $$\mprset{flushleft}
+              \inferrule* [right={\tiny ax}] {
+                \,
+              }{[[y0 : Gf B |- y0 : Gf B]]}
+            }{[[y0 : Gf B; . |- F y0 : F Gf B]]}
+            \\
+            $$\mprset{flushleft}
+            \inferrule* [right={\tiny Fr}] {
+              $$\mprset{flushleft}
+              \inferrule* [right={\tiny ax}] {
+                \,
+              }{[[x0 : Gf A |- x0 : Gf A]]}
+            }{[[x0 : Gf A; . |- F x0 : F Gf A]]}
+          }{[[y0 : Gf B, x0 : Gf A ; . |- h(F y0) (x) F x0 : h(F Gf B) (x) F Gf A]]}
+        }{[[x1 : Gf A, y1 : Gf B ; . |- ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0) : h(F Gf B) (x) F Gf A]]}
+      }{[[x1 : Gf A ; y2 : F Gf B |- let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)) : h(F Gf B) (x) F Gf A]]}
+    }{[[. ; x2 : F Gf A, y2 : F Gf B |- let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0))) : h(F Gf B) (x) F Gf A]]}
+    }{[[.
+; z : h(F Gf A) (x) F Gf B |- let z : h(F Gf A) (x) F Gf B be x2 (x) y2 in (let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)))) : (h(F Gf B) (x) F Gf A)]]}
+    }{[[.
+; .
+|- \l z : h(F Gf A) (x) F Gf B .
+let z : h(F Gf A) (x) F Gf B be x2 (x) y2 in (let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)))) : (h(F Gf A) (x) F Gf B) -> (h(F Gf B) (x) F Gf A)]]}
+  \end{math}
+\end{center}
 

### 2017-06-28 Elle/Elle.tex
Definition for \eta, \mu, and strength \tau in Elle

@@
 
-\noindent
 Deriving exchange in Elle comonadicly:
@@
         }{[[x0 : Gf A ; . |- weak x0 in triv : Unit]]}
-      }{[[x1 : F Gf A ; . |- let x1 : F Gf A be F x0 in weak x0 in triv : Unit]]}
+      }{[[. ; x1 : F Gf A |- let x1 : F Gf A be F x0 in weak x0 in triv : Unit]]}
     }{[[. ; . |- \l x1 : F Gf A . let x1 : F Gf A be F x0 in weak x0 in triv : (F Gf A) -> (Unit)]]}
@@
 \end{center}
+
+$GF$ is a monad:
+\begin{itemize}
+\item Deriving $\eta$:
+  \begin{center}
+    \tiny
+    \begin{math}
+      $$\mprset{flushleft}
+      \inferrule* [right={\tiny impR}] {
+        $$\mprset{flushleft}
+        \inferrule* [right={\tiny Gr}] {
+          $$\mprset{flushleft}
+          \inferrule* [right={\tiny Gl}] {
+            $$\mprset{flushleft}
+            \inferrule* [right={\tiny Fl}] {
+              $$\mprset{flushleft}
+              \inferrule* [right={\tiny Gl}] {
+                $$\mprset{flushleft}
+                \inferrule* [right={\tiny ax}] {
+                  \,
+                }{[[. ; x0 : F X |- x0 : F X]]}
+              }{[[x1 : Gf F X ; . |- let x1 : Gf F X be Gf x0 in x0 : F X]]}
+            }{[[. ; x2 : F Gf F X |- let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0) : F X]]}
+          }{[[x3 : Gf F Gf F X ; . |- let x3 : Gf F Gf F X be Gf x2 in (let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0)) : F X]]}
+        }{[[x3 : Gf F Gf F X |- Gf (let x3 : Gf F Gf F X be Gf x2 in (let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0))) : Gf F X]]}
+      }{[[ . |- \l x3 : Gf F Gf F X . Gf (let x3 : Gf F Gf F X be Gf x2 in (let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0))) : (Gf F Gf F X) -> (Gf F X)]]}
+    \end{math}
+  \end{center}
+\item Deriving $\mu$:
+  \begin{center}
+    \tiny
+    \begin{math}
+      $$\mprset{flushleft}
+      \inferrule* [right={\tiny impR}] {
+        $$\mprset{flushleft}
+        \inferrule* [right={\tiny Gr}] {
+          $$\mprset{flushleft}
+          \inferrule* [right={\tiny Fr}] {
+            $$\mprset{flushleft}
+            \inferrule* [right={\tiny ax}] {
+              \,
+            }{[[x : X |- x : X]]}
+          }{[[x : X ; . |- F x : F X]]} 
+        }{[[x : X |- Gf F x : Gf F X]]}
+      }{[[. |- \l x : X . Gf F x : (X) -> (Gf F X)]]}
+    \end{math}
+  \end{center}
+\end{itemize}
+
+The monad $GF$ is strong:
+\begin{itemize}
+\item Deriving the tensorial strength $\tau$:
+  \begin{center}
+    \tiny
+    \begin{math}
+      $$\mprset{flushleft}
+      \inferrule* [right={\tiny impR}] {
+        $$\mprset{flushleft}
+        \inferrule* [right={\tiny tenL}] {
+          $$\mprset{flushleft}
+          \inferrule* [right={\tiny beta}] {
+            $$\mprset{flushleft}
+            \inferrule* [right={\tiny Gr}] {
+              $$\mprset{flushleft}
+              \inferrule* [right={\tiny Gl}] {
+                $$\mprset{flushleft}
+                \inferrule* [right={\tiny Fl}] {
+                  $$\mprset{flushleft}
+                  \inferrule* [right={\tiny Fr}] {
+                    $$\mprset{flushleft}
+                    \inferrule* [right={\tiny tenR}] {
+                      $$\mprset{flushleft}
+                      \inferrule* [right={\tiny ax}] {
+                        \,
+                      }{[[x0 : X |- x0 : X]]}
+                      $$\mprset{flushleft}
+                      \inferrule* [right={\tiny ax}] {
+                        \,
+                      }{[[y0 : Y |- y0 : Y]]}
+                    }{[[x0 : X , y0 : Y |- x0 (x) y0 : h(X) (x) Y]]}
+                  }{[[x0 : X , y0 : Y ; . |- F (x0 (x) y0) : F (h(X) (x) Y)]]}
+                }{[[x0 : X ; y1 : F Y |- let y1 : F Y be F y0 in F (x0 (x) y0) : F (h(X) (x) Y)]]}
+              }{[[y2 : Gf F Y , x0 : X ; . |- let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0)) : F (h(X) (x) Y)]]}
+            }{[[y2 : Gf F Y , x0 : X |- Gf (let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0))) : Gf F (h(X) (x) Y)]]}
+          }{[[x1 : X , y3 : Gf F Y |- ex y3 , x1 with y2 , x0 in (Gf (let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0)))) : Gf F (h(X) (x) Y)]]}
+        }{[[z : h(X) (x) Gf F Y |- let z : h(X) (x) Gf F Y be x1 (x) y3 in (ex y3 , x1 with y2 , x0 in (Gf (let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0))))) : Gf F (h(X) (x) Y)]]}
+      }{[[.
+|- \l z : h(X) (x) Gf F Y .
+let z : h(X) (x) Gf F Y be x1 (x) y3 in (ex y3 , x1 with y2 , x0 in (Gf (let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0))))) : (h(X) (x) Gf F Y) -> (Gf F (h(X) (x) Y))]]}
+    \end{math}
+  \end{center}
+\end{itemize}
 

### 2017-06-28 Elle/Elle-output.tex
Elle to ND attempted

\documentclass[11pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{supertabular}
\usepackage{cmll}
\usepackage{txfonts}
\usepackage{color}
\usepackage{tikz}
\usepackage{mathpartir}

\newcommand\encircle[1]{%
  \tikz[baseline=(X.base)] 
    \node (X) [draw, shape=circle, inner sep=-1.5pt] {\strut #1};}

\newcommand{\circop}[1]{\mathop{\encircle{#1}}}

\input{Elle-ott}

\begin{document}

Deriving exchange in Elle comonadicly:

\begin{center}
  \tiny
  \begin{math}
    $$\mprset{flushleft}
    \inferrule* [right={\tiny impR}] {
      $$\mprset{flushleft}
    \inferrule* [right={\tiny tenL}] {
      $$\mprset{flushleft}
    \inferrule* [right={\tiny Fl}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny Fl}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny beta}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny tenR}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny Fr}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny ax}] {
                \,
              }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
            }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}  }
            \\
            $$\mprset{flushleft}
            \inferrule* [right={\tiny Fr}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny ax}] {
                \,
              }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
            }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
          }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
        }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{;}   \cdot   \vdash   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
      }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}  \ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
    }{ \cdot   \ottsym{;}  \ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{,}  \ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
    }{ \cdot   \ottsym{;}  \ottmv{z}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash   \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{2}}}}  \otimes  \ottmv{y_{{\mathrm{2}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
    }{ \cdot   \ottsym{;}   \cdot   \vdash   \lambda_l  \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}   .  \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{2}}}}  \otimes  \ottmv{y_{{\mathrm{2}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \rightharpoonup  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
  \end{math}
\end{center}

Deriving right contraction in Elle comonadicly:
\begin{center}
  \tiny
  \begin{math}
    $$\mprset{flushleft}
    \inferrule* [right={\tiny impR}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny tenL}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny Fl}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny Fl}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny contrR}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny tenR}] {
                $$\mprset{flushleft}
                \inferrule* [right={\tiny Fr}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny ax}] {
                    \,
                  }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
                }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
                \\
                \inferrule* [right={\tiny tenR}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny Fr}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny ax}] {
                      \,
                    }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
                  }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}  }
                  \\
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny Fr}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny ax}] {
                      \,
                    }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
                  }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
                }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
              }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \otimes  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
            }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \otimes  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
          }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{;}  \ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \otimes  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
        }{ \cdot   \ottsym{;}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{,}  \ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \otimes  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
      }{ \cdot   \ottsym{;}  \ottmv{z}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash   \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\, \ottmv{y_{{\mathrm{1}}}}  \otimes  \ottmv{x_{{\mathrm{3}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \otimes  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
    }{ \cdot   \ottsym{;}   \cdot   \vdash   \lambda_l  \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}   .  \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\, \ottmv{y_{{\mathrm{1}}}}  \otimes  \ottmv{x_{{\mathrm{3}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \otimes  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}  \rightharpoonup  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}  \ottsym{)}}
  \end{math}
\end{center}

Deriving left contraction in Elle comonadicly:
\begin{center}
  \tiny
  \begin{math}
    $$\mprset{flushleft}
    \inferrule* [right={\tiny impR}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny tenL}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny Fl}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny Fl}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny contrR}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny tenR}] {
                $$\mprset{flushleft}
                \inferrule* [right={\tiny tenR}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny Fr}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny ax}] {
                      \,
                    }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
                  }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
                  \\
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny Fr}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny ax}] {
                      \,
                    }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
                  }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}  }
                }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{;}   \cdot   \vdash    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}  }
                \\
                \inferrule* [right={\tiny Fr}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny ax}] {
                    \,
                  }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
                }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
              }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \otimes   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
            }{\ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{;}   \cdot   \vdash   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \otimes   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
          }{\ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \otimes   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
        }{ \cdot   \ottsym{;}  \ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{,}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \otimes   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
      }{ \cdot   \ottsym{;}  \ottmv{z}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash   \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{3}}}}  \otimes  \ottmv{y_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \otimes   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
    }{ \cdot   \ottsym{;}   \cdot   \vdash   \lambda_l  \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}   .  \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{3}}}}  \otimes  \ottmv{y_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{3}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \otimes  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \rightharpoonup  \ottsym{(}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
  \end{math}
\end{center}

Deriving weakening in Elle comonadicly:
\begin{center}
  \tiny
  \begin{math}
    $$\mprset{flushleft}
    \inferrule* [right={\tiny impR}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny Fl}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny weak}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny unitR}] {
            \,
          }{ \cdot   \vdash   \mathsf{triv}   \ottsym{:}   \mathsf{Unit} }
        }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash   \mathsf{weak}\, \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\,  \mathsf{triv}    \ottsym{:}   \mathsf{Unit} }
      }{ \cdot   \ottsym{;}  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{weak}\, \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\,  \mathsf{triv}     \ottsym{:}   \mathsf{Unit} }
    }{ \cdot   \ottsym{;}   \cdot   \vdash   \lambda_l  \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   .  \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{weak}\, \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\,  \mathsf{triv}      \ottsym{:}  \ottsym{(}   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}  \rightharpoonup  \ottsym{(}   \mathsf{Unit}   \ottsym{)}}
  \end{math}
\end{center}

$GF$ is a monad:
\begin{itemize}
\item Deriving $\eta$:
  \begin{center}
    \tiny
    \begin{math}
      $$\mprset{flushleft}
      \inferrule* [right={\tiny impR}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny Gr}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny Gl}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny Fl}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny Gl}] {
                $$\mprset{flushleft}
                \inferrule* [right={\tiny ax}] {
                  \,
                }{ \cdot   \ottsym{;}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{F} \ottnt{X}   \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{F} \ottnt{X} }
              }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{X}    \ottsym{;}   \cdot   \vdash   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F} \ottnt{X} }
            }{ \cdot   \ottsym{;}  \ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     \vdash   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}    \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{:}   \mathsf{F} \ottnt{X} }
          }{\ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}      \ottsym{;}   \cdot   \vdash   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}    \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{F} \ottnt{X} }
        }{\ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}      \vdash   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}    \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{X}  }
      }{ \cdot   \vdash   \lambda_l  \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     .  \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}    \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}      \ottsym{)}  \rightharpoonup  \ottsym{(}   \mathsf{G}  \mathsf{F} \ottnt{X}    \ottsym{)}}
    \end{math}
  \end{center}
\item Deriving $\mu$:
  \begin{center}
    \tiny
    \begin{math}
      $$\mprset{flushleft}
      \inferrule* [right={\tiny impR}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny Gr}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny Fr}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny ax}] {
              \,
            }{\ottmv{x}  \ottsym{:}  \ottnt{X}  \vdash  \ottmv{x}  \ottsym{:}  \ottnt{X}}
          }{\ottmv{x}  \ottsym{:}  \ottnt{X}  \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{x}   \ottsym{:}   \mathsf{F} \ottnt{X} } 
        }{\ottmv{x}  \ottsym{:}  \ottnt{X}  \vdash   \mathsf{G}  \mathsf{F} \ottmv{x}    \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{X}  }
      }{ \cdot   \vdash   \lambda_l  \ottmv{x}  :  \ottnt{X} .  \mathsf{G}  \mathsf{F} \ottmv{x}     \ottsym{:}  \ottsym{(}  \ottnt{X}  \ottsym{)}  \rightharpoonup  \ottsym{(}   \mathsf{G}  \mathsf{F} \ottnt{X}    \ottsym{)}}
    \end{math}
  \end{center}
\end{itemize}

The monad $GF$ is strong:
\begin{itemize}
\item Deriving the tensorial strength $\tau$:
  \begin{center}
    \tiny
    \begin{math}
      $$\mprset{flushleft}
      \inferrule* [right={\tiny impR}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny tenL}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny beta}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny Gr}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny Gl}] {
                $$\mprset{flushleft}
                \inferrule* [right={\tiny Fl}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny Fr}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny tenR}] {
                      $$\mprset{flushleft}
                      \inferrule* [right={\tiny ax}] {
                        \,
                      }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}}
                      $$\mprset{flushleft}
                      \inferrule* [right={\tiny ax}] {
                        \,
                      }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{Y}  \vdash  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{Y}}
                    }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{Y}  \vdash  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \ottnt{X}   \otimes  \ottnt{Y}}
                  }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{Y}  \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}   \ottsym{:}   \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)} }
                }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \ottsym{;}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F} \ottnt{Y}   \vdash   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{:}   \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)} }
              }{\ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{Y}    \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \ottsym{;}   \cdot   \vdash   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{:}   \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)} }
            }{\ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{Y}    \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \vdash   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)}  }
          }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}  \ottnt{X}  \ottsym{,}  \ottmv{y_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{Y}    \vdash   \mathsf{ex}\, \ottmv{y_{{\mathrm{3}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{2}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)}  }
        }{\ottmv{z}  \ottsym{:}   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}    \vdash   \mathsf{let}\, \ottmv{z}  :   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{1}}}}  \otimes  \ottmv{y_{{\mathrm{3}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{3}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{2}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)}  }
      }{ \cdot   \vdash   \lambda_l  \ottmv{z}  :   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}   .  \mathsf{let}\, \ottmv{z}  :   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{1}}}}  \otimes  \ottmv{y_{{\mathrm{3}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{3}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{2}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}    \ottsym{)}  \rightharpoonup  \ottsym{(}   \mathsf{G}  \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)}    \ottsym{)}}
    \end{math}
  \end{center}
\end{itemize}

\appendix

\section{Full Ott Spec}
\label{sec:full_ott_spec}
\footnotesize
\ottall
% section full_ott_spec (end)

\end{document}

### 2017-07-14 natural-deduction.tex
reduction rules

\subsection{Categorical Interpretation of Natural Deductions}

$T$ rules: in the symmetric monoidal closed category of the adjunction model

T\_identity: $id_X:X\rightarrow X$

T\_unitI:

T\_unitE: given $t_1:\Delta\rightarrow Unit$ and $t_2:\Gamma\rightarrow Y$, returns
$\lambda_Y\circ(t_1\otimes t_2):\Gamma\otimes\Delta\rightarrow Unit\otimes Y\rightarrow Y$

T\_tenI: given $t_1:\Gamma\rightarrow X$ and $t_2:\Delta\rightarrow Y$, returns
$t_1\otimes t_2:\Gamma\otimes\Delta\rightarrow X\otimes Y$

T\_tenE: given $t_1:\Gamma\rightarrow X\otimes Y$ and
$t_2:\Delta\otimes X\otimes Y\rightarrow Z$, returns \\
$t_2\circ\e{X\otimes Y,\Delta}\circ t_1\otimes id_\Delta:\Gamma\otimes\Delta\rightarrow(X\otimes Y)\otimes\Delta\rightarrow\Delta\otimes(X\otimes Y)\rightarrow Z$

T\_implI:

T\_implE:

T\_imprI:

T\_imprE:

T\_GI: given $s:FX_1\otimes'...\otimes' FX_n\rightarrow A$, returns \\
$Gs\circ G\m{}^{-1}\circ\eta:X_1\otimes...\otimes X_n\rightarrow GF(X_1\otimes...\otimes X_n)\rightarrow G(FX_1\otimes'...\otimes'FX_n)\rightarrow GA$

S rules: in the Lambek category of the adjunction model

S\_identity: $id_A:A\rightarrow A$

S\_unitI:

S\_unitE:

\subsection{Normaalization and Reduction}

### 2017-07-17 Elle-ND/implementation/Evaluation.hs
Implementation of the T terms

@@ -1,0 +1,45 @@
+{-# LANGUAGE FlexibleContexts #-}
+-----------------------------------------------------------------------
+-- One-step evaluation functions for the terms                       --
+-----------------------------------------------------------------------
+module Evaluation where
+
+import Text.Parsec
+import Control.Monad.Except
+import Data.List
+
+import Syntax
+import TypeCheck
+
+eval :: Fresh m => Ctx -> Term -> ExceptT TypeException m Term
+eval _ Triv = return Triv
+eval g (LetU t1 t2) = do
+  ctx1 <- extractCtx g t1
+  ty <- typeCheck ctx1 t1
+  case ty of
+    Unit -> return t2
+    _ -> throwError InvalidTypeError
+eval g (LetT (Tens t1 t2) (Tensor ty1 ty2) b) = do
+  (tm1, b') <- unbind b
+  (tm2, t) <- unbind b'
+  ctx1 <- extractCtx g t1
+  ctx2 <- extractCtx g t2
+  ty1' <- typeCheck ctx1 t1
+  ty2' <- typeCheck ctx2 t2
+  if ((ty1', ty2') == (ty1, ty2))
+    then return (subst tm2 t2 (subst tm1 t1 t))
+    else throwError InvalidTypeError
+eval g (App (Lam ty b) t) = do
+  (tm, t') <- unbind b
+  ctx <- extractCtx g t
+  ty' <- typeCheck ctx t
+  if (ty' == ty)
+    then return (subst tm t t')
+    else throwError InvalidTypeError
+eval g (App t1 t2) = do
+  ctx1 <- extractCtx g t1
+  ctx2 <- extractCtx g t2
+  t1' <- eval ctx1 t1
+  t2' <- eval ctx2 t2
+  return (App t1' t2')
+  

### 2017-07-17 Elle-ND/implementation/Parser.hs

@@ -1,0 +1,189 @@
+{-# LANGUAGE NoMonomorphismRestriction, PackageImports,
+             FlexibleContexts, PackageImports #-}
+
+------------------------------------------------------------------------
+-- This file contains the ILL-Impl parsers utilizing Parsec library.  --
+------------------------------------------------------------------------
+
+module Parser where
+
+import Prelude
+import Data.List
+import Data.Char
+import Text.Parsec
+import Text.Parsec.Expr
+import qualified Text.Parsec.Token as Token
+import Text.Parsec.Language
+import Control.Monad
+import Data.Functor.Identity
+
+import Syntax
+
+lexer = haskellStyle {
+  Token.reservedNames = ["let", "be", "in", "for", "as", "triv", "Unit"],
+  Token.reservedOpNames = ["(x)", "tens", "-o", "\\", ":", ":show", ":t", ":type", ":u",
+                           ":unfold", ":d", ":dump"]
+}
+
+tokenizer  = Token.makeTokenParser lexer
+ident      = Token.identifier tokenizer
+reserved   = Token.reserved tokenizer
+reservedOp = Token.reservedOp tokenizer
+parens     = Token.parens tokenizer
+angles     = Token.angles tokenizer
+brackets   = Token.brackets tokenizer
+braces     = Token.braces tokenizer
+ws         = Token.whiteSpace tokenizer
+natural    = Token.natural tokenizer
+dot        = Token.dot tokenizer
+comma      = Token.comma tokenizer
+colon      = Token.colon tokenizer
+symbol     = Token.symbol tokenizer
+identifier = Token.identifier tokenizer
+
+unexpColon msg = unexpected msg
+
+------------------------------------------------------------------------
+-- Type parsers                                                       --
+------------------------------------------------------------------------
+tyUnit = do
+  reservedOp "Unit"
+  return Unit
+
+------------------------------------------------------------------------
+-- Type parser tables                                                 --
+------------------------------------------------------------------------
+tyTable = [[binOp AssocLeft "(x)" (\d r -> Tensor d r)],
+           [binOp AssocRight "-o" (\d r -> Imp d r)]]
+binOp assoc op f = Text.Parsec.Expr.Infix (do{ reservedOp op; return f}) assoc
+typeParser = buildExpressionParser tyTable typeParser'
+typeParser' = parens typeParser <|> tyUnit
+
[…]

### 2017-07-17 Elle-ND/implementation/Pretty.hs

@@ -1,0 +1,101 @@
+{-# LANGUAGE FlexibleContexts #-}
+
+------------------------------------------------------------------------
+-- This file contains the ILL-Impl pretty printers.                   --
+------------------------------------------------------------------------
+
+module Pretty where
+
+import Data.List
+import Data.Char
+import Text.Parsec
+import Unbound.LocallyNameless
+import Unbound.LocallyNameless.Alpha
+import Control.Monad.Except
+
+import Syntax
+import Parser
+
+
+
+------------------------------------------------------------------------
+-- Converts a type into a string                                      --
+------------------------------------------------------------------------
+prettyType :: Fresh m => Type -> m String
+prettyType Unit = return "Unit"
+prettyType (Tensor a b) = do
+  a' <- prettyType a
+  b' <- prettyType b
+  return (a' ++ "(x)" ++ b')
+prettyType (Imp a b) = do
+  a' <- prettyType a
+  b' <- prettyType b
+  return ("(" ++ a' ++ ")" ++ "-o" ++ b')
+
+------------------------------------------------------------------------
+-- Converts a term into a string                                      --
+------------------------------------------------------------------------
+prettyTerm :: Fresh m => Term -> m String
+prettyTerm Triv = return "Triv"
+prettyTerm (Var x) = return.n2s $ x
+prettyTerm (LetU t1 t2) = do
+  t1' <- prettyTerm t1
+  t2' <- prettyTerm t2
+  return $ "let " ++ t1' ++ " : Unit be Triv in " ++ t2'
+prettyTerm (LetT t1 ty b) = do
+  t1' <- prettyTerm t1
+  ty' <- prettyType ty
+  (x, b') <- unbind b
+  (y, t2) <- unbind b'
+  let x' = n2s x
+  let y' = n2s y
+  t2' <- prettyTerm t2
+  return $ "let " ++ x' ++ " (x) " ++ y' ++ " : " ++ ty' ++ " be " ++ t1' ++ " in " ++ t2'
+prettyTerm (Tens t1 t2) = do
+  t1' <- prettyTerm t1
+  t2' <- prettyTerm t2
+  return $ "(tens " ++ t1' ++ ", " ++ t2' ++ ")"
+prettyTerm (Lam ty b) = do
+  ty' <- prettyType ty
+  (x, t) <- unbind b
+  t' <- prettyTerm t
+  return $ "\\(" ++ (n2s x) ++ ":" ++ ty' ++ ")." ++ t'
+prettyTerm (App t1 t2) = do
[…]

### 2017-07-17 Elle-ND/implementation/Syntax.hs

@@ -1,0 +1,92 @@
+{-# LANGUAGE TemplateHaskell,       FlexibleInstances,
+            MultiParamTypeClasses, FlexibleContexts, 
+            UndecidableInstances                      #-}
+--------------------------------------------------------------------------------------
+-- This file contains the syntax and syntax manipulators of the non linear of Elle. --
+--------------------------------------------------------------------------------------
+
+module Syntax (module Unbound.LocallyNameless,
+               module Unbound.LocallyNameless.Alpha,
+               Type(..),
+               Term(..),
+               TmName,
+               replace,
+               replaceTest,
+               TypeException(..),
+               n2s) where
+
+import Prelude
+import Data.List
+import Unbound.LocallyNameless hiding (fv)
+import Unbound.LocallyNameless.Alpha
+import Errors
+
+data Type = Unit
+          | Tensor Type Type
+          | Imp Type Type
+          | ImpL Type Type
+          | ImpR Type Type
+          deriving (Show, Eq)
+
+
+-- Name:
+-- an abstract type for representing names, provided by Unbound
+-- Names are indexed by the sorts of things to which they can refer,
+-- or more precisely, the sorts of things which can be substituted for them
+type TmName = Name Term
+
+data Term = Triv
+          | Var TmName     -- Variable is simply a name for some Term
+          -- LetU t1 t2
+          -- let t1 : Unit be triv in t2
+          | LetU Term Term
+          -- Bind p b:
+          -- a pair consisting of a pattern p and a body b
+          -- The pattern may bind names which occur in the body
+          -- LetT t1 (X * Y) (Bind x (Bind y t2))
+          -- let t1 : X * Y be x * y in t2
+          --
+          | LetT Term Type (Bind TmName (Bind TmName Term))
+          | Tens Term Term
+          | Lam Type (Bind TmName Term)
+          | App Term Term
+          -- Ex t1 t2 (Bind x1 (Bind x2 t3))
+          -- ex x1, x2 with t1, t2 in t3
+          | Ex Term Term (Bind TmName (Bind TmName Term))
+          -- ContrR t1 t2 (Bind x t3)
+          -- contrR x as t1, t2 in t3
+          | ContrR Term Term (Bind TmName Term)
+          -- ContrL t1 t2 (Bind x t3)
+          -- contrL x as t1, t2 in t3
+          | ContrL Term Term (Bind TmName Term)
+          -- Weak (Bind x t)
[…]

### 2017-07-17 Elle-ND/implementation/Testing.hs

@@ -1,0 +1,49 @@
+module Testing where
+
+import Syntax
+import Parser
+import Pretty
+
+------------------------------------------------------------------------
+-- Lambda testing                                                     --
+------------------------------------------------------------------------
+
+lamtest0 = parseTester lamParse "\\(x:Unit).y"
+
+lamtest1 = parseTester lamParse "\\(x:Unit (x) Unit).y"
+
+lamtest' = parseTester lamParse "\\(x:Unit(x)Unit.(tens y z)"
+
+lamtest2 = parseTester lamParse "\\(x:Unit-oUnit).y"
+
+lamtest3 = parseTester lamParse "\\(x:Unit -o Unit).y"
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2017-07-17 Elle-ND/implementation/TypeCheck.hs

@@ -1,0 +1,155 @@
+{-# LANGUAGE FlexibleContexts #-}
+
+---------------------------------------------------------
+-- Type checking the terms defined in Syntax.hs        --
+---------------------------------------------------------
+
+module TypeCheck where
+
+import Text.Parsec
+import Control.Monad.Except
+import Data.List
+
+import Syntax
+
+-----------------------------------------------------------------------
+-- Typing contexts                                                   --
+-----------------------------------------------------------------------
+type Ctx = [(TmName, Type)]
+
+emptyCtx :: Ctx
+emptyCtx = []
+
+extCtx :: Ctx -> TmName -> Type -> Ctx
+extCtx ctx nm ty = (nm, ty) : ctx
+
+infixr 5 |:|
+(|:|) :: (TmName, Type) -> Ctx -> Ctx
+(x,t) |:| ctx = extCtx ctx x t
+
+-----------------------------------------------------------------------
+-- Free Variable Collection                                          --
+-----------------------------------------------------------------------
+-- The Fresh type class:
+-- governs monads which can generate new globally unique Names based on a given Name
+fv :: Fresh m => Term -> m [TmName]
+fv Triv = return []
+fv (Var t) = return [t]
+fv (LetU t1 t2) = do
+  t1' <- fv t1
+  t2' <- fv t2
+  return (t1' ++ t2')
+-- unbind:
+-- always generates a new globally fresh name
+-- no matter what other names are or aren't in scope
+-- (doesn't look pretty when printing)
+fv (LetT t ty b) = do
+  (tm, b') <- unbind b
+  (tm', t') <- unbind b'
+  t1 <- fv t
+  t2 <- fv t'
+  return (t1 ++ (t2 \\ [tm, tm']))
+fv (Tens t1 t2) = do
+  t1' <- fv t1
+  t2' <- fv t2
+  return (t1' ++ t2')
+fv (Lam ty b) = do
+  (tm, t) <- unbind b
+  t' <- fv t
+  return (t' \\ [tm])
+fv (App t1 t2) = do
+  t1' <- fv t1
+  t2' <- fv t2
+  return (t1' ++ t2')
+
+-----------------------------------------------------------------------
+-- Takes a list of free variables and a context,                     --
[…]

### 2017-07-19 Elle-ND/implementation/Evaluation.hs
Implementation for S terms

@@ -11,35 +11,96 @@ import Data.List
 import Syntax
 import TypeCheck
 
-eval :: Fresh m => Ctx -> Term -> ExceptT TypeException m Term
-eval _ Triv = return Triv
-eval g (LetU t1 t2) = do
-  ctx1 <- extractCtx g t1
-  ty <- typeCheck ctx1 t1
+eval_T :: Fresh m => Ctx_T -> Term_T -> ExceptT TypeException m Term_T
+eval_T _ Triv_T = return Triv_T
+eval_T g (LetU_T t1 t2) = do
+  ctx1 <- extractCtx_T g t1
+  ty <- typeCheck_T ctx1 t1
   case ty of
-    Unit -> return t2
+    Unit_T -> return t2
     _ -> throwError InvalidTypeError
-eval g (LetT (Tens t1 t2) (Tensor ty1 ty2) b) = do
+eval_T g (LetT_T (Tens_T t1 t2) (Tensor_T ty1 ty2) b) = do
   (tm1, b') <- unbind b
   (tm2, t) <- unbind b'
-  ctx1 <- extractCtx g t1
-  ctx2 <- extractCtx g t2
-  ty1' <- typeCheck ctx1 t1
-  ty2' <- typeCheck ctx2 t2
+  ctx1 <- extractCtx_T g t1
+  ctx2 <- extractCtx_T g t2
+  ty1' <- typeCheck_T ctx1 t1
+  ty2' <- typeCheck_T ctx2 t2
   if ((ty1', ty2') == (ty1, ty2))
     then return (subst tm2 t2 (subst tm1 t1 t))
     else throwError InvalidTypeError
-eval g (App (Lam ty b) t) = do
+eval_T g (App_T (Lam_T ty b) t) = do
   (tm, t') <- unbind b
-  ctx <- extractCtx g t
-  ty' <- typeCheck ctx t
+  ctx <- extractCtx_T g t
+  ty' <- typeCheck_T ctx t
   if (ty' == ty)
     then return (subst tm t t')
     else throwError InvalidTypeError
-eval g (App t1 t2) = do
-  ctx1 <- extractCtx g t1
-  ctx2 <- extractCtx g t2
-  t1' <- eval ctx1 t1
-  t2' <- eval ctx2 t2
-  return (App t1' t2')
+eval_T g (App_T t1 t2) = do
+  ctx1 <- extractCtx_T g t1
[…]

### 2017-07-19 Elle-ND/implementation/Parser.hs

@@ -46,104 +46,104 @@ unexpColon msg = unexpected msg
 ------------------------------------------------------------------------
 -- Type parsers                                                       --
 ------------------------------------------------------------------------
-tyUnit = do
+tyUnit_T = do
   reservedOp "Unit"
-  return Unit
+  return Unit_T
 
 ------------------------------------------------------------------------
 -- Type parser tables                                                 --
 ------------------------------------------------------------------------
-tyTable = [[binOp AssocLeft "(x)" (\d r -> Tensor d r)],
-           [binOp AssocRight "-o" (\d r -> Imp d r)]]
+tyTable_T = [[binOp AssocLeft "(x)" (\d r -> Tensor_T d r)],
+           [binOp AssocRight "-o" (\d r -> Imp_T d r)]]
 binOp assoc op f = Text.Parsec.Expr.Infix (do{ reservedOp op; return f}) assoc
-typeParser = buildExpressionParser tyTable typeParser'
-typeParser' = parens typeParser <|> tyUnit
+typeParser_T = buildExpressionParser tyTable_T typeParser'_T
+typeParser'_T = parens typeParser_T <|> tyUnit_T
 
 ------------------------------------------------------------------------
 -- Term parsers                                                       --
 ------------------------------------------------------------------------
-aterm = parens termParser <|> trivParse <|> var
-termParser = lamParse <|> try letTParse <|> letUParse <|> tensParse <|> appParse <?> "Parser error"
+aterm_T = parens termParser_T <|> trivParse_T <|> var_T
+termParser_T = lamParse_T <|> try letTParse_T <|> letUParse_T <|> tensParse_T <|> appParse_T <?> "Parser error"
 
-var = var' varName Var
-var' p c = do
-  var_name <- p
-  return (c var_name)
+var_T = var'_T varName_T Var_T
+var'_T p c = do
+  var_name_T <- p
+  return (c var_name_T)
 
-varName = varName' isUpper "Term variables must begin with a lowercase letter."
-varName' p msg = do
+varName_T = varName'_T isUpper "Term variables must begin with a lowercase letter."
+varName'_T p msg = do
   n <- identifier
   when ((length n) > 0) $
     let h = head n in
       when (p h || isNumber h) $ unexpColon (n++" : "++msg)
[…]

### 2017-07-19 Elle-ND/implementation/Pretty.hs

@@ -21,81 +21,81 @@ import Parser
 ------------------------------------------------------------------------
 -- Converts a type into a string                                      --
 ------------------------------------------------------------------------
-prettyType :: Fresh m => Type -> m String
-prettyType Unit = return "Unit"
-prettyType (Tensor a b) = do
-  a' <- prettyType a
-  b' <- prettyType b
+prettyType_T :: Fresh m => Type_T -> m String
+prettyType_T Unit_T = return "Unit"
+prettyType_T (Tensor_T a b) = do
+  a' <- prettyType_T a
+  b' <- prettyType_T b
   return (a' ++ "(x)" ++ b')
-prettyType (Imp a b) = do
-  a' <- prettyType a
-  b' <- prettyType b
+prettyType_T (Imp_T a b) = do
+  a' <- prettyType_T a
+  b' <- prettyType_T b
   return ("(" ++ a' ++ ")" ++ "-o" ++ b')
 
 ------------------------------------------------------------------------
 -- Converts a term into a string                                      --
 ------------------------------------------------------------------------
-prettyTerm :: Fresh m => Term -> m String
-prettyTerm Triv = return "Triv"
-prettyTerm (Var x) = return.n2s $ x
-prettyTerm (LetU t1 t2) = do
-  t1' <- prettyTerm t1
-  t2' <- prettyTerm t2
+prettyTerm_T :: Fresh m => Term_T -> m String
+prettyTerm_T Triv_T = return "Triv"
+prettyTerm_T (Var_T x) = return.n2s $ x
+prettyTerm_T (LetU_T t1 t2) = do
+  t1' <- prettyTerm_T t1
+  t2' <- prettyTerm_T t2
   return $ "let " ++ t1' ++ " : Unit be Triv in " ++ t2'
-prettyTerm (LetT t1 ty b) = do
-  t1' <- prettyTerm t1
-  ty' <- prettyType ty
+prettyTerm_T (LetT_T t1 ty b) = do
+  t1' <- prettyTerm_T t1
+  ty' <- prettyType_T ty
   (x, b') <- unbind b
   (y, t2) <- unbind b'
   let x' = n2s x
   let y' = n2s y
-  t2' <- prettyTerm t2
+  t2' <- prettyTerm_T t2
   return $ "let " ++ x' ++ " (x) " ++ y' ++ " : " ++ ty' ++ " be " ++ t1' ++ " in " ++ t2'
-prettyTerm (Tens t1 t2) = do
[…]

### 2017-07-19 Elle-ND/implementation/Syntax.hs

@@ -7,11 +7,16 @@
 
 module Syntax (module Unbound.LocallyNameless,
                module Unbound.LocallyNameless.Alpha,
-               Type(..),
-               Term(..),
-               TmName,
-               replace,
-               replaceTest,
+               Type_T(..),
+               Type_S(..),
+               Term_T(..),
+               Term_S(..),
+               TmName_T,
+               TmName_S,
+               replace_T,
+               replaceTest_T,
+               varT2varS,
+               varS2varT,
                TypeException(..),
                n2s) where
 
@@ -21,72 +26,114 @@ import Unbound.LocallyNameless hiding (fv)
 import Unbound.LocallyNameless.Alpha
 import Errors
 
-data Type = Unit
-          | Tensor Type Type
-          | Imp Type Type
-          | ImpL Type Type
-          | ImpR Type Type
+data Type_T = Unit_T
+          | Tensor_T Type_T Type_T
+          | Imp_T Type_T Type_T
+          | Gty_T Type_S
           deriving (Show, Eq)
+
+data Type_S = Unit_S
+            | Tensor_S Type_S Type_S
+            | Imp_S Type_S Type_S
+            | ImpL_S Type_S Type_S
+            | ImpR_S Type_S Type_S
+            | Fty_S Type_T
+            deriving (Show, Eq)
 
 
 -- Name:
 -- an abstract type for representing names, provided by Unbound
 -- Names are indexed by the sorts of things to which they can refer,
 -- or more precisely, the sorts of things which can be substituted for them
-type TmName = Name Term
+type TmName_T = Name Term_T
 
-data Term = Triv
-          | Var TmName     -- Variable is simply a name for some Term
-          -- LetU t1 t2
+data Term_T = Triv_T
+          | Var_T TmName_T     -- Variable is simply a name for some Term
+          -- LetU_T t1 t2
           -- let t1 : Unit be triv in t2
-          | LetU Term Term
+          | LetU_T Term_T Term_T
           -- Bind p b:
           -- a pair consisting of a pattern p and a body b
           -- The pattern may bind names which occur in the body
-          -- LetT t1 (X * Y) (Bind x (Bind y t2))
[…]

### 2017-07-19 Elle-ND/implementation/Testing.hs

@@ -8,15 +8,15 @@ import Pretty
 -- Lambda testing                                                     --
 ------------------------------------------------------------------------
 
-lamtest0 = parseTester lamParse "\\(x:Unit).y"
+lamtest0_T = parseTester_T lamParse_T "\\(x:Unit).y"
 
-lamtest1 = parseTester lamParse "\\(x:Unit (x) Unit).y"
+lamtest1_T = parseTester_T lamParse_T "\\(x:Unit (x) Unit).y"
 
-lamtest' = parseTester lamParse "\\(x:Unit(x)Unit.(tens y z)"
+lamtest'_T = parseTester_T lamParse_T "\\(x:Unit(x)Unit.(tens y z)"
 
-lamtest2 = parseTester lamParse "\\(x:Unit-oUnit).y"
+lamtest2_T = parseTester_T lamParse_T "\\(x:Unit-oUnit).y"
 
-lamtest3 = parseTester lamParse "\\(x:Unit -o Unit).y"
+lamtest3_T = parseTester_T lamParse_T "\\(x:Unit -o Unit).y"
 
 
 

### 2017-07-19 Elle-ND/implementation/TypeCheck.hs

@@ -15,135 +15,285 @@ import Syntax
 -----------------------------------------------------------------------
 -- Typing contexts                                                   --
 -----------------------------------------------------------------------
-type Ctx = [(TmName, Type)]
+type Ctx_T = [(TmName_T, Type_T)]
 
-emptyCtx :: Ctx
-emptyCtx = []
+emptyCtx_T :: Ctx_T
+emptyCtx_T = []
 
-extCtx :: Ctx -> TmName -> Type -> Ctx
-extCtx ctx nm ty = (nm, ty) : ctx
+extCtx_T :: Ctx_T -> TmName_T -> Type_T -> Ctx_T
+extCtx_T ctx nm ty = (nm, ty) : ctx
 
 infixr 5 |:|
-(|:|) :: (TmName, Type) -> Ctx -> Ctx
-(x,t) |:| ctx = extCtx ctx x t
+(|:|) :: (TmName_T, Type_T) -> Ctx_T -> Ctx_T
+(x,t) |:| ctx = extCtx_T ctx x t
+
+
+
+type Ctx_S = [(TmName_S, Type_S)]
+
+emptyCtx_S :: Ctx_S
+emptyCtx_S = []
+
+extCtx_S :: Ctx_S -> TmName_S -> Type_S -> Ctx_S
+extCtx_S ctx nm ty = (nm, ty) : ctx
+
+infixr 5 |::|
+(|::|) :: (TmName_S, Type_S) -> Ctx_S -> Ctx_S
+(x,t) |::| ctx = extCtx_S ctx x t
 
 -----------------------------------------------------------------------
 -- Free Variable Collection                                          --
 -----------------------------------------------------------------------
 -- The Fresh type class:
 -- governs monads which can generate new globally unique Names based on a given Name
-fv :: Fresh m => Term -> m [TmName]
-fv Triv = return []
-fv (Var t) = return [t]
-fv (LetU t1 t2) = do
-  t1' <- fv t1
-  t2' <- fv t2
+fv_T :: Fresh m => Term_T -> m [TmName_T]
+fv_T Triv_T = return []
+fv_T (Var_T x) = return [x]
+fv_T (LetU_T t1 t2) = do
+  t1' <- fv_T t1
+  t2' <- fv_T t2
   return (t1' ++ t2')
 -- unbind:
[…]

### 2017-07-22 Elle-ND/implementation/Evaluation.hs
Type checking, reduction, and parser

@@ -1,7 +1,4 @@
 {-# LANGUAGE FlexibleContexts #-}
------------------------------------------------------------------------
--- One-step evaluation functions for the terms                       --
------------------------------------------------------------------------
 module Evaluation where
 
 import Text.Parsec
@@ -9,93 +6,109 @@ import Control.Monad.Except
 import Data.List
 
 import Syntax
-import TypeCheck
 
-eval_T :: Fresh m => Ctx_T -> Term_T -> ExceptT TypeException m Term_T
-eval_T _ Triv_T = return Triv_T
-eval_T g (LetU_T t1 t2) = do
-  ctx1 <- extractCtx_T g t1
-  ty <- typeCheck_T ctx1 t1
-  case ty of
-    Unit_T -> return t2
-    _ -> throwError InvalidTypeError
-eval_T g (LetT_T (Tens_T t1 t2) (Tensor_T ty1 ty2) b) = do
+-----------------------------------------------------------------------
+-- Checks if a T term is a value, i.e. cannot be further evaluated   --
+-----------------------------------------------------------------------
+isVal_T :: Fresh m => Term_T -> m Bool
+isVal_T Triv_T = return True
+isVal_T (Var_T x) = return True
+isVal_T (Tens_T t1 t2) = do
+  t1' <- isVal_T t1
+  case t1' of
+    True  -> isVal_T t2
+    False -> return False
+isVal_T (Lam_T ty b) = do
+  (x, t) <- unbind b
+  isVal_T t
+isVal_T (Gt_T s) = isVal_S s
+isVal_T _ = return False
+
+-----------------------------------------------------------------------
+-- Checks if a S term is a value, i.e. cannot be further evaluated   --
+-----------------------------------------------------------------------
+isVal_S :: Fresh m => Term_S -> m Bool
+isVal_S Triv_S = return True
+isVal_S (Var_S x) = return True
+isVal_S (Tens_S s1 s2) = do
+  s1' <- isVal_S s1
+  case s1' of
+    True  -> isVal_S s2
+    False -> return False
+isVal_S (LamL_S ty b) = do
+  (x, s) <- unbind b
+  isVal_S s
+isVal_S (LamR_S ty b) = do
+  (x, s) <- unbind b
[…]

### 2017-07-22 Elle-ND/implementation/Parser.hs

@@ -50,17 +50,28 @@ tyUnit_T = do
   reservedOp "Unit"
   return Unit_T
 
+tyUnit_S = do
+  reservedOp "Unit"
+  return Unit_S
+
 ------------------------------------------------------------------------
 -- Type parser tables                                                 --
 ------------------------------------------------------------------------
-tyTable_T = [[binOp AssocLeft "(x)" (\d r -> Tensor_T d r)],
-           [binOp AssocRight "-o" (\d r -> Imp_T d r)]]
-binOp assoc op f = Text.Parsec.Expr.Infix (do{ reservedOp op; return f}) assoc
+tyTable_T = [[binOp_T AssocLeft "(x)" (\d r -> Tensor_T d r)],
+           [binOp_T AssocRight "-o" (\d r -> Imp_T d r)]]
+binOp_T assoc op f = Text.Parsec.Expr.Infix (do{ reservedOp op; return f}) assoc
 typeParser_T = buildExpressionParser tyTable_T typeParser'_T
 typeParser'_T = parens typeParser_T <|> tyUnit_T
 
+tyTable_S = [[binOp_S AssocLeft "(x)" (\d r -> Tensor_S d r)],
+           [binOp_S AssocRight "->" (\d r -> ImpL_S d r)],
+           [binOp_S AssocRight "<-" (\d r -> ImpR_S d r)]]
+binOp_S assoc op f = Text.Parsec.Expr.Infix (do{ reservedOp op; return f}) assoc
+typeParser_S = buildExpressionParser tyTable_S typeParser'_S
+typeParser'_S = parens typeParser_S <|> tyUnit_S
+
 ------------------------------------------------------------------------
--- Term parsers                                                       --
+-- Term_T parsers                                                     --
 ------------------------------------------------------------------------
 aterm_T = parens termParser_T <|> trivParse_T <|> var_T
 termParser_T = lamParse_T <|> try letTParse_T <|> letUParse_T <|> tensParse_T <|> appParse_T <?> "Parser error"
@@ -129,7 +140,104 @@ letTParse_T = do
   return $ LetT_T t1 (Tensor_T ty1 ty2) (bind x (bind y t2))
 
 ------------------------------------------------------------------------
--- Functions String -> Term or String -> Type                         --
+-- Term_S parsers                                                     --
[…]

### 2017-07-22 Elle-ND/implementation/Syntax.hs

@@ -58,10 +58,6 @@ data Term_T = Triv_T
           -- LetT_T t1 (X * Y) (Bind x (Bind y t2))
           -- let t1 : X * Y be x * y in t2
           | LetT_T Term_T Type_T (Bind TmName_T (Bind TmName_T Term_T))
-          -- LetG_T t (Gt_T ty) (Bind x s)
-          -- let t : (Gt_T ty) be x in s
-          -- ?
-          | LetG_T Term_T Type_T (Bind TmName_T Term_T)
           | Tens_T Term_T Term_T
           | Lam_T Type_T (Bind TmName_T Term_T)
           | App_T Term_T Term_T
@@ -73,17 +69,22 @@ type TmName_S = Name Term_S
 data Term_S = Triv_S
             | Var_S TmName_S
             | LetU_S Term_S Term_S
+            -- LetT_S s ty (Bind x (Bind y s'))
+            -- let (x*y) : ty be s in s'
             | LetT_S Term_S Type_S (Bind TmName_S (Bind TmName_S Term_S))
-            -- ?
+            -- LetF_S s (Fty_S ty) (Bind x s')
+            -- let F x : F ty be s in s'
             | LetF_S Term_S Type_S (Bind TmName_S Term_S)
+            -- LetG_T t (Gty_T ty) (Bind x s)
+            -- let G x : G ty be s in s'
+            | LetG_S Term_T Type_T (Bind TmName_S Term_S)
             | Tens_S Term_S Term_S
             | LamL_S Type_S (Bind TmName_S Term_S)
             | LamR_S Type_S (Bind TmName_S Term_S)
             | AppL_S Term_S Term_S
             | AppR_S Term_S Term_S
-            | Ex_S Term_S Term_S (Bind TmName_S (Bind TmName_S Term_S))
+            | Ex_S Term_T Term_T (Bind TmName_S (Bind TmName_S Term_S))
             | Ft_S Term_T
-            | Derelict_S Term_T     -- Term_T must be Gt_T Term_S
             deriving (Show)
 
 

### 2017-07-22 Elle-ND/implementation/Testing.hs

@@ -9,6 +9,7 @@ import Pretty
 ------------------------------------------------------------------------
 
 lamtest0_T = parseTester_T lamParse_T "\\(x:Unit).y"
+lamtest0_S = parseTester_T lamParse_T "\\l(x:Unit).y"
 
 lamtest1_T = parseTester_T lamParse_T "\\(x:Unit (x) Unit).y"
 

### 2017-07-22 Elle-ND/implementation/TypeCheck.hs

@@ -11,9 +11,10 @@ import Control.Monad.Except
 import Data.List
 
 import Syntax
+import Parser
 
 -----------------------------------------------------------------------
--- Typing contexts                                                   --
+-- (T) Typing contexts                                               --
 -----------------------------------------------------------------------
 type Ctx_T = [(TmName_T, Type_T)]
 
@@ -21,28 +22,51 @@ emptyCtx_T :: Ctx_T
 emptyCtx_T = []
 
 extCtx_T :: Ctx_T -> TmName_T -> Type_T -> Ctx_T
-extCtx_T ctx nm ty = (nm, ty) : ctx
+extCtx_T ctx x ty = (x, ty) : ctx
 
 infixr 5 |:|
 (|:|) :: (TmName_T, Type_T) -> Ctx_T -> Ctx_T
 (x,t) |:| ctx = extCtx_T ctx x t
 
-
-
+-----------------------------------------------------------------------
+-- (S) Typing contexts                                               --
+-----------------------------------------------------------------------
 type Ctx_S = [(TmName_S, Type_S)]
 
 emptyCtx_S :: Ctx_S
 emptyCtx_S = []
 
 extCtx_S :: Ctx_S -> TmName_S -> Type_S -> Ctx_S
-extCtx_S ctx nm ty = (nm, ty) : ctx
+extCtx_S ctx x ty = (x, ty) : ctx
 
 infixr 5 |::|
 (|::|) :: (TmName_S, Type_S) -> Ctx_S -> Ctx_S
 (x,t) |::| ctx = extCtx_S ctx x t
 
 -----------------------------------------------------------------------
--- Free Variable Collection                                          --
+-- Typing contexts                                               --
+-----------------------------------------------------------------------
+type Ctx = (Ctx_T, Ctx_S)
+
+emptyCtx :: Ctx
+emptyCtx = ([], [])
+
+extCtx1 :: Ctx -> TmName_T -> Type_T -> Ctx
+extCtx1 (ctxT, ctxS) x ty = ((x, ty) : ctxT, ctxS)
+
+infix 5 |+|
+(|+|) :: (TmName_T, Type_T) -> Ctx -> Ctx
+(x, t) |+| ctx = extCtx1 ctx x t
+
+extCtx2 :: Ctx -> TmName_S -> Type_S -> Ctx
[…]

### 2017-07-27 natural-deduction.tex
Implementation of the T terms
Type checking, reduction, and parser
Some work on the results

@@
+The term assignment for natural deduction of the non-commutative part of the model, i.e. the
+SMCC of the adjunction, is defined in Figure~\ref{fig:elle-nd-smcc}. And the term assignme for
+the commutative part, i.e. the Lambek category of the adjunction, is defined in
+Figure~\ref{fig:elle-nd-lambek}. $[[P]]$ and $[[I]]$ are contexts for the non-commutative part
+and they are lists. $[[G]]$ and $[[D]]$ are contexts for the commutative part and they are
+multisets, therefore the following exchange rules are implicit.
+\scriptsize
+\begin{mathpar}
+  \ottdruleTXXbeta{} \qquad\qquad \ottdruleSXXbeta{}
+\end{mathpar}
+
+\begin{figure}
+ \scriptsize
+  \begin{mdframed}
+    \begin{mathpar}
+      \ottdruleTXXidentity{} \qquad\qquad \ottdruleTXXunitI{} \qquad\qquad \ottdruleTXXunitE{} \\
+      \ottdruleTXXtenI{} \qquad\qquad \ottdruleTXXtenE{} \\
+      \ottdruleTXXimpI{} \qquad\qquad \ottdruleTXXimpE{} \qquad\qquad \ottdruleTXXGI{}
+    \end{mathpar}
+  \end{mdframed}
+\caption{Commutative Part}
+\label{fig:elle-nd-smcc}
+\end{figure}
+
+\begin{figure}
+ \scriptsize
+  \begin{mdframed}
+    \begin{mathpar}
+      \ottdruleSXXidentity{} \qquad\qquad \ottdruleSXXunitI{} \qquad\qquad \ottdruleSXXunitE{} \\
+      \ottdruleSXXtenI{} \qquad\qquad \ottdruleSXXtenEOne{} \\
+      \ottdruleSXXtenETwo{} \qquad\qquad \ottdruleSXXimplI{} \\
+      \ottdruleSXXimplE{} \qquad\qquad \ottdruleSXXimprI{} \\
+      \ottdruleSXXimprE{} \qquad\qquad \ottdruleSXXFI{} \\
+      \ottdruleSXXFE{} \qquad\qquad \ottdruleSXXGE{}
+    \end{mathpar}
+  \end{mdframed}
+\caption{Non-Commutative Part}
+\label{fig:elle-nd-lambek}
+\end{figure}
+
+\begin{center}
+  \tiny
+  \begin{math}
+    $$\mprset{flushleft}
+    \inferrule* [right={\tiny impR}] {
+      $$\mprset{flushleft}
+    \inferrule* [right={\tiny tenL}] {
+      $$\mprset{flushleft}
+    \inferrule* [right={\tiny Fl}] {
+      $$\mprset{flushleft}
+      \inferrule* [right={\tiny FI}] {
+        $$\mprset{flushleft}
+        \inferrule* [right={\tiny beta}] {
+          $$\mprset{flushleft}
+          \inferrule* [right={\tiny tenI}] {
+            $$\mprset{flushleft}
+            \inferrule* [right={\tiny FI}] {
+              $$\mprset{flushleft}
+              \inferrule* [right={\tiny identity}] {
+                \,
+              }{[[y0 : Gf B |- y0 : Gf B]]}
+            }{[[y0 : Gf B; . |- F y0 : F Gf B]]}
+            \\
+            $$\mprset{flushleft}
+            \inferrule* [right={\tiny FI}] {
+              $$\mprset{flushleft}
+              \inferrule* [right={\tiny identity}] {
+                \,
+              }{[[x0 : Gf A |- x0 : Gf A]]}
+            }{[[x0 : Gf A; . |- F x0 : F Gf A]]}
+          }{[[y0 : Gf B, x0 : Gf A ; . |- h(F y0) (>) F x0 : h(F Gf B) (>) F Gf A]]}
+        }{[[x1 : Gf A, y1 : Gf B ; . |- ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0) : h(F Gf B) (>) F Gf A]]}
+      }{[[x1 : Gf A ; y2 : F Gf B |- let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)) : h(F Gf B) (x) F Gf A]]}
+    }{[[. ; x2 : F Gf A, y2 : F Gf B |- let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0))) : h(F Gf B) (x) F Gf A]]}
+    }{[[.
+; z : h(F Gf A) (x) F Gf B |- let z : h(F Gf A) (x) F Gf B be x2 (x) y2 in (let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)))) : (h(F Gf B) (x) F Gf A)]]}
+    }{[[.
+; .
+|- \l z : h(F Gf A) (x) F Gf B .
+let z : h(F Gf A) (x) F Gf B be x2 (x) y2 in (let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)))) : (h(F Gf A) (x) F Gf B) -> (h(F Gf B) (x) F Gf A)]]}
+  \end{math}
+\end{center}
+
 \subsection{Categorical Interpretation of Natural Deductions}

### 2017-08-01 adjoint-model.tex
Partial proof for Eilenberg-Moore of the comonad being symmetric

Our adjoint model, SMCC-Lambek model, has a similar structure as Benton's LNL model \cite{}.
Benton's LNL model consists of a symmetric monoidal adjunction $F:\cat{C}\dashv\cat{L}:G$
between a cartesian closed category $\cat{C}$ and a symmetric monoidal closed category
$\cat{L}$.

\begin{definition}
  A \textbf{SMCC-Lambek model} consists of
  \begin{itemize}
  \item a symmetric monoidal closed category $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$;
  \item a Lambek category $(\cat{L},\tri,I',\alpha',\lambda',\rho')$;
  \item a monoidal adjunction $F:\cat{C}\dashv\cat{L}:G$, where $F:\cat{C}\rightarrow\cat{L}$
        and $G:\cat{L}\rightarrow\cat{C}$ are monoidal functors.
  \end{itemize}
\end{definition}

Thus, in a SMCC-Lambek model, the following four diagrams commute because $\eta$ and
$\varepsilon$ are monoidal natural transformations:
\begin{mathpar}
\bfig
  \square/=`->`->`/<1600,400>[
    X\otimes Y`X\otimes Y`GFX\otimes GFY`GF(X\otimes Y);
    id_{X\otimes Y}`\eta_X\otimes\eta_Y`\eta_{X\otimes Y}`]
  \morphism<800,0>[GFX\otimes GFY`G(FX\otimes FY);\n{FX,FY}]
  \morphism(800,0)<800,0>[G(FX\otimes FY)`GF(X\otimes Y);G\m{X,Y}]
\efig
\and
\bfig
  \square/->`=`<-`->/<400,400>[I`GFI`I`GI';\eta_I``G\m{I}`\n{I'}]
\efig
\end{mathpar}
\begin{mathpar}
\bfig
  \square/`->`->`=/<1600,400>[
    FGA\otimes FGB`FG(A\otimes B)`A\otimes B`A\otimes B;
    `
    \varepsilon_A\otimes\varepsilon_B`\varepsilon_{A\otimes B}`]
  \morphism(0,400)<800,0>[FGA\otimes FGB`F(GA\otimes GB);\m{GA,GB}]
  \morphism(800,400)<800,0>[F(GA\otimes GB)`FG(A\otimes B);F\n{A,B}]
\efig
\and
\bfig
  \square/->`<-`=`<-/<400,400>[FGI'`I'`FI`I';\varepsilon_{I'}`F\n{I'}``\m{I}]
\efig
\end{mathpar}
And the following two diagrams commute because of the adjunction:
\begin{mathpar}
\bfig
  \Vtriangle/->`=`->/<400,400>[FX`FGFX`FX;F\eta_X``\varepsilon_{FX}]
\efig
\and
\bfig
  \Vtriangle/->`=`->/<400,400>[GA`GFGA`GA;\eta_{GA}``G\varepsilon_A]
\efig
\end{mathpar}
Following the tradition, we use letters $X$, $Y$, $Z$ for objects in $\cat{C}$ and $A$, $B$, $C$
for objects in $\cat{L}$. The following lemmas and theorems establish the essential properties
of the monad and the comomad derived from the adjunction.

\begin{lemma}
  \label{lem:monoidal-monad}
  The monad on the symmetric monoidal closed category $\cat{C}$ in a SMCC-Lambek model is
  monoidal.
\end{lemma}
\begin{proof}
  We define the monad $T$ on the $\cat{C}$ in the adjunction of a SMCC-Lambek model as $T=GF$,
  and the two corresponding natural transformations $\eta:id_\cat{C}\rightarrow T$ and
  $\mu:T^2\rightarrow T$ as
  $$\eta_X:X\rightarrow GFX \qquad\qquad\qquad \mu_X=G\varepsilon_{FX}:GFGFX\rightarrow GFX$$
  where $\eta$ is the unit and $\varepsilon:FG\rightarrow id_\cat{L}$ is the counit of the
  adjunction $F:\cat{C}\dashv\cat{L}:G$. Since the adjunction is monoidal, then $(F,\m{})$ and
  $(G,\n{})$ are monoidal functors. Thus, we have
  $$\t{X,Y}=G\m{X,Y}\circ\n{FX,FY}:TX\otimes TY\rightarrow T(X\otimes Y)
  \qquad\qquad\qquad\t{I}=G\m{I}\circ\n{I'}:I\rightarrow TI$$
  The monad $T$ being monoidal means
  \begin{enumerate}
  \item $T$ is a monoidal functor, i.e. the folllowing diagrams commute:
        \begin{mathpar}
        \bfig
          \hSquares/->`->`->``->`->`->/<400>[
            (TX\otimes TY)\otimes TZ`TX\otimes(TY\otimes TZ)`TX\otimes T(Y\otimes Z)`
            T(X\otimes Y)\otimes TZ`T((X\otimes Y)\otimes Z)`T(X\otimes(Y\otimes Z));
            \alpha_{TX,TY,TZ}`id_{TX}\otimes\t{Y,Z}`\t{X,Y}\otimes id_{TZ}``
            \t{X,Y\otimes Z}`\t{X\otimes Y,Z}`T\alpha_{X,Y,Z}]
          \morphism(1300,200)//<0,0>[`;(1)]
        \efig
        \and
        \bfig
          \square/->`->`<-`->/<600,400>[
            I\otimes TX`TX`TI\otimes TX`T(I\otimes X);
            \lambda_{TX}`\t{I}\otimes id_{TX}`T\lambda_X`\t{I,X}]
          \morphism(350,200)//<0,0>[`;(2)]
        \efig
        \and
        \bfig
          \square/->`->`<-`->/<600,400>[
            TX\otimes I`TX`TX\otimes TI`T(X\otimes I);
            \rho_{TX}`id_{TX}\otimes\t{I}`T\rho_X`\t{X,I}]
          \morphism(350,200)//<0,0>[`;(3)]
        \efig
        \end{mathpar}
        We write $GF$ instead of $T$ in the proof for clarity. \\
        By replacing $\t{X,Y}$ with its definition, diagram (1) above commutes by the following
        commutative diagram, in which the two hexagons commute because $G$ and $F$ are monoidal
        functors, and the two quadrilaterals commute by the naturality of $\n{}$.
        \begin{mathpar}
        \bfig
          \iiixiii/->`->`->``->```->`<-`->``/<1400,400>[
            (GFX\otimes GFY)\otimes GFZ`GFX\otimes(GFY\otimes GFZ)`GFX\otimes G(FY\tri FZ)`
            G(FX\tri FY)\otimes GFZ`G(FX\tri(FY\tri FZ))`GFX\otimes GF(Y\otimes Z)`
            GF(X\otimes Y)\otimes GFZ`G((FX\tri FY)\tri FZ)`G(FX\tri F(Y\otimes Z));
            \alpha_{GFX,GFY,GFZ}`id_{GFX}\otimes\n{FY,FZ}`\n{FX,FY}\otimes id_{GFZ}``
            id_{GFX}\otimes G\m{Y,Z}```G\m{X,Y}\otimes id_{GFZ}`G\alpha'_{FX,FY,FZ}`
            \n{FX,F(Y\otimes Z)}``]
          \morphism(2800,800)|m|<-1400,-400>[
            GFX\otimes G(FY\tri FZ)`G(FX\tri(FY\tri FZ));\n{FX,FY\tri FZ}]
          \morphism(0,400)|m|<1400,-400>[
            G(FX\tri FY)\otimes GFZ`G((FX\tri FY)\tri FZ);\n{FX\tri FY,FZ}]
          \morphism(1400,400)|m|<1400,-400>[
            G(FX\tri(FY\tri FZ))`G(FX\tri F(Y\otimes Z));G(id_{FX}\tri\m{Y,Z})]
          \ptriangle(0,-400)|mlm|/`->`->/<1400,400>[
            GF(X\otimes Y)\otimes GFZ`G((FX\tri FY)\tri FZ)`G(F(X\otimes Y)\tri FZ);
            `\n{F(X\otimes Y),FZ}`G(\m{X,Y}\otimes id_{FZ})]
          \morphism(0,-400)|b|<1400,0>[
            G(F(X\otimes Y)\tri FZ)`GF((X\otimes Y)\otimes Z);G\m{X\otimes Y,Z}]
          \dtriangle(1400,-400)|mrb|/`->`->/<1400,400>[
            G(FX\tri F(Y\otimes Z))`GF((X\otimes Y)\otimes Z)`GF(X\otimes(Y\otimes Z));
            `G\m{X,Y\otimes Z}`GF\alpha_{X,Y,Z}]
        \efig
        \end{mathpar}
        Diagram (2) commutes by the following commutative diagrams, in which the top
        quadrilateral commutes because $G$ is monoidal, the right quadrilateral commutes because
        $F$ is monoidal, and the left square commutes by the naturality of $\n{}$.
        \begin{mathpar}
        \bfig
          \ptriangle/->`->`/<1600,400>[
            I\otimes GFX`GFX`GI'\otimes GFX;\lambda_{GFX}`\n{I'}\otimes id_{GFX}`]
          \square(0,-400)|lmmb|<800,400>[
            GI'\otimes GFX`G(I'\tri FX)`GFI\otimes GFX`G(FI\tri FX);
            \n{I',FX}`G\m{I}\otimes id_{GFX}`G(\m{I}\tri id_{FX})`\n{FI,FX}]
          \morphism(800,0)|m|<800,400>[G(I'\tri FX)`GFX;G\lambda'_{FX}]
          \dtriangle(800,-400)/`<-`->/<800,800>[
            GFX`G(FI\tri FX)`GF(I\otimes X);
            `GF\lambda_X`G\m{I,X}]
        \efig
        \end{mathpar}
        Similarly, diagram (3) commutes as follows:
        \begin{mathpar}
        \bfig
          \ptriangle/->`->`/<1600,400>[
            GFX\otimes I`GFX`GFX\otimes GI';\rho_{GFX}`id_{GFX}\otimes\n{I'}`]
          \square(0,-400)|lmmb|<800,400>[
            GFX\otimes GI'`G(FX\tri I')`GFX\otimes GFI`G(FX\tri FI);
            \n{FX,I'}`id_{GFX}\otimes G\m{I}`G(id_{FX}\otimes\m{I})`\n{FX,FI}]
          \morphism(800,0)|m|<800,400>[G(FX\tri I')`GFX;G\rho'_{FX}]
          \dtriangle(800,-400)/`<-`->/<800,800>[
            GFX`G(FX\tri FI)`GF(X\otimes I);
            `GF\rho_X`G\m{X,I}]
        \efig
        \end{mathpar}
  \item $\eta$ is a monoidal natural transformation. In fact, since $\eta$ is the unit of the
        monoidal adjunction, $\eta$ is monoidal by definition and thus the following two
        diagrams commute.
        \begin{mathpar}
        \bfig
          \square/=`->`->`->/<600,400>[
            X\otimes Y`X\otimes Y`TX\otimes TY`T(X\otimes Y);
            `\eta_X\otimes\eta_Y`\eta_{X\otimes Y}`\t{X,Y}]
        \efig
        \and
        \bfig
          \Vtriangle/->`=`<-/<400,400>[I`TI`I;\eta_I``\t{I}]
        \efig
        \end{mathpar}
  \item $\mu$ is a monoidal natural transformation. It is obvious that since
        $\mu=G\varepsilon_{FA}$ and $\varepsilon$ is monoidal, so is $\mu$. Thus the following
        diagrams commute.
        \begin{mathpar}
        \bfig
          \square/`->`->`->/<1500,400>[
            T^2X\otimes T^2Y`T^2(X\otimes Y)`TX\otimes TY`T(X\otimes Y);
            `\mu_X\otimes\mu_Y`\mu_{X\otimes Y}`\t{X,Y}]
          \morphism(0,400)<800,0>[T^2X\otimes T^2Y`T(TX\otimes TY);\t{TX,TY}]
          \morphism(800,400)<700,0>[T(TX\otimes TY)`T^2(X\otimes Y);T\t{X,Y}]
        \efig
        \and
        \bfig
          \square/->`<-`<-`<-/<400,400>[T^2I`TI`TI`I;\mu_I`T\t{I}`\t{I}`\t{I}]
        \efig
        \end{mathpar}
  \end{enumerate}
\end{proof}

However, the monad is not symmetric becauase the following diagram does not commute, for the
lambek category $\cat{L}$ is not symmetric.
\begin{mathpar}
\bfig
  \ptriangle/->`->`/<900,400>[
    GFX\otimes GFY`GFY\otimes GFX`G(FX\tri FY);\e{GFX,GFY}`\n{FX,FY}`]
  \morphism(900,400)<900,0>[GFY\otimes GFX`G(FY\tri FX);\n{FY,FX}]
  \dtriangle(900,0)/`->`->/<900,400>[
    G(FY\tri FX)`GF(X\otimes Y)`GF(Y\otimes X);`G\m{Y,X}`GF\e{X,Y}]
  \morphism|b|<900,0>[G(FX\tri FY)`GF(X\otimes Y);G\m{X,Y}]
\efig
\end{mathpar}

\begin{lemma}
  \label{lem:strong-monad}
  The monad on the symmetric monoidal closed category in a SMCC-Lambek model is strong.
\end{lemma}
\begin{proof}
  Let $F:\cat{C}\vdash\cat{L}:G$ be a SMCC-Lambek model, where
  $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$ is symmetric monoidal closed,
  $(\cat{L},\tri,I',\alpha',\lambda',\rho')$ is a Lambek category, and $(F,\m{})$ and
  $(G,\n{})$ are monoidal functors. We have proved that the monad $(T=GF,\eta,\mu)$ is monoidal
  with the natural transformation $\t{X,Y}:TX\otimes TY\rightarrow T(X\otimes Y)$ and the
  morphism $\t{I}:I\rightarrow TI$ defined as in Lemma~\ref{lem:monoidal-monad}. \\
  We define the tensorial strength $\tau_{X,Y}:X\otimes TY\rightarrow T(X\otimes Y)$ as
  $\tau_{X,Y}=\t{X,Y}\circ(\eta_X\otimes id_{TY})$. \\
  Since $\eta$ is a monoidal natural transformation, we have $\eta_I=G\m{I}\circ\n{I'}$.
  Therefore $\eta_I=\t{I}$. Thus the following diagram commutes because $T$ is monoidal,
  where the composition $\t{I,X}\circ(\t{I}\otimes id_{TX})$ is the definition of $\tau_{I,X}$.
  So the first triangle in Defition~\ref{def:strong-monad} commutes.
  \begin{mathpar}
  \bfig
    \square/->`->`->`<-/<600,400>[
      I\otimes TX`TI\otimes TX`TX`T(I\otimes X);
      \t{I}\otimes id_{TX}`\lambda_{TX}`\t{I,X}`T\lambda_X]
  \efig
  \end{mathpar}
  Similarly, by using the definition of $\tau$, the the second triangle in the definition is
  equivalent to the following diagram, which commutes because $\eta$ is a monoidal natural
  transformation:
  \begin{mathpar}
  \bfig
    \square/->`->`->`<-/<600,400>[
      X\otimes Y`X\otimes TY`T(X\otimes Y)`TX\otimes TY;
      id_X\otimes\eta_Y`\eta_{X\otimes Y}`\eta_X\otimes id_{TY}`\t{X,Y}]
    \morphism(0,400)|m|<600,-400>[X\otimes Y`TX\otimes TY;\eta_X\otimes\eta_Y]
  \efig
  \end{mathpar}
  The first pentagon in the definition commutes by the following commutative diagrams, because
  $\eta$ are $\alpha$ natural transformations and $T$ is monoidal:
  \begin{mathpar}
  \bfig
    \qtriangle|amm|/->`->`<-/<1000,400>[
      (X\otimes Y)\otimes TZ`T(X\otimes Y)\otimes TZ`(TX\otimes TY)\otimes TZ;
      \eta_{X\otimes Y}\otimes id_{TZ}`
      (\eta_X\otimes\eta_Y)\otimes id_{TZ}`
      \t{X,Y}\otimes id_{TZ}]
    \morphism(0,400)<0,-400>[(X\otimes Y)\otimes TZ`X\otimes(Y\otimes TZ);\alpha_{X,Y,TZ}]
    \morphism(1000,0)|m|<0,-400>[
      (TX\otimes TY)\otimes TZ`TX\otimes(TY\otimes TZ);\alpha_{TX,TY,TZ}]
    \Dtriangle(0,-800)|lmm|/->`->`<-/<1000,400>[
      X\otimes(Y\otimes TZ)`TX\otimes(TY\otimes TZ)`X\otimes(TY\otimes TZ);
      id_X\otimes(\eta_Y\otimes id_{TZ})`
      \eta_X\otimes(\eta_Y\otimes id_{TZ})`
      \eta_X\otimes id_{TY\otimes TZ}]
    \morphism(0,-800)|b|<1000,0>[
      X\otimes(TY\otimes TZ)`X\otimes T(Y\otimes Z);id_X\otimes\t{Y,Z}]
    \qtriangle(1000,0)|amr|/->``->/<1000,400>[
      T(X\otimes Y)\otimes TZ`T((X\otimes Y)\otimes Z)`T(X\otimes(Y\otimes Z));
      \t{X\otimes Y,Z}``T\alpha_{X,Y,Z}]
    \morphism(2000,-800)<0,800>[
      TX\otimes T(Y\otimes Z)`T(X\otimes(Y\otimes Z));\t{X,Y\otimes Z}]
    \btriangle(1000,-800)|mmb|/`->`->/<1000,400>[
      TX\otimes(TY\otimes TZ)`X\otimes T(Y\otimes Z)`TX\otimes T(Y\otimes Z);
      `id_{TX}\otimes\t{Y,Z}`\eta_X\otimes id_{T(Y\otimes Z)}]
  \efig
  \end{mathpar}
  The last diagram in the definition commtues by the following commutative diagram, because
  $T$ is a monad, $\t{}$ is a natural transformation, and $\mu$ is a monoidal natural
  transformation:
  \begin{mathpar}
  \bfig
    \ptriangle/->`->`/<700,400>[
      X\otimes T^2Y`TX\otimes T^2Y`X\otimes TY;\eta_X\otimes id_{T^2Y}`id_X\otimes\mu_Y`]
    \btriangle(0,-400)/->``->/<700,400>[
      X\otimes TY`TX\otimes TY`T(X\otimes Y);\eta_X\otimes id_{TY}``\t{X,Y}]
    \morphism(700,400)|m|<-700,-800>[TX\otimes T^2Y`TX\otimes TY;id_{TX}\otimes\mu_Y]
    \morphism(700,0)|m|<-700,-400>[TX\otimes T^2Y`TX\otimes TY;id_{TX}\otimes\mu_Y]
    \qtriangle(700,0)/->``->/<1800,400>[
      TX\otimes T^2Y`T(X\otimes TY)`T(TX\otimes TY);\t{X,TY}``T(\eta_X\otimes id_{TY})]
    \btriangle(700,0)|mmm|/=`->`<-/<900,400>[
      TX\otimes T^2Y`TX\otimes T^2Y`T^2X\otimes T^2Y;
      `T\eta_X\otimes id_{T^2Y}`\mu_X\otimes id_{T^2Y}]
    \morphism(1600,0)|m|<900,0>[T^2X\otimes T^2Y`T(TX\otimes TY);\t{TX,TY}]
    \morphism(1600,0)|m|<-1600,-400>[T^2X\otimes T^2Y`TX\otimes TY;\mu_X\otimes\mu_Y]
    \dtriangle(700,-400)/`->`<-/<1800,400>[
      T(TX\otimes TY)`T(X\otimes Y)`T^2(X\otimes Y);`T\t{X,Y}`\mu_{X\otimes Y}]
  \efig
  \end{mathpar}
\end{proof}

\begin{lemma}[\cite{kock1970monads}]
  Let $\cat{M}$ be a symmetric monoidal category and $T$ be a strong monad on $\cat{M}$. Then
  $T$ is symmetric iff it is commutative.
\end{lemma}

\begin{theorem}
  The monad on the SMCC in a SMCC-Lambek model is monoidal and non-commutative.
\end{theorem}

\begin{lemma}
  The comonad on the Lambek category in a SMCC-Lambek model is monoidal.
\end{lemma}
\begin{proof}
  We define the comonad $S$ on the Lambek category $\cat{L}$ in the adjunction
  $F:\cat{C}\vdash\cat{L}:G$ of a SMCC-Lambek model as $S=FG$. The two corresponding natural
  transformations $\varepsilon:S\rightarrow id_\cat{L}$ and $\delta:S\rightarrow S^2$ are
  defined as
  $$\varepsilon_A:SA\rightarrow A \qquad\qquad\qquad \delta_A=F\eta_{GA}:SA\rightarrow S^2A$$
  where $\varepsilon$ is the counit and $\eta:id_\cat{L}\rightarrow GF$ is the unit of the
  adjunction, and $(F,\m{})$ and $(G,\n{})$ are monoidal functors. Thus, we have
  $$\s{A,B}=F\n{A,B}\circ\m{GA,GB}:SA\tri SB\rightarrow SA\tri SB \qquad\qquad\qquad
  \s{I}=F\n{I'}\circ\m{I}:I'\rightarrow SI'$$
  The comonad $S$ being monoidal means
  \begin{enumerate}
  \item $S$ is a monoidal functor, i.e. the following diagrams commute:
        \begin{mathpar}
        \bfig
          \hSquares/->`->`->``->`->`->/<400>[
            (SA\tri SB)\tri SC`SA\tri(SB\tri SC)`SA\tri S(B\tri C)`
            S(A\tri B)\tri SC`S((A\tri B)\tri C)`S(A\tri(B\tri C));
            \alpha_{SA,SB,SC}'`id_{SA}\tri\s{B,C}`\s{A,B}\tri id_{SC}``
            \s{A,B\tri C}`\s{A\tri B,C}`S\alpha_{A,B,C}']
        \efig
        \and
        \bfig
          \square/->`->`<-`->/<600,400>[
            I'\tri SA`SA`SI'\tri SA`S(I'\tri A);
            \lambda_{SA}'`\s{I'}\tri id_{SA}`S\lambda_A'`\s{I',A}]
        \efig
        \and
        \bfig
          \square/->`->`<-`->/<600,400>[
            SA\tri I'`SA`SA\tri SI'`S(A\tri I');
            \rho_{SA}'`id_{SA}'\tri\s{I'}`S\rho_A'`\s{A,I'}]
        \efig
        \end{mathpar}
  \item $\varepsilon$ is a monoidal natural transformation:
        \begin{mathpar}
        \bfig
          \square/->`->`->`=/<600,400>[
            SA\tri SB`S(A\tri B)`A\tri B`A\tri B;
            \s{A,B}`\varepsilon_A\tri\varepsilon_B`\varepsilon_{A\tri B}`]
        \efig
        \and
        \bfig
          \Vtriangle/->`<-`=/<400,400>[SI'`I'`I';\varepsilon_{I'}`\s{I'}`]
        \efig
        \end{mathpar}
  \item $\delta$ is a monoidal natural transformation:
        \begin{mathpar}
        \bfig
          \square/->`->`->`/<1500,400>[
            SA\tri SA`S(A\tri B)`S^2A\tri S^2B`S^2(A\tri B);
            \s{A,B}`\delta_A\tri\delta_B`\delta_{A\tri B}`]
          \morphism<800,0>[S^2A\tri S^2B`S(SA\tri SB);\s{SA,SB}]
          \morphism(800,0)<700,0>[S(SA\tri SB)`S^2(A\tri B);S\s{A,B}]
        \efig
        \and
        \bfig
          \square/->`<-`<-`->/<400,400>[
            SI'`S^2I'`I'`SI';\delta_{I'}`\s{I'}`S\s{I'}`\s{I'}]
        \efig
        \end{mathpar}
  \end{enumerate}
  The proof for the commutativity of the diagrams are similar as the proof in
  Lemma~\ref{lem:monoidal-monad}. We do not include the proof here for simplicity.
\end{proof}

The comonad $S$ on the Lambek category $\cat{L}$ of the adjunction is clearly not symmetric
because $\cat{L}$ is not. However, it is symmetric on the co-Eilenberg-Moore category of the
comonad.

\begin{definition}
  Let $(S,\varepsilon,\delta)$ be a comonad on a category $\cat{L}$. Then the
  \textbf{co-Eilenberg-Moore category $\cat{L}^S$} of the comonad has
  \begin{itemize}
  \item as objects the S-coalgebras $(A,h_A:A\rightarrow SA)$, where $A$ is an object in
        $\cat{L}$, s.t. the following diagrams commute:
        \begin{mathpar}
        \bfig
          \square<400,400>[A`SA`SA`S^2A;h_A`h_A`\delta_A`Sh_A]
        \efig
        \and
        \bfig
          \Atriangle/<-`->`=/<200,400>[SA`A`A;h_A`\varepsilon_A`]
        \efig
        \end{mathpar}
  \item as morphisms the coalgebra morphisms, i.e. morphisms $f:(A,h_A)\rightarrow(B,h_B)$
        between coalgebras s.t. the diagram commutes:
        $$\bfig
          \square<400,400>[A`B`SA`SB;f`h_A`h_B`Sf]
        \efig$$
  \end{itemize}
\end{definition}

\begin{lemma}
  \label{lem:em-exchange}
  Given a SMCC-Lambek model $F:\cat{C}\dashv\cat{L}:G$ and the comonad $S$ on $\cat{L}$, the
  co-Eilenberg-Moore category $\cat{L}^S$ of has an exchange natural transformation
  $\e{A,B}^S:A\tri B\rightarrow B\tri A$.
\end{lemma}
\begin{proof}
  We define the exchange $\e{A,B}^S:A\tri B\rightarrow B\tri A$ as
  $$\bfig
    \morphism<600,0>[A\tri B`FGA\tri FGB;h_A\tri h_B]
    \morphism(600,0)<800,0>[FGA\tri FGB`F(GA\otimes GB);\m{GA,GB}]
    \morphism(1400,0)<800,0>[F(GA\otimes GB)`F(GB\otimes GA);F\e{GA,GB}]
    \morphism(2200,0)<700,0>[F(GB\otimes GA)`FG(B\tri A);F\n{B,A}]
    \morphism(2900,0)<500,0>[FG(B\tri A)`B\tri A;\varepsilon_{B\tri A}]
  \efig$$
  in which $(F,\m{})$ and $(G,\n{})$ are monoidal functors, and $\e{}$ is the exchange for
  $\cat{C}$. $\e{}^S$ is a natural transformation because the following diagrams commute for
  morphisms $f:A\rightarrow A'$ and $g:B\rightarrow B'$:
  \begin{mathpar}
  \bfig
    \square|almb|<700,400>[
      A\tri B`FGA\tri FGB`A'\tri B'`FGA'\tri FGB';
      h_A\tri h_B`f\tri g`FGf\tri FGg`h_{A'}\tri h_{B'}]
    \square(700,0)|ammb|/->``->`->/<800,400>[
      FGA\tri FGB`F(GA\otimes GB)`FGA'\tri FGB'`F(GA'\otimes GB');
      \m{GA,GB}``F(Gf\otimes Gg)`\m{GA',GB'}]
    \square(1500,0)|ammb|/->``->`->/<800,400>[
      F(GA\otimes GB)`F(GB\otimes GA)`F(GA'\otimes GB')`F(GB'\otimes GA');
      F\e{A,B}``F(Gg\otimes Gf)`F\e{A',B'}]
    \square(2300,0)|ammb|/->``->`->/<800,400>[
      F(GB\otimes GA)`FG(B\tri A)`F(GB'\otimes GA')`FG(B'\tri A');
      F\n{B,A}``FG(g\tri f)`F\n{B',A'}]
    \square(3100,0)|amrb|/->``->`->/<600,400>[
      FG(B\tri A)`B\tri A`FG(B'\tri A')`B'\tri A';
      \varepsilon_{B\tri A}``g\tri f`\varepsilon_{B'\tri A'}]
  \efig
  \end{mathpar}
\end{proof}

\begin{lemma}
  The following diagrams commute in the co-Eilenberg-Moore category $\cat{L}^S$:
  \begin{mathpar}
  \bfig
    \iiixiii/->`->`->``->```->``->`->`->/<1300,400>[
      F((GA\otimes GB)\otimes GC)`F(G(A\tri B)\otimes GC)`FG((A\tri B)\tri C)`
      F(G(B\tri A)\otimes GC)``(A\tri B)\tri C`
      F(G(B\tri A)\otimes GC)`FG((B\tri A)\tri C)`(B\tri A)\tri C;
      F(\n{A,B}\otimes id_{GC})`F(\e{A,B}\otimes id_{GC})`
      F(\e{A,B}\otimes id_{GC})``\varepsilon_{(A\tri B)\tri C}```
      F(\n{B,A}\otimes id_{GC})``\e{A,B}^S\tri id_C`
      F\n{B\tri A,C}`\varepsilon_{(B\tri A)\tri C}]
  \efig
  \end{mathpar}
  \begin{mathpar}
  \bfig
    \iiixiii/->`->`->``->```->``->`->`->/<1300,400>[
      F(GB\otimes(GC\otimes GA))`F(GB\otimes G(C\tri A))`FG(B\tri(C\tri A))`
      F(GB\otimes(GA\otimes GC))``B\tri(C\tri A)`
      F(GB\otimes G(A\tri C))`FG(B\tri(A\tri C))`B\tri(A\tri C);
      F(id_{GB}\otimes\n{C,A})`F\n{B,C\tri A}`
      F(id_{GB}\otimes\e{C,A})``\varepsilon_{B\tri(C\tri A)}```
      F(id_{GB}\otimes\n{A,C})``id_A\tri\e{C,A}^S`
      F\n{B,A\tri C}`\varepsilon_{B\tri(A\tri C)}]
  \efig
  \end{mathpar}
\end{lemma}
\begin{proof}
  We only write the proof for the first diagram. The proof for the second one is similar.
  (1), (2), (3)--naturality of $\m{}$; (4)--F is monoidal; (5), (12)--$\varepsilon$ is monoidal;
  (6), (7), (8), (9), (10)--obvious; (11)--coalgebra.
  \begin{mathpar}
  \bfig
    \Vtrianglepair|aammm|/->`->`<-``<-/<1000,400>[
      F(G(A\tri B)\otimes GC)`FG((A\tri B)\tri C)`(A\tri B)\tri C`FG(A\tri B)\tri FGC;
      F\n{A\tri B,C}`\varepsilon_{(A\tri B)\tri C}`
      \m{G(A\tri B),GC}``\varepsilon_{A\tri B}\tri\varepsilon_C]
    \qtriangle(2000,0)|amr|/=`<-`->/<1000,400>[
      (A\tri B)\tri C`(A\tri B)\tri C`(FGA\tri FGB)\tri C;
      `(\varepsilon_A\tri\varepsilon_B)\tri id_C`(h_A\tri h_B)\tri id_C]
    \morphism|l|<0,400>[
      F((GA\otimes GB)\otimes GC)`F(G(A\tri B)\otimes GC);F(\n{A,B}\otimes id_{GC})]
    \dtriangle(1000,0)|mmm|/`<-`->/<1000,400>[
      (A\tri B)\tri C`FG(A\tri B)\tri FGC`FG(A\tri B)\tri C;
      `\varepsilon_{A\tri B}\tri id_C`id\tri\varepsilon_C]
    \btriangle(0,-400)|lmm|/->`<-`/<1000,400>[
      F((GA\otimes GB)\otimes GC)`F((GB\otimes GA)\otimes GC)`F(GA\otimes GB)\tri FGC;
      F(\e{A,B}\otimes id_{GC})`\m{GA\otimes GB,GC}`]
    \btriangle(1000,-400)|mmm|/<-``->/<2000,400>[
      FG(A\tri B)\tri FGC`F(GA\otimes GB)\tri FGC`F(GA\otimes GB)\tri C;
      F\n{A,B}\tri id_{FGC}``id_{F(GA\otimes GB)}\tri\varepsilon_C]
    \qtriangle(2000,-400)|mmr|/`<-`->/<1000,400>[
      FG(A\tri B)\tri C`(FGA\tri FGB)\tri C`F(GA\otimes GB)\tri C;
      `F\n{A,B}\otimes id_C`\m{GA,GB}\tri id_C]
    \btriangle(0,-800)|lmm|/->`<-`/<2000,400>[
      F((GB\otimes GA)\otimes GC)`F(G(B\tri A)\otimes GC)`F(GB\otimes GA)\tri FGC;
      F(\n{B,A}\otimes id_{GC})`\m{GB\otimes GA,GC}`]
    \morphism(1000,-400)|m|<1000,-400>[
      F(GA\otimes GB)\tri FGC`F(GB\otimes GA)\tri FGC;F\e{A,B}\tri id_{FGC}]
    \dtriangle(2000,-800)|mra|/`->`->/<1000,400>[
      F(GA\otimes GB)\tri C`F(GB\otimes GA)\tri FGC`F(GB\otimes GA)\tri C;
      `F\e{A,B}\tri id_C`id\tri\varepsilon_C]
    \square(0,-1200)|almb|/<-`->`->`->/<1000,400>[
      F(G(B\tri A)\otimes GC)`FG(B\tri A)\tri FGC`FG((B\tri A)\tri C)`(B\tri A)\tri C;
      \m{G(B\tri A),GC}`F\n{B\tri A,C}`
      \varepsilon_{B\tri A}\tri\varepsilon_C`\varepsilon_{(B\tri A)\tri C}]
    \morphism(1000,-800)|b|/<-/<1000,0>[
      FG(B\tri A)\tri FGC`F(GB\otimes GA)\tri FGC;F\n{B,A}\tri id]
    \dtriangle(1000,-1200)/`->`<-/<2000,400>[
      F(GB\otimes GA)\tri C`(B\tri A)\tri C`FG(B\tri A)\tri C;
      `F\n{B,A}\tri id_C`\varepsilon_{B\tri A}\tri id_C]
    \morphism(1000,-800)|m|<2000,-400>[
      FG(B\tri A)\tri FGC`FG(B\tri A)\tri C;id_{FG(B\tri A)}\tri\varepsilon_C]
    \morphism(500,50)//<0,0>[`;(1)]
    \morphism(500,-300)//<0,0>[`;(2)]
    \morphism(400,-550)//<0,0>[`;(3)]
    \morphism(500,-950)//<0,0>[`;(4)]
    \morphism(1000,300)//<0,0>[`;(5)]
    \morphism(1600,200)//<0,0>[`;(6)]
    \morphism(1800,-150)//<0,0>[`;(7)]
    \morphism(2400,-550)//<0,0>[`;(8)]
    \morphism(1300,-950)//<0,0>[`;(9)]
    \morphism(2700,-900)//<0,0>[`;(10)]
    \morphism(2800,300)//<0,0>[`;(11)]
    \morphism(2500,50)//<0,0>[`;(12)]
  \efig
  \end{mathpar}
\end{proof}

\begin{theorem}
  The co-Eilenberg-Moore category $\cat{L}^S$ of $S$ is symmetric monoidal closed.
\end{theorem}
\begin{proof}
  Let $(\cat{L},\tri,I',\alpha',\lambda',\rho')$ be the Lambek cateogry in a SMCC-Lambek model
  and $S$ be the comonad on $\cat{L}$. Since $\cat{L}$ is a Lambek category, it is obvious that
  $\cat{L}$ is also Lambek. By Corollary~\ref{corollary:LC-with-ex-mc}, we only need to prove
  the exchange defined in Lemma~\ref{lem:em-exchange} satisfies the three commutative diagrams
  in Definition~\ref{def:smcc}.

  The first triangle in Definition~\ref{def:smcc} commutes as follows:
  (1)--coalgebra; (2)--$\varepsilon$ is monoidal; (3)--naturality of $\rho$; (4)--naturality of
  $\varepsilon$; (5)--naturality of $\m{}$; (6)--$F$ is monoidal; (7)--$\cat{C}$ is symmetric;
  (8)--naturality of $\e{}$; (9)--$G$ is monoidal.
  \begin{mathpar}
  \bfig
    \Vtriangle/->`=`/<800,800>[A\tri I'`FGA\tri FGI'`A\tri I';h_A\tri h_{I'}``]
    \Ctrianglepair(1600,0)|mmmmm|/->`<-``=`<-/<800,400>[
      FGA\tri FGI'`FGA\tri I'`FGA\tri FI`FGA\tri I';
      id_{FGA}\tri\varepsilon_{I'}`id_{FGA}\tri F\n{I'}```id_{FGA}\tri\m{I}]
    \morphism(800,400)|m|<0,-400>[FGA\tri I'`A\tri I';\varepsilon_{FGA}\tri id_{I'}]
    \morphism(1600,400)|m|<800,0>[FGA\tri FI`F(GA\otimes I);\m{GA,I}]
    \morphism(1600,0)|m|<0,-400>[FGA\tri I'`FGA;\rho_{FGA}']
    \dtriangle(1600,-400)|mmm|/->`->`<-/<800,800>[
      F(GA\otimes I)`FGA`F(I\otimes GA);
      F\rho_{GA}`F\e{GA,I}`F\lambda_{GA}]
    \square(1600,-800)/->``->`<-/<1600,1600>[
      FGA\tri FGI'`F(GA\otimes GI')`FG(I'\tri A)`F(GI'\otimes GA);
      \m{GA,GI'}``F\e{GA,GI'}`F\n{I',A}]
    \morphism(2400,400)|m|<800,400>[F(GA\otimes I)`F(GA\otimes GI');F(id_{GA}\otimes\n{I'})]
    \morphism(2400,-400)|m|<800,-400>[F(I\otimes GA)`F(GI'\otimes GA);F(\n{I'}\otimes id_{GA})]
    \morphism(0,800)|l|<0,-1200>[A\tri I'`A;\rho_A']
    \square(0,-800)|mlmb|/<-`->`<-`<-/<1600,400>[
      A`FGA`I'\tri A`FG(I'\tri A);\varepsilon_A`\lambda_A'`FG\lambda_A'`\varepsilon_{I'\tri A}]
    \morphism(800,600)//<0,0>[`;(1)]
    \morphism(1300,400)//<0,0>[`;(2)]
    \morphism(800,-200)//<0,0>[`;(3)]
    \morphism(800,-600)//<0,0>[`;(4)]
    \morphism(2150,600)//<0,0>[`;(5)]
    \morphism(1950,200)//<0,0>[`;(6)]
    \morphism(2200,-200)//<0,0>[`;(7)]
    \morphism(2800,0)//<0,0>[`;(8)]
    \morphism(2200,-600)//<0,0>[`;(9)]
  \efig
  \end{mathpar}
  The second triangle in the proof commutes as follows: (1) and (5)--coalgebra; (2) and
  (4)--$\varepsilon$ is monoidal; (3)--$\cat{C}$ is symmetric.
  \begin{mathpar}
  \bfig
    \ptriangle|amm|/->`=`->/<600,600>[
      A\tri B`FGA\tri FGB`A\tri B;h_A\tri h_B``\varepsilon_A\tri\varepsilon_B]
    \morphism(600,0)|b|<-600,0>[FG(A\tri B)`A\tri B;\varepsilon_{A\tri B}]
    \morphism(600,600)<700,0>[FGA\tri FGB`F(GA\otimes GB);\m{GA,GB}]
    \morphism(1300,0)|b|<-700,0>[F(GA\otimes GB)`FG(A\tri B);F\n{A,B}]
    \square(1300,0)/->`=`=`<-/<800,600>[
      F(GA\otimes GB)`F(GB\otimes GA)`F(GA\otimes GB)`F(GB\otimes GA);F\e{A,B}```F\e{B,A}]
    \qtriangle(2100,0)|amr|/->``->/<1400,600>[F(GB\otimes GA)`FG(B\tri A)`B\tri A;F\n{B,A}``\varepsilon_{B\tri A}]
    \morphism(2900,0)|b|<-800,0>[FGB\tri FGA`F(GB\otimes GA);\m{GB,GA}]
    \btriangle(2900,0)|mmb|/<-`=`<-/<600,400>[
      B\tri A`FGB\tri FGA`B\tri A;
      \varepsilon_B\tri\varepsilon_A``h_A\tri h_A])
    \morphism(200,500)//<0,0>[`;(1)]
    \morphism(800,300)//<0,0>[`;(2)]
    \morphism(1700,300)//<0,0>[`;(3)]
    \morphism(2500,300)//<0,0>[`;(4)]
    \morphism(3100,200)//<0,0>[`;(5)]
  \efig
  \end{mathpar}
  TODO:
  \begin{mathpar}
  \bfig
    \hSquares/->`->`->``->`->`->/<400>[
      (A\tri B)\tri C`A\tri(B\tri C)`(B\tri C)\tri A`
      (B\tri A)\tri C`B\tri(A\tri C)`B\tri(C\tri A);
      \alpha_{A,B,C}`\e{A,B\tri C}^S`\e{A,B}^S\tri id_C``
      \alpha_{B,A,C}`\alpha_{B,A,C}`id_B\tri\e{A,C}^S]
  \efig
  \end{mathpar}
\end{proof}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: main.tex
%%% End:

### 2017-08-01 category-theory-basics.tex
Partial proof for Eilenberg-Moore of the comonad being symmetric

@@
 \label{def:mc}
-  A \textbf{monoidal category} $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ is a category $\cat{M}$
+  A \textbf{monoidal category} $(\cat{M},\tri,I,\alpha,\lambda,\rho)$ is a category $\cat{M}$
   consists of
   \begin{itemize}
-  \item a bifunctor $\otimes:\cat{M}\times\cat{M}\rightarrow\cat{M}$, called the tensor product;
+  \item a bifunctor $\tri:\cat{M}\times\cat{M}\rightarrow\cat{M}$, called the tensor product;
   \item an object $I$, called the unit object;
   \item three natural isomorphisms $\alpha$, $\lambda$, and $\rho$ with components
-        $$\alpha_{A,B,C}:(A\otimes B)\otimes C\rightarrow A\otimes(B\otimes C)$$
-        $$\lambda_A:I\otimes A\rightarrow A$$
-        $$\rho_A:A\otimes I\rightarrow A$$
+        $$\alpha_{A,B,C}:(A\tri B)\tri C\rightarrow A\tri(B\tri C)$$
+        $$\lambda_A:I\tri A\rightarrow A$$
+        $$\rho_A:A\tri I\rightarrow A$$
         where $\alpha$ is called associator, $\lambda$ is left unitor, and $\rho$ is right
@@
     \square/`->`->`->/<2100,400>[
-      ((A\otimes B)\otimes C)\otimes D`
-      A\otimes((B\otimes C)\otimes D)`
-      (A\otimes B)\otimes(C\otimes D)`
-      A\otimes(B\otimes(C\otimes D));
+      ((A\tri B)\tri C)\tri D`
+      A\tri((B\tri C)\tri D)`
+      (A\tri B)\tri(C\tri D)`
+      A\tri(B\tri(C\tri D));
       `
-      \alpha_{A\otimes B,C,D}`
-      id_A\otimes\alpha_{B,C,D}`
-      \alpha_{A,B,C\otimes D}]
+      \alpha_{A\tri B,C,D}`
+      id_A\tri\alpha_{B,C,D}`
+      \alpha_{A,B,C\tri D}]
     \morphism(0,400)<1100,0>[
-      ((A\otimes B)\otimes C)\otimes D`
-      (A\otimes(B\otimes C))\otimes D;
-      \alpha_{A,B,C}\otimes id_D]
+      ((A\tri B)\tri C)\tri D`
+      (A\tri(B\tri C))\tri D;
+      \alpha_{A,B,C}\tri id_D]
     \morphism(1100,400)<1000,0>[
-      (A\otimes(B\otimes C))\otimes D`
-      A\otimes((B\otimes C)\otimes D);
-      \alpha_{A,B\otimes C,D}]
+      (A\tri(B\tri C))\tri D`
+      A\tri((B\tri C)\tri D);
+      \alpha_{A,B\tri C,D}]
   \efig
@@
     \Vtriangle<400,400>[
-      (A\otimes I)\otimes B`
-      A\otimes(I\otimes B)`
-      A\otimes B;
+      (A\tri I)\tri B`
+      A\tri(I\tri B)`
+      A\tri B;
       \alpha_{A,I,B}`
-      \rho_A\otimes id_B`
-      id_A\otimes\lambda_B]
+      \rho_A\tri id_B`
+      id_A\tri\lambda_B]
   \efig
@@
   A \textbf{Lambek category} (or a \textbf{biclosed monoidal category}) is a monoidal category
-  $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ equipped with two bifunctors
+  $(\cat{M},\tri,I,\alpha,\lambda,\rho)$ equipped with two bifunctors
   $\rightharpoonup:\cat{M}^{op}\times\cat{M}\rightarrow\cat{M}$ and
@@
   \begin{array}{lll}
-    \Hom{L}{X\otimes A}{B}\cong\Hom{L}{X}{A\lto B} & \quad\quad\quad\quad & 
-    \Hom{L}{A\otimes X}{B}\cong\Hom{L}{X}{B\rto A}
+    \Hom{L}{X\tri A}{B}\cong\Hom{L}{X}{A\lto B} & \quad\quad\quad\quad & 
+    \Hom{L}{A\tri X}{B}\cong\Hom{L}{X}{B\rto A}
   \end{array}
@@
 \begin{definition}
+  \label{def:smcc}
   A \textbf{symmetric monoidal category} (SMCC) is a monoidal category
@@
 \end{definition}
+
+We use $\tri$ for non-symmetric monoidal categories while $\otimes$ for symmetric ones.
 
@@
 \begin{definition}
-  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
-  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories. A \textbf{monoidal
+  Let $(\cat{M},\tri,I,\alpha,\lambda,\rho)$ and
+  $(\cat{M'},\tri',I',\alpha',\lambda',\rho')$ be monoidal categories. A \textbf{monoidal
   functor} $(F,\m{})$ from $\cat{M}$ to $\cat{M'}$ is a functor $F:\cat{M}\rightarrow\cat{M'}$
   together with a morphism $\m{I}:I'\rightarrow F(I)$ and a natural transformation
-  $\m{A,B}:FA'\otimes FB'\rightarrow F(A\otimes B)$, such that the following diagrams commute
+  $\m{A,B}:FA'\tri FB'\rightarrow F(A\tri B)$, such that the following diagrams commute
   for any objects $A$, $B$, and $C$ in $\cat{M}$:
@@
     \hSquares/->`->`->``->`->`->/<400>[
-      (FA\otimes'FB)\otimes'FC`FA\otimes'(FB\otimes'FC)`FA\otimes'F(B\otimes C)`
-      F(A\otimes B)\otimes'FC`F((A\otimes B)\otimes C)`F(A\otimes(B\otimes C));
-      \alpha'_{FA,FB,FC}`id_{FA}\otimes'\m{A,B}`\m{A,B}\otimes'id_{FC}``
-      \m{A,B\otimes C}`\m{A\otimes B,C}`F\alpha_{A,B,C}]
+      (FA\tri'FB)\tri'FC`FA\tri'(FB\tri'FC)`FA\tri'F(B\tri C)`
+      F(A\tri B)\tri'FC`F((A\tri B)\tri C)`F(A\tri(B\tri C));
+      \alpha'_{FA,FB,FC}`id_{FA}\tri'\m{A,B}`\m{A,B}\tri'id_{FC}``
+      \m{A,B\tri C}`\m{A\tri B,C}`F\alpha_{A,B,C}]
   \efig
@@
     \square/->`->`<-`->/<600,400>[
-      I'\otimes'FA`FA`FI\otimes'FA`F(I\otimes A);
-      \lambda'_{FA}`\m{I}\otimes id_{FA}`F\lambda_A`\m{I,A}]
+      I'\tri'FA`FA`FI\tri'FA`F(I\tri A);
+      \lambda'_{FA}`\m{I}\tri id_{FA}`F\lambda_A`\m{I,A}]
   \efig
@@
     \square/->`->`<-`->/<600,400>[
-      FA\otimes'I'`FA`FA\otimes'FI`F(A\otimes I);
-      \rho'_{FA}`\id_{FA}\otimes\m{I}`F\rho_A`\m{A,I}]
+      FA\tri'I'`FA`FA\tri'FI`F(A\tri I);
+      \rho'_{FA}`\id_{FA}\tri\m{I}`F\rho_A`\m{A,I}]
   \efig
@@
 \begin{definition}
-  Let $(F,\m{})$ and $(G,\n{})$ be monoidal functors from a monoidal category $\cat{M}$ to a
-  monoidal category $\cat{M'}$. A \textbf{monoidal natural transformation} from $(F,\m{})$ to 
-  $(G,\n{})$ is a natural transformation $\theta:(F,\m{})\rightarrow(G,\n{})$ such that the
-  following diagrams commute for any objects $A$ and $B$ in $\cat{M}$:
+  Let $(F,\m{})$ and $(G,\n{})$ be monoidal functors from a monoidal category
+  $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ to a monoidal category
+  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$. A \textbf{monoidal natural transformation}
+  from $(F,\m{})$ to $(G,\n{})$ is a natural transformation $\theta:(F,\m{})\rightarrow(G,\n{})$
+  such that the following diagrams commute for any objects $A$ and $B$ in $\cat{M}$:
   \begin{mathpar}
@@
     \square<700,400>[
-      FA\otimes'FB`F(A\otimes B)`GA\otimes'GB`G(A\otimes B);
-      \m{A,B}`\theta_A\otimes'\theta_B`\theta_{A\otimes B}`\n{A,B}]
+      FA\tri'FB`F(A\tri B)`GA\tri'GB`G(A\tri B);
+      \m{A,B}`\theta_A\tri'\theta_B`\theta_{A\tri B}`\n{A,B}]
   \efig
@@
 \begin{definition}
-  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
-  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories,
+  Let $(\cat{M},\tri,I,\alpha,\lambda,\rho)$ and
+  $(\cat{M'},\tri',I',\alpha',\lambda',\rho')$ be monoidal categories,
   $F:\cat{M}\rightarrow\cat{M'}$ and $G:\cat{M}'\rightarrow\cat{M}$ be functors. The adjunction
@@
   \label{def:strong-monad}
-  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ be a monoidal category and $(T,\eta,\mu)$ be a
+  Let $(\cat{M},\tri,I,\alpha,\lambda,\rho)$ be a monoidal category and $(T,\eta,\mu)$ be a
   monad on $\cat{M}$. $T$ is a \textbf{strong monad} if there is natural transformation $\tau$, 
   called the \textbf{tensorial strength}, with components
-  $\tau_{A,B}:A\otimes TB\rightarrow T(A\otimes B)$ such that the following diagrams commute:
+  $\tau_{A,B}:A\tri TB\rightarrow T(A\tri B)$ such that the following diagrams commute:
   \begin{mathpar}
   \bfig
-    \Vtriangle<400,400>[I\otimes TA`T(I\otimes A)`TA;\tau_{I,A}`\lambda_{TA}`T\lambda_A]
+    \Vtriangle<400,400>[I\tri TA`T(I\tri A)`TA;\tau_{I,A}`\lambda_{TA}`T\lambda_A]
   \efig
@@
     \Vtriangle<400,400>[
-      A\otimes B`A\otimes TB`T(A\otimes B);id_A\otimes\eta_B`\eta_{A\otimes B}`\tau_{A,B}]
+      A\tri B`A\tri TB`T(A\tri B);id_A\tri\eta_B`\eta_{A\tri B}`\tau_{A,B}]
   \efig
@@
     \square/->`->`->`/<1800,400>[
-      (A\otimes B)\otimes TC`T((A\otimes B)\otimes C)`
-      A\otimes(B\otimes TC)`T(A\otimes(B\otimes C));
-      \tau_{A\otimes B,C}`\alpha_{A,B,TC}`T\alpha_{A,B,C}`]
-    \morphism<900,0>[A\otimes(B\otimes TC)`A\otimes T(B\otimes C);id_A\otimes\tau_{B,C}]
-    \morphism(900,0)<900,0>[A\otimes T(B\otimes C)`T(A\otimes(B\otimes C));\tau_{A,B\otimes C}]
+      (A\tri B)\tri TC`T((A\tri B)\tri C)`
+      A\tri(B\tri TC)`T(A\tri(B\tri C));
+      \tau_{A\tri B,C}`\alpha_{A,B,TC}`T\alpha_{A,B,C}`]
+    \morphism<900,0>[A\tri(B\tri TC)`A\tri T(B\tri C);id_A\tri\tau_{B,C}]
+    \morphism(900,0)<900,0>[A\tri T(B\tri C)`T(A\tri(B\tri C));\tau_{A,B\tri C}]
   \efig
@@
     \square/`->`->`->/<1400,400>[
-      A\otimes T^2B`T^2(A\otimes B)`A\otimes TB`T(A\otimes B);
-      `id_A\otimes\mu_B`\mu_{A\otimes B}`\tau_{A,B}]
-    \morphism(0,400)<700,0>[A\otimes T^2B`T(A\otimes TB);\tau_{A,TB}]
-    \morphism(700,400)<700,0>[T(A\otimes TB)`T^2(A\otimes B);T\tau_{A,B}]
+      A\tri T^2B`T^2(A\tri B)`A\tri TB`T(A\tri B);
+      `id_A\tri\mu_B`\mu_{A\tri B}`\tau_{A,B}]
+    \morphism(0,400)<700,0>[A\tri T^2B`T(A\tri TB);\tau_{A,TB}]
+    \morphism(700,400)<700,0>[T(A\tri TB)`T^2(A\tri B);T\tau_{A,B}]
   \efig

### 2017-08-04 adjoint-model.tex
EM symmetric proof; exchange comonadically proof

@@
 \begin{lemma}
+  \label{lem:em-ex}
   The following diagrams commute in the co-Eilenberg-Moore category $\cat{L}^S$:
@@
   \end{mathpar}
-  TODO:
+  The third diagram commutes as follows, which uses Lemma~\ref{lem:emex}.
   \begin{mathpar}
   \bfig
-    \hSquares/->`->`->``->`->`->/<400>[
-      (A\tri B)\tri C`A\tri(B\tri C)`(B\tri C)\tri A`
-      (B\tri A)\tri C`B\tri(A\tri C)`B\tri(C\tri A);
-      \alpha_{A,B,C}`\e{A,B\tri C}^S`\e{A,B}^S\tri id_C``
-      \alpha_{B,A,C}`\alpha_{B,A,C}`id_B\tri\e{A,C}^S]
+    \morphism(0,400)<1600,0>[(A\tri B)\tri C`A\tri(B\tri C);\alpha_{A,B,C}']
+    \Vtriangle(1600,0)|amm|/->`=`->/<800,400>[
+      A\tri(B\tri C)`FGA\tri FG(B\tri C)`A\tri(B\tri C);
+      h_A\tri h_{B\tri C}``\varepsilon_A\tri\varepsilon_{B\tri C}]
+    \morphism(800,0)|m|<-800,400>[
+      FG((A\tri B)\tri C)`(A\tri B)\tri C;\varepsilon_{(A\tri B)\tri C}]
+    \qtriangle(800,-400)|mmm|/`->`<-/<1600,400>[
+      FG((A\tri B)\tri C)`A\tri(B\tri C)`FG(A\tri(B\tri C));
+      `FG\alpha_{A,B,C}'`\varepsilon_{A\tri(B\tri C)}]
+    \Ctriangle(2400,-1200)|mrm|/`->`<-/<800,800>[
+      FGA\tri FG(B\tri C)`FG(A\tri(B\tri C))`F(GA\otimes G(B\tri C));
+      `\m{GA,G(B\tri C)}`F\n{A,B\tri C}]
+    \morphism(800,-400)<0,400>[F(G(A\tri B)\otimes GC)`FG((A\tri B)\tri C);F\n{A\tri B,C}]
+    \btriangle(800,-800)|mmm|/<-``->/<1400,400>[
+      F(G(A\tri B)\otimes GC)`F((GA\otimes GB)\otimes GC)`F(GA\otimes(GB\otimes GC));
+      F(\n{A,B}\otimes id_{GC})``F\alpha_{GA,GB,GC}]
+    \morphism(800,-800)|m|<0,-400>[
+      F((GA\otimes GB)\otimes GC)`F((GB\otimes GA)\otimes GC);F(\e{A,B}\otimes id_{GC})]
+    \morphism(2200,-800)|m|<1000,-400>[
+      F(GA\otimes(GB\otimes GC))`F(GA\otimes G(B\tri C));F(id_{GA}\otimes\n{B,C})]
+    \morphism(2200,-800)|m|<0,-400>[
+      F(GA\otimes(GB\otimes GC))`F((GB\otimes GC)\otimes GA);F\e{GA,GB\otimes GC}]
+    \qtriangle(2200,-1600)|mmr|/`->`->/<1000,400>[
+      F((GB\otimes GC)\otimes GA)`F(GA\otimes G(B\tri C))`F(G(B\tri C)\otimes GA);
+      `F(\n{B,C}\otimes id_{GA})`F\e{A,B\tri C}]
+    \morphism(800,-1200)|m|<0,-400>[
+      F((GB\otimes GA)\otimes GC)`F(G(B\tri A)\otimes GC);F(\n{B,A}\otimes id_{GC})]
+    \morphism(2200,-1200)|m|<0,-300>[
+      F((GB\otimes GC)\otimes GA)`F(GB\otimes(GC\otimes GA));F\alpha_{GB,GC,GA}]
+    \morphism(800,-1200)|m|<700,-600>[
+      F((GB\otimes GA)\otimes GC)`F(GB\otimes(GA\otimes GC));F\alpha]
+    \morphism(2200,-1500)|m|<-700,-300>[
+      F(GB\otimes(GC\otimes GA))`F(GB\otimes(GA\otimes GC));F(id_{GC}\otimes\e{C,A})]
+    \morphism(800,-1600)|m|<0,-400>[F(G(B\tri A)\otimes GC)`FG((B\tri A)\tri C);F\n{B\tri A,C}]
+    \morphism(2200,-1500)|m|<0,-500>[
+      F(GB\otimes(GC\otimes GA))`F(GB\otimes G(C\tri A));F(id_{GB}\otimes\n{C,A})]
+    \morphism(2200,-2000)|m|<0,-400>[
+      F(GB\otimes G(C\tri A))`FG(B\tri(C\tri A));F\n{B,C\tri A}]
+    \morphism(1500,-1800)|m|<0,-400>[
+      F(GB\otimes(GA\otimes GC))`F(GB\otimes G(A\tri C));F(id_{GB}\otimes\n{A,C})]
+    \morphism(1500,-2200)|m|<0,-400>[F(GB\otimes G(A\tri C))`FG(B\tri(A\tri C));F\n{B,A\tri C}]
+    \morphism(0,400)|l|<0,-2000>[(A\tri B)\tri C`(B\tri A)\tri C;\e{A,B}^S\tri id_C]
+    \morphism(800,-2000)|m|<-800,400>[
+      FG((B\tri A)\tri C)`(B\tri A)\tri C;\varepsilon_{(B\tri A)\tri C}]
+    \morphism(0,-1600)|l|<0,-1000>[(B\tri A)\tri C`B\tri(A\tri C);\alpha_{B,A,C}']
+    \morphism(1500,-2600)|m|<-1500,0>[
+      FG(B\tri(A\tri C))`B\tri(A\tri C);\varepsilon_{B\tri(A\tri C)}]
+    \morphism(0,-2600)|l|<0,-400>[B\tri(A\tri C)`B\tri(C\tri A);\id_B\tri\e{A,C}^S]
+    \morphism(1600,-3000)|b|<-1600,0>[(B\tri C)\tri A`B\tri(C\tri A);\alpha_{B,C,A}']
+    \morphism(3200,-1600)|r|<0,-1400>[
+      F(G(B\tri C)\otimes GA)`FG((B\tri C)\tri A);F\n{B\tri C,A}]
+    \morphism(3200,-3000)|m|<-1000,600>[FG((B\tri C)\tri A)`FG(B\tri(C\tri A));FG\alpha_{B,C,A}]
+    \morphism(3200,-3000)|b|<-1600,0>[
+      FG((B\tri C)\tri A)`(B\tri C)\tri A;\varepsilon_{(B\tri C)\tri A}]
   \efig

### 2017-08-13 Elle/Elle-output.tex
Elle updated

@@
               }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
-            }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}  }
+            }{\texttt{\textcolor{red}{<<no parses (char 10): y0 : Gf B;*** . \mbox{$\mid$}- F y0 : F Gf B >>}}}
             \\
@@
               }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
-            }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
-          }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
-        }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{;}   \cdot   \vdash   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
-      }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}  \ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
-    }{ \cdot   \ottsym{;}  \ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{,}  \ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
-    }{ \cdot   \ottsym{;}  \ottmv{z}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash   \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{2}}}}  \otimes  \ottmv{y_{{\mathrm{2}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
-    }{ \cdot   \ottsym{;}   \cdot   \vdash   \lambda_l  \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}   .
-\mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{2}}}}  \otimes  \ottmv{y_{{\mathrm{2}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \rightharpoonup  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
+            }{\texttt{\textcolor{red}{<<no parses (char 10): x0 : Gf A;*** . \mbox{$\mid$}- F x0 : F Gf A >>}}}
+          }{\texttt{\textcolor{red}{<<no parses (char 22): y0 : Gf B, x0 : Gf A ;*** . \mbox{$\mid$}- h(F y0) (x) F x0 : h(F Gf B) (x) F Gf A >>}}}
+        }{\texttt{\textcolor{red}{<<no parses (char 22): x1 : Gf A, y1 : Gf B ;*** . \mbox{$\mid$}- ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0) : h(F Gf B) (x) F Gf A >>}}}
+      }{\texttt{\textcolor{red}{<<no parses (char 11): x1 : Gf A ;*** y2 : F Gf B \mbox{$\mid$}- let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)) : h(F Gf B) (x) F Gf A >>}}}
+    }{\texttt{\textcolor{red}{<<no parses (char 3): .
+;*** x2 : F Gf A, y2 : F Gf B \mbox{$\mid$}- let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0))) : h(F Gf B) (x) F Gf A >>}}}
+    }{\texttt{\textcolor{red}{<<no parses (char 3): .
+;*** z : h(F Gf A) (x) F Gf B \mbox{$\mid$}- let z : h(F Gf A) (x) F Gf B be x2 (x) y2 in (let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)))) : (h(F Gf B) (x) F Gf A) >>}}}
+    }{\texttt{\textcolor{red}{<<no parses (char 3): .
+;*** .
+\mbox{$\mid$}- \mbox{$\backslash{}$}l z : h(F Gf A) (x) F Gf B .
+let z : h(F Gf A) (x) F Gf B be x2 (x) y2 in (let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)))) : (h(F Gf A) (x) F Gf B) -> (h(F Gf B) (x) F Gf A) >>}}}
   \end{math}
@@
                   }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
-                }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+                }{\texttt{\textcolor{red}{<<no parses (char 10): x1 : Gf A;*** . \mbox{$\mid$}- F x1 : F Gf A >>}}}
                 \\
@@
                     }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
-                  }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}  }
+                  }{\texttt{\textcolor{red}{<<no parses (char 10): y0 : Gf B;*** . \mbox{$\mid$}- F y0 : F Gf B >>}}}
                   \\
@@
                     }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
-                  }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
-                }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
-              }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \otimes  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
-            }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \otimes  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
-          }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{;}  \ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \otimes  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
-        }{ \cdot   \ottsym{;}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{,}  \ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \otimes  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
-      }{ \cdot   \ottsym{;}  \ottmv{z}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash   \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\, \ottmv{y_{{\mathrm{1}}}}  \otimes  \ottmv{x_{{\mathrm{3}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \otimes  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
-    }{ \cdot   \ottsym{;}   \cdot   \vdash   \lambda_l  \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}   .
-\mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\, \ottmv{y_{{\mathrm{1}}}}  \otimes  \ottmv{x_{{\mathrm{3}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \otimes  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}  \rightharpoonup  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}  \ottsym{)}}
+                  }{\texttt{\textcolor{red}{<<no parses (char 10): x0 : Gf A;*** . \mbox{$\mid$}- F x0 : F Gf A >>}}}
+                }{\texttt{\textcolor{red}{<<no parses (char 22): y0 : Gf B, x0 : Gf A ;*** . \mbox{$\mid$}- h(F y0) (x) F x0 : h(F Gf B) (x) F Gf A >>}}}
+              }{\texttt{\textcolor{red}{<<no parses (char 33): x1 : Gf A, y0 : Gf B, x0 : Gf A ;*** . \mbox{$\mid$}- h(F x1) (x) (h(F y0) (x) F x0) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
+            }{\texttt{\textcolor{red}{<<no parses (char 22): y0 : Gf B, x2 : Gf A ;*** .
+\mbox{$\mid$}- contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0)) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
+          }{\texttt{\textcolor{red}{<<no parses (char 11): y0 : Gf B ;*** x3 : F Gf A \mbox{$\mid$}- let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
+        }{\texttt{\textcolor{red}{<<no parses (char 3): .
+;*** y1 : F Gf B, x3 : F Gf A \mbox{$\mid$}- let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0)))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
+      }{\texttt{\textcolor{red}{<<no parses (char 3): .
+;*** z : h(F Gf B) (x) F Gf A \mbox{$\mid$}- let z : h(F Gf B) (x) F Gf A be y1 (x) x3 in (let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
+    }{\texttt{\textcolor{red}{<<no parses (char 3): .
+;*** .
+\mbox{$\mid$}- \mbox{$\backslash{}$}l z : h(F Gf B) (x) F Gf A .
+let z : h(F Gf B) (x) F Gf A be y1 (x) x3 in (let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))))) : (h(F Gf B) (x) F Gf A) -> (h(F Gf A) (x) (h(F Gf B) (x) F Gf A)) >>}}}
   \end{math}
@@
                     }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
-                  }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+                  }{\texttt{\textcolor{red}{<<no parses (char 10): x0 : Gf A;*** . \mbox{$\mid$}- F x0 : F Gf A >>}}}
                   \\
@@
                     }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
-                  }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}  }
-                }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{;}   \cdot   \vdash    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}  }
+                  }{\texttt{\textcolor{red}{<<no parses (char 10): y0 : Gf B;*** . \mbox{$\mid$}- F y0 : F Gf B >>}}}
+                }{\texttt{\textcolor{red}{<<no parses (char 22): x0 : Gf A, y0 : Gf B ;*** . \mbox{$\mid$}- h(F x0) (x) F y0 : h(F Gf A) (x) F Gf B >>}}}
                 \\
@@
                   }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
-                }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
-              }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \otimes   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
-            }{\ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{;}   \cdot   \vdash   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \otimes   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
-          }{\ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \otimes   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
-        }{ \cdot   \ottsym{;}  \ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{,}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \otimes   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
-      }{ \cdot   \ottsym{;}  \ottmv{z}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash   \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{3}}}}  \otimes  \ottmv{y_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \otimes   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}  }
-    }{ \cdot   \ottsym{;}   \cdot   \vdash   \lambda_l  \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}   .
-\mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{3}}}}  \otimes  \ottmv{y_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{3}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \otimes  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \otimes   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \rightharpoonup  \ottsym{(}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \otimes   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \otimes   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
+                }{\texttt{\textcolor{red}{<<no parses (char 10): x1 : Gf A;*** . \mbox{$\mid$}- F x1 : F Gf A >>}}}
+              }{\texttt{\textcolor{red}{<<no parses (char 33): x0 : Gf A, y0 : Gf B, x1 : Gf A ;*** . \mbox{$\mid$}- (h(F x0) (x) F y0) (x) F x1 : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
+            }{\texttt{\textcolor{red}{<<no parses (char 22): x2 : Gf A, y0 : Gf B ;*** . \mbox{$\mid$}- contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1) : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
+          }{\texttt{\textcolor{red}{<<no parses (char 11): x2 : Gf A ;*** y1 : F Gf B \mbox{$\mid$}- let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1)) : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
+        }{\texttt{\textcolor{red}{<<no parses (char 3): .
+;*** x3 : F Gf A, y1 : F Gf B \mbox{$\mid$}- let x3 : F Gf A be F x2 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1))) : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
+      }{\texttt{\textcolor{red}{<<no parses (char 3): .
+;*** z : h(F Gf A) (x) F Gf B \mbox{$\mid$}- let z : h(F Gf A) (x) F Gf B be x3 (x) y1 in (let x3 : F Gf A be F x2 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1)))) : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
+    }{\texttt{\textcolor{red}{<<no parses (char 3): .
+;*** .
+\mbox{$\mid$}- \mbox{$\backslash{}$}l z : h(F Gf A) (x) F Gf B .
+let z : h(F Gf A) (x) F Gf B be x3 (x) y1 in (let x3 : F Gf A be F x3 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in (h(F x0) (x) (h(F y0) (x) F x1))))) : (h(F Gf A) (x) F Gf B) -> ((h(F Gf A) (x) F Gf B) (x) F Gf A) >>}}}
   \end{math}
@@
             \,
-          }{ \cdot   \vdash   \mathsf{triv}   \ottsym{:}   \mathsf{Unit} }
-        }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{;}   \cdot   \vdash   \mathsf{weak}\, \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\,  \mathsf{triv}    \ottsym{:}   \mathsf{Unit} }
-      }{ \cdot   \ottsym{;}  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{weak}\, \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\,  \mathsf{triv}     \ottsym{:}   \mathsf{Unit} }
-    }{ \cdot   \ottsym{;}   \cdot   \vdash   \lambda_l  \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   .
-\mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{weak}\, \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\,  \mathsf{triv}      \ottsym{:}  \ottsym{(}   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}  \rightharpoonup  \ottsym{(}   \mathsf{Unit}   \ottsym{)}}
+          }{\texttt{\textcolor{red}{<<no parses (char 10): . \mbox{$\mid$}- triv ***: Unit >>}}}
+        }{\texttt{\textcolor{red}{<<no parses (char 11): x0 : Gf A ;*** . \mbox{$\mid$}- weak x0 in triv : Unit >>}}}
+      }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** x1 : F Gf A \mbox{$\mid$}- let x1 : F Gf A be F x0 in weak x0 in triv : Unit >>}}}
+    }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** . \mbox{$\mid$}- \mbox{$\backslash{}$}l x1 : F Gf A . let x1 : F Gf A be F x0 in weak x0 in triv : (F Gf A) -> (Unit) >>}}}
   \end{math}
@@
                   \,
-                }{ \cdot   \ottsym{;}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{F} \ottnt{X}   \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{F} \ottnt{X} }
-              }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{X}    \ottsym{;}   \cdot   \vdash   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F} \ottnt{X} }
-            }{ \cdot   \ottsym{;}  \ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     \vdash   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}    \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{:}   \mathsf{F} \ottnt{X} }
-          }{\ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}      \ottsym{;}   \cdot   \vdash   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}    \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{F} \ottnt{X} }
+                }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** x0 : F X \mbox{$\mid$}- x0 : F X >>}}}
+              }{\texttt{\textcolor{red}{<<no parses (char 13): x1 : Gf F X ;*** . \mbox{$\mid$}- let x1 : Gf F X be Gf x0 in x0 : F X >>}}}
+            }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** x2 : F Gf F X \mbox{$\mid$}- let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0) : F X >>}}}
+          }{\texttt{\textcolor{red}{<<no parses (char 18): x3 : Gf F Gf F X ;*** .
+\mbox{$\mid$}- let x3 : Gf F Gf F X be Gf x2 in (let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0)) : F X >>}}}
         }{\ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}      \vdash   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}    \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{X}  }
-      }{ \cdot   \vdash   \lambda_l  \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     .
-\mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}    \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}      \ottsym{)}  \rightharpoonup  \ottsym{(}   \mathsf{G}  \mathsf{F} \ottnt{X}    \ottsym{)}}
+      }{\texttt{\textcolor{red}{<<no parses (char 15):  .
+\mbox{$\mid$}- \mbox{$\backslash{}$}l x3 : G***f F Gf F X .
+Gf (let x3 : Gf F Gf F X be Gf x2 in (let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0))) : (Gf F Gf F X) -> (Gf F X) >>}}}
     \end{math}
@@
             }{\ottmv{x}  \ottsym{:}  \ottnt{X}  \vdash  \ottmv{x}  \ottsym{:}  \ottnt{X}}
-          }{\ottmv{x}  \ottsym{:}  \ottnt{X}  \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottmv{x}   \ottsym{:}   \mathsf{F} \ottnt{X} } 
+          }{\texttt{\textcolor{red}{<<no parses (char 7): x : X ;*** . \mbox{$\mid$}- F x : F X >>}}} 
         }{\ottmv{x}  \ottsym{:}  \ottnt{X}  \vdash   \mathsf{G}  \mathsf{F} \ottmv{x}    \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{X}  }
-      }{ \cdot   \vdash   \lambda_l  \ottmv{x}  :  \ottnt{X} .
-\mathsf{G}  \mathsf{F} \ottmv{x}     \ottsym{:}  \ottsym{(}  \ottnt{X}  \ottsym{)}  \rightharpoonup  \ottsym{(}   \mathsf{G}  \mathsf{F} \ottnt{X}    \ottsym{)}}
+      }{\texttt{\textcolor{red}{<<no parses (char 13): . \mbox{$\mid$}- \mbox{$\backslash{}$}l x : X*** . Gf F x : (X) -> (Gf F X) >>}}}
     \end{math}
@@
                     }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{Y}  \vdash  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \ottnt{X}   \otimes  \ottnt{Y}}
-                  }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{Y}  \ottsym{;}   \cdot   \vdash   \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}   \ottsym{:}   \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)} }
-                }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \ottsym{;}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F} \ottnt{Y}   \vdash   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{:}   \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)} }
-              }{\ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{Y}    \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \ottsym{;}   \cdot   \vdash   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{:}   \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)} }
+                  }{\texttt{\textcolor{red}{<<no parses (char 17): x0 : X , y0 : Y ;*** . \mbox{$\mid$}- F (x0 (x) y0) : F (h(X) (x) Y) >>}}}
+                }{\texttt{\textcolor{red}{<<no parses (char 8): x0 : X ;*** y1 : F Y \mbox{$\mid$}- let y1 : F Y be F y0 in F (x0 (x) y0) : F (h(X) (x) Y) >>}}}
+              }{\texttt{\textcolor{red}{<<no parses (char 22): y2 : Gf F Y , x0 : X ;*** . \mbox{$\mid$}- let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0)) : F (h(X) (x) Y) >>}}}
             }{\ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{Y}    \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \vdash   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)}  }
@@
         }{\ottmv{z}  \ottsym{:}   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}    \vdash   \mathsf{let}\, \ottmv{z}  :   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{1}}}}  \otimes  \ottmv{y_{{\mathrm{3}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{3}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{2}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)}  }
-      }{ \cdot   \vdash   \lambda_l  \ottmv{z}  :   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}   .
-\mathsf{let}\, \ottmv{z}  :   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{1}}}}  \otimes  \ottmv{y_{{\mathrm{3}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{3}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{2}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}    \ottsym{)}  \rightharpoonup  \ottsym{(}   \mathsf{G}  \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)}    \ottsym{)}}
+      }{\texttt{\textcolor{red}{<<no parses (char 15): .
+\mbox{$\mid$}- \mbox{$\backslash{}$}l z : h(X***) (x) Gf F Y .
+let z : h(X) (x) Gf F Y be x1 (x) y3 in (ex y3 , x1 with y2 , x0 in (Gf (let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0))))) : (h(X) (x) Gf F Y) -> (Gf F (h(X) (x) Y)) >>}}}
     \end{math}

### 2017-08-17 Elle/Elle.tex
Deriving exchange, contractions, weakening comonadically; GF is a monad; tensorial strength

--- 2017-06-27 Elle-non-com/Elle.tex
@@
 
-\noindent
-Should not be able to derive exchange in Elle comonadicly or monadicly.:
+Deriving exchange in Elle comonadicly:
+
+\begin{center}
+  \tiny
+  \begin{math}
+    $$\mprset{flushleft}
+    \inferrule* [right={\tiny imprR}] {
+      $$\mprset{flushleft}
+    \inferrule* [right={\tiny tenL}] {
+      $$\mprset{flushleft}
+    \inferrule* [right={\tiny Fl}] {
+      $$\mprset{flushleft}
+      \inferrule* [right={\tiny Fl}] {
+        $$\mprset{flushleft}
+        \inferrule* [right={\tiny beta}] {
+          $$\mprset{flushleft}
+          \inferrule* [right={\tiny tenR}] {
+            $$\mprset{flushleft}
+            \inferrule* [right={\tiny Fr}] {
+              $$\mprset{flushleft}
+              \inferrule* [right={\tiny ax}] {
+                \,
+              }{[[y0 : Gf B |-c y0 : Gf B]]}
+            }{[[y0 : Gf B |-l F y0 : F Gf B]]}
+            \\
+            $$\mprset{flushleft}
+            \inferrule* [right={\tiny Fr}] {
+              $$\mprset{flushleft}
+              \inferrule* [right={\tiny ax}] {
+                \,
+              }{[[x0 : Gf A |-c x0 : Gf A]]}
+            }{[[x0 : Gf A |-l F x0 : F Gf A]]}
+          }{[[y0 : Gf B, x0 : Gf A |-l h(F y0) (>) F x0 : h(F Gf B) (>) F Gf A]]}
+        }{[[x1 : Gf A, y1 : Gf B |-l ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0) : h(F Gf B) (>) F Gf A]]}
+      }{[[x1 : Gf A , y2 : F Gf B |-l let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0)) : h(F Gf B) (>) F Gf A]]}
+    }{[[x2 : F Gf A, y2 : F Gf B |-l let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0))) : h(F Gf B) (>) F Gf A]]}
+    }{[[z : h(F Gf A) (>) F Gf B |-l let z : h(F Gf A) (>) F Gf B be x2 (>) y2 in (let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0)))) : (h(F Gf B) (>) F Gf A)]]}
+    }{[[.
+|-l \r z : h(F Gf A) (>) F Gf B .
+let z : h(F Gf A) (>) F Gf B be x2 (>) y2 in (let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0)))) : (h(F Gf A) (>) F Gf B) -> (h(F Gf B) (>) F Gf A)]]}
+  \end{math}
+\end{center}
 
@@
     $$\mprset{flushleft}
-    \inferrule* [right={\tiny impR}] {
+    \inferrule* [right={\tiny imprR}] {
       $$\mprset{flushleft}
@@
                     \,
-                  }{[[x1 : Gf A |- x1 : Gf A]]}
-                }{[[x1 : Gf A; . |- F x1 : F Gf A]]}
+                  }{[[x1 : Gf A |-c x1 : Gf A]]}
+                }{[[x1 : Gf A |-l F x1 : F Gf A]]}
                 \\
@@
                       \,
-                    }{[[y0 : Gf B |- y0 : Gf B]]}
-                  }{[[y0 : Gf B; . |- F y0 : F Gf B]]}
+                    }{[[y0 : Gf B |-c y0 : Gf B]]}
+                  }{[[y0 : Gf B |-l F y0 : F Gf B]]}
                   \\
@@
                       \,
-                    }{[[x0 : Gf A |- x0 : Gf A]]}
-                  }{[[x0 : Gf A; . |- F x0 : F Gf A]]}
-                }{[[y0 : Gf B, x0 : Gf A ; . |- h(F y0) (x) F x0 : h(F Gf B) (x) F Gf A]]}
-              }{[[x1 : Gf A, y0 : Gf B, x0 : Gf A ; . |- h(F x1) (x) (h(F y0) (x) F x0) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A)]]}
-            }{[[y0 : Gf B, x2 : Gf A ; . |- contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0)) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A)]]}
-          }{[[y0 : Gf B ; x3 : F Gf A |- let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A)]]}
-        }{[[. ; y1 : F Gf B, x3 : F Gf A |- let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0)))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A)]]}
+                    }{[[x0 : Gf A |-c x0 : Gf A]]}
+                  }{[[x0 : Gf A |-l F x0 : F Gf A]]}
+                }{[[y0 : Gf B, x0 : Gf A |-l h(F y0) (>) F x0 : h(F Gf B) (>) F Gf A]]}
+              }{[[x1 : Gf A, y0 : Gf B, x0 : Gf A |-l h(F x1) (>) (h(F y0) (>) F x0) : h(F Gf A) (>) (h(F Gf B) (>) F Gf A)]]}
+            }{[[y0 : Gf B, x2 : Gf A |-l contrR x2 as x1, x0 in (h(F x1) (>) (h(F y0) (>) F x0)) : h(F Gf A) (>) (h(F Gf B) (>) F Gf A)]]}
+          }{[[y0 : Gf B , x3 : F Gf A |-l let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (>) (h(F y0) (>) F x0))) : h(F Gf A) (>) (h(F Gf B) (>) F Gf A)]]}
+        }{[[y1 : F Gf B, x3 : F Gf A |-l let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (>) (h(F y0) (>) F x0)))) : h(F Gf A) (>) (h(F Gf B) (>) F Gf A)]]}
+      }{[[z : h(F Gf B) (>) F Gf A |-l let z : h(F Gf B) (>) F Gf A be y1 (>) x3 in (let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (>) (h(F y0) (>) F x0))))) : h(F Gf A) (>) (h(F Gf B) (>) F Gf A)]]}
     }{[[.
-; z : h(F Gf B) (x) F Gf A |- let z : h(F Gf B) (x) F Gf A be y1 (x) x3 in (let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A)]]}
-    }{[[.
-; .
-|- \l z : h(F Gf B) (x) F Gf A .
-let z : h(F Gf B) (x) F Gf A be y1 (x) x3 in (let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))))) : (h(F Gf B) (x) F Gf A) -> (h(F Gf A) (x) (h(F Gf B) (x) F Gf A))]]}
+|-l \r z : h(F Gf B) (>) F Gf A .
+let z : h(F Gf B) (>) F Gf A be y1 (>) x3 in (let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (>) (h(F y0) (>) F x0))))) : (h(F Gf B) (>) F Gf A) -> (h(F Gf A) (>) (h(F Gf B) (>) F Gf A))]]}
   \end{math}
@@
                       \,
-                    }{[[x0 : Gf A |- x0 : Gf A]]}
-                  }{[[x0 : Gf A; . |- F x0 : F Gf A]]}
+                    }{[[x0 : Gf A |-c x0 : Gf A]]}
+                  }{[[x0 : Gf A |-l F x0 : F Gf A]]}
                   \\
@@
                       \,
-                    }{[[y0 : Gf B |- y0 : Gf B]]}
-                  }{[[y0 : Gf B; . |- F y0 : F Gf B]]}
-                }{[[x0 : Gf A, y0 : Gf B ; . |- h(F x0) (x) F y0 : h(F Gf A) (x) F Gf B]]}
+                    }{[[y0 : Gf B |-c y0 : Gf B]]}
+                  }{[[y0 : Gf B |-l F y0 : F Gf B]]}
+                }{[[x0 : Gf A, y0 : Gf B |-l h(F x0) (>) F y0 : h(F Gf A) (>) F Gf B]]}
                 \\
@@
                     \,
-                  }{[[x1 : Gf A |- x1 : Gf A]]}
-                }{[[x1 : Gf A; . |- F x1 : F Gf A]]}
-              }{[[x0 : Gf A, y0 : Gf B, x1 : Gf A ; . |- (h(F x0) (x) F y0) (x) F x1 : (h(F Gf A) (x) F Gf B) (x) F Gf A]]}
-            }{[[x2 : Gf A, y0 : Gf B ; . |- contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1) : (h(F Gf A) (x) F Gf B) (x) F Gf A]]}
-          }{[[x2 : Gf A ; y1 : F Gf B |- let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1)) : (h(F Gf A) (x) F Gf B) (x) F Gf A]]}
-        }{[[. ; x3 : F Gf A, y1 : F Gf B |- let x3 : F Gf A be F x2 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1))) : (h(F Gf A) (x) F Gf B) (x) F Gf A]]}
+                  }{[[x1 : Gf A |-c x1 : Gf A]]}
+                }{[[x1 : Gf A |-l F x1 : F Gf A]]}
+              }{[[x0 : Gf A, y0 : Gf B, x1 : Gf A |-l (h(F x0) (>) F y0) (>) F x1 : (h(F Gf A) (>) F Gf B) (>) F Gf A]]}
+            }{[[x2 : Gf A, y0 : Gf B |-l contrL x2 as x0, x1 in ((h(F x0) (>) F y0) (>) F x1) : (h(F Gf A) (>) F Gf B) (>) F Gf A]]}
+          }{[[x2 : Gf A , y1 : F Gf B |-l let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (>) F y0) (>) F x1)) : (h(F Gf A) (>) F Gf B) (>) F Gf A]]}
+        }{[[x3 : F Gf A, y1 : F Gf B |-l let x3 : F Gf A be F x2 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (>) F y0) (>) F x1))) : (h(F Gf A) (>) F Gf B) (>) F Gf A]]}
+      }{[[z : h(F Gf A) (>) F Gf B |-l let z : h(F Gf A) (>) F Gf B be x3 (>) y1 in (let x3 : F Gf A be F x2 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (>) F y0) (>) F x1)))) : (h(F Gf A) (>) F Gf B) (>) F Gf A]]}
     }{[[.
-; z : h(F Gf A) (x) F Gf B |- let z : h(F Gf A) (x) F Gf B be x3 (x) y1 in (let x3 : F Gf A be F x2 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1)))) : (h(F Gf A) (x) F Gf B) (x) F Gf A]]}
-    }{[[.
-; .
-|- \l z : h(F Gf A) (x) F Gf B .
-let z : h(F Gf A) (x) F Gf B be x3 (x) y1 in (let x3 : F Gf A be F x3 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in (h(F x0) (x) (h(F y0) (x) F x1))))) : (h(F Gf A) (x) F Gf B) -> ((h(F Gf A) (x) F Gf B) (x) F Gf A)]]}
+|-l \r z : h(F Gf A) (>) F Gf B .
+let z : h(F Gf A) (>) F Gf B be x3 (>) y1 in (let x3 : F Gf A be F x3 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in (h(F x0) (>) (h(F y0) (>) F x1))))) : (h(F Gf A) (>) F Gf B) -> ((h(F Gf A) (>) F Gf B) (>) F Gf A)]]}
   \end{math}
@@
             \,
-          }{[[. |- triv : Unit]]}
-        }{[[x0 : Gf A ; . |- weak x0 in triv : Unit]]}
-      }{[[x1 : F Gf A ; . |- let x1 : F Gf A be F x0 in weak x0 in triv : Unit]]}
-    }{[[. ; . |- \l x1 : F Gf A . let x1 : F Gf A be F x0 in weak x0 in triv : (F Gf A) -> (Unit)]]}
+          }{[[. |-l trivS : UnitS]]}
+        }{[[x0 : Gf A |-l weak x0 in trivS : UnitS]]}
+      }{[[x1 : F Gf A |-l let x1 : F Gf A be F x0 in weak x0 in trivS : UnitS]]}
+    }{[[. |-l \r x1 : F Gf A . let x1 : F Gf A be F x0 in weak x0 in trivS : (F Gf A) -> (UnitS)]]}
   \end{math}
 \end{center}
+
+$GF$ is a monad:
+\begin{itemize}
+\item Deriving $\eta$:
+  \begin{center}
+    \tiny
+    \begin{math}
+      $$\mprset{flushleft}
+      \inferrule* [right={\tiny imprR}] {
+        $$\mprset{flushleft}
+        \inferrule* [right={\tiny Gr}] {
+          $$\mprset{flushleft}
+          \inferrule* [right={\tiny Gl}] {
+            $$\mprset{flushleft}
+            \inferrule* [right={\tiny Fl}] {
+              $$\mprset{flushleft}
+              \inferrule* [right={\tiny Gl}] {
+                $$\mprset{flushleft}
+                \inferrule* [right={\tiny ax}] {
+                  \,
+                }{[[x0 : F X |-l x0 : F X]]}
+              }{[[x1 : Gf F X |-l let x1 : Gf F X be Gf x0 in x0 : F X]]}
+            }{[[x2 : F Gf F X |-l let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0) : F X]]}
+          }{[[x3 : Gf F Gf F X |-l let x3 : Gf F Gf F X be Gf x2 in (let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0)) : F X]]}
+        }{[[x3 : Gf F Gf F X |-c Gf (let x3 : Gf F Gf F X be Gf x2 in (let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0))) : Gf F X]]}
+      }{[[ . |-c \ x3 : Gf F Gf F X . Gf (let x3 : Gf F Gf F X be Gf x2 in (let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0))) : (Gf F Gf F X) -o (Gf F X)]]}
+    \end{math}
+  \end{center}
+\item Deriving $\mu$:
+  \begin{center}
+    \tiny
+    \begin{math}
+      $$\mprset{flushleft}
+      \inferrule* [right={\tiny imprR}] {
+        $$\mprset{flushleft}
+        \inferrule* [right={\tiny Gr}] {
+          $$\mprset{flushleft}
+          \inferrule* [right={\tiny Fr}] {
+            $$\mprset{flushleft}
+            \inferrule* [right={\tiny ax}] {
+              \,
+            }{[[x : X |-c x : X]]}
+          }{[[x : X |-l F x : F X]]} 
+        }{[[x : X |-c Gf F x : Gf F X]]}
+      }{[[. |-c \ x : X . Gf F x : (X) -o (Gf F X)]]}
+    \end{math}
+  \end{center}
+\end{itemize}
+
+The monad $GF$ is strong:
+\begin{itemize}
+\item Deriving the tensorial strength $\tau$:
+  \begin{center}
+    \tiny
+    \begin{math}
+      $$\mprset{flushleft}
+      \inferrule* [right={\tiny imprR}] {
+        $$\mprset{flushleft}
+        \inferrule* [right={\tiny tenL}] {
+          $$\mprset{flushleft}
+          \inferrule* [right={\tiny beta}] {
+            $$\mprset{flushleft}
+            \inferrule* [right={\tiny Gr}] {
+              $$\mprset{flushleft}
+              \inferrule* [right={\tiny Gl}] {
+                $$\mprset{flushleft}
+                \inferrule* [right={\tiny Fl}] {
+                  $$\mprset{flushleft}
+                  \inferrule* [right={\tiny Fr}] {
+                    $$\mprset{flushleft}
+                    \inferrule* [right={\tiny tenR}] {
+                      $$\mprset{flushleft}
+                      \inferrule* [right={\tiny ax}] {
+                        \,
+                      }{[[x0 : X |-c x0 : X]]}
+                      $$\mprset{flushleft}
+                      \inferrule* [right={\tiny ax}] {
+                        \,
+                      }{[[y0 : Y |-c y0 : Y]]}
+                    }{[[x0 : X , y0 : Y |-c x0 (x) y0 : h(X) (x) Y]]}
+                  }{[[x0 : X , y0 : Y |-l F (x0 (x) y0) : F (h(X) (x) Y)]]}
+                }{[[x0 : X , y1 : F Y |-l let y1 : F Y be F y0 in F (x0 (x) y0) : F (h(X) (x) Y)]]}
+              }{[[y2 : Gf F Y , x0 : X |-l let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0)) : F (h(X) (x) Y)]]}
+            }{[[y2 : Gf F Y , x0 : X |-c Gf (let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0))) : Gf F (h(X) (x) Y)]]}
+          }{[[x1 : X , y3 : Gf F Y |-c ex y3 , x1 with y2 , x0 in (Gf (let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0)))) : Gf F (h(X) (x) Y)]]}
+        }{[[z : h(X) (x) Gf F Y |-c let z : h(X) (x) Gf F Y be x1 (x) y3 in (ex y3 , x1 with y2 , x0 in (Gf (let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0))))) : Gf F (h(X) (x) Y)]]}
+      }{[[.
+|-c \ z : h(X) (x) Gf F Y .
+let z : h(X) (x) Gf F Y be x1 (x) y3 in (ex y3 , x1 with y2 , x0 in (Gf (let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0))))) : (h(X) (x) Gf F Y) -o (Gf F (h(X) (x) Y))]]}
+    \end{math}
+  \end{center}
+\end{itemize}
 

### 2017-08-23 natural-deduction.tex
error in compilation

--- 2017-07-14 natural-deduction.tex
@@
-\subsection{Categorical Interpretation of Natural Deductions}
+The term assignment for natural deduction of the commutative part of the model, i.e. the SMCC of
+the adjunction, is defined in Figure~\ref{fig:elle-nd-smcc}. And the term assignme for the
+non-commutative part, i.e. the Lambek category of the adjunction, is defined in
+Figure~\ref{fig:elle-nd-lambek}. $[[P]]$ and $[[I]]$ are contexts for the non-commutative part
+and they are lists. $[[G]]$ and $[[D]]$ are contexts for the commutative part and they are
+multisets, therefore the following exchange rules are implicit.
+\scriptsize
+\begin{mathpar}
+  \ottdruleTXXbeta{} \qquad\qquad \ottdruleSXXbeta{}
+\end{mathpar}
 
-$T$ rules: in the symmetric monoidal closed category of the adjunction model
+\begin{figure}[!h]
+ \scriptsize
+  \begin{mdframed}
+    \begin{mathpar}
+      \ottdruleTXXid{} \qquad\qquad \ottdruleTXXunitI{} \qquad\qquad \ottdruleTXXunitE{} \\
+      \ottdruleTXXtenI{} \qquad\qquad \ottdruleTXXtenE{} \\
+      \ottdruleTXXimpI{} \qquad\qquad \ottdruleTXXimpE{} \qquad\qquad \ottdruleTXXGI{}
+    \end{mathpar}
+  \end{mdframed}
+\caption{Commutative Part}
+\label{fig:elle-nd-smcc}
+\end{figure}
 
-T\_identity: $id_X:X\rightarrow X$
+\begin{figure}[!h]
+ \scriptsize
+  \begin{mdframed}
+    \begin{mathpar}
+      \ottdruleSXXid{} \qquad\qquad \ottdruleSXXunitI{} \qquad\qquad \ottdruleSXXunitEOne{} \\
+      \ottdruleSXXunitETwo{} \qquad\qquad \ottdruleSXXunitEThree{} \\
+      \ottdruleSXXunitEFour{} \qquad\qquad \ottdruleSXXtenI{} \\
+      \ottdruleSXXtenEOne{} \qquad\qquad \ottdruleSXXtenETwo{} \\
+      \ottdruleSXXimprI{} \qquad\qquad \ottdruleSXXimprE{} \qquad\qquad \ottdruleSXXimplI{} \\
+      \ottdruleSXXimplE{} \qquad\qquad \ottdruleSXXFI{} \\
+      \ottdruleSXXFE{} \qquad\qquad \ottdruleSXXGE{}
+    \end{mathpar}
+  \end{mdframed}
+\caption{Non-Commutative Part}
+\label{fig:elle-nd-lambek}
+\end{figure}
 
-T\_unitI:
-
-T\_unitE: given $t_1:\Delta\rightarrow Unit$ and $t_2:\Gamma\rightarrow Y$, returns
-$\lambda_Y\circ(t_1\otimes t_2):\Gamma\otimes\Delta\rightarrow Unit\otimes Y\rightarrow Y$
-
-T\_tenI: given $t_1:\Gamma\rightarrow X$ and $t_2:\Delta\rightarrow Y$, returns
-$t_1\otimes t_2:\Gamma\otimes\Delta\rightarrow X\otimes Y$
-
-T\_tenE: given $t_1:\Gamma\rightarrow X\otimes Y$ and
-$t_2:\Delta\otimes X\otimes Y\rightarrow Z$, returns \\
-$t_2\circ\e{X\otimes Y,\Delta}\circ t_1\otimes id_\Delta:\Gamma\otimes\Delta\rightarrow(X\otimes Y)\otimes\Delta\rightarrow\Delta\otimes(X\otimes Y)\rightarrow Z$
-
-T\_implI:
-
-T\_implE:
-
-T\_imprI:
-
-T\_imprE:
-
-T\_GI: given $s:FX_1\otimes'...\otimes' FX_n\rightarrow A$, returns \\
-$Gs\circ G\m{}^{-1}\circ\eta:X_1\otimes...\otimes X_n\rightarrow GF(X_1\otimes...\otimes X_n)\rightarrow G(FX_1\otimes'...\otimes'FX_n)\rightarrow GA$
-
-S rules: in the Lambek category of the adjunction model
-
-S\_identity: $id_A:A\rightarrow A$
-
-S\_unitI:
-
-S\_unitE:
-
-\subsection{Normaalization and Reduction}
+\begin{center}
+  \tiny
+  \begin{math}
+  $$\mprset{flushleft}
+  \inferrule* [right={\tiny imprI}] {
+    $$\mprset{flushleft}
+    \inferrule* [right={\tiny tenE2}] {
+      $$\mprset{flushleft}
+      \inferrule* [right={\tiny id}] {
+        \,
+      }{[[z : h(F Gf A) (>) F Gf B |-l z : h(F Gf A) (>) F Gf B]]}
+        $$\mprset{flushleft}
+        \inferrule* [right={\tiny FE}] {
+          $$\mprset{flushleft}
+          \inferrule* [right={\tiny id}] {
+            \,
+          }{[[x2 : F Gf A |-l x2 : F Gf A]]}
+            $$\mprset{flushleft}
+            \inferrule* [right={\tiny FE}] {
+              $$\mprset{flushleft}
+              \inferrule* [right={\tiny id}] {
+                \,
+              }{[[y2 : F Gf B |-l y2 : F Gf B]]}
+              \inferrule* [right={\tiny beta}] {
+                $$\mprset{flushleft}
+                \inferrule* [right={\tiny FE}] {
+                  $$\mprset{flushleft}
+                  \inferrule* [right={\tiny FI}] {
+                    $$\mprset{flushleft}
+                    \inferrule* [right={\tiny id}] {
+                      \,
+                    }{[[y0 : Gf B |-c y0 : Gf B]]}
+                  }{[[y0 : Gf B |-l F y0 : F Gf B]]}
+                  $$\mprset{flushleft}
+                  \inferrule* [right={\tiny FI}] {
+                    $$\mprset{flushleft}
+                    \inferrule* [right={\tiny id}] {
+                      \,
+                    }{[[x0 : Gf A |-c x0 : Gf A]]}
+                  }{[[x0 : Gf A |-l F x0 : F Gf A]]}
+                }{[[y0 : Gf B, x0 : Gf A |-l h(F y0) (>) F x0 : h(F Gf B) (>) F Gf A]]}
+              }{[[x1 : Gf A, y1 : Gf B |-l ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0) : h(F Gf B) (>) F Gf A]]}
+            }{[[x1 : Gf A , y2 : F Gf B |-l let F y1 : F Gf B be y2 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0)) : h(F Gf B) (>) F Gf A]]}
+          }{[[x2 : F Gf A , y2 : F Gf B |-l let F x1 : F Gf A be x2 in (let F y1 : F Gf B be y2 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0))) : h(F Gf B) (>) F Gf A]]}
+        }{[[z : h(F Gf A) (>) F Gf B |-l let z : h(F Gf A) (>) F Gf B be x2 (>) y2 in (let F x1 : F Gf A be x2 in (let F y1 : F Gf B be y2 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0)))) : h(F Gf B) (>) F Gf A]]}
+      }{[[ .
+|-l \r z : h(F Gf A) (>) F Gf B.let z : h(F Gf A) (>) F Gf B be x2 (>) y2 in (let F x1 : F Gf A be x2 in (let F y1 : F Gf B be y2 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0)))) : (h(F Gf A) (>) F Gf B) -> (h(F Gf B) (>) F Gf A)]]}
+  \end{math}
+\end{center}

### 2017-08-29 introduction.tex
introduction + related work

Linear logic is a well-known resource-sensitive logic. It has been used extensively to model
attack trees. This paper concerns a non-commutative variant of linear logic and combines the
non-commutative variant with Girard's linear logic \cite{}. We will only focus on the
multiplicative (i.e. $\otimes$, $\multimap$) part of linear logic for simplicity. We construct
the non-commutative variant by using a non-commutative tensor product $\tri$ instead of the
commutative $\otimes$, and two implications $\rto$ and $\lto$ for the two directions of
$\multimap$.

We model the non-commutative linear logic categorically using an ajunction between a symmetric
monoidal closed category and a Lambek category. Our categorial adjoint model has a similar
structure as Benton's adjoint model \cite{}, in which the multiplicative part of intuitionistic
linear logic (ILL) is modeled using an adjunction between a cartesian closed category and a
symmetric monoidal closed category. On the other hand, Moggi \cite{} uses monad models to map
intuitionistic logic into ILL. As discussed in \cite{benton+Wadler}, Benton's adjoint models
only gives rise to commutative monad models and the non-commutative part remained as an open
problem. Therefore, by combining our adjoint models with Benton's, we would be able to get
non-commutative monad models and thus non-commutative ILL.

The rest of the paper is organized as follows. Section~\ref{sec:related_work} discusses existing
approaches on constructing non-commutative linear logic.
Section~\ref{sec:category_theory_basics} contains the basic definitions in category theory that
we will be using in our adjoint model. Familiar readers may skip this section.
Section~\ref{sec:adjoint_model} contains the definition and essential properties of our adjoint
model. Section~\ref{sec:logic} discusses the sequent calculus and natural deduction rules for
our non-commutative linear logic. We prove that our sequent calculus has the property of
cut-elimination and the natural deduction is strongly normalizing. Section~\ref{sec:combining}
talks about the preliminary result after combing our non-commutative model with Benton's
commutative model. Section~\ref{sec:applications} briefly mentions how our model could be used
in attack trees and other areas. Section~\ref{sec:conclusion} concludes this paper with future
work.

### 2017-08-29 natural-deduction.tex
introduction + related work

@@
 non-commutative part, i.e. the Lambek category of the adjunction, is defined in
-Figure~\ref{fig:elle-nd-lambek}. $[[P]]$ and $[[I]]$ are contexts for the non-commutative part
-and they are lists. $[[G]]$ and $[[D]]$ are contexts for the commutative part and they are
-multisets, therefore the following exchange rules are implicit.
+Figure~\ref{fig:elle-nd-lambek}. $[[P]]$ and $[[I]]$ are contexts for the commutative part
+and they are multisets. $[[G]]$ and $[[D]]$ are contexts for the mix of the commutative part and
+the non-commutative part, and they are lists. Therefore the following exchange rule is implicit.
+
+\begin{figure}[!h]
   \scriptsize
   \begin{mathpar}
-  \ottdruleTXXbeta{} \qquad\qquad \ottdruleSXXbeta{}
+    \NDdruleTXXbeta{}
   \end{mathpar}
+\end{figure}
 
@@
     \begin{mathpar}
-      \ottdruleTXXid{} \qquad\qquad \ottdruleTXXunitI{} \qquad\qquad \ottdruleTXXunitE{} \\
-      \ottdruleTXXtenI{} \qquad\qquad \ottdruleTXXtenE{} \\
-      \ottdruleTXXimpI{} \qquad\qquad \ottdruleTXXimpE{} \qquad\qquad \ottdruleTXXGI{}
+      \NDdruleTXXid{} \qquad\qquad \NDdruleTXXunitI{} \qquad\qquad \NDdruleTXXunitE{} \\
+      \NDdruleTXXtenI{} \qquad\qquad \NDdruleTXXtenE{} \\
+      \NDdruleTXXimpI{} \qquad\qquad \NDdruleTXXimpE{} \qquad\qquad \NDdruleTXXGI{} \\
+      \NDdruleSXXbeta{}
     \end{mathpar}
@@
     \begin{mathpar}
-      \ottdruleSXXid{} \qquad\qquad \ottdruleSXXunitI{} \qquad\qquad \ottdruleSXXunitEOne{} \\
-      \ottdruleSXXunitETwo{} \qquad\qquad \ottdruleSXXunitEThree{} \\
-      \ottdruleSXXunitEFour{} \qquad\qquad \ottdruleSXXtenI{} \\
-      \ottdruleSXXtenEOne{} \qquad\qquad \ottdruleSXXtenETwo{} \\
-      \ottdruleSXXimprI{} \qquad\qquad \ottdruleSXXimprE{} \qquad\qquad \ottdruleSXXimplI{} \\
-      \ottdruleSXXimplE{} \qquad\qquad \ottdruleSXXFI{} \\
-      \ottdruleSXXFE{} \qquad\qquad \ottdruleSXXGE{}
+      \NDdruleSXXid{} \qquad\qquad \NDdruleSXXunitI{} \qquad\qquad \NDdruleSXXunitEOne{} \\
+      \NDdruleSXXunitEOne{} \qquad\qquad \NDdruleSXXunitETwo{} \\
+      \NDdruleSXXtenI{} \qquad\qquad \NDdruleSXXtenEOne{} \\
+      \NDdruleSXXtenETwo{} \qquad\qquad \NDdruleSXXimprI{} \\
+      \NDdruleSXXimprE{} \qquad\qquad \NDdruleSXXimplI{} \\
+      \NDdruleSXXimplE{} \qquad\qquad \NDdruleSXXGE{} \qquad\qquad \NDdruleSXXFI{} \\
+      \NDdruleSXXFE{}
     \end{mathpar}
@@
 \end{figure}
+
+We could derive exchange comonadically as follows:
 
@@
 \end{center}
+
+We also have the three cut rules derivable in the natural deduction:
+
+\begin{figure}[!h]
+  \scriptsize
+  \begin{mathpar}
+    \NDdruleTXXcut{} \qquad\qquad \NDdruleSXXcutOne{} \qquad\qquad \NDdruleSXXcutTwo{}
+  \end{mathpar}
+\end{figure}
+
+\begin{center}
+  \tiny
+  \begin{math}
+  $$\mprset{flushleft}
+  \inferrule* [right={\tiny FI}] {
+    {[[I |-c t : X]]}
+  }{[[I |-l F t : F X]]}
+  \end{math}
+\end{center}

### 2017-08-29 related-work.tex
introduction + related work

Polakow and Pfenning discuseed Ordered Linear Logic (OLL) \cite{}, which combines
intuitionistic, commutative linear and non-commutative linear logic, OLL contains sequents of
the form $\Gamma,\Delta,\Omega\vdash A$, where $\Gamma$ is a multiset of intuitionistic
assumptions, $\Delta$ is a multiset of commutative linear assumptions, and $\Omega$ is a list of
non-commutative linear assumptions. OLL contains logical connectives from all three the logics.
Therefore, our non-commutative adjoint model is a part of OLL and after combining with Benton's
commutative adjoint model, we would get a simplification of OLL.

Greco and Palmigiano \cite{} also presents a variant of the multiplicative fragment of
non-commutative ILL. But they focus on proper display calculi while we use sequent calculi.

### 2017-08-29 sequent-calculus-ott.tex
introduction + related work

--- 2017-07-14 natural-deduction.tex
@@
-\subsection{Categorical Interpretation of Natural Deductions}
+The term assignment for sequent calculus of the commutative part of the model, i.e. the SMCC of
+the adjunction, is defined in Figure~\ref{fig:elle-smcc}. And the term assignme for the
+non-commutative part, i.e. the Lambek category of the adjunction, is defined in
+Figure~\ref{fig:elle-lambek}. $\Psi$ and $\Phi$ are contexts for the non-commutative part
+and they are lists. $\Gamma$ and $\Delta$ are contexts for the commutative part and they are
+multisets, therefore the following exchange rules are implicit.
 
-$T$ rules: in the symmetric monoidal closed category of the adjunction model
+\begin{mathpar}
+\scriptsize
+\end{mathpar}
 
-T\_identity: $id_X:X\rightarrow X$
-
-T\_unitI:
-
-T\_unitE: given $t_1:\Delta\rightarrow Unit$ and $t_2:\Gamma\rightarrow Y$, returns
-$\lambda_Y\circ(t_1\otimes t_2):\Gamma\otimes\Delta\rightarrow Unit\otimes Y\rightarrow Y$
-
-T\_tenI: given $t_1:\Gamma\rightarrow X$ and $t_2:\Delta\rightarrow Y$, returns
-$t_1\otimes t_2:\Gamma\otimes\Delta\rightarrow X\otimes Y$
-
-T\_tenE: given $t_1:\Gamma\rightarrow X\otimes Y$ and
-$t_2:\Delta\otimes X\otimes Y\rightarrow Z$, returns \\
-$t_2\circ\e{X\otimes Y,\Delta}\circ t_1\otimes id_\Delta:\Gamma\otimes\Delta\rightarrow(X\otimes Y)\otimes\Delta\rightarrow\Delta\otimes(X\otimes Y)\rightarrow Z$
-
-T\_implI:
-
-T\_implE:
-
-T\_imprI:
-
-T\_imprE:
-
-T\_GI: given $s:FX_1\otimes'...\otimes' FX_n\rightarrow A$, returns \\
-$Gs\circ G\m{}^{-1}\circ\eta:X_1\otimes...\otimes X_n\rightarrow GF(X_1\otimes...\otimes X_n)\rightarrow G(FX_1\otimes'...\otimes'FX_n)\rightarrow GA$
-
-S rules: in the Lambek category of the adjunction model
-
-S\_identity: $id_A:A\rightarrow A$
-
-S\_unitI:
-
-S\_unitE:
-
-\subsection{Normaalization and Reduction}
+\begin{figure}[!h]
+ \scriptsize
+  \begin{mdframed}
+    \begin{mathpar}
+    \end{mathpar}
+  \end{mdframed}
+\caption{Commutative Part}
+\label{fig:elle-nd-smcc}
+\end{figure}

### 2017-08-30 category-theory-basics.tex
Add texts

@@
+This section contains the basic definitions in category theory that we will be using in our
+adjoint model. Our model is based on special kinds of monoidal categories: Lambek categories and
+symmetric monoidal closed categories and Lambek categories, as defined in
+Definitions~\ref{def:lambek-cat} and~\ref{def:smcc}.
+
 \begin{definition}
@@
 \begin{definition}
+\label{def:lambek-cat}
   A \textbf{Lambek category} (or a \textbf{biclosed monoidal category}) is a monoidal category
@@
 
+The relation between SMMCs and Lambek categories are demonstrated in
+Lemma~\ref{lemma:internal-homs-collapse} and Corollary~\ref{corollary:LC-with-ex-mc}.
+
 \begin{lemma}
@@
 \end{proof}
+
 \begin{corollary}
@@
 
+The essential component in our non-commutative adjoint model is a monoidal adjunction, defined
+in Definitions~\ref{def:monoidal-functor}-\ref{def:monoidal-adjunction}.
+
 \begin{definition}
+\label{def:monoidal-functor}
   Let $(\cat{M},\tri,I,\alpha,\lambda,\rho)$ and
@@
 \begin{definition}
+\label{def:monoidal-adjunction}
   Let $(\cat{M},\tri,I,\alpha,\lambda,\rho)$ and
@@
 
+In Moggi's monad model \cite{}, the monad is required to be strong, as defined in
+Definitions~\ref{def:monad} and~\ref{def:strong-monad}.
+
 \begin{definition}
+\label{def:monad}
   Let $\cat{C}$ be a category. A \textbf{monad} on $\cat{C}$ consists of an endofunctor

### 2017-08-30 natural-deduction-ott.tex
Makefile error fixed

The term assignment for natural deduction of the commutative part of the model, i.e. the SMCC of
the adjunction, is defined in Figure~\ref{fig:elle-nd-smcc}. And the term assignme for the
non-commutative part, i.e. the Lambek category of the adjunction, is defined in
Figure~\ref{fig:elle-nd-lambek}. $\Psi$ and $\Phi$ are contexts for the commutative part
and they are multisets. $\Gamma$ and $\Delta$ are contexts for the mix of the commutative part and
the non-commutative part, and they are lists. Therefore the following exchange rule is implicit.

\begin{figure}[!h]
  \scriptsize
  \begin{mathpar}
    \NDdruleTXXbeta{}
  \end{mathpar}
\end{figure}

\begin{figure}[!h]
  \scriptsize
  \begin{mdframed}
    \begin{mathpar}
      \NDdruleTXXid{} \qquad\qquad \NDdruleTXXunitI{} \qquad\qquad \NDdruleTXXunitE{} \\
      \NDdruleTXXtenI{} \qquad\qquad \NDdruleTXXtenE{} \\
      \NDdruleTXXimpI{} \qquad\qquad \NDdruleTXXimpE{} \qquad\qquad \NDdruleTXXGI{} \\
      \NDdruleSXXbeta{}
    \end{mathpar}
  \end{mdframed}
\caption{Commutative Part}
\label{fig:elle-nd-smcc}
\end{figure}

\begin{figure}[!h]
 \scriptsize
  \begin{mdframed}
    \begin{mathpar}
      \NDdruleSXXid{} \qquad\qquad \NDdruleSXXunitI{} \qquad\qquad \NDdruleSXXunitEOne{} \\
      \NDdruleSXXunitEOne{} \qquad\qquad \NDdruleSXXunitETwo{} \\
      \NDdruleSXXtenI{} \qquad\qquad \NDdruleSXXtenEOne{} \\
      \NDdruleSXXtenETwo{} \qquad\qquad \NDdruleSXXimprI{} \\
      \NDdruleSXXimprE{} \qquad\qquad \NDdruleSXXimplI{} \\
      \NDdruleSXXimplE{} \qquad\qquad \NDdruleSXXGE{} \qquad\qquad \NDdruleSXXFI{} \\
      \NDdruleSXXFE{}
    \end{mathpar}
  \end{mdframed}
\caption{Non-Commutative Part}
\label{fig:elle-nd-lambek}
\end{figure}

We could derive exchange comonadically as follows:

\begin{center}
  \tiny
  \begin{math}
  $$\mprset{flushleft}
  \inferrule* [right={\tiny imprI}] {
    $$\mprset{flushleft}
    \inferrule* [right={\tiny tenE2}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny id}] {
        \,
      }{\NDmv{z}  \NDsym{:}    \mathsf{F}  \mathsf{G} \NDnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \NDnt{B}    \vdash_\mathcal{L}  \NDmv{z}  \NDsym{:}    \mathsf{F}  \mathsf{G} \NDnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \NDnt{B}  }
        $$\mprset{flushleft}
        \inferrule* [right={\tiny FE}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny id}] {
            \,
          }{\NDmv{x_{{\mathrm{2}}}}  \NDsym{:}   \mathsf{F}  \mathsf{G} \NDnt{A}    \vdash_\mathcal{L}  \NDmv{x_{{\mathrm{2}}}}  \NDsym{:}   \mathsf{F}  \mathsf{G} \NDnt{A}  }
            $$\mprset{flushleft}
            \inferrule* [right={\tiny FE}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny id}] {
                \,
              }{\NDmv{y_{{\mathrm{2}}}}  \NDsym{:}   \mathsf{F}  \mathsf{G} \NDnt{B}    \vdash_\mathcal{L}  \NDmv{y_{{\mathrm{2}}}}  \NDsym{:}   \mathsf{F}  \mathsf{G} \NDnt{B}  }
              \inferrule* [right={\tiny beta}] {
                $$\mprset{flushleft}
                \inferrule* [right={\tiny FE}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny FI}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny id}] {
                      \,
                    }{\NDmv{y_{{\mathrm{0}}}}  \NDsym{:}   \mathsf{G} \NDnt{B}   \vdash_\mathcal{C}  \NDmv{y_{{\mathrm{0}}}}  \NDsym{:}   \mathsf{G} \NDnt{B} }
                  }{\NDmv{y_{{\mathrm{0}}}}  \NDsym{:}   \mathsf{G} \NDnt{B}   \vdash_\mathcal{L}   \mathsf{F} \NDmv{y_{{\mathrm{0}}}}   \NDsym{:}   \mathsf{F}  \mathsf{G} \NDnt{B}  }
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny FI}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny id}] {
                      \,
                    }{\NDmv{x_{{\mathrm{0}}}}  \NDsym{:}   \mathsf{G} \NDnt{A}   \vdash_\mathcal{C}  \NDmv{x_{{\mathrm{0}}}}  \NDsym{:}   \mathsf{G} \NDnt{A} }
                  }{\NDmv{x_{{\mathrm{0}}}}  \NDsym{:}   \mathsf{G} \NDnt{A}   \vdash_\mathcal{L}   \mathsf{F} \NDmv{x_{{\mathrm{0}}}}   \NDsym{:}   \mathsf{F}  \mathsf{G} \NDnt{A}  }
                }{\NDmv{y_{{\mathrm{0}}}}  \NDsym{:}   \mathsf{G} \NDnt{B}   \NDsym{,}  \NDmv{x_{{\mathrm{0}}}}  \NDsym{:}   \mathsf{G} \NDnt{A}   \vdash_\mathcal{L}    \mathsf{F} \NDmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \NDmv{x_{{\mathrm{0}}}}   \NDsym{:}    \mathsf{F}  \mathsf{G} \NDnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \NDnt{A}  }
              }{\NDmv{x_{{\mathrm{1}}}}  \NDsym{:}   \mathsf{G} \NDnt{A}   \NDsym{,}  \NDmv{y_{{\mathrm{1}}}}  \NDsym{:}   \mathsf{G} \NDnt{B}   \vdash_\mathcal{L}   \mathsf{ex}\, \NDmv{y_{{\mathrm{1}}}} , \NDmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \NDmv{y_{{\mathrm{0}}}} , \NDmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \NDsym{(}    \mathsf{F} \NDmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \NDmv{x_{{\mathrm{0}}}}   \NDsym{)}   \NDsym{:}    \mathsf{F}  \mathsf{G} \NDnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \NDnt{A}  }
            }{\NDmv{x_{{\mathrm{1}}}}  \NDsym{:}   \mathsf{G} \NDnt{A}   \NDsym{,}  \NDmv{y_{{\mathrm{2}}}}  \NDsym{:}   \mathsf{F}  \mathsf{G} \NDnt{B}    \vdash_\mathcal{L}   \mathsf{let}\,  \mathsf{F} \NDmv{y_{{\mathrm{1}}}}   :   \mathsf{F}  \mathsf{G} \NDnt{B}   \,\mathsf{be}\, \NDmv{y_{{\mathrm{2}}}} \,\mathsf{in}\, \NDsym{(}   \mathsf{ex}\, \NDmv{y_{{\mathrm{1}}}} , \NDmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \NDmv{y_{{\mathrm{0}}}} , \NDmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \NDsym{(}    \mathsf{F} \NDmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \NDmv{x_{{\mathrm{0}}}}   \NDsym{)}   \NDsym{)}   \NDsym{:}    \mathsf{F}  \mathsf{G} \NDnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \NDnt{A}  }
          }{\NDmv{x_{{\mathrm{2}}}}  \NDsym{:}   \mathsf{F}  \mathsf{G} \NDnt{A}    \NDsym{,}  \NDmv{y_{{\mathrm{2}}}}  \NDsym{:}   \mathsf{F}  \mathsf{G} \NDnt{B}    \vdash_\mathcal{L}   \mathsf{let}\,  \mathsf{F} \NDmv{x_{{\mathrm{1}}}}   :   \mathsf{F}  \mathsf{G} \NDnt{A}   \,\mathsf{be}\, \NDmv{x_{{\mathrm{2}}}} \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\,  \mathsf{F} \NDmv{y_{{\mathrm{1}}}}   :   \mathsf{F}  \mathsf{G} \NDnt{B}   \,\mathsf{be}\, \NDmv{y_{{\mathrm{2}}}} \,\mathsf{in}\, \NDsym{(}   \mathsf{ex}\, \NDmv{y_{{\mathrm{1}}}} , \NDmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \NDmv{y_{{\mathrm{0}}}} , \NDmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \NDsym{(}    \mathsf{F} \NDmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \NDmv{x_{{\mathrm{0}}}}   \NDsym{)}   \NDsym{)}   \NDsym{)}   \NDsym{:}    \mathsf{F}  \mathsf{G} \NDnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \NDnt{A}  }
        }{\NDmv{z}  \NDsym{:}    \mathsf{F}  \mathsf{G} \NDnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \NDnt{B}    \vdash_\mathcal{L}   \mathsf{let}\, \NDmv{z}  :    \mathsf{F}  \mathsf{G} \NDnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \NDnt{B}   \,\mathsf{be}\, \NDmv{x_{{\mathrm{2}}}}  \triangleright  \NDmv{y_{{\mathrm{2}}}} \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\,  \mathsf{F} \NDmv{x_{{\mathrm{1}}}}   :   \mathsf{F}  \mathsf{G} \NDnt{A}   \,\mathsf{be}\, \NDmv{x_{{\mathrm{2}}}} \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\,  \mathsf{F} \NDmv{y_{{\mathrm{1}}}}   :   \mathsf{F}  \mathsf{G} \NDnt{B}   \,\mathsf{be}\, \NDmv{y_{{\mathrm{2}}}} \,\mathsf{in}\, \NDsym{(}   \mathsf{ex}\, \NDmv{y_{{\mathrm{1}}}} , \NDmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \NDmv{y_{{\mathrm{0}}}} , \NDmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \NDsym{(}    \mathsf{F} \NDmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \NDmv{x_{{\mathrm{0}}}}   \NDsym{)}   \NDsym{)}   \NDsym{)}   \NDsym{)}   \NDsym{:}    \mathsf{F}  \mathsf{G} \NDnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \NDnt{A}  }
      }{ \cdot   \vdash_\mathcal{L}   \lambda_r  \NDmv{z}  :    \mathsf{F}  \mathsf{G} \NDnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \NDnt{B}   .  \mathsf{let}\, \NDmv{z}  :    \mathsf{F}  \mathsf{G} \NDnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \NDnt{B}   \,\mathsf{be}\, \NDmv{x_{{\mathrm{2}}}}  \triangleright  \NDmv{y_{{\mathrm{2}}}} \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\,  \mathsf{F} \NDmv{x_{{\mathrm{1}}}}   :   \mathsf{F}  \mathsf{G} \NDnt{A}   \,\mathsf{be}\, \NDmv{x_{{\mathrm{2}}}} \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\,  \mathsf{F} \NDmv{y_{{\mathrm{1}}}}   :   \mathsf{F}  \mathsf{G} \NDnt{B}   \,\mathsf{be}\, \NDmv{y_{{\mathrm{2}}}} \,\mathsf{in}\, \NDsym{(}   \mathsf{ex}\, \NDmv{y_{{\mathrm{1}}}} , \NDmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \NDmv{y_{{\mathrm{0}}}} , \NDmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \NDsym{(}    \mathsf{F} \NDmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \NDmv{x_{{\mathrm{0}}}}   \NDsym{)}   \NDsym{)}   \NDsym{)}   \NDsym{)}    \NDsym{:}  \NDsym{(}    \mathsf{F}  \mathsf{G} \NDnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \NDnt{B}    \NDsym{)}  \rightharpoonup  \NDsym{(}    \mathsf{F}  \mathsf{G} \NDnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \NDnt{A}    \NDsym{)}}
  \end{math}
\end{center}

We also have the three cut rules derivable in the natural deduction:

\begin{figure}[!h]
  \scriptsize
  \begin{mathpar}
    \NDdruleTXXcut{} \qquad\qquad \NDdruleSXXcutOne{} \qquad\qquad \NDdruleSXXcutTwo{}
  \end{mathpar}
\end{figure}

\begin{center}
  \tiny
  \begin{math}
  $$\mprset{flushleft}
  \inferrule* [right={\tiny FI}] {
    {\Phi  \vdash_\mathcal{C}  \NDnt{t}  \NDsym{:}  \NDnt{X}}
  }{\Phi  \vdash_\mathcal{L}   \mathsf{F} \NDnt{t}   \NDsym{:}   \mathsf{F} \NDnt{X} }
  \end{math}
\end{center}

### 2017-11-06 Elle/Elle-output.tex

@@
                 \,
-              }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
-            }{\texttt{\textcolor{red}{<<no parses (char 10): y0 : Gf B;*** . \mbox{$\mid$}- F y0 : F Gf B >>}}}
+              }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash_\mathcal{C}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
+            }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash_\mathcal{L}   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}  }
             \\
@@
                 \,
-              }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
-            }{\texttt{\textcolor{red}{<<no parses (char 10): x0 : Gf A;*** . \mbox{$\mid$}- F x0 : F Gf A >>}}}
-          }{\texttt{\textcolor{red}{<<no parses (char 22): y0 : Gf B, x0 : Gf A ;*** . \mbox{$\mid$}- h(F y0) (x) F x0 : h(F Gf B) (x) F Gf A >>}}}
-        }{\texttt{\textcolor{red}{<<no parses (char 22): x1 : Gf A, y1 : Gf B ;*** . \mbox{$\mid$}- ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0) : h(F Gf B) (x) F Gf A >>}}}
-      }{\texttt{\textcolor{red}{<<no parses (char 11): x1 : Gf A ;*** y2 : F Gf B \mbox{$\mid$}- let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)) : h(F Gf B) (x) F Gf A >>}}}
-    }{\texttt{\textcolor{red}{<<no parses (char 3): .
-;*** x2 : F Gf A, y2 : F Gf B \mbox{$\mid$}- let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0))) : h(F Gf B) (x) F Gf A >>}}}
-    }{\texttt{\textcolor{red}{<<no parses (char 3): .
-;*** z : h(F Gf A) (x) F Gf B \mbox{$\mid$}- let z : h(F Gf A) (x) F Gf B be x2 (x) y2 in (let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)))) : (h(F Gf B) (x) F Gf A) >>}}}
-    }{\texttt{\textcolor{red}{<<no parses (char 3): .
-;*** .
-\mbox{$\mid$}- \mbox{$\backslash{}$}l z : h(F Gf A) (x) F Gf B .
-let z : h(F Gf A) (x) F Gf B be x2 (x) y2 in (let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)))) : (h(F Gf A) (x) F Gf B) -> (h(F Gf B) (x) F Gf A) >>}}}
+              }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{C}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
+            }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+          }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+        }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash_\mathcal{L}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+      }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+    }{\ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{,}  \ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+    }{\ottmv{z}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{2}}}}  \triangleright  \ottmv{y_{{\mathrm{2}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
+    }{ \cdot   \vdash_\mathcal{L}   \lambda_r  \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}   .
+\mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{2}}}}  \triangleright  \ottmv{y_{{\mathrm{2}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \rightharpoonup  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
   \end{math}
@@
                     \,
-                  }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
-                }{\texttt{\textcolor{red}{<<no parses (char 10): x1 : Gf A;*** . \mbox{$\mid$}- F x1 : F Gf A >>}}}
+                  }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{C}  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
+                }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
                 \\
@@
                       \,
-                    }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
-                  }{\texttt{\textcolor{red}{<<no parses (char 10): y0 : Gf B;*** . \mbox{$\mid$}- F y0 : F Gf B >>}}}
+                    }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash_\mathcal{C}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
+                  }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash_\mathcal{L}   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}  }
                   \\
@@
                       \,
-                    }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
-                  }{\texttt{\textcolor{red}{<<no parses (char 10): x0 : Gf A;*** . \mbox{$\mid$}- F x0 : F Gf A >>}}}
-                }{\texttt{\textcolor{red}{<<no parses (char 22): y0 : Gf B, x0 : Gf A ;*** . \mbox{$\mid$}- h(F y0) (x) F x0 : h(F Gf B) (x) F Gf A >>}}}
-              }{\texttt{\textcolor{red}{<<no parses (char 33): x1 : Gf A, y0 : Gf B, x0 : Gf A ;*** . \mbox{$\mid$}- h(F x1) (x) (h(F y0) (x) F x0) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
-            }{\texttt{\textcolor{red}{<<no parses (char 22): y0 : Gf B, x2 : Gf A ;*** .
-\mbox{$\mid$}- contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0)) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
-          }{\texttt{\textcolor{red}{<<no parses (char 11): y0 : Gf B ;*** x3 : F Gf A \mbox{$\mid$}- let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
-        }{\texttt{\textcolor{red}{<<no parses (char 3): .
-;*** y1 : F Gf B, x3 : F Gf A \mbox{$\mid$}- let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0)))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
-      }{\texttt{\textcolor{red}{<<no parses (char 3): .
-;*** z : h(F Gf B) (x) F Gf A \mbox{$\mid$}- let z : h(F Gf B) (x) F Gf A be y1 (x) x3 in (let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
-    }{\texttt{\textcolor{red}{<<no parses (char 3): .
-;*** .
-\mbox{$\mid$}- \mbox{$\backslash{}$}l z : h(F Gf B) (x) F Gf A .
-let z : h(F Gf B) (x) F Gf A be y1 (x) x3 in (let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))))) : (h(F Gf B) (x) F Gf A) -> (h(F Gf A) (x) (h(F Gf B) (x) F Gf A)) >>}}}
+                    }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{C}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
+                  }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+                }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+              }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \triangleright  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
+            }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \triangleright  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
+          }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \triangleright  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
+        }{\ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{,}  \ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \triangleright  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
+      }{\ottmv{z}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\, \ottmv{y_{{\mathrm{1}}}}  \triangleright  \ottmv{x_{{\mathrm{3}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \triangleright  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
+    }{ \cdot   \vdash_\mathcal{L}   \lambda_r  \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}   .
+\mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\, \ottmv{y_{{\mathrm{1}}}}  \triangleright  \ottmv{x_{{\mathrm{3}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \triangleright  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}  \rightharpoonup  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}  \ottsym{)}}
   \end{math}
@@
                       \,
-                    }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
-                  }{\texttt{\textcolor{red}{<<no parses (char 10): x0 : Gf A;*** . \mbox{$\mid$}- F x0 : F Gf A >>}}}
+                    }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{C}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
+                  }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
                   \\
@@
                       \,
-                    }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
-                  }{\texttt{\textcolor{red}{<<no parses (char 10): y0 : Gf B;*** . \mbox{$\mid$}- F y0 : F Gf B >>}}}
-                }{\texttt{\textcolor{red}{<<no parses (char 22): x0 : Gf A, y0 : Gf B ;*** . \mbox{$\mid$}- h(F x0) (x) F y0 : h(F Gf A) (x) F Gf B >>}}}
+                    }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash_\mathcal{C}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
+                  }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash_\mathcal{L}   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}  }
+                }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash_\mathcal{L}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}  }
                 \\
@@
                     \,
-                  }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
-                }{\texttt{\textcolor{red}{<<no parses (char 10): x1 : Gf A;*** . \mbox{$\mid$}- F x1 : F Gf A >>}}}
-              }{\texttt{\textcolor{red}{<<no parses (char 33): x0 : Gf A, y0 : Gf B, x1 : Gf A ;*** . \mbox{$\mid$}- (h(F x0) (x) F y0) (x) F x1 : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
-            }{\texttt{\textcolor{red}{<<no parses (char 22): x2 : Gf A, y0 : Gf B ;*** . \mbox{$\mid$}- contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1) : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
-          }{\texttt{\textcolor{red}{<<no parses (char 11): x2 : Gf A ;*** y1 : F Gf B \mbox{$\mid$}- let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1)) : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
-        }{\texttt{\textcolor{red}{<<no parses (char 3): .
-;*** x3 : F Gf A, y1 : F Gf B \mbox{$\mid$}- let x3 : F Gf A be F x2 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1))) : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
-      }{\texttt{\textcolor{red}{<<no parses (char 3): .
-;*** z : h(F Gf A) (x) F Gf B \mbox{$\mid$}- let z : h(F Gf A) (x) F Gf B be x3 (x) y1 in (let x3 : F Gf A be F x2 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1)))) : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
-    }{\texttt{\textcolor{red}{<<no parses (char 3): .
-;*** .
-\mbox{$\mid$}- \mbox{$\backslash{}$}l z : h(F Gf A) (x) F Gf B .
-let z : h(F Gf A) (x) F Gf B be x3 (x) y1 in (let x3 : F Gf A be F x3 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in (h(F x0) (x) (h(F y0) (x) F x1))))) : (h(F Gf A) (x) F Gf B) -> ((h(F Gf A) (x) F Gf B) (x) F Gf A) >>}}}
+                  }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{C}  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
+                }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+              }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+            }{\ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash_\mathcal{L}   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+          }{\ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+        }{\ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{,}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+      }{\ottmv{z}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{3}}}}  \triangleright  \ottmv{y_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}  \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{)}  \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
+    }{ \cdot   \vdash_\mathcal{L}   \lambda_r  \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}   .
+\mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{3}}}}  \triangleright  \ottmv{y_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{3}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrL}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{0}}}}    \triangleright  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \rightharpoonup  \ottsym{(}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
   \end{math}
@@
             \,
-          }{\texttt{\textcolor{red}{<<no parses (char 10): . \mbox{$\mid$}- triv ***: Unit >>}}}
-        }{\texttt{\textcolor{red}{<<no parses (char 11): x0 : Gf A ;*** . \mbox{$\mid$}- weak x0 in triv : Unit >>}}}
-      }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** x1 : F Gf A \mbox{$\mid$}- let x1 : F Gf A be F x0 in weak x0 in triv : Unit >>}}}
-    }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** . \mbox{$\mid$}- \mbox{$\backslash{}$}l x1 : F Gf A . let x1 : F Gf A be F x0 in weak x0 in triv : (F Gf A) -> (Unit) >>}}}
+          }{ \cdot   \vdash_\mathcal{L}   \mathsf{trivS}   \ottsym{:}   \mathsf{UnitS} }
+        }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}   \mathsf{weak}\, \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\,  \mathsf{trivS}    \ottsym{:}   \mathsf{UnitS} }
+      }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{weak}\, \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\,  \mathsf{trivS}     \ottsym{:}   \mathsf{UnitS} }
+    }{ \cdot   \vdash_\mathcal{L}   \lambda_r  \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   .
+\mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{weak}\, \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\,  \mathsf{trivS}      \ottsym{:}  \ottsym{(}   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}  \rightharpoonup  \ottsym{(}   \mathsf{UnitS}   \ottsym{)}}
   \end{math}
@@
       $$\mprset{flushleft}
-      \inferrule* [right={\tiny impR}] {
+      \inferrule* [right={\tiny imprR}] {
         $$\mprset{flushleft}
@@
                   \,
-                }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** x0 : F X \mbox{$\mid$}- x0 : F X >>}}}
-              }{\texttt{\textcolor{red}{<<no parses (char 13): x1 : Gf F X ;*** . \mbox{$\mid$}- let x1 : Gf F X be Gf x0 in x0 : F X >>}}}
-            }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** x2 : F Gf F X \mbox{$\mid$}- let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0) : F X >>}}}
-          }{\texttt{\textcolor{red}{<<no parses (char 18): x3 : Gf F Gf F X ;*** .
-\mbox{$\mid$}- let x3 : Gf F Gf F X be Gf x2 in (let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0)) : F X >>}}}
-        }{\ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}      \vdash   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}    \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{X}  }
-      }{\texttt{\textcolor{red}{<<no parses (char 15):  .
-\mbox{$\mid$}- \mbox{$\backslash{}$}l x3 : G***f F Gf F X .
-Gf (let x3 : Gf F Gf F X be Gf x2 in (let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0))) : (Gf F Gf F X) -> (Gf F X) >>}}}
+                }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{F} \ottnt{X}   \vdash_\mathcal{L}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{F} \ottnt{X} }
+              }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{X}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F} \ottnt{X} }
+            }{\ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}    \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{:}   \mathsf{F} \ottnt{X} }
+          }{\ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}      \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}    \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{F} \ottnt{X} }
+        }{\ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}      \vdash_\mathcal{C}   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}    \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{X}  }
+      }{ \cdot   \vdash_\mathcal{C}   \lambda  \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     .
+\mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}     \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}    \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{1}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{X}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{x_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}   \mathsf{G}  \mathsf{F}  \mathsf{G}  \mathsf{F} \ottnt{X}      \ottsym{)}  \multimap  \ottsym{(}   \mathsf{G}  \mathsf{F} \ottnt{X}    \ottsym{)}}
     \end{math}
@@
               \,
-            }{\ottmv{x}  \ottsym{:}  \ottnt{X}  \vdash  \ottmv{x}  \ottsym{:}  \ottnt{X}}
-          }{\texttt{\textcolor{red}{<<no parses (char 7): x : X ;*** . \mbox{$\mid$}- F x : F X >>}}} 
-        }{\ottmv{x}  \ottsym{:}  \ottnt{X}  \vdash   \mathsf{G}  \mathsf{F} \ottmv{x}    \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{X}  }
-      }{\texttt{\textcolor{red}{<<no parses (char 13): . \mbox{$\mid$}- \mbox{$\backslash{}$}l x : X*** . Gf F x : (X) -> (Gf F X) >>}}}
+            }{\ottmv{x}  \ottsym{:}  \ottnt{X}  \vdash_\mathcal{C}  \ottmv{x}  \ottsym{:}  \ottnt{X}}
+          }{\ottmv{x}  \ottsym{:}  \ottnt{X}  \vdash_\mathcal{L}   \mathsf{F} \ottmv{x}   \ottsym{:}   \mathsf{F} \ottnt{X} } 
+        }{\ottmv{x}  \ottsym{:}  \ottnt{X}  \vdash_\mathcal{C}   \mathsf{G}  \mathsf{F} \ottmv{x}    \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{X}  }
+      }{ \cdot   \vdash_\mathcal{C}   \lambda  \ottmv{x}  :  \ottnt{X} .
+\mathsf{G}  \mathsf{F} \ottmv{x}     \ottsym{:}  \ottsym{(}  \ottnt{X}  \ottsym{)}  \multimap  \ottsym{(}   \mathsf{G}  \mathsf{F} \ottnt{X}    \ottsym{)}}
     \end{math}
@@
                         \,
-                      }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}}
+                      }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \vdash_\mathcal{C}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}}
                       $$\mprset{flushleft}
@@
                         \,
-                      }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{Y}  \vdash  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{Y}}
-                    }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{Y}  \vdash  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \ottnt{X}   \otimes  \ottnt{Y}}
-                  }{\texttt{\textcolor{red}{<<no parses (char 17): x0 : X , y0 : Y ;*** . \mbox{$\mid$}- F (x0 (x) y0) : F (h(X) (x) Y) >>}}}
-                }{\texttt{\textcolor{red}{<<no parses (char 8): x0 : X ;*** y1 : F Y \mbox{$\mid$}- let y1 : F Y be F y0 in F (x0 (x) y0) : F (h(X) (x) Y) >>}}}
-              }{\texttt{\textcolor{red}{<<no parses (char 22): y2 : Gf F Y , x0 : X ;*** . \mbox{$\mid$}- let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0)) : F (h(X) (x) Y) >>}}}
-            }{\ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{Y}    \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \vdash   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)}  }
-          }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}  \ottnt{X}  \ottsym{,}  \ottmv{y_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{Y}    \vdash   \mathsf{ex}\, \ottmv{y_{{\mathrm{3}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{2}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)}  }
-        }{\ottmv{z}  \ottsym{:}   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}    \vdash   \mathsf{let}\, \ottmv{z}  :   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{1}}}}  \otimes  \ottmv{y_{{\mathrm{3}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{3}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{2}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)}  }
-      }{\texttt{\textcolor{red}{<<no parses (char 15): .
-\mbox{$\mid$}- \mbox{$\backslash{}$}l z : h(X***) (x) Gf F Y .
-let z : h(X) (x) Gf F Y be x1 (x) y3 in (ex y3 , x1 with y2 , x0 in (Gf (let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0))))) : (h(X) (x) Gf F Y) -> (Gf F (h(X) (x) Y)) >>}}}
+                      }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{Y}  \vdash_\mathcal{C}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{Y}}
+                    }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{Y}  \vdash_\mathcal{C}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \ottnt{X}   \otimes  \ottnt{Y}}
+                  }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{Y}  \vdash_\mathcal{L}   \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}   \ottsym{:}   \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)} }
+                }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \ottsym{,}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F} \ottnt{Y}   \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{:}   \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)} }
+              }{\ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{Y}    \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{:}   \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)} }
+            }{\ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{Y}    \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}  \ottnt{X}  \vdash_\mathcal{C}   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)}  }
+          }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}  \ottnt{X}  \ottsym{,}  \ottmv{y_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{G}  \mathsf{F} \ottnt{Y}    \vdash_\mathcal{C}   \mathsf{ex}\, \ottmv{y_{{\mathrm{3}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{2}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)}  }
+        }{\ottmv{z}  \ottsym{:}   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}    \vdash_\mathcal{C}   \mathsf{let}\, \ottmv{z}  :   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{1}}}}  \otimes  \ottmv{y_{{\mathrm{3}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{3}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{2}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}   \mathsf{G}  \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)}  }
+      }{ \cdot   \vdash_\mathcal{C}   \lambda  \ottmv{z}  :   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}   .
+\mathsf{let}\, \ottmv{z}  :   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{1}}}}  \otimes  \ottmv{y_{{\mathrm{3}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{3}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{2}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{G} \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{G}  \mathsf{F} \ottnt{Y}   \,\mathsf{be}\,  \mathsf{G}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F} \ottnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\,  \mathsf{F} \ottsym{(}  \ottmv{x_{{\mathrm{0}}}}  \otimes  \ottmv{y_{{\mathrm{0}}}}  \ottsym{)}    \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}   \ottnt{X}   \otimes   \mathsf{G}  \mathsf{F} \ottnt{Y}    \ottsym{)}  \multimap  \ottsym{(}   \mathsf{G}  \mathsf{F} \ottsym{(}   \ottnt{X}   \otimes  \ottnt{Y}  \ottsym{)}    \ottsym{)}}
     \end{math}

### 2017-11-07 exchange-draft/adjoint-model.tex
Adding a new directory.

--- 2017-08-04 adjoint-model.tex
@@
-Our adjoint model, SMCC-Lambek model, has a similar structure as Benton's LNL model \cite{}.
-Benton's LNL model consists of a symmetric monoidal adjunction $F:\cat{C}\dashv\cat{L}:G$
-between a cartesian closed category $\cat{C}$ and a symmetric monoidal closed category
-$\cat{L}$.
+Our adjoint model, Lambek Adjoint Model (LAM), has a similar structure as Benton's LNL model
+\cite{}. Benton's LNL model consists of a symmetric monoidal adjunction
+$F:\cat{C}\dashv\cat{L}:G$ between a cartesian closed category $\cat{C}$ and a symmetric
+monoidal closed category $\cat{L}$. LAM consists of a monoidal adjunction between a symmetric
+monoidal closed category and a Lambek category.
 
 \begin{definition}
-  A \textbf{SMCC-Lambek model} consists of
+  A \textbf{Lambek Adjoint Model (LAM)} $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$ consists of
   \begin{itemize}
@@
   \item a Lambek category $(\cat{L},\tri,I',\alpha',\lambda',\rho')$;
-  \item a monoidal adjunction $F:\cat{C}\dashv\cat{L}:G$, where $F:\cat{C}\rightarrow\cat{L}$
-        and $G:\cat{L}\rightarrow\cat{C}$ are monoidal functors.
+  \item a monoidal adjunction $F:\cat{C}\dashv\cat{L}:G$ with unit $\eta_X:X\rightarrow GFX$ and
+        counit $\varepsilon:FG\rightarrow id_\cat{L}$, where $(F:\cat{C}\rightarrow\cat{L}, m)$
+        and $(G:\cat{L}\rightarrow\cat{C}, n)$ are monoidal functors.
   \end{itemize}
@@
 
-Thus, in a SMCC-Lambek model, the following four diagrams commute because $\eta$ and
-$\varepsilon$ are monoidal natural transformations:
+Thus, in LAM, the following four diagrams commute because $\eta$ and $\varepsilon$ are monoidal
+natural transformations:
 \begin{mathpar}
@@
 \end{mathpar}
-And the following two diagrams commute because of the adjunction:
+And the following two triangles commute because of the adjunction:
 \begin{mathpar}
@@
 \end{mathpar}
+
 Following the tradition, we use letters $X$, $Y$, $Z$ for objects in $\cat{C}$ and $A$, $B$, $C$
-for objects in $\cat{L}$. The following lemmas and theorems establish the essential properties
-of the monad and the comomad derived from the adjunction.
+for objects in $\cat{L}$. The rest of this section proves essential properties of a LAM.
+
+\subsection{An Isomorphism}
+
+Let $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$ be a LAM, where $(F,\m{})$ and $(G,\n{})$ are
+monoidal functors. Similarly as in Benton's LNL model, $\m{X,Y}$ are components of a natural
+isomorphism and $\m{I}$ is an isomorphism. This is essential for deriving certain rules of
+our non-commutative linear logic, such as tensor elimination in natural deduction.
+
+We define the inverses of $\m{X,Y}:FX\tri FY\rightarrow F(X\otimes Y)$ and
+$\m{I}:I'\rightarrow FI$ as:
+
+\begin{mathpar}
+\bfig
+  \morphism<1000,0>[\p{X,Y}:F(X\otimes Y)`F(GFX\otimes GFY);F(\eta_X\otimes\eta_Y)]
+  \morphism(1000,0)<900,0>[F(GFX\otimes GFY)`FG(FX\tri FY);F\n{FX,FY}]
+  \morphism(1900,0)<750,0>[FG(FX\tri FY)`FX\tri FY;\varepsilon_{FX\tri FX}]
+\efig
+\and
+\bfig
+  \morphism<500,0>[\p{I}:FI`FGI';F\n{I'}]
+  \morphism(500,0)<400,0>[FGI'`I';\varepsilon_{I'}]
+\efig
+\end{mathpar}
+
+\begin{theorem}
+  $\m{X,Y}$ are components of a natural isomorphism and their inverses are $\p{X,Y}$.
+\end{theorem}
+\begin{proof}
+  We need to show that $\m{X,Y}\circ\p{X,Y}=id_{F(X\otimes Y)}$ and
+  $\p{X,Y}\circ\m{X,Y}=id_{FX\tri FX}$. The two equations hold because the following diagrams
+  commute: (1)-adjunction; (2)-$\eta$ is a monoidal natural transformation; (3)-naturality of
+  $\varepsilon$; (4)-adjunction; (5)-naturality of $\m{}$; (6)-$\varepsilon$ is a monoidal
+  natural transformation.
+  \begin{mathpar}
+  \bfig
+    \square/->`=`->`/<1600,800>[
+      F(X\otimes Y)`F(GFX\otimes GFY)`F(X\otimes Y)`FG(FX\tri FY);
+      F(\eta_X\otimes\eta_Y)``F\n{FX,FY}`]
+    \Atrianglepair|mmmbb|/->``->`<-`<-/<800,400>[
+      FGF(X\otimes Y)`F(X\otimes Y)`FX\tri FY`FG(FX\tri FY);
+      \varepsilon_{F(X\otimes Y)}``FG\m{X,Y}`\m{X,Y}`\varepsilon_{FX\tri FY}]
+    \morphism(0,800)|m|<800,-400>[F(X\otimes Y)`FGF(X\otimes Y);F\eta_{X\otimes Y}]
+    \morphism(300,450)//<0,0>[`;(1)]
+    \morphism(1200,600)//<0,0>[`;(2)]
+    \morphism(800,200)//<0,0>[`;(3)]
+  \efig
+  \and
+  \bfig
+    \square/->`=`->`/<1800,800>[
+      FX\tri FY`F(X\otimes Y)`FX\tri FY`F(GFX\otimes GFY);
+      \m{X,Y}``F(\eta_X\otimes\eta_Y)`]
+    \Atrianglepair|mmmbb|/->``->`<-`<-/<900,400>[
+      FGFX\tri FGFY`FX\tri FY`FG(FX\tri FY)`F(GFX\otimes GFY);
+      \varepsilon_{FX}\tri\varepsilon_{FY}``\m{GFX,GFY}`\varepsilon_{FX\tri FY}`F\n{FX,FY}]
+    \morphism(0,800)|m|<900,-400>[FX\tri FY`FGFX\tri FGFY;F\eta_X\tri F\eta_Y]
+    \morphism(300,450)//<0,0>[`;(4)]
+    \morphism(1300,600)//<0,0>[`;(5)]
+    \morphism(900,200)//<0,0>[`;(6)]
+  \efig
+  \end{mathpar}
+\end{proof}
+
+\begin{theorem}
+  $\m{I}$ is an isomorphism and its inverse is $\p{I}$.
+\end{theorem}
+\begin{proof}
+  This is equivalent to equations $\m{I}\circ\p{I}=id_{FI}$ and $\p{I}\circ\m{I}=id_{I'}$,
+  equivalent to the following diagrams, which commute because $\varepsilon$ is a monoidal
+  natural transformation.
+  \begin{mathpar}
+  \bfig
+    \square/->`=`->`<-/<400,400>[FI`FGI'`FI`I';F\n{I'}``\varepsilon_{I'}`\m{I}]
+  \efig
+  \and
+  \bfig
+    \square/->`=`->`<-/<400,400>[I'`FI`I'`FGI';\m{I}``F\n{I'}`\varepsilon_{I'}]
+  \efig
+  \end{mathpar}
+\end{proof}
+
+\subsection{Monad on $\cat{C}$}
+
+We first show that the monad on $\cat{C}$ in LAM is strong but non-commutative. In Benton's
+LNL model, the monad on the cartesian closed category is commutative.
 
@@
 \label{lem:monoidal-monad}
-  The monad on the symmetric monoidal closed category $\cat{C}$ in a SMCC-Lambek model is
-  monoidal.
+  The monad on the symmetric monoidal closed category $\cat{C}$ in LAM is monoidal.
 \end{lemma}
 \begin{proof}
-  We define the monad $T$ on the $\cat{C}$ in the adjunction of a SMCC-Lambek model as $T=GF$,
-  and the two corresponding natural transformations $\eta:id_\cat{C}\rightarrow T$ and
-  $\mu:T^2\rightarrow T$ as
-  $$\eta_X:X\rightarrow GFX \qquad\qquad\qquad \mu_X=G\varepsilon_{FX}:GFGFX\rightarrow GFX$$
-  where $\eta$ is the unit and $\varepsilon:FG\rightarrow id_\cat{L}$ is the counit of the
-  adjunction $F:\cat{C}\dashv\cat{L}:G$. Since the adjunction is monoidal, then $(F,\m{})$ and
-  $(G,\n{})$ are monoidal functors. Thus, we have
+  Let $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$ be a LAM. We define the monad
+  $(T,\eta:id_\cat{C}\rightarrow T,\mu:T^2\rightarrow T)$ on $\cat{C}$ as
+  $$T=GF \qquad\qquad\qquad \eta_X:X\rightarrow GFX \qquad\qquad\qquad \mu_X=G\varepsilon_{FX}:GFGFX\rightarrow GFX$$
+  Since $(F,\m{})$ and $(G,\n{})$ are monoidal functors, we have
   $$\t{X,Y}=G\m{X,Y}\circ\n{FX,FY}:TX\otimes TY\rightarrow T(X\otimes Y)
   \qquad\qquad\qquad\t{I}=G\m{I}\circ\n{I'}:I\rightarrow TI$$
-  The monad $T$ being monoidal means
+  The monad $T$ being monoidal means:
   \begin{enumerate}
@@
 However, the monad is not symmetric becauase the following diagram does not commute, for the
-lambek category $\cat{L}$ is not symmetric.
+Lambek category $\cat{L}$ is not symmetric.
 \begin{mathpar}
@@
   \label{lem:strong-monad}
-  The monad on the symmetric monoidal closed category in a SMCC-Lambek model is strong.
+  The monad on the symmetric monoidal closed category in LAM is strong.
 \end{lemma}
 \begin{proof}
-  Let $F:\cat{C}\vdash\cat{L}:G$ be a SMCC-Lambek model, where
-  $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$ is symmetric monoidal closed,
-  $(\cat{L},\tri,I',\alpha',\lambda',\rho')$ is a Lambek category, and $(F,\m{})$ and
-  $(G,\n{})$ are monoidal functors. We have proved that the monad $(T=GF,\eta,\mu)$ is monoidal
-  with the natural transformation $\t{X,Y}:TX\otimes TY\rightarrow T(X\otimes Y)$ and the
-  morphism $\t{I}:I\rightarrow TI$ defined as in Lemma~\ref{lem:monoidal-monad}. \\
+  Let $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$ be a LAM, where
+  $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$ is symmetric monoidal closed, \\
+  $(\cat{L},\tri,I',\alpha',\lambda',\rho')$ is Lambek. In Lemma~\ref{lem:monoidal-monad}, we
+  have proved that the monad $(T=GF,\eta,\mu)$ is monoidal with the natural transformation
+  $\t{X,Y}:TX\otimes TY\rightarrow T(X\otimes Y)$ and the morphism $\t{I}:I\rightarrow TI$. \\
   We define the tensorial strength $\tau_{X,Y}:X\otimes TY\rightarrow T(X\otimes Y)$ as
@@
   The first pentagon in the definition commutes by the following commutative diagrams, because
-  $\eta$ are $\alpha$ natural transformations and $T$ is monoidal:
+  $\eta$ and $\alpha$ are natural transformations and $T$ is monoidal:
   \begin{mathpar}
@@
 
-\begin{lemma}[\cite{kock1970monads}]
+The following lemma is adopted from \cite{}.
+\begin{lemma}
+\label{lem:monad-com-iff-sym}
   Let $\cat{M}$ be a symmetric monoidal category and $T$ be a strong monad on $\cat{M}$. Then
-  $T$ is symmetric iff it is commutative.
+  $T$ is commutative iff it is symmetric.
 \end{lemma}
@@
 \begin{theorem}
-  The monad on the SMCC in a SMCC-Lambek model is monoidal and non-commutative.
+  The monad on the SMCC in LAM is strong but non-commutative.
 \end{theorem}
+\begin{proof}
+  The proof is obvious. Based on Lemma~\ref{lem:strong-monad} and
+  Lemma~\ref{lem:monad-com-iff-sym}, the monad is non-commutative. 
+\end{proof}
+
+\subsection{Comonad on $\cat{L}$}
 
 \begin{lemma}
-  The comonad on the Lambek category in a SMCC-Lambek model is monoidal.
+  The comonad on the Lambek category in a LAM is monoidal.
 \end{lemma}
 \begin{proof}
-  We define the comonad $S$ on the Lambek category $\cat{L}$ in the adjunction
-  $F:\cat{C}\vdash\cat{L}:G$ of a SMCC-Lambek model as $S=FG$. The two corresponding natural
-  transformations $\varepsilon:S\rightarrow id_\cat{L}$ and $\delta:S\rightarrow S^2$ are
-  defined as
-  $$\varepsilon_A:SA\rightarrow A \qquad\qquad\qquad \delta_A=F\eta_{GA}:SA\rightarrow S^2A$$
-  where $\varepsilon$ is the counit and $\eta:id_\cat{L}\rightarrow GF$ is the unit of the
-  adjunction, and $(F,\m{})$ and $(G,\n{})$ are monoidal functors. Thus, we have
+  We define the comonad $(S,\varepsilon:S\rightarrow id_\cat{L},\delta:S\rightarrow S^2)$ on
+  the Lambek category $\cat{L}$ as:
+  $$S=FG \qquad\qquad\qquad \varepsilon_A:SA\rightarrow A \qquad\qquad\qquad \delta_A=F\eta_{GA}:SA\rightarrow S^2A$$
+  Thus, we have natural transformation $\s{}$ and morphism $\s{I}$ defined as:
   $$\s{A,B}=F\n{A,B}\circ\m{GA,GB}:SA\tri SB\rightarrow SA\tri SB \qquad\qquad\qquad
@@
 
-The comonad $S$ on the Lambek category $\cat{L}$ of the adjunction is clearly not symmetric
-because $\cat{L}$ is not. However, it is symmetric on the co-Eilenberg-Moore category of the
-comonad.
+We then show that the co-Eilenberg-Moore category of the comonad $S$ is symmetric monoidal
+closed.
 
@@
   \label{lem:em-exchange}
-  Given a SMCC-Lambek model $F:\cat{C}\dashv\cat{L}:G$ and the comonad $S$ on $\cat{L}$, the
-  co-Eilenberg-Moore category $\cat{L}^S$ of has an exchange natural transformation
+  Given a LAM $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$ and the comonad $S$ on $\cat{L}$,
+  the co-Eilenberg-Moore category $\cat{L}^S$ has an exchange natural transformation
   $\e{A,B}^S:A\tri B\rightarrow B\tri A$.
@@
   in which $(F,\m{})$ and $(G,\n{})$ are monoidal functors, and $\e{}$ is the exchange for
-  $\cat{C}$. $\e{}^S$ is a natural transformation because the following diagrams commute for
-  morphisms $f:A\rightarrow A'$ and $g:B\rightarrow B'$:
+  $\cat{C}$. Then $\e{}^S$ is a natural transformation because the following diagrams commute
+  for morphisms $f:A\rightarrow A'$ and $g:B\rightarrow B'$:
   \begin{mathpar}
@@
   \bfig
-    \Vtrianglepair|aammm|/->`->`<-``<-/<1000,400>[
+    \Vtrianglepair|aammm|/->`->`<-``<-/<1100,400>[
       F(G(A\tri B)\otimes GC)`FG((A\tri B)\tri C)`(A\tri B)\tri C`FG(A\tri B)\tri FGC;
@@
       \m{G(A\tri B),GC}``\varepsilon_{A\tri B}\tri\varepsilon_C]
-    \qtriangle(2000,0)|amr|/=`<-`->/<1000,400>[
+    \qtriangle(2200,0)|amr|/=`<-`->/<1000,400>[
       (A\tri B)\tri C`(A\tri B)\tri C`(FGA\tri FGB)\tri C;
@@
       F((GA\otimes GB)\otimes GC)`F(G(A\tri B)\otimes GC);F(\n{A,B}\otimes id_{GC})]
-    \dtriangle(1000,0)|mmm|/`<-`->/<1000,400>[
+    \dtriangle(1100,0)|mmm|/`<-`->/<1100,400>[
       (A\tri B)\tri C`FG(A\tri B)\tri FGC`FG(A\tri B)\tri C;
       `\varepsilon_{A\tri B}\tri id_C`id\tri\varepsilon_C]
-    \btriangle(0,-400)|lmm|/->`<-`/<1000,400>[
+    \btriangle(0,-400)|lmm|/->`<-`/<1100,400>[
       F((GA\otimes GB)\otimes GC)`F((GB\otimes GA)\otimes GC)`F(GA\otimes GB)\tri FGC;
       F(\e{A,B}\otimes id_{GC})`\m{GA\otimes GB,GC}`]
-    \btriangle(1000,-400)|mmm|/<-``->/<2000,400>[
+    \btriangle(1100,-400)|mmm|/<-``->/<2100,400>[
       FG(A\tri B)\tri FGC`F(GA\otimes GB)\tri FGC`F(GA\otimes GB)\tri C;
       F\n{A,B}\tri id_{FGC}``id_{F(GA\otimes GB)}\tri\varepsilon_C]
-    \qtriangle(2000,-400)|mmr|/`<-`->/<1000,400>[
+    \qtriangle(2200,-400)|mmr|/`<-`->/<1000,400>[
       FG(A\tri B)\tri C`(FGA\tri FGB)\tri C`F(GA\otimes GB)\tri C;
       `F\n{A,B}\otimes id_C`\m{GA,GB}\tri id_C]
-    \btriangle(0,-800)|lmm|/->`<-`/<2000,400>[
+    \btriangle(0,-800)|lmm|/->`<-`/<2200,400>[
       F((GB\otimes GA)\otimes GC)`F(G(B\tri A)\otimes GC)`F(GB\otimes GA)\tri FGC;
       F(\n{B,A}\otimes id_{GC})`\m{GB\otimes GA,GC}`]
-    \morphism(1000,-400)|m|<1000,-400>[
+    \morphism(1100,-400)|m|<1100,-400>[
       F(GA\otimes GB)\tri FGC`F(GB\otimes GA)\tri FGC;F\e{A,B}\tri id_{FGC}]
-    \dtriangle(2000,-800)|mra|/`->`->/<1000,400>[
+    \dtriangle(2200,-800)|mra|/`->`->/<1000,400>[
       F(GA\otimes GB)\tri C`F(GB\otimes GA)\tri FGC`F(GB\otimes GA)\tri C;
       `F\e{A,B}\tri id_C`id\tri\varepsilon_C]
-    \square(0,-1200)|almb|/<-`->`->`->/<1000,400>[
+    \square(0,-1300)|almb|/<-`->`->`->/<1100,500>[
       F(G(B\tri A)\otimes GC)`FG(B\tri A)\tri FGC`FG((B\tri A)\tri C)`(B\tri A)\tri C;
@@
       \varepsilon_{B\tri A}\tri\varepsilon_C`\varepsilon_{(B\tri A)\tri C}]
-    \morphism(1000,-800)|b|/<-/<1000,0>[
+    \morphism(1100,-800)|b|/<-/<1100,0>[
       FG(B\tri A)\tri FGC`F(GB\otimes GA)\tri FGC;F\n{B,A}\tri id]
-    \dtriangle(1000,-1200)/`->`<-/<2000,400>[
+    \dtriangle(1100,-1300)/`->`<-/<2100,500>[
       F(GB\otimes GA)\tri C`(B\tri A)\tri C`FG(B\tri A)\tri C;
       `F\n{B,A}\tri id_C`\varepsilon_{B\tri A}\tri id_C]
-    \morphism(1000,-800)|m|<2000,-400>[
+    \morphism(1100,-800)|m|<2100,-500>[
       FG(B\tri A)\tri FGC`FG(B\tri A)\tri C;id_{FG(B\tri A)}\tri\varepsilon_C]
-    \morphism(500,50)//<0,0>[`;(1)]
-    \morphism(500,-300)//<0,0>[`;(2)]
+    \morphism(550,50)//<0,0>[`;(1)]
+    \morphism(550,-300)//<0,0>[`;(2)]
     \morphism(400,-550)//<0,0>[`;(3)]
-    \morphism(500,-950)//<0,0>[`;(4)]
-    \morphism(1000,300)//<0,0>[`;(5)]
-    \morphism(1600,200)//<0,0>[`;(6)]
+    \morphism(550,-1000)//<0,0>[`;(4)]
+    \morphism(1100,300)//<0,0>[`;(5)]
+    \morphism(1900,200)//<0,0>[`;(6)]
     \morphism(1800,-150)//<0,0>[`;(7)]
     \morphism(2400,-550)//<0,0>[`;(8)]
-    \morphism(1300,-950)//<0,0>[`;(9)]
-    \morphism(2700,-900)//<0,0>[`;(10)]
-    \morphism(2800,300)//<0,0>[`;(11)]
-    \morphism(2500,50)//<0,0>[`;(12)]
+    \morphism(1550,-1050)//<0,0>[`;(9)]
+    \morphism(2700,-950)//<0,0>[`;(10)]
+    \morphism(3000,300)//<0,0>[`;(11)]
+    \morphism(2700,50)//<0,0>[`;(12)]
   \efig
@@
   \end{mathpar}
-  The third diagram commutes as follows, which uses Lemma~\ref{lem:emex}.
+  The third diagram commutes as follows: (1) and (7)--Lemma~\ref{lem:em-ex}; (2)--naturality of
+  $\alpha'$; (3) and (8)--naturality of $\varepsilon$; (4), (6) and (12)--G is a monoidal
+  functor; (5)--$\cat{C}$ is symmetrical monoidal closed; (9)--coalgebra; (10)--$\varepsilon$
+  is a monoidal natural transformation; (11)--naturality of $\e{}$.
   \begin{mathpar}
@@
       F(GB\otimes(GC\otimes GA))`F(GB\otimes G(C\tri A));F(id_{GB}\otimes\n{C,A})]
-    \morphism(2200,-2000)|m|<0,-400>[
+    \morphism(2200,-2000)|m|<0,-600>[
       F(GB\otimes G(C\tri A))`FG(B\tri(C\tri A));F\n{B,C\tri A}]
@@
       F(GB\otimes(GA\otimes GC))`F(GB\otimes G(A\tri C));F(id_{GB}\otimes\n{A,C})]
-    \morphism(1500,-2200)|m|<0,-400>[F(GB\otimes G(A\tri C))`FG(B\tri(A\tri C));F\n{B,A\tri C}]
+    \morphism(1500,-2200)|m|<-500,-400>[
+      F(GB\otimes G(A\tri C))`FG(B\tri(A\tri C));F\n{B,A\tri C}]
     \morphism(0,400)|l|<0,-2000>[(A\tri B)\tri C`(B\tri A)\tri C;\e{A,B}^S\tri id_C]
@@
     \morphism(0,-1600)|l|<0,-1000>[(B\tri A)\tri C`B\tri(A\tri C);\alpha_{B,A,C}']
-    \morphism(1500,-2600)|m|<-1500,0>[
+    \morphism(1000,-2600)|m|<-1000,0>[
       FG(B\tri(A\tri C))`B\tri(A\tri C);\varepsilon_{B\tri(A\tri C)}]
@@
       F(G(B\tri C)\otimes GA)`FG((B\tri C)\tri A);F\n{B\tri C,A}]
-    \morphism(3200,-3000)|m|<-1000,600>[FG((B\tri C)\tri A)`FG(B\tri(C\tri A));FG\alpha_{B,C,A}]
+    \morphism(3200,-3000)|m|<-1000,400>[FG((B\tri C)\tri A)`FG(B\tri(C\tri A));FG\alpha_{B,C,A}]
     \morphism(3200,-3000)|b|<-1600,0>[
       FG((B\tri C)\tri A)`(B\tri C)\tri A;\varepsilon_{(B\tri C)\tri A}]
+    \morphism(2200,-2600)|m|<-2200,-400>[
+      FG(B\tri(C\tri A))`B\tri(C\tri A);\varepsilon_{B\tri(C\tri A)}]
+    \morphism(800,-2000)|m|<200,-600>[FG((B\tri A)\tri C)`FG(B\tri(A\tri C));FG\alpha'_{B,A,C}]
+    \morphism(300,-700)//<0,0>[`;(1)]
+    \morphism(500,-2200)//<0,0>[`;(2)]
+    \morphism(1500,100)//<0,0>[`;(3)]
+    \morphism(1500,-500)//<0,0>[`;(4)]
+    \morphism(1500,-1100)//<0,0>[`;(5)]
+    \morphism(1100,-2200)//<0,0>[`;(6)]
+    \morphism(1800,-2400)//<0,0>[`;(7)]
+    \morphism(2000,-2800)//<0,0>[`;(8)]
+    \morphism(2450,200)//<0,0>[`;(9)]
+    \morphism(2900,-300)//<0,0>[`;(10)]
+    \morphism(2800,-1200)//<0,0>[`;(11)]
+    \morphism(2720,-2200)//<0,0>[`;(12)]
   \efig

### 2017-11-07 linearity-2018/Elle-ND/implementation/Evaluation0.hs
Starting on the LINEARITY draft.

@@ -1,0 +1,106 @@
+{-# LANGUAGE FlexibleContexts #-}
+-----------------------------------------------------------------------
+-- One-step evaluation functions for the terms                       --
+-----------------------------------------------------------------------
+module Evaluation0 where
+
+import Text.Parsec
+import Control.Monad.Except
+import Data.List
+
+import Syntax
+import TypeCheck
+
+eval_T :: Fresh m => Ctx_T -> Term_T -> ExceptT TypeException m Term_T
+eval_T _ Triv_T = return Triv_T
+eval_T g (LetU_T t1 t2) = do
+  ctx1 <- extractCtx_T g t1
+  ty <- typeCheck_T ctx1 t1
+  case ty of
+    Unit_T -> return t2
+    _ -> throwError InvalidTypeError
+eval_T g (LetT_T (Tens_T t1 t2) (Tensor_T ty1 ty2) b) = do
+  (tm1, b') <- unbind b
+  (tm2, t) <- unbind b'
+  ctx1 <- extractCtx_T g t1
+  ctx2 <- extractCtx_T g t2
+  ty1' <- typeCheck_T ctx1 t1
+  ty2' <- typeCheck_T ctx2 t2
+  if ((ty1', ty2') == (ty1, ty2))
+    then return (subst tm2 t2 (subst tm1 t1 t))
+    else throwError InvalidTypeError
+eval_T g (App_T (Lam_T ty b) t) = do
+  (tm, t') <- unbind b
+  ctx <- extractCtx_T g t
+  ty' <- typeCheck_T ctx t
+  if (ty' == ty)
+    then return (subst tm t t')
+    else throwError InvalidTypeError
+eval_T g (App_T t1 t2) = do
+  ctx1 <- extractCtx_T g t1
+  ctx2 <- extractCtx_T g t2
+  t1' <- eval_T ctx1 t1
+  t2' <- eval_T ctx2 t2
+  return (App_T t1' t2')
+
+
+
+eval_S :: Fresh m => Ctx_T -> Ctx_S -> Term_S -> ExceptT TypeException m Term_S
+eval_S _ _ Triv_S = return Triv_S
+eval_S g d (LetU_S s1 s2) = do
+  d' <- extractCtx_S d s1
+  ty <- typeCheck_S g d' s1
+  case ty of
+    Unit_S -> return s2
[…]

### 2017-11-07 linearity-2018/Elle-ND/implementation/Pretty.hs

@@ -1,0 +1,101 @@
+{-# LANGUAGE FlexibleContexts #-}
+
+------------------------------------------------------------------------
+-- This file contains the ILL-Impl pretty printers.                   --
+------------------------------------------------------------------------
+
+module Pretty where
+
+import Data.List
+import Data.Char
+import Text.Parsec
+import Unbound.LocallyNameless
+import Unbound.LocallyNameless.Alpha
+import Control.Monad.Except
+
+import Syntax
+import Parser
+
+
+
+------------------------------------------------------------------------
+-- Converts a type into a string                                      --
+------------------------------------------------------------------------
+prettyType_T :: Fresh m => Type_T -> m String
+prettyType_T Unit_T = return "Unit"
+prettyType_T (Tensor_T a b) = do
+  a' <- prettyType_T a
+  b' <- prettyType_T b
+  return (a' ++ "(x)" ++ b')
+prettyType_T (Imp_T a b) = do
+  a' <- prettyType_T a
+  b' <- prettyType_T b
+  return ("(" ++ a' ++ ")" ++ "-o" ++ b')
+
+------------------------------------------------------------------------
+-- Converts a term into a string                                      --
+------------------------------------------------------------------------
+prettyTerm_T :: Fresh m => Term_T -> m String
+prettyTerm_T Triv_T = return "Triv"
+prettyTerm_T (Var_T x) = return.n2s $ x
+prettyTerm_T (LetU_T t1 t2) = do
+  t1' <- prettyTerm_T t1
+  t2' <- prettyTerm_T t2
+  return $ "let " ++ t1' ++ " : Unit be Triv in " ++ t2'
+prettyTerm_T (LetT_T t1 ty b) = do
+  t1' <- prettyTerm_T t1
+  ty' <- prettyType_T ty
+  (x, b') <- unbind b
+  (y, t2) <- unbind b'
+  let x' = n2s x
+  let y' = n2s y
+  t2' <- prettyTerm_T t2
+  return $ "let " ++ x' ++ " (x) " ++ y' ++ " : " ++ ty' ++ " be " ++ t1' ++ " in " ++ t2'
+prettyTerm_T (Tens_T t1 t2) = do
+  t1' <- prettyTerm_T t1
+  t2' <- prettyTerm_T t2
+  return $ "(tens " ++ t1' ++ ", " ++ t2' ++ ")"
+prettyTerm_T (Lam_T ty b) = do
[…]

### 2017-11-07 linearity-2018/Elle-ND/implementation/Syntax.hs

@@ -1,0 +1,140 @@
+{-# LANGUAGE TemplateHaskell,       FlexibleInstances,
+            MultiParamTypeClasses, FlexibleContexts, 
+            UndecidableInstances                      #-}
+--------------------------------------------------------------------------------------
+-- This file contains the syntax and syntax manipulators of the non linear of Elle. --
+--------------------------------------------------------------------------------------
+
+module Syntax (module Unbound.LocallyNameless,
+               module Unbound.LocallyNameless.Alpha,
+               Type_T(..),
+               Type_S(..),
+               Term_T(..),
+               Term_S(..),
+               TmName_T,
+               TmName_S,
+               replace_T,
+               replaceTest_T,
+               varT2varS,
+               varS2varT,
+               TypeException(..),
+               n2s) where
+
+import Prelude
+import Data.List
+import Unbound.LocallyNameless hiding (fv)
+import Unbound.LocallyNameless.Alpha
+import Errors
+
+data Type_T = Unit_T
+          | Tensor_T Type_T Type_T
+          | Imp_T Type_T Type_T
+          | Gty_T Type_S
+          deriving (Show, Eq)
+
+data Type_S = Unit_S
+            | Tensor_S Type_S Type_S
+            | Imp_S Type_S Type_S
+            | ImpL_S Type_S Type_S
+            | ImpR_S Type_S Type_S
+            | Fty_S Type_T
+            deriving (Show, Eq)
+
+
+-- Name:
+-- an abstract type for representing names, provided by Unbound
+-- Names are indexed by the sorts of things to which they can refer,
+-- or more precisely, the sorts of things which can be substituted for them
+type TmName_T = Name Term_T
+
+data Term_T = Triv_T
+          | Var_T TmName_T     -- Variable is simply a name for some Term
+          -- LetU_T t1 t2
+          -- let t1 : Unit be triv in t2
+          | LetU_T Term_T Term_T
+          -- Bind p b:
+          -- a pair consisting of a pattern p and a body b
+          -- The pattern may bind names which occur in the body
+          -- LetT_T t1 (X * Y) (Bind x (Bind y t2))
+          -- let t1 : X * Y be x * y in t2
[…]

### 2017-11-07 linearity-2018/Elle-ND/implementation/Testing.hs

@@ -1,0 +1,50 @@
+module Testing where
+
+import Syntax
+import Parser
+import Pretty
+
+------------------------------------------------------------------------
+-- Lambda testing                                                     --
+------------------------------------------------------------------------
+
+lamtest0_T = parseTester_T lamParse_T "\\(x:Unit).y"
+lamtest0_S = parseTester_T lamParse_T "\\l(x:Unit).y"
+
+lamtest1_T = parseTester_T lamParse_T "\\(x:Unit (x) Unit).y"
+
+lamtest'_T = parseTester_T lamParse_T "\\(x:Unit(x)Unit.(tens y z)"
+
+lamtest2_T = parseTester_T lamParse_T "\\(x:Unit-oUnit).y"
+
+lamtest3_T = parseTester_T lamParse_T "\\(x:Unit -o Unit).y"
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2017-11-07 linearity-2018/Elle-ND/implementation/TypeCheck_Backup.hs

@@ -1,0 +1,308 @@
+{-# LANGUAGE FlexibleContexts #-}
+
+---------------------------------------------------------
+-- Type checking the terms defined in Syntax.hs        --
+---------------------------------------------------------
+
+module TypeCheck_Backup where
+
+import Text.Parsec
+import Control.Monad.Except
+import Data.List
+
+import Syntax
+
+-----------------------------------------------------------------------
+-- Typing contexts for T terms                                       --
+-----------------------------------------------------------------------
+type Ctx_T = [(TmName_T, Type_T)]
+
+emptyCtx_T :: Ctx_T
+emptyCtx_T = []
+
+extCtx_T :: Ctx_T -> TmName_T -> Type_T -> Ctx_T
+extCtx_T ctx nm ty = (nm, ty) : ctx
+
+infixr 5 |:|
+(|:|) :: (TmName_T, Type_T) -> Ctx_T -> Ctx_T
+(x,t) |:| ctx = extCtx_T ctx x t
+
+-----------------------------------------------------------------------
+-- Typing contexts for S terms                                       --
+-----------------------------------------------------------------------
+type Ctx_S = [(TmName_S, Type_S)]
+
+emptyCtx_S :: Ctx_S
+emptyCtx_S = []
+
+extCtx_S :: Ctx_S -> TmName_S -> Type_S -> Ctx_S
+extCtx_S ctx nm ty = (nm, ty) : ctx
+
+infixr 5 |::|
+(|::|) :: (TmName_S, Type_S) -> Ctx_S -> Ctx_S
+(x,t) |::| ctx = extCtx_S ctx x t
+
+-----------------------------------------------------------------------
+-- Free Variable Collection                                          --
+-----------------------------------------------------------------------
+-- The Fresh type class:
+-- governs monads which can generate new globally unique Names based on a given Name
+fv_T :: Fresh m => Term_T -> m [TmName_T]
+fv_T Triv_T = return []
+fv_T (Var_T x) = return [x]
[…]

### 2017-11-13 linearity-2018/introduction.tex
First page of the introduction.
Need to think more about motivation.  I think perhaps some motivation
from the syntactic side might be next up.

Perhaps the most elegant model of intuitionistic linear logic is
Benton's linear/non-linear (LNL) models \cite{Benton:1994}. On the
semantic side, LNL models are very compact and intuitive, but on the
syntactic side, they correspond to a logic and type theory, called LNL
logic, that allows one to reason with or without weakening and
contraction without the need to annotate every formula of the logic
with the of-course!  modality.  This is possible, because formulas
like $A \to B$ are primitives of the logic, and not encoded using the
of-course! modality.  Therefore, we ask the question, ``can a similar
elegant, intuitive, and flexible model and corresponding logic be
defined for the Lambek Calculus?''

LNL models are symmetric monoidal adjunctions, $\cat{C} : F \dashv G :
\cat{I}$, where $\cat{C}$ is a symmetric monoidal closed category with
weakening and contraction, hence is a cartesian closed category, and
$\cat{I}$ is a symmetric monoidal closed category.  Thus, a LNL model
consists of a model of intuitionistic logic on the left and a model of
intuitionistic linear logic on the right related via a pair of adjoint
functors.  Then Benton shows that the of-course! modality can be
recovered by $!A = F(G\,A)$.  These models suggest a more general
framework for working with structural rules.

Suppose $\cat{M}_1$ and $\cat{M}_2$ are two categories with a
bifunctor $\odot_i : \cat{M}_i \times \cat{M}_i \mto \cat{M}_i$, a
distinguished object $I_i \in \mathsf{Obj}(\cat{M}_i)$, and the two
natural isomorphisms $\lambda_A : A \odot I_i \mto A$ and $\rho_A :
I_i \odot A \mto A$.  We call these categories \emph{magmoidal
  categories with a unit}.  Examples of magmoidal categories with a
unit are monoidal categories, symmetric monoidal categories, and
cartesian closed categories.  Benton's LNL models can be generalized
to magmodial categories.  Simply, take an adjunction $\cat{M}_1 : F
\dashv G : \cat{M}_2$ called an \emph{adjoint model} where the
functors $F$ and $G$ preserve the magmoidal structure similarly to
monoidal functors, but without the coherence diagram for the
associator.  Now if we add to $\cat{M}_1$ and $\cat{M}_2$ some
structural rules, for example, by making $\cat{M}_1$ a symmetric
monoidal category and $\cat{M}_2$ a monoidal category, then we obtain
an adjoint model that corresponds to a logic where intuitionistic
linear logic ($\cat{M}_1$) and the Lambek calculus ($\cat{M}_2$) are
mixed similarly to LNL models.  However, this also leads to a new
solution to an existing problem.

Linguists have wondered if a modality for exchange can be added to the
Lambek Calculus similarly to how the of-course! modality adds
weakening and contraction to linear logic.  de Paiva and
Eades~\cite{?} show that this is possible by adding a modality $\kappa
A$ with the property that $(\kappa A \otimes B) \multimap (B \otimes
\kappa A)$.  The adjoint model introduced above induces the modality
$eA = F(G\,A)$ with the property $eA \otimes eB \multimap eB \otimes
eA$.  Thus providing a second solution to the problem, but we go
further, and show such a modality can be given for associativity. It
arises as the induced comonad of the adjoint model where $\cat{M}_1$
is a monoidal category, and $\cat{M}_2$ is a magmoidal category with a
unit.

%% Security, concurrency, and PL motivation

### 2017-11-13 linearity-2018/introduction.tex
A few additions.

@@
 
-Suppose $\cat{M}_1$ and $\cat{M}_2$ are two categories with a
-bifunctor $\odot_i : \cat{M}_i \times \cat{M}_i \mto \cat{M}_i$, a
-distinguished object $I_i \in \mathsf{Obj}(\cat{M}_i)$, and the two
-natural isomorphisms $\lambda_A : A \odot I_i \mto A$ and $\rho_A :
-I_i \odot A \mto A$.  We call these categories \emph{magmoidal
-  categories with a unit}.  Examples of magmoidal categories with a
-unit are monoidal categories, symmetric monoidal categories, and
-cartesian closed categories.  Benton's LNL models can be generalized
-to magmodial categories.  Simply, take an adjunction $\cat{M}_1 : F
-\dashv G : \cat{M}_2$ called an \emph{adjoint model} where the
-functors $F$ and $G$ preserve the magmoidal structure similarly to
-monoidal functors, but without the coherence diagram for the
-associator.  Now if we add to $\cat{M}_1$ and $\cat{M}_2$ some
-structural rules, for example, by making $\cat{M}_1$ a symmetric
-monoidal category and $\cat{M}_2$ a monoidal category, then we obtain
-an adjoint model that corresponds to a logic where intuitionistic
-linear logic ($\cat{M}_1$) and the Lambek calculus ($\cat{M}_2$) are
-mixed similarly to LNL models.  However, this also leads to a new
-solution to an existing problem.
+Our main contributions in this paper are to the Lambek Calculus, but
+we make use of a new more general framework that will put this work in
+line with planned future work.  Suppose $\cat{M}_1$ and $\cat{M}_2$
+are two categories with a bifunctor $\odot_i : \cat{M}_i \times
+\cat{M}_i \mto \cat{M}_i$, a distinguished object $I_i \in
+\mathsf{Obj}(\cat{M}_i)$, and the two natural isomorphisms $\lambda_A
+: A \odot I_i \mto A$ and $\rho_A : I_i \odot A \mto A$.  We call
+these categories \emph{magmoidal categories with a unit}.  Examples of
+magmoidal categories with a unit are monoidal categories, symmetric
+monoidal categories, and cartesian closed categories.  Benton's LNL
+models can be generalized to magmodial categories.  Simply, take an
+adjunction $\cat{M}_1 : F \dashv G : \cat{M}_2$ called an
+\emph{adjoint model} where the functors $F$ and $G$ preserve the
+magmoidal structure similarly to monoidal functors, but without the
+coherence diagram for the associator.  Now if we add to $\cat{M}_1$
+and $\cat{M}_2$ some structural rules, for example, by making
+$\cat{M}_1$ a symmetric monoidal category and $\cat{M}_2$ a monoidal
+category, then we obtain an adjoint model that corresponds to a logic
+where intuitionistic linear logic ($\cat{M}_1$) and the Lambek
+calculus ($\cat{M}_2$) are mixed similarly to LNL models.  However,
+this also leads to a new solution to an existing problem.
 

### 2017-11-16 linearity-2018/introduction.tex
One paragraph away from the full introductino.

@@
 magmoidal categories with a unit are monoidal categories, symmetric
-monoidal categories, and cartesian closed categories.  Benton's LNL
-models can be generalized to magmodial categories.  Simply, take an
-adjunction $\cat{M}_1 : F \dashv G : \cat{M}_2$ called an
-\emph{adjoint model} where the functors $F$ and $G$ preserve the
+monoidal categories, and cartesian closed categories.
+
+Benton's LNL models can be generalized to magmodial categories.
+Simply, take an adjunction $\cat{M}_1 : F \dashv G : \cat{M}_2$ called
+an \emph{adjoint model} where the functors $F$ and $G$ preserve the
 magmoidal structure similarly to monoidal functors, but without the
@@
 arises as the induced comonad of the adjoint model where $\cat{M}_1$
-is a monoidal category, and $\cat{M}_2$ is a magmoidal category with a
-unit.
+is a monoidal category, and $\cat{M}_2$ is a vanilla magmoidal
+category with a unit.  Then we will obtain the property $(aA \otimes
+aB) \otimes aC) \multimap aA \otimes (aB \otimes aC)$.
+
+Linguists as well as computer scientists have found many applications
+of substructural logics that contain more than one tensor product
+satisfying different structural rules.  For example, a commutative
+tensor product and a non-commutative tensor product within the same
+logic.  An example of such a logic is the logic of bunched
+implications, but there sequents $\Gamma \vdash A$ depend on contexts
+$\Gamma$ that are trees with multiple different branching nodes
+instead of lists.  The branching nodes are necessary to accommodate
+multiple different tensor products with different structural
+properties.  We show how adjoint models can be used to build similar
+logics, but without the need for multiple different branching nodes.
+Furthermore, adjoints compose, and this property can be exploited to
+compose modalities.
 

### 2017-11-20 linearity-2018/adjoint-models.tex
Finished the introduction, and moving on to:
The first section on adjoint models, and then the systems.

We first introduce adjoint models, and the two particular adjoint
models that will be used to model the Lambek Calculus with and without
associativity.  However, before we can do this we have to define a
very simple categorical structure known as a magmoidal category with a
unit.
%% \begin{definition}
%%   \label{def:magmoidal-categories}
%%   1
%% \end{definition}

### 2017-11-20 linearity-2018/introduction.tex
Finished the introduction, and moving on to:
The first section on adjoint models, and then the systems.

@@
 contraction without the need to annotate every formula of the logic
-with the of-course!  modality.  This is possible, because formulas
-like $A \to B$ are primitives of the logic, and not encoded using the
+with the of-course!  modality.  This is possible because formulas like
+$A \to B$ are primitives of the logic, and not encoded using the
 of-course! modality.  Therefore, we ask the question, ``can a similar
@@
 is a monoidal category, and $\cat{M}_2$ is a vanilla magmoidal
-category with a unit.  Then we will obtain the property $(aA \otimes
-aB) \otimes aC) \multimap aA \otimes (aB \otimes aC)$.
+category with a unit.  Then we will obtain the isomorphism $(aA
+\otimes aB) \otimes aC) \multimap aA \otimes (aB \otimes aC)$.
 
@@
 multiple different tensor products with different structural
-properties.  We show how adjoint models can be used to build similar
-logics, but without the need for multiple different branching nodes.
-Furthermore, adjoints compose, and this property can be exploited to
-compose modalities.
+properties.  We introduce, but leave the details to future work, the
+idea of using adjoint models to build similar logics, but without the
+need for multiple different branching nodes.  Furthermore, adjoints
+compose, and this property can be exploited to compose modalities.
 
-%% Security, concurrency, and PL motivation
+We introduce the idea above of having a modality for exchange and one
+for associativity, but what about weakening and contraction?  Indeed
+it is possible to give modalities for just weakening, $wA$, and just
+contraction, $cA$, using adjoint models.  Now that we have each
+structural rule isolated into their own modality is it possible to put
+them together to form new modalities that combine structural rules?
+The answer to this question has already been show to be positive, at
+least for weakening and contraction, but we extend this line of work
+to include exchange and associativity as well.
+Jacobs~\cite{JACOBS199473} used monads and distributive laws to relate
+modalities, but Melli{\'e}s~\cite{Mellies:2004} shows how to use
+adjunctions to accomplish the same, but in a more intuitive and
+natural way.  Thus, this part of our work is a natural extension of
+Melli{\'e}s'.  At this point we are starting to see that this is a
+very general framework.
+
+This work can be used to define a general core logic that is capable
+of encoding several different substructural logics.  Some examples are
+intuitionistic linear logic, affine logic, contraction logic, and the
+(non-associative) Lambek Calculus.  This does have some similarities
+to Licata et al.~\cite{licata2017fibrational}, but there they embrace
+the tree based structures with multiple different branching node for
+contexts from the logic of bunched implications.  However, our work is
+trying to understand if this is truly necessary, and if adjunctions
+provide a means of, at the very least, hiding these multiple branching
+nodes.  Thus, adjunctions may lead to a simplification.

### 2017-12-10 linearity-2018/adjoint-models.tex
More writing.
I was thinking that we could also include associtivity here, but it is
proving more difficult than I thought.

@@
 unit.
-%% \begin{definition}
-%%   \label{def:magmoidal-categories}
-%%   1
-%% \end{definition}
+\begin{definition}
+  \label{def:magmoidal-categories}
+  A \textbf{magmoidal category with a unit (MCU)}, $(\cat{M}, \otimes,
+  I, u_l,u_r)$, is a category $\cat{M}$ with a distinguished object,
+  $I$, called the unit, a bifunctor $\otimes : \cat{M} \times \cat{M}
+  \to \cat{M}$, and two natural isomorphisms $u_l : I \otimes A \mto
+  A$ and $u_r : A \otimes I \mto A$ called the left and right unitors
+  respectively.
+\end{definition}
+\noindent
+A MCU is then a generalization of a monoidal category by removing the
+associator.  This is necessary in order to model the non-associative
+Lambek calculus.

### 2017-12-10 linearity-2018/introduction.tex
More writing.
I was thinking that we could also include associtivity here, but it is
proving more difficult than I thought.

@@
 $eA = F(G\,A)$ with the property $eA \otimes eB \multimap eB \otimes
-eA$.  Thus providing a second solution to the problem, but we go
-further, and show such a modality can be given for associativity. It
-arises as the induced comonad of the adjoint model where $\cat{M}_1$
-is a monoidal category, and $\cat{M}_2$ is a vanilla magmoidal
-category with a unit.  Then we will obtain the isomorphism $(aA
-\otimes aB) \otimes aC) \multimap aA \otimes (aB \otimes aC)$.
+eA$.  Thus providing a second solution to the problem.
 
@@
 
-We introduce the idea above of having a modality for exchange and one
-for associativity, but what about weakening and contraction?  Indeed
-it is possible to give modalities for just weakening, $wA$, and just
-contraction, $cA$, using adjoint models.  Now that we have each
-structural rule isolated into their own modality is it possible to put
-them together to form new modalities that combine structural rules?
-The answer to this question has already been show to be positive, at
-least for weakening and contraction, but we extend this line of work
-to include exchange and associativity as well.
-Jacobs~\cite{JACOBS199473} used monads and distributive laws to relate
-modalities, but Melli{\'e}s~\cite{Mellies:2004} shows how to use
-adjunctions to accomplish the same, but in a more intuitive and
-natural way.  Thus, this part of our work is a natural extension of
-Melli{\'e}s'.  At this point we are starting to see that this is a
-very general framework.
+We introduce the idea above of having a modality for exchange, but
+what about associativity, weakening and contraction?  Indeed it is
+possible to give modalities for these structural rules as well using
+adjoint models.  Now that we have each structural rule isolated into
+their own modality is it possible to put them together to form new
+modalities that combine structural rules?  The answer to this question
+has already been show to be positive, at least for weakening and
+contraction, but we extend this line of work to include exchange, and
+in the future associativity as well.  Jacobs~\cite{JACOBS199473} used
+monads and distributive laws to relate modalities, but
+Melli{\'e}s~\cite{Mellies:2004} shows how to use adjunctions to
+accomplish the same, but in a more intuitive and natural way.  Thus,
+this part of our work is a natural extension of Melli{\'e}s'.  At this
+point we are starting to see that this is a very general framework.
 

### 2017-12-13 linearity-2018/adjoint-models.tex
More writing.

--- 2017-11-20 linearity-2018/adjoint-models.tex
@@
 unit.
-%% \begin{definition}
-%%   \label{def:magmoidal-categories}
-%%   1
-%% \end{definition}
+\begin{definition}
+  \label{def:magmoidal-categories}
+  A \textbf{magmoidal category with a unit (MCU)}, $(\cat{M}, \otimes,
+  I, \lambda,\rho)$, is a category $\cat{M}$ with a distinguished object,
+  $I$, called the unit, a bifunctor $\otimes : \cat{M} \times \cat{M}
+  \to \cat{M}$, and two natural isomorphisms $\lambda_A : I \otimes A \mto
+  A$ and $\rho_A : A \otimes I \mto A$ called the left and right unitors
+  respectively.
+\end{definition}
+\noindent
+A MCU is then a generalization of a monoidal category by removing the
+associator.  This is necessary in order to model the non-associative
+Lambek calculus.

### 2017-12-13 linearity-2018/introduction.tex
More writing.

@@
 
-Linguists have wondered if a modality for exchange can be added to the
-Lambek Calculus similarly to how the of-course! modality adds
-weakening and contraction to linear logic.  de Paiva and
+Linguists \cite{?} have wondered if a modality for exchange can be
+added to the Lambek Calculus similarly to how the of-course! modality
+adds weakening and contraction to linear logic.  de Paiva and
 Eades~\cite{?} show that this is possible by adding a modality $\kappa
@@
 accomplish the same, but in a more intuitive and natural way.  Thus,
-this part of our work is a natural extension of Melli{\'e}s'.  At this
-point we are starting to see that this is a very general framework.
+this part of our work is a natural extension of Melli{\'e}s'.
 
@@
 nodes.  Thus, adjunctions may lead to a simplification.
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: main.tex
+%%% End:

### 2018-01-02 linearity-2018/introduction.tex
Lots more work.
The plan of the paper is becoming clear.  I should have a full draft this week.

@@
-Perhaps the most elegant model of intuitionistic linear logic is
-Benton's linear/non-linear (LNL) models \cite{Benton:1994}. On the
-semantic side, LNL models are very compact and intuitive, but on the
-syntactic side, they correspond to a logic and type theory, called LNL
-logic, that allows one to reason with or without weakening and
-contraction without the need to annotate every formula of the logic
-with the of-course!  modality.  This is possible because formulas like
-$A \to B$ are primitives of the logic, and not encoded using the
-of-course! modality.  Therefore, we ask the question, ``can a similar
-elegant, intuitive, and flexible model and corresponding logic be
-defined for the Lambek Calculus?''
+Joachim Lambek first introduced the Syntactic Calculus, now known as
+the Lambek Calculus, in 1958 \cite{Lambek1958}.  Since then the Lambek
+Calculus has largely been motivated by providing an explanation of the
+mathematics of sentence structure, and can be found at the core of
+Categorial Grammar; a term first used in the title of Bar-Hillel,
+Gaifman and Shamir (1960), but categorical grammar began with
+Ajdukiewicz (1935) quite a few years earlier. For many years the
+Lambek Calculus went without use, but around 1980 it was taken up by
+logicians interested in Computational Linguistics, especially the ones
+interested in Categorial Grammars.
 
-LNL models are symmetric monoidal adjunctions, $\cat{C} : F \dashv G :
-\cat{I}$, where $\cat{C}$ is a symmetric monoidal closed category with
-weakening and contraction, hence is a cartesian closed category, and
-$\cat{I}$ is a symmetric monoidal closed category.  Thus, a LNL model
-consists of a model of intuitionistic logic on the left and a model of
-intuitionistic linear logic on the right related via a pair of adjoint
-functors.  Then Benton shows that the of-course! modality can be
-recovered by $!A = F(G\,A)$.  These models suggest a more general
-framework for working with structural rules.
+It was computational linguists, ???, who posed the question of whether
+it is possible to isolate exchange using a modality in the same way
+that the of-course modality of linear logic, $!A$, isolates weakening
+and contraction.  de Paiva and Eades III \cite{dePaiva2018} propose
+one solution to this problem by extending the Lambek calculus with the
+modality characterized by the following sequent calculus inference
+rules:
+\[
+\small
+\begin{array}{ccccccccccccccccccccc}  
+  \LdruleEr{} & & \LdruleEl{} & & \LdruleEOne{} & & \LdruleETwo{} 
+\end{array}
+\]
+The thing to note is that the modality $\kappa A$ appears on only one
+of the operands being exchanged.  That is, these rules along with
+those for the tensor product allow one to prove that $\kappa A \otimes
+B \multimap B \otimes \kappa A$ holds.  This is somewhat at odds with
+algebraic intuition, and it is unclear how this modality could be
+decomposed into adjoint functors in a linear/non-linear (LNL)
+formalization of the Lambek calculus.
 
-Our main contributions in this paper are to the Lambek Calculus, but
-we make use of a new more general framework that will put this work in
-line with planned future work.  Suppose $\cat{M}_1$ and $\cat{M}_2$
-are two categories with a bifunctor $\odot_i : \cat{M}_i \times
-\cat{M}_i \mto \cat{M}_i$, a distinguished object $I_i \in
-\mathsf{Obj}(\cat{M}_i)$, and the two natural isomorphisms $\lambda_A
-: A \odot I_i \mto A$ and $\rho_A : I_i \odot A \mto A$.  We call
-these categories \emph{magmoidal categories with a unit}.  Examples of
-magmoidal categories with a unit are monoidal categories, symmetric
-monoidal categories, and cartesian closed categories.
+In this paper we show how to add an exchange modality, $eA$, where the
+modality now occurs on both operands being exchanged. That is, one can
+show that $eA \otimes eB \multimap eB \otimes eA$ holds.  We give a
+LNL natural deduction formalization for the Lambek calculus with this
+new modality, and two categorical models: a LNL model and a concrete
+model in dialectica spaces.  Thus giving a second solution to the
+problem proposed above.
 
-Benton's LNL models can be generalized to magmodial categories.
-Simply, take an adjunction $\cat{M}_1 : F \dashv G : \cat{M}_2$ called
-an \emph{adjoint model} where the functors $F$ and $G$ preserve the
-magmoidal structure similarly to monoidal functors, but without the
-coherence diagram for the associator.  Now if we add to $\cat{M}_1$
-and $\cat{M}_2$ some structural rules, for example, by making
-$\cat{M}_1$ a symmetric monoidal category and $\cat{M}_2$ a monoidal
-category, then we obtain an adjoint model that corresponds to a logic
-where intuitionistic linear logic ($\cat{M}_1$) and the Lambek
-calculus ($\cat{M}_2$) are mixed similarly to LNL models.  However,
-this also leads to a new solution to an existing problem.
-
-Linguists \cite{?} have wondered if a modality for exchange can be
-added to the Lambek Calculus similarly to how the of-course! modality
-adds weakening and contraction to linear logic.  de Paiva and
-Eades~\cite{?} show that this is possible by adding a modality $\kappa
-A$ with the property that $(\kappa A \otimes B) \multimap (B \otimes
-\kappa A)$.  The adjoint model introduced above induces the modality
-$eA = F(G\,A)$ with the property $eA \otimes eB \multimap eB \otimes
-eA$.  Thus providing a second solution to the problem.
-
-Linguists as well as computer scientists have found many applications
-of substructural logics that contain more than one tensor product
-satisfying different structural rules.  For example, a commutative
-tensor product and a non-commutative tensor product within the same
-logic.  An example of such a logic is the logic of bunched
-implications, but there sequents $\Gamma \vdash A$ depend on contexts
-$\Gamma$ that are trees with multiple different branching nodes
-instead of lists.  The branching nodes are necessary to accommodate
-multiple different tensor products with different structural
-properties.  We introduce, but leave the details to future work, the
-idea of using adjoint models to build similar logics, but without the
-need for multiple different branching nodes.  Furthermore, adjoints
-compose, and this property can be exploited to compose modalities.
+The Lambek Calculus also has the potential for many applications in
+other areas of computer science, such as, modeling processes.  Linear
+Logic has been at the forefront of the study of process calculi for
+many years \cite{HONDA20102223,Pratt:1997,ABRAMSKY19945}. We can think
+of the commutative tensor product of linear logic as a parallel
+operator.  For example, given a process $A$ and a process $B$, then we
+can form the process $A \otimes B$ which runs both processes in
+parallel.  If we remove commutativity from the tensor product we
+obtain a sequential composition instead of parallel composition.  That
+is, the process $A \rhd B$ first runs process $A$ and then process $B$
+in that order.  Vaughan Pratt has stated that , ``sequential
+composition has no evident counterpart in type theory'' see page 11 of
+\cite{Pratt:1997}.  We believe that the Lambek Calculus will lead to
+filling this hole.
 
 We introduce the idea above of having a modality for exchange, but
-what about associativity, weakening and contraction?  Indeed it is
-possible to give modalities for these structural rules as well using
-adjoint models.  Now that we have each structural rule isolated into
-their own modality is it possible to put them together to form new
-modalities that combine structural rules?  The answer to this question
-has already been show to be positive, at least for weakening and
-contraction, but we extend this line of work to include exchange, and
-in the future associativity as well.  Jacobs~\cite{JACOBS199473} used
-monads and distributive laws to relate modalities, but
-Melli{\'e}s~\cite{Mellies:2004} shows how to use adjunctions to
-accomplish the same, but in a more intuitive and natural way.  Thus,
-this part of our work is a natural extension of Melli{\'e}s'.
+what about a individual modalities for weakening and contraction?
+Indeed it is possible to give modalities for these structural rules as
+well using adjoint models.  Now that we have each structural rule
+isolated into their own modality is it possible to put them together
+to form new modalities that combine structural rules?  The answer to
+this question has already been show to be positive, at least for
+weakening and contraction, but we extend this line of work to include
+exchange, and in the future associativity as well.
+Jacobs~\cite{JACOBS199473} used monads and distributive laws to relate
+modalities, but Melli{\'e}s~\cite{Mellies:2004} shows how to use
+adjunctions to accomplish the same, but in a more intuitive and
+natural way.  Thus, this part of our work is a natural extension of
+Melli{\'e}s'.
 
@@
 intuitionistic linear logic, affine logic, contraction logic, and the
-(non-associative) Lambek Calculus.  This does have some similarities
-to Licata et al.~\cite{licata2017fibrational}, but there they embrace
-the tree based structures with multiple different branching node for
-contexts from the logic of bunched implications.  However, our work is
-trying to understand if this is truly necessary, and if adjunctions
-provide a means of, at the very least, hiding these multiple branching
-nodes.  Thus, adjunctions may lead to a simplification.
+Lambek Calculus.  This does have some similarities to Licata et
+al.~\cite{licata2017fibrational}, but there they embrace the tree
+based structures with multiple different branching node for contexts
+from the logic of bunched implications.  However, our work is trying
+to understand if this is truly necessary, and if adjunctions provide a
+means of, at the very least, hiding these multiple branching nodes.
+Thus, adjunctions may lead to a simplification.
 

### 2018-03-27 linearity-2018/introduction.tex
First draft of the section on the calculus.
Moving onto the section on the adjoint model.

@@
 
-This work can be used to define a general core logic that is capable
-of encoding several different substructural logics.  Some examples are
-intuitionistic linear logic, affine logic, contraction logic, and the
-Lambek Calculus.  This does have some similarities to Licata et
-al.~\cite{licata2017fibrational}, but there they embrace the tree
-based structures with multiple different branching node for contexts
-from the logic of bunched implications.  However, our work is trying
-to understand if this is truly necessary, and if adjunctions provide a
-means of, at the very least, hiding these multiple branching nodes.
-Thus, adjunctions may lead to a simplification.
-
 %%% Local Variables: 

### 2018-03-28 linearity-2018/adjoint-models.tex
Imported all of the results for LAMs.
Next I have to add some narative, spruse some of it up, and add proof
summaries.

--- 2017-11-20 linearity-2018/adjoint-models.tex
@@
-We first introduce adjoint models, and the two particular adjoint
-models that will be used to model the Lambek Calculus with and without
-associativity.  However, before we can do this we have to define a
-very simple categorical structure known as a magmoidal category with a
-unit.
-%% \begin{definition}
-%%   \label{def:magmoidal-categories}
-%%   1
-%% \end{definition}
+In this section we introduce Lambek Adjoint Models (LAMs). Benton's
+LNL model consists of a symmetric monoidal adjunction
+$F:\cat{C}\dashv\cat{L}:G$ between a cartesian closed category
+$\cat{C}$ and a symmetric monoidal closed category $\cat{L}$. LAM
+consists of a monoidal adjunction between a symmetric monoidal closed
+category and a Lambek category.
+\begin{definition}
+  \label{def:lambek-category}
+  A \textbf{Lambek category} is a monoidal category $(\cat{L},\tri,I',\alpha',\lambda',\rho')$
+  with two functors $- \rightharpoonup - : \cat{L}^{\mathsf{op}} \times \cat{L} \mto \cat{L}$ and
+  $- \leftharpoonup - : \cat{L} \times \cat{L}^{\mathsf{op}} \mto \cat{L}$ such that the following
+  two natural bijections hold:
+  \[
+  \begin{array}{lllll}
+    \Hom{L}{A \tri B}{C} \cong \Hom{L}{A}{B \rightharpoonup C} & \quad &
+    \Hom{L}{A \tri B}{C} \cong \Hom{L}{B}{C \leftharpoonup A}\\
+  \end{array}
+  \]  
+\end{definition}
+
+\begin{definition}
+  A \textbf{Lambek Adjoint Model (LAM)}, $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$, consists of
+  \begin{itemize}
+  \item a symmetric monoidal closed category $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$;
+  \item a Lambek category $(\cat{L},\tri,I',\alpha',\lambda',\rho')$;
+  \item a monoidal adjunction $F:\cat{C}\dashv\cat{L}:G$ with unit $\eta_X:X\rightarrow GFX$ and
+        counit $\varepsilon:FG\rightarrow id_\cat{L}$, where $(F:\cat{C}\rightarrow\cat{L}, m)$
+        and $(G:\cat{L}\rightarrow\cat{C}, n)$ are monoidal functors.
+  \end{itemize}
+\end{definition}
+\noindent
+Following the tradition, we use letters $X$, $Y$, $Z$ for objects in
+$\cat{C}$ and $A$, $B$, $C$ for objects in $\cat{L}$. The rest of this
+section proves essential properties of any LAM.
+
+\textbf{An isomorphism}. Let $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$
+be a LAM, where $(F,\m{})$ and $(G,\n{})$ are monoidal
+functors. Similarly as in Benton's LNL model, $\m{X,Y} : FX \tri FY
+\mto F(X \otimes Y)$ are components of a natural isomorphism, and
+$\m{I} : I' \mto FI$ is an isomorphism. This is essential for deriving certain
+rules of CNC logic, such as tensor elimination in natural deduction.
+
+We define the inverses of $\m{X,Y}:FX\tri FY\rightarrow F(X\otimes Y)$
+and $\m{I}:I'\rightarrow FI$ as:
+
+\begin{mathpar}
+\bfig
+  \morphism<1000,0>[\p{X,Y}:F(X\otimes Y)`F(GFX\otimes GFY);F(\eta_X\otimes\eta_Y)]
+  \morphism(1000,0)<900,0>[F(GFX\otimes GFY)`FG(FX\tri FY);F\n{FX,FY}]
+  \morphism(1900,0)<750,0>[FG(FX\tri FY)`FX\tri FY;\varepsilon_{FX\tri FX}]
+\efig
+\and
+\bfig
+  \morphism<500,0>[\p{I}:FI`FGI';F\n{I'}]
+  \morphism(500,0)<400,0>[FGI'`I';\varepsilon_{I'}]
+\efig
+\end{mathpar}
+
+\begin{theorem}
+  $\m{X,Y}$ are components of a natural isomorphism and their inverses are $\p{X,Y}$.
+\end{theorem}
+\begin{proof}
+  This proof follows by a diagram chase using the adjunction in the
+  definition of a LAM and naturality.
+\end{proof}
+
+\textbf{Strong non-commutative monad}. Next we show that the monad on
+$\cat{C}$ in LAM is strong but non-commutative. In Benton's LNL model,
+the monad on the cartesian closed category is commutative.
+\begin{lemma}
+\label{lem:monoidal-monad}
+The monad induced by any LAM, $GF : \cat{C} \mto \cat{C}$, is monoidal.
+\end{lemma}
+\noindent
+However, the monad is not symmetric becauase the following diagram does not commute, for the
+Lambek category $\cat{L}$ is not symmetric.
+\begin{mathpar}
+\bfig
+  \ptriangle/->`->`/<900,400>[
+    GFX\otimes GFY`GFY\otimes GFX`G(FX\tri FY);\e{GFX,GFY}`\n{FX,FY}`]
+  \morphism(900,400)<900,0>[GFY\otimes GFX`G(FY\tri FX);\n{FY,FX}]
+  \dtriangle(900,0)/`->`->/<900,400>[
+    G(FY\tri FX)`GF(X\otimes Y)`GF(Y\otimes X);`G\m{Y,X}`GF\e{X,Y}]
+  \morphism|b|<900,0>[G(FX\tri FY)`GF(X\otimes Y);G\m{X,Y}]
+\efig
+\end{mathpar}
+
+\begin{lemma}
+  \label{lem:strong-monad}
+  The monad on the symmetric monoidal closed category in LAM is strong.
+\end{lemma}
+
+The following lemma is adopted from \cite{}.
+\begin{lemma}
+\label{lem:monad-com-iff-sym}
+  Let $\cat{M}$ be a symmetric monoidal category and $T$ be a strong monad on $\cat{M}$. Then
+  $T$ is commutative iff it is symmetric.
+\end{lemma}
+
+\begin{theorem}
+  The monad on the SMCC in LAM is strong but non-commutative.
+\end{theorem}
+\begin{proof}
+  The proof is obvious. Based on Lemma~\ref{lem:strong-monad} and
+  Lemma~\ref{lem:monad-com-iff-sym}, the monad is non-commutative. 
+\end{proof}
+
+\textbf{Comonad for exchange}.
+
+\begin{lemma}
+  The comonad on the Lambek category in a LAM is monoidal.
+\end{lemma}
+
+We then show that the co-Eilenberg-Moore category of the comonad $S$ is symmetric monoidal
+closed.
+
+\begin{lemma}
+  \label{lem:em-exchange}
+  Given a LAM $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$ and the comonad $S$ on $\cat{L}$,
+  the co-Eilenberg-Moore category $\cat{L}^S$ has an exchange natural transformation
+  $\e{A,B}^S:A\tri B\rightarrow B\tri A$.
+\end{lemma}
+
+\begin{theorem}
+  The co-Eilenberg-Moore category $\cat{L}^S$ of $S$ is symmetric monoidal closed.
+\end{theorem}

### 2018-04-12 linearity-2018/adjoint-models.tex
Finished the section on adjoint models.

@@
   \item a Lambek category $(\cat{L},\tri,I',\alpha',\lambda',\rho')$;
-  \item a monoidal adjunction $F:\cat{C}\dashv\cat{L}:G$ with unit $\eta_X:X\rightarrow GFX$ and
-        counit $\varepsilon:FG\rightarrow id_\cat{L}$, where $(F:\cat{C}\rightarrow\cat{L}, m)$
+  \item a monoidal adjunction $F:\cat{C}\dashv\cat{L}:G$ with unit $\eta:\Id_{\cat{C}} \rightarrow GF$ and
+        counit $\varepsilon:FG\rightarrow \Id_\cat{L}$, where $(F:\cat{C}\rightarrow\cat{L}, m)$
         and $(G:\cat{L}\rightarrow\cat{C}, n)$ are monoidal functors.
@@
 \mto F(X \otimes Y)$ are components of a natural isomorphism, and
-$\m{I} : I' \mto FI$ is an isomorphism. This is essential for deriving certain
-rules of CNC logic, such as tensor elimination in natural deduction.
-
-We define the inverses of $\m{X,Y}:FX\tri FY\rightarrow F(X\otimes Y)$
-and $\m{I}:I'\rightarrow FI$ as:
+$\m{I} : I' \mto FI$ is an isomorphism. This is essential for modeling
+certain rules of CNC logic, such as tensor elimination in natural
+deduction.  We define the inverses of $\m{X,Y}:FX\tri FY\rightarrow
+F(X\otimes Y)$ and $\m{I}:I'\rightarrow FI$ as:
 
@@
 \end{mathpar}
+We can now see that this straightforwardly follows from Benton's proof.
 
@@
 $\cat{C}$ in LAM is strong but non-commutative. In Benton's LNL model,
-the monad on the cartesian closed category is commutative.
+the monad on the cartesian closed category is commutative, but later
+Benton and Wadler \cite{Benton:1996} wonder, is it possible to model
+non-commutative monads using adjoint models similar to LNL models? The
+following answers their question in the positive.
 \begin{lemma}
@@
 \noindent
-However, the monad is not symmetric becauase the following diagram does not commute, for the
-Lambek category $\cat{L}$ is not symmetric.
+However, the monad is not symmetric because the following diagram does
+not commute.
 \begin{mathpar}
@@
 \end{mathpar}
-
+Commutativity fails, because the functors defining the monad are not
+symmetric monoidal, but only monoidal.  This means that the diagram
+\[
+\bfig
+\square<700,400>[
+  FA\otimes'FB`FB\otimes'FA`F(A\otimes B)`F(B\otimes A);
+  \e{FA,FB}`\m{A,B}`\m{B,A}`F\e{A,B}]
+\efig
+\]
+does not hold for $G$ nor $F$.  However, we can prove the monad is
+strong.
 \begin{lemma}
   \label{lem:strong-monad}
-  The monad on the symmetric monoidal closed category in LAM is strong.
+  The monad, $GF : \cat{C} \mto \cat{C}$, on the symmetric monoidal
+  closed category in LAM is strong.
 \end{lemma}
-
-The following lemma is adopted from \cite{}.
-\begin{lemma}
+\noindent
+Finally, we obtain the non-communativity of the monad induced by any
+LAM as follows.
+\begin{lemma}[Due to \cite{}]
 \label{lem:monad-com-iff-sym}
@@
 \begin{theorem}
-  The monad on the SMCC in LAM is strong but non-commutative.
+  The monad, $GF : \cat{C} \mto \cat{C}$, on the SMCC in LAM is strong
+  but non-commutative.
 \end{theorem}
 \begin{proof}
-  The proof is obvious. Based on Lemma~\ref{lem:strong-monad} and
-  Lemma~\ref{lem:monad-com-iff-sym}, the monad is non-commutative. 
+  This proof follows from Lemma~\ref{lem:strong-monad} and
+  Lemma~\ref{lem:monad-com-iff-sym}.
 \end{proof}
 
-\textbf{Comonad for exchange}.
+\textbf{Comonad for exchange}.  We conclude this section by showing
+that the comonad induced by any LAM is monoidal and extends $\cat{L}$
+with exchange.  The latter is shown by proving that its corresponding
+co-Eilenberg-Moore category is symmetric monoidal closed.
 
 \begin{lemma}
-  The comonad on the Lambek category in a LAM is monoidal.
+  The comonad, $FG : \cat{L} \mto \cat{L}$, on the Lambek category in any LAM is monoidal.
 \end{lemma}
-
-We then show that the co-Eilenberg-Moore category of the comonad $S$ is symmetric monoidal
-closed.
-
-\begin{lemma}
-  \label{lem:em-exchange}
-  Given a LAM $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$ and the comonad $S$ on $\cat{L}$,
-  the co-Eilenberg-Moore category $\cat{L}^S$ has an exchange natural transformation
-  $\e{A,B}^S:A\tri B\rightarrow B\tri A$.
-\end{lemma}
+\begin{proof}
+  This proof follows by several diagram chases, but really does not
+  depart much from Benton's proof \cite{Benton:1994}.
+\end{proof}
 
 \begin{theorem}
-  The co-Eilenberg-Moore category $\cat{L}^S$ of $S$ is symmetric monoidal closed.
+  \label{thm:em-exchange}
+  Given a LAM $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$ and the comonad
+  $FG : \cat{L} \mto \cat{L}$, the co-Eilenberg-Moore category
+  $\cat{L}^{FG}$ has an exchange natural transformation $\e{A,B}^{FG}:A\tri
+  B\rightarrow B\tri A$.
 \end{theorem}
+\begin{proof}
+  The natural transformation $\e{A,B}^{FG}:A\tri B\rightarrow B\tri A$ is defied
+  as follows:
+  $$\bfig
+    \morphism<600,0>[A\tri B`FGA\tri FGB;h_A\tri h_B]
+    \morphism(600,0)<800,0>[FGA\tri FGB`F(GA\otimes GB);\m{GA,GB}]
+    \morphism(1400,0)<800,0>[F(GA\otimes GB)`F(GB\otimes GA);F\e{GA,GB}]
+    \morphism(2200,0)<700,0>[F(GB\otimes GA)`FG(B\tri A);F\n{B,A}]
+    \morphism(2900,0)<500,0>[FG(B\tri A)`B\tri A;\varepsilon_{B\tri A}]
+  \efig$$
+  in which $\e{}$ is the exchange for $\cat{C}$.  The remainder of the
+  proof is fairly straightforward, and shows that the typical diagrams
+  for any symmetric monoidal category hold.
+\end{proof}
+
+\begin{corollary}
+  The co-Eilenberg-Moore category $\cat{L}^{FG}$ of $FG : \cat{L} \mto
+  \cat{L}$ is symmetric monoidal closed.
+\end{corollary}
+\begin{proof}
+  The proof that $\cat{L}^{FG}$ is monoidal closed follows similarly
+  to Benton~\cite{Benton:1994}.
+\end{proof}

### 2018-04-12 linearity-2018/dialectica-spaces.tex
First full draft.

\newcommand{\Set}{\mathsf{Set}}
\newcommand{\Dial}[2]{\mathsf{Dial}_{#1}(#2)}

In this section we give a different categorical model in terms of
dialectica categories; which are a sound and complete categorical
model of the Lambek Calculus as was shown by de Paiva and Eades
\cite{dePaiva2018}. This section is largely the same as the
corresponding section de Paiva and Eades give, but with some
modifications to their definition of biclosed posets with exchange
(see Definition~\ref{def:biclosed-exchange}).  However, we try to make
this section as self contained as possible.

Dialectica categories were first introduced by de Paiva as a
categorification of G\"odel's Dialectica interpretation
\cite{depaiva1990}.  Dialectica categories were one of the first sound
categorical models of intuitionistic linear logic with linear
modalities.  We show in this section that they can be adapted to
become a sound and complete model for CNC logic, with both the
exchange and of-course modalities.  Due to the complexities of working
with dialectica categories we have formally verified\footnote{The
  complete formalization can be found online at \url{???}.}  this
section in the proof assistant Agda~\cite{bove2009}.

First, we define the notion of a biclosed poset.  These are used to
control the definition of morphisms in the dialectica model.
\begin{definition}
  \label{def:biclosed-poset}
  Suppose $(M, \leq, \circ, e)$ is an ordered non-commutative monoid.
  If there exists a largest $x \in M$ such that $a \circ x \leq b$ for
  any $a, b \in M$, then we denote $x$ by $a \lto b$ and called it
  the \textbf{left-pseudocomplement} of $a$ w.r.t $b$.  Additionally,
  if there exists a largest $x \in M$ such that $x \circ a \leq b$ for
  any $a, b \in M$, then we denote $x$ by $b \rto a$ and called it
  the \textbf{right-pseudocomplement} of $a$ w.r.t $b$.

  A \textbf{biclosed poset}, $(M, \leq, \circ, e, \lto, \rto)$, is an
  ordered non-commutative monoid, $(M, \leq, \circ, e)$, such that $a
  \lto b$ and $b \rto a$ exist for any $a,b \in M$.
\end{definition}
Now using the previous definition we define dialectica Lambek spaces.
\begin{definition}
  \label{def:dialectica-lambek-spaces}
  Suppose $(M, \leq, \circ, e, \lto, \rto)$ is a biclosed poset. Then
  we define the category of \textbf{dialectica Lambek spaces},
  $\mathsf{Dial}_M(\Set)$, as follows:
  \begin{itemize}
  \item[-] objects, or dialectica Lambek spaces, are triples $(U, X,
    \alpha)$ where $U$ and $X$ are sets, and $\alpha : U \times X \mto
    M$ is a generalized relation over $M$, and

  \item[-] maps that are pairs $(f, F) : (U , X, \alpha) \mto (V , Y ,
    \beta)$ where $f : U \mto V$, and $F : Y \mto X$ are functions
    such that the weak adjointness condition
    $\forall u \in U.\forall y \in Y. \alpha(u , F(y)) \leq \beta(f(u), y)$
    holds.
  \end{itemize}
\end{definition}
Notice that the biclosed poset is used here as the target of the
relations in objects, but also as providing the order  relation in the weak adjoint condition on morphisms.  This will allow the structure of the biclosed
poset to lift up into $\Dial{M}{\Set}$.

We will show that $\Dial{M}{\Set}$ is a model of the Lambek Calculus
with modalities.  First, we must show that $\Dial{M}{\Set}$ is
monoidal biclosed.
\begin{definition}
  \label{def:dial-monoidal-structure}
  Suppose $(U, X, \alpha)$ and $(V, Y, \beta)$ are two objects of
  $\Dial{M}{\Set}$. Then their tensor product is defined as follows:
  \[ \small
  (U, X, \alpha) \rhd (V, Y, \beta) = (U \times V, (V \to X) \times (U \to Y), \alpha \rhd \beta)
  \]
  where $- \to -$ is the function space from $\Set$, and $(\alpha
  \rhd \beta)((u, v), (f, g)) = \alpha(u, f(v)) \circ \beta(g(u), v)$.
\end{definition}

\noindent
It follows from de Paiva and Eades \cite{dePaiva2018} that this does
indeed define a monoidal tensor product, but take note of the fact
that this tensor product is indeed non-commutative, because the
non-commutative multiplication of the biclosed poset is used to define
the relation of the tensor product.

The tensor product has two right adjoints making $\Dial{M}{\Set}$
biclosed.
\begin{definition}
  \label{def:dial-is-biclosed}
  Suppose $(U, X, \alpha)$ and $(V, Y, \beta)$ are two objects of
  $\Dial{M}{\Set}$. Then two internal-homs can be defined as follows:
  \[ \small
  \begin{array}{lll}
    (U, X, \alpha) \lto (V, Y, \beta) = ((U \to V) \times (Y \to X), U \times Y, \alpha \lto \beta)\\
    (V, Y, \beta) \rto (U, X, \alpha) = ((U \to V) \times (Y \to X), U \times Y, \alpha \rto \beta)\\
  \end{array}
  \]
\end{definition}
\noindent
It is straightforward to show that the typical bijections defining the
corresponding adjunctions hold; see de Paiva and Eades for the details
\cite{dePaiva2018}.

We now extend $\Dial{M}{\Set}$ with two modalities: the usual
modality, of-course, denoted $!A$, and the exchange modality denoted
$\xi A$.  However, we must first extended biclosed posets to
include an exchange operation.
\begin{definition}
  \label{def:biclosed-exchange}
  A \textbf{biclosed poset with exchange} is a biclosed poset $(M,
  \leq, \circ, e, \lto, \rto)$ equipped with an unary operation
  $\xi : M \to M$ satisfying the following:
  \[ \small
  \setlength{\arraycolsep}{4px}
  \begin{array}{lll}
    \begin{array}{lll}
    \text{(Compatibility)} & a \leq b \text{ implies } \xi a \leq \xi b \text{ for all } a,b,c \in M\\
    \text{(Minimality)} & \xi a \leq a \text{ for all } a \in M\\    
  \end{array}
  &
  \begin{array}{lll}
    \text{(Duplication)} & \xi a \leq \xi\xi a \text{ for all } a \in M\\
    \text{(Exchange)} & (\xi a \circ \xi b) \leq (\xi b \circ \xi a) \text{ for all } a, b \in M\\
  \end{array}
  \end{array}
  \]
\end{definition}
\noindent
This definition is where the construction given here departs from the
definition of biclosed posets with exchange given by de Paiva and
Eades \cite{dePaiva2018}.

We can now define the two modalities in $\Dial{M}{\Set}$ where $M$ is
a biclosed poset with exchange.
\begin{definition}
  \label{def:modalities-dial}
  Suppose $(U, X, \alpha)$ is an object of $\Dial{M}{\Set}$ where $M$
  is a biclosed poset with exchange. Then the \textbf{of-course} and
  \textbf{exchange} modalities can be defined as 
  $! (U, X, \alpha) = (U, U \to X^*, !\alpha)$ and
  $\xi (U, X, \alpha) = (U, X, \xi \alpha)$
  where $X^*$ is the free commutative monoid on $X$, $(!\alpha)(u, f)
  = \alpha(u, x_1) \circ \cdots \circ \alpha(u, x_i)$ for $f(u) =
  (x_1, \ldots, x_i)$, and $(\xi \alpha)(u, x) = \xi (\alpha(u,
  x))$.
\end{definition}
This definition highlights a fundamental difference between the two
modalities.  The definition of the exchange modality relies on an
extension of biclosed posets with essentially the exchange modality in
the category of posets.  However, the of-course modality is defined by
the structure already present in $\Dial{M}{\Set}$, specifically, the
structure of $\Set$.

Both of the modalities have the structure of a comonad.  That is,
there are monoidal natural transformations $\varepsilon_! : !A \mto
A$, $\varepsilon_\xi : \xi A \mto A$, $\delta_! : !A \mto !!A$,
and $\delta_\xi : \xi A \mto \xi\xi A$ which satisfy the
appropriate diagrams; see the formalization for the full
proofs. Furthermore, these comonads come equipped with arrows $w : !A
\mto I$, $d : !A \mto !A \otimes !A$, $\e{A,B} : \xi A \otimes \xi B \mto \xi B
\otimes \xi A$.

Finally, using the fact that $\Dial{M}{\Set}$ for any biclosed poset
is essentially a non-commutative formalization of Bierman's linear
categories \cite{Bierman:1994} we can use Benton's construction of an
LNL model from a linear category to obtain a LAM model, and hence,
obtain the following.
\begin{theorem}
  \label{theorem:sound-dial-exchange-!}
  Suppose $M$ is a biclosed poset with exchange.  Then
  $\Dial{M}{\Set}$ is a sound and complete model for CNC logic.
\end{theorem}

### 2018-04-12 linearity-2018/introduction.tex
First full draft.

@@
 
-We introduce the idea above of having a modality for exchange, but
-what about a individual modalities for weakening and contraction?
-Indeed it is possible to give modalities for these structural rules as
-well using adjoint models.  Now that we have each structural rule
-isolated into their own modality is it possible to put them together
-to form new modalities that combine structural rules?  The answer to
-this question has already been show to be positive, at least for
-weakening and contraction, but we extend this line of work to include
-exchange, and in the future associativity as well.
-Jacobs~\cite{JACOBS199473} used monads and distributive laws to relate
-modalities, but Melli{\'e}s~\cite{Mellies:2004} shows how to use
-adjunctions to accomplish the same, but in a more intuitive and
-natural way.  Thus, this part of our work is a natural extension of
-Melli{\'e}s'.
+%% We introduce the idea above of having a modality for exchange, but
+%% what about a individual modalities for weakening and contraction?
+%% Indeed it is possible to give modalities for these structural rules as
+%% well using adjoint models.  Now that we have each structural rule
+%% isolated into their own modality is it possible to put them together
+%% to form new modalities that combine structural rules?  The answer to
+%% this question has already been show to be positive, at least for
+%% weakening and contraction, but we extend this line of work to include
+%% exchange, and in the future associativity as well.
+%% Jacobs~\cite{JACOBS199473} used monads and distributive laws to relate
+%% modalities, but Melli{\'e}s~\cite{Mellies:2004} shows how to use
+%% adjunctions to accomplish the same, but in a more intuitive and
+%% natural way.  Thus, this part of our work is a natural extension of
+%% Melli{\'e}s'.
 

### 2018-04-13 linearity-2018/fw.tex
Some additions.

We introduce the idea above of having a modality for exchange, but
what about a individual modalities for weakening and contraction?
Indeed it is possible to give modalities for these structural rules as
well using adjoint models.  Now that we have each structural rule
isolated into their own modality is it possible to put them together
to form new modalities that combine structural rules?  The answer to
this question has already been show to be positive, at least for
weakening and contraction, but we extend this line of work to include
exchange, and in the future associativity as well.
Jacobs~\cite{JACOBS199473} used monads and distributive laws to relate
modalities, but Melli{\'e}s~\cite{Mellies:2004} shows how to use
adjunctions to accomplish the same, but in a more intuitive and
natural way.  Thus, this part of our work is a natural extension of
Melli{\'e}s'.

### 2018-04-13 linearity-2018/fwork.tex
Some additions.

--- 2018-04-13 linearity-2018/fw.tex
@@
 this question has already been show to be positive, at least for
-weakening and contraction, but we extend this line of work to include
-exchange, and in the future associativity as well.
-Jacobs~\cite{JACOBS199473} used monads and distributive laws to relate
-modalities, but Melli{\'e}s~\cite{Mellies:2004} shows how to use
-adjunctions to accomplish the same, but in a more intuitive and
-natural way.  Thus, this part of our work is a natural extension of
-Melli{\'e}s'.
+weakening and contraction, but we plan to extend this line of work to
+include exchange.  Jacobs~\cite{JACOBS199473} used monads and
+distributive laws to relate modalities, but
+Melli{\'e}s~\cite{Mellies:2004} shows how to use adjunctions to
+accomplish the same, but in a more intuitive and natural way.
+
+The monads induced by the adjunction in CNC logic is non-commutative,
+but Benton and Wadler show that the monads induced by the adjunction
+in LNL logic \cite{Benton:1996} are commutative.  Using the extension
+of Melli{\'e}s work we mention above would allow us to combine both
+CNC logic with LNL logic, and then be able to support both commutative
+monads as well as non-commutative monads.  We plan on exploring this
+in the future.

### 2018-04-13 linearity-2018/introduction.tex
Some additions.

--- 2018-03-27 linearity-2018/introduction.tex
@@
 
-It was computational linguists, ???, who posed the question of whether
-it is possible to isolate exchange using a modality in the same way
-that the of-course modality of linear logic, $!A$, isolates weakening
-and contraction.  de Paiva and Eades III \cite{dePaiva2018} propose
-one solution to this problem by extending the Lambek calculus with the
+It was computational linguists who posed the question of whether it is
+possible to isolate exchange using a modality in the same way that the
+of-course modality of linear logic, $!A$, isolates weakening and
+contraction.  de Paiva and Eades \cite{dePaiva2018} propose one
+solution to this problem by extending the Lambek calculus with the
 modality characterized by the following sequent calculus inference
@@
 
-We introduce the idea above of having a modality for exchange, but
-what about a individual modalities for weakening and contraction?
-Indeed it is possible to give modalities for these structural rules as
-well using adjoint models.  Now that we have each structural rule
-isolated into their own modality is it possible to put them together
-to form new modalities that combine structural rules?  The answer to
-this question has already been show to be positive, at least for
-weakening and contraction, but we extend this line of work to include
-exchange, and in the future associativity as well.
-Jacobs~\cite{JACOBS199473} used monads and distributive laws to relate
-modalities, but Melli{\'e}s~\cite{Mellies:2004} shows how to use
-adjunctions to accomplish the same, but in a more intuitive and
-natural way.  Thus, this part of our work is a natural extension of
-Melli{\'e}s'.
+\textbf{Acknowledgments.}  The first two authors were supported by NSF
+award \#1565557.
 

### 2018-04-13 linearity-2018/dialectica-spaces.tex
Removed.

@@
 with dialectica categories we have formally verified\footnote{The
-  complete formalization can be found online at \url{???}.}  this
+  complete formalization can be found online at \url{}.}  this
 section in the proof assistant Agda~\cite{bove2009}.

### 2018-04-13 linearity-2018/dialectica-spaces.tex
Adding a link to the Agda formalization.

@@
 with dialectica categories we have formally verified\footnote{The
-  complete formalization can be found online at \url{}.}  this
-section in the proof assistant Agda~\cite{bove2009}.
+  complete formalization can be found online at
+  \url{https://github.com/MonoidalAttackTrees/non-comm-monads-adjoint-models/tree/master/dialectica-formalization}.}
+this section in the proof assistant Agda~\cite{bove2009}.
 

### 2018-05-22 linearity-2018/fwork.tex
Adding Valeria's feedback.

@@
 We introduce the idea above of having a modality for exchange, but
-what about a individual modalities for weakening and contraction?
+what about individual modalities for weakening and contraction?
 Indeed it is possible to give modalities for these structural rules as
@@
 to form new modalities that combine structural rules?  The answer to
-this question has already been show to be positive, at least for
-weakening and contraction, but we plan to extend this line of work to
-include exchange.  Jacobs~\cite{JACOBS199473} used monads and
-distributive laws to relate modalities, but
-Melli{\'e}s~\cite{Mellies:2004} shows how to use adjunctions to
-accomplish the same, but in a more intuitive and natural way.
+this question has already been shown to be positive, at least for
+weakening and contraction, by Melli{\'e}s~\cite{Mellies:2004}, but we
+plan to extend this line of work to include exchange.
 
@@
 in LNL logic \cite{Benton:1996} are commutative.  Using the extension
-of Melli{\'e}s work we mention above would allow us to combine both
+of Melli{\'e}s' work we mention above would allow us to combine both
 CNC logic with LNL logic, and then be able to support both commutative

### 2018-05-22 linearity-2018/introduction.tex
Adding Valeria's feedback.

@@
 Gaifman and Shamir (1960), but categorical grammar began with
-Ajdukiewicz (1935) quite a few years earlier. For many years the
-Lambek Calculus went without use, but around 1980 it was taken up by
-logicians interested in Computational Linguistics, especially the ones
-interested in Categorial Grammars.
+Ajdukiewicz (1935) quite a few years earlier. At the end of the
+eighties the Lambek calculus and other systems of categorial grammars
+were taken up by computational linguists as exemplified by
+\cite{oehrle2012categorial,moortgat1988categorial,Barry:1991:PFS:977180.977215,hepple1990grammar}.
 

### 2018-09-13 post-linearity-2018/reviews-and-responses.txt
Uncompilable Post Proceeding for Linearity

# Linearity Paper Final Version Revision

May 22, 2018

## -------------------- Review 1 --------------------
PAPER: 3
TITLE: On the Lambek Calculus with an Exchange Modality AUTHORS: Jiaming Jiang, Harley Eades Iii and Valeria de Paiva
Overall evaluation: 1 (weak accept)
----------- Overall evaluation -----------

This paper introduces a type system for (non-symmetric) monoidal
adjunctions between a symmetric monoidal closed category and a
monoidal bi-closed category called CNC logic. It can be considered as
a variant of Benton's LNL logic for symmetric monoidal adjunctions
between a cartesian closed category and a symmetric monoidal closed
category.  This paper is in general clearly written and should be easy
to follow for readers familiar with the categorical models of linear
logic. I did not check the detail of CNC logic (largely because there
is no information on its equational or rewriting theory). However,
since it is based on well-established categorical structures, I
believe that there should be no substantial errors.  My knowledge on
the Lambek Calculus is rather limited, but I think that having a good
categorical semantics and type system for Lambek Calculus should be
useful and makes a good case of technology-transfer from Linear Logic
to the Lambek Calculus. Thus I recommend acceptance.

- Lemma 7:

I think that this result was already in Kock's 1970 original paper.

- Corollary 11:

I think that the statement of this corollary is wrong. As Benton (and
many other people) points out, the category of coalgebras of a linear
exponential comonad on a symmetric monoidal closed category does not
have to be cartesian closed (and we should take some subcategory
instead). The same applies to the setting of this paper.

- Theorem 18:

I am not sure what "a complete moel" means - completeness
w.r.t. derivablity or w.r.t. equational theory? (It seems that the
same question applies to [8].)

- Section 4:

I agree that the Dialectica categories developped here are
interesting, but also wonder if some much easier models could also do
the good job without much technical complication.  For instance,
starting with a strong monoidal functor F:C->D from a symmetric
monoidal category C to a monoidal category D, the monoidal
cocompletion (i.e. taking the presheaf categories) immediately gives
an LAM [C^op,Set] -> [D^op.Set], thus a sound model of CNC logic.

- A work which might be related to this paper is

Masahito Hasegawa:

Linear Exponential Comonads without Symmetry. LINEARITY 2016: 54-63
where the author axiomatizes comonads corresponding to monoidal
adjunctions between a cartesian category and a monoidal category. It
might be interesting to do the same for LAM (which should be something
like "linear exchange comonads").

- On the direction of arrows:

It seems that the direction of arrow types is not in harmony with the
standard Lambek Calculus nor with the usual convention for internal
homs in monoidal bi-closed categories. Is there any reason for this
choice?

### Response to Review 1:
* Will add the reference by Hasegawa.

* Lemma 7

Only found half of it is in Kock's 1970 paper. The full if and only if
version is in Kock's 1972 paper.  As said at the beginning of the 1972
paper: "In [4] (i.e., *Monads on Symmetric Monoidal Closed
Categories*) we proved that a commutative monad on a symmetric
monoidal closed category carries the structure of a symmetric monoidal
monad ([4], Theorem 3.2). We here prove the converse, so that, taken
together, we have: there is a 1-1 correspondence between commutative
monads and symmetric monoidal monads (Theorem 2.3 below)."

**Have added the reference and changed the citation for Lemma 7.**
* Corollary 11

The reviewer thought we were trying to prove that it is cartesian
closed.  The reviewer writes "As Benton (and many other people) points
out, the category of coalgebras of a linear exponential comonad on a
symmetric monoidal closed category does not have to be cartesian
closed (and we should take some subcategory instead)."

HDE: They are actually correct, and it is about closure rather than
carteisan.  I reworded the corollary to be more precise.

**Didn't change anything**
* Theorem 18
The reviewer is not sure what "complete" means.
**Added "(w.r.t. derivability and quational theory)"**
* Direction of Arrows
Not sure why the reviewer thinks the direction of arrows is
wrong. Wikipedia on closed monoidal category uses $\Rightarrow$ for
right adjoint and $\Leftarrow$ for left adjoint. The original Lambek
paper uses \ and /. The page on closed monoidal cateogry in nLab
(https://ncatlab.org/nlab/show/closed+monoidal+category) uses square
brackets, i.e., $[b,c]$ for $b\Rightarrow c$.
**Didn't change anything**

## ----------------------- Review 2 ---------------------
PAPER: 3
TITLE: On the Lambek Calculus with an Exchange Modality AUTHORS: Jiaming Jiang, Harley Eades Iii and Valeria de Paiva
Overall evaluation: 2 (accept)
----------- Overall evaluation -----------

The paper seems as a good contribution to the development of the
research in Lambek Calculus and its extensions and in Non Commutative
Linear Logic. The results seem accurate and well presented. The
authors have a very good experience in this field. It would be
interesting to compare this work with Non Commutative Logic introduced
by Abrusci and Ruet.

### Response to Review 2
* Reference by Abrusci and Ruet:
**Will add the reference.**

### 2018-09-13 reviews-and-responses.txt
Uncompilable Post Proceeding for Linearity

--- 2018-09-13 post-linearity-2018/reviews-and-responses.txt
@@
 ----------- Overall evaluation -----------
-
-This paper introduces a type system for (non-symmetric) monoidal
-adjunctions between a symmetric monoidal closed category and a
-monoidal bi-closed category called CNC logic. It can be considered as
-a variant of Benton's LNL logic for symmetric monoidal adjunctions
-between a cartesian closed category and a symmetric monoidal closed
-category.  This paper is in general clearly written and should be easy
-to follow for readers familiar with the categorical models of linear
-logic. I did not check the detail of CNC logic (largely because there
-is no information on its equational or rewriting theory). However,
-since it is based on well-established categorical structures, I
-believe that there should be no substantial errors.  My knowledge on
-the Lambek Calculus is rather limited, but I think that having a good
-categorical semantics and type system for Lambek Calculus should be
-useful and makes a good case of technology-transfer from Linear Logic
-to the Lambek Calculus. Thus I recommend acceptance.
-
+This paper introduces a type system for (non-symmetric) monoidal adjunctions between a symmetric monoidal closed category and a monoidal bi-closed category called CNC logic.
+It can be considered as a variant of Benton's LNL logic for symmetric monoidal adjunctions between a cartesian closed category and a symmetric monoidal closed category.
+This paper is in general clearly written and should be easy to follow for readers familiar with the categorical models of linear logic. I did not check the detail
+of CNC logic (largely because there is no information on its equational or rewriting theory).
+However, since it is based on well-established categorical structures, I believe that there should be no substantial errors.
+My knowledge on the Lambek Calculus is rather limited, but I think that having a good categorical semantics and type system for Lambek Calculus should be useful and makes a good case of technology-transfer from Linear Logic to the Lambek Calculus.
+Thus I recommend acceptance.
 - Lemma 7:
-
 I think that this result was already in Kock's 1970 original paper.
-
 - Corollary 11:
-
-I think that the statement of this corollary is wrong. As Benton (and
-many other people) points out, the category of coalgebras of a linear
-exponential comonad on a symmetric monoidal closed category does not
-have to be cartesian closed (and we should take some subcategory
-instead). The same applies to the setting of this paper.
-
+I think that the statement of this corollary is wrong.
+As Benton (and many other people) points out, the category of coalgebras of a linear exponential comonad on a symmetric monoidal closed category does not have to be cartesian closed (and we should take some subcategory instead).
+The same applies to the setting of this paper.
 - Theorem 18:
-
-I am not sure what "a complete moel" means - completeness
-w.r.t. derivablity or w.r.t. equational theory? (It seems that the
-same question applies to [8].)
-
+I am not sure what "a complete moel" means - completeness w.r.t. derivablity or w.r.t. equational theory? (It seems that the same question applies to
+[8].)
 - Section 4:
-
-I agree that the Dialectica categories developped here are
-interesting, but also wonder if some much easier models could also do
-the good job without much technical complication.  For instance,
-starting with a strong monoidal functor F:C->D from a symmetric
-monoidal category C to a monoidal category D, the monoidal
-cocompletion (i.e. taking the presheaf categories) immediately gives
-an LAM [C^op,Set] -> [D^op.Set], thus a sound model of CNC logic.
-
+I agree that the Dialectica categories developped here are interesting,
+but also wonder if some much easier models could also do the good job without
+much technical complication.
+For instance, starting with a strong monoidal functor F:C->D from a symmetric monoidal category C to a monoidal category D, the monoidal cocompletion (i.e.
+taking the presheaf categories) immediately gives an LAM [C^op,Set] -> [D^op.Set], thus
+a sound model of CNC logic.
 - A work which might be related to this paper is
-
 Masahito Hasegawa:
-
 Linear Exponential Comonads without Symmetry. LINEARITY 2016: 54-63
-where the author axiomatizes comonads corresponding to monoidal
-adjunctions between a cartesian category and a monoidal category. It
-might be interesting to do the same for LAM (which should be something
-like "linear exchange comonads").
-
+where the author axiomatizes comonads corresponding to monoidal adjunctions between a cartesian category and a monoidal category. It might be interesting
+to do the same for LAM (which should be something like "linear exchange comonads").
 - On the direction of arrows:
-
-It seems that the direction of arrow types is not in harmony with the
-standard Lambek Calculus nor with the usual convention for internal
-homs in monoidal bi-closed categories. Is there any reason for this
-choice?
+It seems that the direction of arrow types is not in harmony with the standard Lambek Calculus nor with the usual convention for internal homs in monoidal bi-closed categories.
+Is there any reason for this choice?
 
@@
 * Will add the reference by Hasegawa. 
-
 * Lemma 7
-
-Only found half of it is in Kock's 1970 paper. The full if and only if
-version is in Kock's 1972 paper.  As said at the beginning of the 1972
-paper: "In [4] (i.e., *Monads on Symmetric Monoidal Closed
-Categories*) we proved that a commutative monad on a symmetric
-monoidal closed category carries the structure of a symmetric monoidal
-monad ([4], Theorem 3.2). We here prove the converse, so that, taken
-together, we have: there is a 1-1 correspondence between commutative
-monads and symmetric monoidal monads (Theorem 2.3 below)."
-
+Only found half of it is in Kock's 1970 paper. The full if and only if version is in Kock's 1972 paper.
+As said at the beginning of the 1972 paper: "In [4] (i.e., *Monads on Symmetric Monoidal Closed Categories*) we proved that a commutative monad on a symmetric monoidal closed category carries the structure of a symmetric monoidal monad ([4], Theorem 3.2).
+We here prove the converse, so that, taken together, we have: there is a 1-1 correspondence between commutative monads and symmetric monoidal monads (Theorem 2.3 below)."
 **Have added the reference and changed the citation for Lemma 7.**
 * Corollary 11
-
-The reviewer thought we were trying to prove that it is cartesian
-closed.  The reviewer writes "As Benton (and many other people) points
-out, the category of coalgebras of a linear exponential comonad on a
-symmetric monoidal closed category does not have to be cartesian
-closed (and we should take some subcategory instead)."
-
-HDE: They are actually correct, and it is about closure rather than
-carteisan.  I reworded the corollary to be more precise.
-
+The reviewer thought we were trying to prove that it is cartesian closed.
+The reviewer writes "As Benton (and many other people) points out, the category of coalgebras of a linear exponential comonad on a symmetric monoidal closed category does not have to be cartesian closed (and we should take some subcategory instead)."
 **Didn't change anything**
@@
 * Direction of Arrows
-Not sure why the reviewer thinks the direction of arrows is
-wrong. Wikipedia on closed monoidal category uses $\Rightarrow$ for
-right adjoint and $\Leftarrow$ for left adjoint. The original Lambek
-paper uses \ and /. The page on closed monoidal cateogry in nLab
-(https://ncatlab.org/nlab/show/closed+monoidal+category) uses square
-brackets, i.e., $[b,c]$ for $b\Rightarrow c$.
+Not sure why the reviewer thinks the direction of arrows is wrong.
+Wikipedia on closed monoidal category uses $\Rightarrow$ for right adjoint and $\Leftarrow$ for left adjoint.
+The original Lambek paper uses \ and /.
+The page on closed monoidal cateogry in nLab (https://ncatlab.org/nlab/show/closed+monoidal+category) uses square brackets, i.e., $[b,c]$ for $b\Rightarrow c$.
 **Didn't change anything**
@@
 ----------- Overall evaluation -----------
-
-The paper seems as a good contribution to the development of the
-research in Lambek Calculus and its extensions and in Non Commutative
-Linear Logic. The results seem accurate and well presented. The
-authors have a very good experience in this field. It would be
-interesting to compare this work with Non Commutative Logic introduced
-by Abrusci and Ruet.
+The paper seems as a good contribution to the development of the research in Lambek Calculus and its extensions and in Non Commutative Linear Logic.
+The results seem accurate and well presented.
+The authors have a very good experience in this field.
+It would be interesting to compare this work with Non Commutative Logic introduced by Abrusci and Ruet.
 

### 2018-09-13 post-linearity-2018/LAM.tex
Uncompilable Post Proceeding for Linearity

We now introduce Commutative/Non-commutative (CNC) logic in the form
of a term assignment.  One should view this logic as composed of two
logics; one sitting to the left of the other.  On the left, there is
intuitionistic linear logic, denoted by $\cat{C}$, and on the right is
the Lambek calculus denoted by $\cat{L}$.  Then we connect these two
systems by a pair of monoidal adjoint functors $\cat{C} : \func{F}
\dashv \func{G} : \cat{L}$.  Keeping this intuition in mind we now
define the syntax for CNC logic.
\begin{definition}
  \label{def:Lambek-syntax}
  The following grammar describes the syntax of CNC logic:
  \begin{center}\vspace{-3px}\small
    \begin{math}
      \begin{array}{lll}        
        \text{($\cat{C}$-Types)} & [[W]],[[X]],[[Y]],[[Z]] ::= [[UnitT]] \mid [[X (*) Y]] \mid [[X -o Y]] \mid [[Gf A]]\\
        \text{($\cat{L}$-Types)} & [[A]],[[B]],[[C]],[[DT]] ::= [[UnitS]] \mid [[A (>) B]] \mid [[A -> B]] \mid [[B <- A]] \mid [[F X]]\\        
        \text{($\cat{C}$-Terms)} & [[t]] ::= [[x]] \mid [[trivT]] \mid [[t1 (*) t2]] \mid [[let t1 : X be q in t2]] \mid [[\x:X.t]] \mid [[t1 t2]] \mid [[ex t1 , t2 with x1 , x2 in t3]] \mid [[Gf s]]\\
        \text{($\cat{L}$-Terms)} & [[s]] ::= [[x]] \mid [[trivS]] \mid [[s1 (>) s2]] \mid [[let s1 : A be p in s2]] \mid [[let t : X be q in s]] \mid [[\l x : A.s]] \mid [[\r x : A . s]] \\
        & \,\,\,\,\,\,\,\,\,\mid [[appl s1 s2]] \mid [[appr s1 s2]] \mid [[F t]]\\        
        \text{($\cat{C}$-Patterns)} & [[q]] ::= [[trivTp]] \mid [[x]] \mid [[q1 (*) q2]] \mid [[Gf p]]\\
        \text{($\cat{L}$-Patterns)} & [[p]] ::= [[trivSp]] \mid [[x]] \mid [[p1 (>) p2]] \mid [[F q]]\\        
        \text{($\cat{C}$-Contexts)} & [[I]],[[P]] ::= [[.]] \mid [[x : X]] \mid [[I,P]]\\
        \text{($\cat{L}$-Contexts)} & [[G]],[[D]] ::= [[.]] \mid [[x : A]] \mid [[x : X]] \mid [[G;D]]\\        
        \text{($\cat{C}$-Typing Judgment)} & [[I |-c t : X]]\\
        \text{($\cat{L}$-Typing Judgment)} & [[G |-l s : A]]\\
      \end{array}
    \end{math}
  \end{center}
\end{definition}

The syntax for $\cat{C}$-types are the standard types for
intuitionistic linear logic.  We have a constant $[[UnitT]]$, tensor
product $[[X (*) Y]]$, and linear implication $[[X -o Y]]$, but just
as in LNL logic we also have a type $[[Gf A]]$ where $[[A]]$ is an
$\cat{L}$-type; that is, a type from the non-commutative side
corresponding to the right-adjoint functor between $\cat{L}$ and
$\cat{C}$. This functor can be used to import types and terms from the
non-commutative side into the commutative side.  Now $\cat{C}$-typing
judgments are denoted by $[[P |-c t : X]]$ where $[[P]]$ is a sequence
of pairs of variables and their types, denoted by $[[x : X]]$, $[[t]]$
is a $\cat{C}$-term, and $[[X]]$ is a $\cat{C}$-type.  The
$\cat{C}$-terms are all standard, but $[[Gf s]]$ corresponds to the
morphism part of the right-adjoint of the adjunction between both
logics, and $[[ex t1 , t2 with x1 , x2 in t3]]$ is the introduction
form for the structural rule exchange.

The non-commutative side is a bit more interesting than the
commutative side just introduced.  The $\cat{L}$-typing judgment has
the form $[[G |-l s : A]]$ where $[[G]]$ is now a $\cat{L}$-context,
denoted by $[[G]]$ or $[[D]]$. These contexts are ordered sequences of
pairs of free variables with their types from \emph{both} sides
denoted by $[[x : B]]$ and $[[x : X]]$ respectively. Finally, the term
$[[s]]$ is a $\cat{L}$-term, and $[[A]]$ is a $\cat{L}$-type.  Given
two typing contexts $[[G]]$ and $[[D]]$ we denote their concatenation
by $[[G;D]]$; we use a semicolon here to emphasize the fact that the
contexts are ordered.

The context consisting of hypotheses from both sides goes back to
Benton~\cite{Benton:1994} and is a property unique to adjoint logics
such as Benton's LNL logic and CNC logic.  This is also a very useful
property because it allows one to make use of both sides within the
Lambek calculus without the need to annotate every formula with a
modality.

The reader familiar with LNL logic will notice that our typing
judgment, $[[G |-l s : A]]$, differs from Benton's. His is of the form
$\Gamma;\Delta \vdash t : A$, where $\Gamma$ contains non-linear
formulas, and $\Delta$ contains linear formulas.  Just as Benton
remarks, the splitting of his contexts was a presentational device.
One should view his contexts as merged, and hence, linear formulas
were fully mixed with non-linear formulas.  Now why did we not use
this presentational device?  Because, when contexts from LNL logic
become out of order Benton could use the exchange rule to put them
back in order again, but we no longer have general exchange. Thus, we
are not able to keep the context organized in this way.

The syntax for $\cat{L}$-types are of the typical form for the Lambek
Calculus.  We have an unit type $[[UnitS]]$, a non-commutative tensor
product $[[A (>) B]]$, right implication $[[A -> B]]$, and left
implication $[[B <- A]]$.  $\cat{L}$-terms correspond to introduction
and elimination forms for each of the previous types.  For example,
$[[s1 (>) s2]]$ introduces a tensor, and $[[let s1 : A (>) B be x (>)
    y in s2]]$ eliminates a tensor.

The typing rules for CNC logic can be found in
Figure~\ref{fig:CNC-typing-rules}.
\begin{figure}
  \footnotesize
  \begin{tabular}{|c|}
    \hline\\
      \begin{mathpar}
      \NDdruleTXXid{} \and
      \NDdruleTXXunitI{} \and
      \NDdruleTXXunitE{} \and
      \NDdruleTXXtenI{} \and
      \NDdruleTXXtenE{} \and
      \NDdruleTXXimpI{} \and
      \NDdruleTXXimpE{} \and
      \NDdruleTXXGI{} \and
      \NDdruleTXXbeta{} \and
      \NDdruleTXXcut{}      
      \end{mathpar}
      \\
      \\
      \hline
      \\[5px]
    \begin{mathpar}
      \NDdruleSXXid{} \and
      \NDdruleSXXunitI{} \and
      \NDdruleSXXunitETwo{} \and
      \NDdruleSXXunitEOne{} \and
      \NDdruleSXXtenI{} \and
      \NDdruleSXXtenETwo{} \and
      \NDdruleSXXtenEOne{} \and
      \NDdruleSXXimprI{} \and
      \NDdruleSXXimprE{} \and
      \NDdruleSXXimplI{} \and
      \NDdruleSXXimplE{} \and
      \NDdruleSXXFI{} \and
      \NDdruleSXXFE{} \and
      \NDdruleSXXGE{} \and
      \NDdruleSXXbeta{} \and
      \NDdruleSXXcutTwo{} \and
      \NDdruleSXXcutOne{}
    \end{mathpar}\\\\
    \hline
  \end{tabular}  
  \caption{Typing Rules for CNC Logic}
  \label{fig:CNC-typing-rules}
\end{figure}
We split the figure in two: the top of the figure are the rules of
intuitionistic linear logic whose judgment is the $\mathcal{C}$-typing
judgment denoted by $[[P |-c t : X]]$, and the bottom of the figure
are the rules for the mixed commutative/non-commutative Lambek
calculus whose judgment is the $\mathcal{L}$-judgment denoted by $[[G
    |-l s : A]]$, but the two halves are connected via the functor
rules $\NDdruleTXXGIName{}$, $\NDdruleSXXGEName{}$,
$\NDdruleSXXFIName{}$, and $\NDdruleSXXFEName{}$.  Just as in LNL
logic, the fact that the context $[[G]]$ on the $\mathcal{L}$ side of
the logic is mixed results in this side having additional elimination
rules, because the type being eliminated is constructed on the
$\mathcal{C}$ side of the logic; for example, the rules
$\NDdruleSXXunitEOneName{}$, $\NDdruleSXXtenEOneName{}$, and
$\NDdruleSXXcutOneName{}$ are additional mixed rules.

The one step $\beta$-reduction rules are listed in
Figure~\ref{fig:CNC-beta-reductions}. Similarly to the typing rules,
the figure is split in two: the top lists the rules of the
intuitionistic linear logic, and the bottom are those of the mixed
commutative/non-commutative Lambek calculus. 
\renewcommand{\NDdruleTbetaXXletUName}{}
\renewcommand{\NDdruleTbetaXXletTName}{}
\renewcommand{\NDdruleTbetaXXlamName}{}
\renewcommand{\NDdruleTbetaXXappOneName}{}
\renewcommand{\NDdruleTbetaXXappTwoName}{}
\renewcommand{\NDdruleTbetaXXappLetName}{}
\renewcommand{\NDdruleTbetaXXletLetName}{}
\renewcommand{\NDdruleTbetaXXletAppName}{}
\renewcommand{\NDdruleSbetaXXletUOneName}{}
\renewcommand{\NDdruleSbetaXXletTOneName}{}
\renewcommand{\NDdruleSbetaXXletTTwoName}{}
\renewcommand{\NDdruleSbetaXXletFName}{}
\renewcommand{\NDdruleSbetaXXlamLName}{}
\renewcommand{\NDdruleSbetaXXlamRName}{}
\renewcommand{\NDdruleSbetaXXapplOneName}{}
\renewcommand{\NDdruleSbetaXXapplTwoName}{}
\renewcommand{\NDdruleSbetaXXapprOneName}{}
\renewcommand{\NDdruleSbetaXXapprTwoName}{}
\renewcommand{\NDdruleSbetaXXderelictName}{}
\renewcommand{\NDdruleSbetaXXapplLetName}{}
\renewcommand{\NDdruleSbetaXXapprLetName}{}
\renewcommand{\NDdruleSbetaXXletLetName}{}
\renewcommand{\NDdruleSbetaXXletApplName}{}
\renewcommand{\NDdruleSbetaXXletApprName}{}
\renewcommand{\NDdruleTcomXXunitEXXunitEName}{}
\renewcommand{\NDdruleTcomXXunitEXXtenEName}{}
\renewcommand{\NDdruleTcomXXunitEXXimpEName}{}
\renewcommand{\NDdruleTcomXXtenEXXunitEName}{}
\renewcommand{\NDdruleTcomXXtenEXXtenEName}{}
\renewcommand{\NDdruleTcomXXtenEXXimpEName}{}
\renewcommand{\NDdruleTcomXXimpEXXunitEName}{}
\renewcommand{\NDdruleScomXXunitEXXunitEName}{}
\renewcommand{\NDdruleScomXXunitETwoXXunitEName}{}
\renewcommand{\NDdruleScomXXunitEXXimprEName}{}
\renewcommand{\NDdruleScomXXunitETwoXXimprEName}{}
\renewcommand{\NDdruleScomXXunitEXXFEName}{}
\renewcommand{\NDdruleScomXXunitETwoXXFEName}{}
\renewcommand{\NDdruleScomXXtenEXXunitEName}{}
\renewcommand{\NDdruleScomXXtenETwoXXunitEName}{}
\renewcommand{\NDdruleScomXXtenEXXtenEName}{}
\renewcommand{\NDdruleScomXXtenETwoXXtenEName}{}
\renewcommand{\NDdruleScomXXtenEXXimprEName}{}
\renewcommand{\NDdruleScomXXtenETwoXXimprEName}{}
\renewcommand{\NDdruleScomXXtenEXXimplEName}{}
\renewcommand{\NDdruleScomXXtenETwoXXimplEName}{}
\renewcommand{\NDdruleScomXXtenEXXFEName}{}
\renewcommand{\NDdruleScomXXtenETwoXXFEName}{}
\renewcommand{\NDdruleScomXXFEXXunitEName}{}
\renewcommand{\NDdruleScomXXFEXXtenEName}{}
\renewcommand{\NDdruleScomXXFEXXimprEName}{}
\renewcommand{\NDdruleScomXXFEXXimplEName}{}
\renewcommand{\NDdruleScomXXFEXXFEName}{}
\begin{figure}[!h]
  \footnotesize
  \begin{tabular}{|c|}
    \hline\\
      \begin{mathpar}
      \NDdruleTbetaXXletU{} \and
      \NDdruleTbetaXXletT{} \and
      \NDdruleTbetaXXlam{}
      \end{mathpar}
      \\
      \\
      \hline
      \\
    \begin{mathpar}
      \NDdruleSbetaXXletUOne{} \and
      \NDdruleSbetaXXletTOne{} \and
      \NDdruleSbetaXXletTTwo{} \and
      \NDdruleSbetaXXletF{} \and
      \NDdruleSbetaXXlamL{} \and
      \NDdruleSbetaXXlamR{} \and
      \NDdruleSbetaXXderelict{}
    \end{mathpar}\\\\
    \hline
  \end{tabular}  
  \caption{$\beta$-reductions for CNC Logic}
  \label{fig:CNC-beta-reductions}
\end{figure}

The commuting conversions can be found in
Figures~\ref{fig:CNC-commutating-conversions-intuitionistic}-\ref{fig:CNC-commutating-conversions-both}. We
divide the rules into three parts due to the length. The first part,
Figure~\ref{fig:CNC-commutating-conversions-intuitionistic}, includes
the rules for the intuitionistic linear logic. The second,
Figure~\ref{fig:CNC-commutating-conversions-mixed}, includes the rules
for the commutative/non-commutative Lambek calculus. The third,
Figure~\ref{fig:CNC-commutating-conversions-both}, includes the mixed
rules $\NDdruleSXXunitEOneName{}$ and $\NDdruleSXXtenEOneName{}$.

\begin{figure}[!h]
  \footnotesize
  \begin{tabular}{|c|}
    \hline\\
    \begin{mathpar}
      \NDdruleTcomXXunitEXXunitE{} \and
      \NDdruleTcomXXunitEXXtenE{} \and
      \NDdruleTcomXXunitEXXimpE{} \and
      \NDdruleTcomXXtenEXXunitE{} \and
      \NDdruleTcomXXtenEXXtenE{} \and
      \NDdruleTcomXXtenEXXimpE{} \and
      \NDdruleTcomXXimpEXXunitE{}
    \end{mathpar}
    \\
    \\
    \hline
  \end{tabular}  
  \caption{Commuting Conversions: Intuitionistic Linear Logic}
  \label{fig:CNC-commutating-conversions-intuitionistic}
\end{figure}
\begin{figure}[!h]
  \footnotesize
  \begin{tabular}{|c|}
    \hline\\
    \begin{mathpar}
      \NDdruleScomXXunitEXXunitE{} \and
      \NDdruleScomXXunitEXXimprE{} \and
      \NDdruleScomXXunitEXXFE{} \and
      \NDdruleScomXXtenEXXunitE{} \and
      \NDdruleScomXXtenEXXtenE{} \and
      \NDdruleScomXXtenEXXimprE{} \and
      \NDdruleScomXXtenEXXimplE{} \and
      \NDdruleScomXXtenEXXFE{} \and
      \NDdruleScomXXFEXXunitE{} \and
      \NDdruleScomXXFEXXtenE{} \and
      \NDdruleScomXXFEXXimprE{} \and
      \NDdruleScomXXFEXXimplE{} \and
      \NDdruleScomXXFEXXFE{}
    \end{mathpar}\\\\
    \hline
  \end{tabular}  
  \caption{Commuting Conversions: Commutative/Non-commutative Lambek Calculus}
  \label{fig:CNC-commutating-conversions-mixed}
\end{figure}
\begin{figure}[!h]
  \footnotesize
  \begin{tabular}{|c|}
    \hline\\
    \begin{mathpar}
      \NDdruleScomXXunitETwoXXunitE{} \and
      \NDdruleScomXXunitETwoXXimprE{} \and
      \NDdruleScomXXunitETwoXXFE{} \and
      \NDdruleScomXXtenETwoXXunitE{} \and
      \NDdruleScomXXtenETwoXXtenE{} \and
      \NDdruleScomXXtenETwoXXimprE{} \and
      \NDdruleScomXXtenETwoXXimplE{} \and
      \NDdruleScomXXtenETwoXXFE{}
    \end{mathpar}\\\\
    \hline
  \end{tabular}  
  \caption{Commuting Conversions: Mixed Rules}
  \label{fig:CNC-commutating-conversions-both}
\end{figure}

\textbf{Additional Results.} The following subsection shows the
reduction rules for CNC Logic. In addition to the results given in this
paper we also have defined a sequent calculus for CNC logic, proved
cut elimination, and proved the the sequent calculus formalization is
equivalent to the natural deduction formalization given here.
Furthermore, we proved strong normalization of CNC logic via a
translation to LNL logic.  We omit these results due to space.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: main.tex
%%% End:

### 2018-09-13 post-linearity-2018/adjoint-models.tex
Uncompilable Post Proceeding for Linearity

--- 2018-04-12 linearity-2018/adjoint-models.tex
@@
 F(X\otimes Y)$ and $\m{I}:I'\rightarrow FI$ as:
-
+\vspace{-20px}
 \begin{mathpar}
@@
 LAM as follows.
-\begin{lemma}[Due to \cite{}]
+\begin{lemma}[Due to Kock~\cite{kock1972strong}]
 \label{lem:monad-com-iff-sym}
   Let $\cat{M}$ be a symmetric monoidal category and $T$ be a strong monad on $\cat{M}$. Then
-  $T$ is commutative iff it is symmetric.
+  $T$ is commutative iff it is symmetric monoidal.
 \end{lemma}
@@
 \begin{corollary}
-  The co-Eilenberg-Moore category $\cat{L}^{FG}$ of $FG : \cat{L} \mto
-  \cat{L}$ is symmetric monoidal closed.
+  The subcategory, $\mathsf{Exp}(\cat{L}^{FG})$, of the
+  co-Eilenberg-Moore category $\cat{L}^{FG}$ consisting of the free
+  exponential coalgebras is symmetric monoidal closed.
 \end{corollary}
 \begin{proof}
-  The proof that $\cat{L}^{FG}$ is monoidal closed follows similarly
-  to Benton~\cite{Benton:1994}.
+  The proof that $\mathsf{Exp}(\cat{L}^{FG})$ is monoidal closed
+  follows similarly to Benton~\cite{Benton:1994}.
 \end{proof}
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: main.tex
+%%% End:

### 2018-09-13 post-linearity-2018/fwork.tex
Uncompilable Post Proceeding for Linearity

--- 2018-05-22 linearity-2018/fwork.tex
@@
 in the future.
+
+Hasegawa~\cite{EPTCS238.6} studies the linear of-course modality,
+$!A$, as a comonad induced by an adjunction between a cartesian closed
+category a (non-symmetric) monoidal category.  The results here
+generalizes his by generalizing the cartesian closed category to a
+symmetric monoidal closed category.  However, his approach focuses on
+the comonad rather than the adjunctions.  It would be interesting to
+do the same for LAM as well.

### 2018-09-13 post-linearity-2018/sequent.tex
Uncompilable Post Proceeding for Linearity

--- 2018-09-13 post-linearity-2018/LAM.tex
@@
-We now introduce Commutative/Non-commutative (CNC) logic in the form
-of a term assignment.  One should view this logic as composed of two
-logics; one sitting to the left of the other.  On the left, there is
-intuitionistic linear logic, denoted by $\cat{C}$, and on the right is
-the Lambek calculus denoted by $\cat{L}$.  Then we connect these two
-systems by a pair of monoidal adjoint functors $\cat{C} : \func{F}
-\dashv \func{G} : \cat{L}$.  Keeping this intuition in mind we now
-define the syntax for CNC logic.
-\begin{definition}
-  \label{def:Lambek-syntax}
-  The following grammar describes the syntax of CNC logic:
-  \begin{center}\vspace{-3px}\small
-    \begin{math}
-      \begin{array}{lll}        
-        \text{($\cat{C}$-Types)} & [[W]],[[X]],[[Y]],[[Z]] ::= [[UnitT]] \mid [[X (*) Y]] \mid [[X -o Y]] \mid [[Gf A]]\\
-        \text{($\cat{L}$-Types)} & [[A]],[[B]],[[C]],[[DT]] ::= [[UnitS]] \mid [[A (>) B]] \mid [[A -> B]] \mid [[B <- A]] \mid [[F X]]\\        
-        \text{($\cat{C}$-Terms)} & [[t]] ::= [[x]] \mid [[trivT]] \mid [[t1 (*) t2]] \mid [[let t1 : X be q in t2]] \mid [[\x:X.t]] \mid [[t1 t2]] \mid [[ex t1 , t2 with x1 , x2 in t3]] \mid [[Gf s]]\\
-        \text{($\cat{L}$-Terms)} & [[s]] ::= [[x]] \mid [[trivS]] \mid [[s1 (>) s2]] \mid [[let s1 : A be p in s2]] \mid [[let t : X be q in s]] \mid [[\l x : A.s]] \mid [[\r x : A . s]] \\
-        & \,\,\,\,\,\,\,\,\,\mid [[appl s1 s2]] \mid [[appr s1 s2]] \mid [[F t]]\\        
-        \text{($\cat{C}$-Patterns)} & [[q]] ::= [[trivTp]] \mid [[x]] \mid [[q1 (*) q2]] \mid [[Gf p]]\\
-        \text{($\cat{L}$-Patterns)} & [[p]] ::= [[trivSp]] \mid [[x]] \mid [[p1 (>) p2]] \mid [[F q]]\\        
-        \text{($\cat{C}$-Contexts)} & [[I]],[[P]] ::= [[.]] \mid [[x : X]] \mid [[I,P]]\\
-        \text{($\cat{L}$-Contexts)} & [[G]],[[D]] ::= [[.]] \mid [[x : A]] \mid [[x : X]] \mid [[G;D]]\\        
-        \text{($\cat{C}$-Typing Judgment)} & [[I |-c t : X]]\\
-        \text{($\cat{L}$-Typing Judgment)} & [[G |-l s : A]]\\
-      \end{array}
-    \end{math}
-  \end{center}
-\end{definition}
+Section for sequent calculus
 
-The syntax for $\cat{C}$-types are the standard types for
-intuitionistic linear logic.  We have a constant $[[UnitT]]$, tensor
-product $[[X (*) Y]]$, and linear implication $[[X -o Y]]$, but just
-as in LNL logic we also have a type $[[Gf A]]$ where $[[A]]$ is an
-$\cat{L}$-type; that is, a type from the non-commutative side
-corresponding to the right-adjoint functor between $\cat{L}$ and
-$\cat{C}$. This functor can be used to import types and terms from the
-non-commutative side into the commutative side.  Now $\cat{C}$-typing
-judgments are denoted by $[[P |-c t : X]]$ where $[[P]]$ is a sequence
-of pairs of variables and their types, denoted by $[[x : X]]$, $[[t]]$
-is a $\cat{C}$-term, and $[[X]]$ is a $\cat{C}$-type.  The
-$\cat{C}$-terms are all standard, but $[[Gf s]]$ corresponds to the
-morphism part of the right-adjoint of the adjunction between both
-logics, and $[[ex t1 , t2 with x1 , x2 in t3]]$ is the introduction
-form for the structural rule exchange.
-
-The non-commutative side is a bit more interesting than the
-commutative side just introduced.  The $\cat{L}$-typing judgment has
-the form $[[G |-l s : A]]$ where $[[G]]$ is now a $\cat{L}$-context,
-denoted by $[[G]]$ or $[[D]]$. These contexts are ordered sequences of
-pairs of free variables with their types from \emph{both} sides
-denoted by $[[x : B]]$ and $[[x : X]]$ respectively. Finally, the term
-$[[s]]$ is a $\cat{L}$-term, and $[[A]]$ is a $\cat{L}$-type.  Given
-two typing contexts $[[G]]$ and $[[D]]$ we denote their concatenation
-by $[[G;D]]$; we use a semicolon here to emphasize the fact that the
-contexts are ordered.
-
-The context consisting of hypotheses from both sides goes back to
-Benton~\cite{Benton:1994} and is a property unique to adjoint logics
-such as Benton's LNL logic and CNC logic.  This is also a very useful
-property because it allows one to make use of both sides within the
-Lambek calculus without the need to annotate every formula with a
-modality.
-
-The reader familiar with LNL logic will notice that our typing
-judgment, $[[G |-l s : A]]$, differs from Benton's. His is of the form
-$\Gamma;\Delta \vdash t : A$, where $\Gamma$ contains non-linear
-formulas, and $\Delta$ contains linear formulas.  Just as Benton
-remarks, the splitting of his contexts was a presentational device.
-One should view his contexts as merged, and hence, linear formulas
-were fully mixed with non-linear formulas.  Now why did we not use
-this presentational device?  Because, when contexts from LNL logic
-become out of order Benton could use the exchange rule to put them
-back in order again, but we no longer have general exchange. Thus, we
-are not able to keep the context organized in this way.
-
-The syntax for $\cat{L}$-types are of the typical form for the Lambek
-Calculus.  We have an unit type $[[UnitS]]$, a non-commutative tensor
-product $[[A (>) B]]$, right implication $[[A -> B]]$, and left
-implication $[[B <- A]]$.  $\cat{L}$-terms correspond to introduction
-and elimination forms for each of the previous types.  For example,
-$[[s1 (>) s2]]$ introduces a tensor, and $[[let s1 : A (>) B be x (>)
-    y in s2]]$ eliminates a tensor.
-
-The typing rules for CNC logic can be found in
-Figure~\ref{fig:CNC-typing-rules}.
-\begin{figure}
-  \footnotesize
-  \begin{tabular}{|c|}
-    \hline\\
 \begin{mathpar}
-      \NDdruleTXXid{} \and
-      \NDdruleTXXunitI{} \and
-      \NDdruleTXXunitE{} \and
-      \NDdruleTXXtenI{} \and
-      \NDdruleTXXtenE{} \and
-      \NDdruleTXXimpI{} \and
-      \NDdruleTXXimpE{} \and
-      \NDdruleTXXGI{} \and
-      \NDdruleTXXbeta{} \and
-      \NDdruleTXXcut{}      
 \end{mathpar}
-      \\
-      \\
-      \hline
-      \\[5px]
-    \begin{mathpar}
-      \NDdruleSXXid{} \and
-      \NDdruleSXXunitI{} \and
-      \NDdruleSXXunitETwo{} \and
-      \NDdruleSXXunitEOne{} \and
-      \NDdruleSXXtenI{} \and
-      \NDdruleSXXtenETwo{} \and
-      \NDdruleSXXtenEOne{} \and
-      \NDdruleSXXimprI{} \and
-      \NDdruleSXXimprE{} \and
-      \NDdruleSXXimplI{} \and
-      \NDdruleSXXimplE{} \and
-      \NDdruleSXXFI{} \and
-      \NDdruleSXXFE{} \and
-      \NDdruleSXXGE{} \and
-      \NDdruleSXXbeta{} \and
-      \NDdruleSXXcutTwo{} \and
-      \NDdruleSXXcutOne{}
-    \end{mathpar}\\\\
-    \hline
-  \end{tabular}  
-  \caption{Typing Rules for CNC Logic}
-  \label{fig:CNC-typing-rules}
-\end{figure}
-We split the figure in two: the top of the figure are the rules of
-intuitionistic linear logic whose judgment is the $\mathcal{C}$-typing
-judgment denoted by $[[P |-c t : X]]$, and the bottom of the figure
-are the rules for the mixed commutative/non-commutative Lambek
-calculus whose judgment is the $\mathcal{L}$-judgment denoted by $[[G
-    |-l s : A]]$, but the two halves are connected via the functor
-rules $\NDdruleTXXGIName{}$, $\NDdruleSXXGEName{}$,
-$\NDdruleSXXFIName{}$, and $\NDdruleSXXFEName{}$.  Just as in LNL
-logic, the fact that the context $[[G]]$ on the $\mathcal{L}$ side of
-the logic is mixed results in this side having additional elimination
-rules, because the type being eliminated is constructed on the
-$\mathcal{C}$ side of the logic; for example, the rules
-$\NDdruleSXXunitEOneName{}$, $\NDdruleSXXtenEOneName{}$, and
-$\NDdruleSXXcutOneName{}$ are additional mixed rules.
-
-The one step $\beta$-reduction rules are listed in
-Figure~\ref{fig:CNC-beta-reductions}. Similarly to the typing rules,
-the figure is split in two: the top lists the rules of the
-intuitionistic linear logic, and the bottom are those of the mixed
-commutative/non-commutative Lambek calculus. 
-\renewcommand{\NDdruleTbetaXXletUName}{}
-\renewcommand{\NDdruleTbetaXXletTName}{}
-\renewcommand{\NDdruleTbetaXXlamName}{}
-\renewcommand{\NDdruleTbetaXXappOneName}{}
-\renewcommand{\NDdruleTbetaXXappTwoName}{}
-\renewcommand{\NDdruleTbetaXXappLetName}{}
-\renewcommand{\NDdruleTbetaXXletLetName}{}
-\renewcommand{\NDdruleTbetaXXletAppName}{}
-\renewcommand{\NDdruleSbetaXXletUOneName}{}
-\renewcommand{\NDdruleSbetaXXletTOneName}{}
-\renewcommand{\NDdruleSbetaXXletTTwoName}{}
-\renewcommand{\NDdruleSbetaXXletFName}{}
-\renewcommand{\NDdruleSbetaXXlamLName}{}
-\renewcommand{\NDdruleSbetaXXlamRName}{}
-\renewcommand{\NDdruleSbetaXXapplOneName}{}
-\renewcommand{\NDdruleSbetaXXapplTwoName}{}
-\renewcommand{\NDdruleSbetaXXapprOneName}{}
-\renewcommand{\NDdruleSbetaXXapprTwoName}{}
-\renewcommand{\NDdruleSbetaXXderelictName}{}
-\renewcommand{\NDdruleSbetaXXapplLetName}{}
-\renewcommand{\NDdruleSbetaXXapprLetName}{}
-\renewcommand{\NDdruleSbetaXXletLetName}{}
-\renewcommand{\NDdruleSbetaXXletApplName}{}
-\renewcommand{\NDdruleSbetaXXletApprName}{}
-\renewcommand{\NDdruleTcomXXunitEXXunitEName}{}
-\renewcommand{\NDdruleTcomXXunitEXXtenEName}{}
-\renewcommand{\NDdruleTcomXXunitEXXimpEName}{}
-\renewcommand{\NDdruleTcomXXtenEXXunitEName}{}
-\renewcommand{\NDdruleTcomXXtenEXXtenEName}{}
-\renewcommand{\NDdruleTcomXXtenEXXimpEName}{}
-\renewcommand{\NDdruleTcomXXimpEXXunitEName}{}
-\renewcommand{\NDdruleScomXXunitEXXunitEName}{}
-\renewcommand{\NDdruleScomXXunitETwoXXunitEName}{}
-\renewcommand{\NDdruleScomXXunitEXXimprEName}{}
-\renewcommand{\NDdruleScomXXunitETwoXXimprEName}{}
-\renewcommand{\NDdruleScomXXunitEXXFEName}{}
-\renewcommand{\NDdruleScomXXunitETwoXXFEName}{}
-\renewcommand{\NDdruleScomXXtenEXXunitEName}{}
-\renewcommand{\NDdruleScomXXtenETwoXXunitEName}{}
-\renewcommand{\NDdruleScomXXtenEXXtenEName}{}
-\renewcommand{\NDdruleScomXXtenETwoXXtenEName}{}
-\renewcommand{\NDdruleScomXXtenEXXimprEName}{}
-\renewcommand{\NDdruleScomXXtenETwoXXimprEName}{}
-\renewcommand{\NDdruleScomXXtenEXXimplEName}{}
-\renewcommand{\NDdruleScomXXtenETwoXXimplEName}{}
-\renewcommand{\NDdruleScomXXtenEXXFEName}{}
-\renewcommand{\NDdruleScomXXtenETwoXXFEName}{}
-\renewcommand{\NDdruleScomXXFEXXunitEName}{}
-\renewcommand{\NDdruleScomXXFEXXtenEName}{}
-\renewcommand{\NDdruleScomXXFEXXimprEName}{}
-\renewcommand{\NDdruleScomXXFEXXimplEName}{}
-\renewcommand{\NDdruleScomXXFEXXFEName}{}
-\begin{figure}[!h]
-  \footnotesize
-  \begin{tabular}{|c|}
-    \hline\\
-      \begin{mathpar}
-      \NDdruleTbetaXXletU{} \and
-      \NDdruleTbetaXXletT{} \and
-      \NDdruleTbetaXXlam{}
-      \end{mathpar}
-      \\
-      \\
-      \hline
-      \\
-    \begin{mathpar}
-      \NDdruleSbetaXXletUOne{} \and
-      \NDdruleSbetaXXletTOne{} \and
-      \NDdruleSbetaXXletTTwo{} \and
-      \NDdruleSbetaXXletF{} \and
-      \NDdruleSbetaXXlamL{} \and
-      \NDdruleSbetaXXlamR{} \and
-      \NDdruleSbetaXXderelict{}
-    \end{mathpar}\\\\
-    \hline
-  \end{tabular}  
-  \caption{$\beta$-reductions for CNC Logic}
-  \label{fig:CNC-beta-reductions}
-\end{figure}
-
-The commuting conversions can be found in
-Figures~\ref{fig:CNC-commutating-conversions-intuitionistic}-\ref{fig:CNC-commutating-conversions-both}. We
-divide the rules into three parts due to the length. The first part,
-Figure~\ref{fig:CNC-commutating-conversions-intuitionistic}, includes
-the rules for the intuitionistic linear logic. The second,
-Figure~\ref{fig:CNC-commutating-conversions-mixed}, includes the rules
-for the commutative/non-commutative Lambek calculus. The third,
-Figure~\ref{fig:CNC-commutating-conversions-both}, includes the mixed
-rules $\NDdruleSXXunitEOneName{}$ and $\NDdruleSXXtenEOneName{}$.
-
-\begin{figure}[!h]
-  \footnotesize
-  \begin{tabular}{|c|}
-    \hline\\
-    \begin{mathpar}
-      \NDdruleTcomXXunitEXXunitE{} \and
-      \NDdruleTcomXXunitEXXtenE{} \and
-      \NDdruleTcomXXunitEXXimpE{} \and
-      \NDdruleTcomXXtenEXXunitE{} \and
-      \NDdruleTcomXXtenEXXtenE{} \and
-      \NDdruleTcomXXtenEXXimpE{} \and
-      \NDdruleTcomXXimpEXXunitE{}
-    \end{mathpar}
-    \\
-    \\
-    \hline
-  \end{tabular}  
-  \caption{Commuting Conversions: Intuitionistic Linear Logic}
-  \label{fig:CNC-commutating-conversions-intuitionistic}
-\end{figure}
-\begin{figure}[!h]
-  \footnotesize
-  \begin{tabular}{|c|}
-    \hline\\
-    \begin{mathpar}
-      \NDdruleScomXXunitEXXunitE{} \and
-      \NDdruleScomXXunitEXXimprE{} \and
-      \NDdruleScomXXunitEXXFE{} \and
-      \NDdruleScomXXtenEXXunitE{} \and
-      \NDdruleScomXXtenEXXtenE{} \and
-      \NDdruleScomXXtenEXXimprE{} \and
-      \NDdruleScomXXtenEXXimplE{} \and
-      \NDdruleScomXXtenEXXFE{} \and
-      \NDdruleScomXXFEXXunitE{} \and
-      \NDdruleScomXXFEXXtenE{} \and
-      \NDdruleScomXXFEXXimprE{} \and
-      \NDdruleScomXXFEXXimplE{} \and
-      \NDdruleScomXXFEXXFE{}
-    \end{mathpar}\\\\
-    \hline
-  \end{tabular}  
-  \caption{Commuting Conversions: Commutative/Non-commutative Lambek Calculus}
-  \label{fig:CNC-commutating-conversions-mixed}
-\end{figure}
-\begin{figure}[!h]
-  \footnotesize
-  \begin{tabular}{|c|}
-    \hline\\
-    \begin{mathpar}
-      \NDdruleScomXXunitETwoXXunitE{} \and
-      \NDdruleScomXXunitETwoXXimprE{} \and
-      \NDdruleScomXXunitETwoXXFE{} \and
-      \NDdruleScomXXtenETwoXXunitE{} \and
-      \NDdruleScomXXtenETwoXXtenE{} \and
-      \NDdruleScomXXtenETwoXXimprE{} \and
-      \NDdruleScomXXtenETwoXXimplE{} \and
-      \NDdruleScomXXtenETwoXXFE{}
-    \end{mathpar}\\\\
-    \hline
-  \end{tabular}  
-  \caption{Commuting Conversions: Mixed Rules}
-  \label{fig:CNC-commutating-conversions-both}
-\end{figure}
-
-\textbf{Additional Results.} The following subsection shows the
-reduction rules for CNC Logic. In addition to the results given in this
-paper we also have defined a sequent calculus for CNC logic, proved
-cut elimination, and proved the the sequent calculus formalization is
-equivalent to the natural deduction formalization given here.
-Furthermore, we proved strong normalization of CNC logic via a
-translation to LNL logic.  We omit these results due to space.
-
-%%% Local Variables: 
-%%% mode: latex
-%%% TeX-master: main.tex
-%%% End:

### 2018-09-13 post-linearity-2018/Elle-ND/implementation/Comonad.hs

@@ -1,0 +1,20 @@
+{-# LANGUAGE FlexibleContexts #-}
+
+--------------------------------------------------
+-- Derive properties of the comonad             --
+--------------------------------------------------
+
+module Comonad where
+
+import Text.Parsec
+import Control.Monad.Except
+import Data.List
+
+import Syntax
+import TypeCheck
+import Parser
+import Pretty
+
+--------------------------------------------------
+-- Derive exchange comonadicly                  --
+--------------------------------------------------

### 2018-09-13 post-linearity-2018/Elle-ND/implementation/Evaluation.hs

@@ -1,0 +1,119 @@
+{-# LANGUAGE FlexibleContexts #-}
+module Evaluation where
+
+import Text.Parsec
+import Control.Monad.Except
+import Data.List
+
+import Syntax
+
+-----------------------------------------------------------------------
+-- Checks if a T term is a value, i.e. cannot be further evaluated   --
+-----------------------------------------------------------------------
+isVal_T :: Fresh m => Term_T -> m Bool
+isVal_T Triv_T = return True
+isVal_T (Var_T x) = return True
+isVal_T (Tens_T t1 t2) = do
+  t1' <- isVal_T t1
+  case t1' of
+    True  -> isVal_T t2
+    False -> return False
+isVal_T (Lam_T ty b) = do
+  (x, t) <- unbind b
+  isVal_T t
+isVal_T (Gt_T s) = isVal_S s
+isVal_T _ = return False
+
+-----------------------------------------------------------------------
+-- Checks if a S term is a value, i.e. cannot be further evaluated   --
+-----------------------------------------------------------------------
+isVal_S :: Fresh m => Term_S -> m Bool
+isVal_S Triv_S = return True
+isVal_S (Var_S x) = return True
+isVal_S (Tens_S s1 s2) = do
+  s1' <- isVal_S s1
+  case s1' of
+    True  -> isVal_S s2
+    False -> return False
+isVal_S (LamL_S ty b) = do
+  (x, s) <- unbind b
+  isVal_S s
+isVal_S (LamR_S ty b) = do
+  (x, s) <- unbind b
+  isVal_S s
+isVal_S (Ft_S t) = isVal_T t
+isVal_S _ = return False
+
+-----------------------------------------------------------------------
+-- One-step evaluation functions for the T terms                     --
+-----------------------------------------------------------------------
+eval_T :: Fresh m => Term_T -> m Term_T
+eval_T (LetU_T t1 t2) = return t2
+eval_T (LetT_T (Tens_T t1 t2) (Tensor_T ty1 ty2) b) = do
+  (tm1, b') <- unbind b
+  (tm2, t) <- unbind b'
+  return $ subst tm2 t2 (subst tm1 t1 t)
+eval_T (App_T (Lam_T ty b) t) = do
+  (tm, t') <- unbind b
+  return $ subst tm t t'
+eval_T (App_T t1 t2) = do
+  t1' <- eval_T t1
+  t2' <- eval_T t2
+  return (App_T t1' t2')
+eval_T t = return t
+
[…]

### 2018-09-13 post-linearity-2018/Elle-ND/implementation/Parser.hs

@@ -1,0 +1,327 @@
+{-# LANGUAGE NoMonomorphismRestriction, PackageImports,
+             FlexibleContexts, PackageImports #-}
+
+------------------------------------------------------------------------
+-- This file contains the ILL-Impl parsers utilizing Parsec library.  --
+------------------------------------------------------------------------
+
+module Parser where
+
+import Prelude
+import Data.List
+import Data.Char
+import Text.Parsec
+import Text.Parsec.Expr
+import qualified Text.Parsec.Token as Token
+import Text.Parsec.Language
+import Control.Monad
+import Data.Functor.Identity
+
+import Syntax
+
+lexer = haskellStyle {
+  Token.reservedNames = ["let", "be", "in", "for", "as", "triv", "Unit"],
+  Token.reservedOpNames = ["(x)", "tens", "-o", "\\", ":", ":show", ":t", ":type", ":u",
+                           ":unfold", ":d", ":dump"]
+}
+
+tokenizer  = Token.makeTokenParser lexer
+ident      = Token.identifier tokenizer
+reserved   = Token.reserved tokenizer
+reservedOp = Token.reservedOp tokenizer
+parens     = Token.parens tokenizer
+angles     = Token.angles tokenizer
+brackets   = Token.brackets tokenizer
+braces     = Token.braces tokenizer
+ws         = Token.whiteSpace tokenizer
+natural    = Token.natural tokenizer
+dot        = Token.dot tokenizer
+comma      = Token.comma tokenizer
+colon      = Token.colon tokenizer
+symbol     = Token.symbol tokenizer
+identifier = Token.identifier tokenizer
+
+unexpColon msg = unexpected msg
+
+------------------------------------------------------------------------
+-- Type parsers                                                       --
+------------------------------------------------------------------------
+tyUnit_T = do
+  reservedOp "Unit"
+  return Unit_T
+
+tyUnit_S = do
+  reservedOp "Unit"
+  return Unit_S
+
+------------------------------------------------------------------------
+-- Type parser tables                                                 --
+------------------------------------------------------------------------
[…]

### 2018-09-13 post-linearity-2018/Elle-ND/implementation/SyntaxS.hs

@@ -1,0 +1,63 @@
+{-# LANGUAGE TemplateHaskell,       FlexibleInstances,
+            MultiParamTypeClasses, FlexibleContexts, 
+            UndecidableInstances                      #-}
+--------------------------------------------------------------------------------------
+-- This file contains the syntax and syntax manipulators of the non linear of Elle. --
+--------------------------------------------------------------------------------------
+
+module SyntaxS (module Unbound.LocallyNameless,
+               module Unbound.LocallyNameless.Alpha,
+               Type_S(..),
+               Term_S(..),
+               TmName,
+               replace_S,
+               replaceTest_S,
+               TypeException(..),
+               n2s) where
+
+import Prelude
+import Data.List
+import Unbound.LocallyNameless hiding (fv)
+import Unbound.LocallyNameless.Alpha
+import Errors
+
+import Syntax
+
+data Type_S = Unit_S
+            | Tensor_S Type_S Type_S
+            | Imp_S Type_S Type_S
+            | ImpL_S Type_S Type_S
+            | ImpR_S Type_S Type_S
+            deriving (Show, Eq)
+--            | F_S Type_T
+
+type TmName = Name Term_S
+
+--          | LetU_T Term_T Term_T
+--          | LetT_T Term_T Type_T (Bind TmName (Bind TmName Term_T))
+--          | Tens_T Term_T Term_T
+--          | Lam_T Type_T (Bind TmName Term_T)
+--          | App_T Term_T Term_T
+
+data Term_S = Triv_S
+            | Var_S TmName
+
+
+$(derive [''Term_S, ''Type_S])
+instance Alpha Term_S
+instance Alpha Type_S
+
+instance Subst Term_S Type_S
+instance Subst Term_S Term_S where
+  isvar (Var_S x) = Just (SubstName x)
+  isvar _         = Nothing
+
+replace_S :: Name Term_S -> Term_S -> Term_S -> Term_S
+replace_S nm t t' = subst nm t t'
+
+replaceTest_S :: Fresh m => Name Term_S -> Term_S -> Term_S -> m Term_S
+replaceTest_S n t t' = return $ replace_S n t t'
+
+-- NameToString
+n2s :: Name a -> String
+n2s = name2String

### 2018-09-13 post-linearity-2018/Elle-ND/implementation/TypeCheck.hs

@@ -1,0 +1,374 @@
+{-# LANGUAGE FlexibleContexts #-}
+
+---------------------------------------------------------
+-- Type checking the terms defined in Syntax.hs        --
+---------------------------------------------------------
+
+module TypeCheck where
+
+import Text.Parsec
+import Control.Monad.Except
+import Data.List
+
+import Syntax
+import Parser
+
+-----------------------------------------------------------------------
+-- (T) Typing contexts                                               --
+-----------------------------------------------------------------------
+type Ctx_T = [(TmName_T, Type_T)]
+
+emptyCtx_T :: Ctx_T
+emptyCtx_T = []
+
+extCtx_T :: Ctx_T -> TmName_T -> Type_T -> Ctx_T
+extCtx_T ctx x ty = (x, ty) : ctx
+
+infixr 5 |:|
+(|:|) :: (TmName_T, Type_T) -> Ctx_T -> Ctx_T
+(x,t) |:| ctx = extCtx_T ctx x t
+
+-----------------------------------------------------------------------
+-- (S) Typing contexts                                               --
+-----------------------------------------------------------------------
+type Ctx_S = [(TmName_S, Type_S)]
+
+emptyCtx_S :: Ctx_S
+emptyCtx_S = []
+
+extCtx_S :: Ctx_S -> TmName_S -> Type_S -> Ctx_S
+extCtx_S ctx x ty = (x, ty) : ctx
+
+infixr 5 |::|
+(|::|) :: (TmName_S, Type_S) -> Ctx_S -> Ctx_S
+(x,t) |::| ctx = extCtx_S ctx x t
+
+-----------------------------------------------------------------------
+-- Typing contexts                                               --
+-----------------------------------------------------------------------
+type Ctx = (Ctx_T, Ctx_S)
+
+emptyCtx :: Ctx
+emptyCtx = ([], [])
+
+extCtx1 :: Ctx -> TmName_T -> Type_T -> Ctx
+extCtx1 (ctxT, ctxS) x ty = ((x, ty) : ctxT, ctxS)
+
+infix 5 |+|
+(|+|) :: (TmName_T, Type_T) -> Ctx -> Ctx
+(x, t) |+| ctx = extCtx1 ctx x t
+
[…]

### 2018-09-22 post-linearity-2018/LAM.tex
Added sequent calculus and cut elimination theorem.

@@
-We now introduce Commutative/Non-commutative (CNC) logic in the form
-of a term assignment.  One should view this logic as composed of two
-logics; one sitting to the left of the other.  On the left, there is
-intuitionistic linear logic, denoted by $\cat{C}$, and on the right is
-the Lambek calculus denoted by $\cat{L}$.  Then we connect these two
-systems by a pair of monoidal adjoint functors $\cat{C} : \func{F}
-\dashv \func{G} : \cat{L}$.  Keeping this intuition in mind we now
-define the syntax for CNC logic.
+Similar as the sequent calculus, the term assignment for CNC logic is also
+composed of two logics; intuitionistic linear logic on the left, denoted by
+$\cat{C}$, and the Lambek calculus on the right, denoted by $\cat{L}$. The
+two systems by a pair of monoidal adjoint functors
+$\cat{C}:\func{F} \dashv \func{G}:\cat{L}$. The syntax for types and
+contexts we use in the term assignment is the same as in the sequent
+calculus. The rest of the syntax for the term assignment is defined as
+follows.
 \begin{definition}
   \label{def:Lambek-syntax}
-  The following grammar describes the syntax of CNC logic:
+  The following grammar describes the syntax of the term assignment of the
+  CNC logic:
   \begin{center}\vspace{-3px}\small
@@
       \begin{array}{lll}        
-        \text{($\cat{C}$-Types)} & [[W]],[[X]],[[Y]],[[Z]] ::= [[UnitT]] \mid [[X (*) Y]] \mid [[X -o Y]] \mid [[Gf A]]\\
-        \text{($\cat{L}$-Types)} & [[A]],[[B]],[[C]],[[DT]] ::= [[UnitS]] \mid [[A (>) B]] \mid [[A -> B]] \mid [[B <- A]] \mid [[F X]]\\        
         \text{($\cat{C}$-Terms)} & [[t]] ::= [[x]] \mid [[trivT]] \mid [[t1 (*) t2]] \mid [[let t1 : X be q in t2]] \mid [[\x:X.t]] \mid [[t1 t2]] \mid [[ex t1 , t2 with x1 , x2 in t3]] \mid [[Gf s]]\\
@@
         \text{($\cat{L}$-Patterns)} & [[p]] ::= [[trivSp]] \mid [[x]] \mid [[p1 (>) p2]] \mid [[F q]]\\        
-        \text{($\cat{C}$-Contexts)} & [[I]],[[P]] ::= [[.]] \mid [[x : X]] \mid [[I,P]]\\
-        \text{($\cat{L}$-Contexts)} & [[G]],[[D]] ::= [[.]] \mid [[x : A]] \mid [[x : X]] \mid [[G;D]]\\        
         \text{($\cat{C}$-Typing Judgment)} & [[I |-c t : X]]\\
@@
 
-The syntax for $\cat{C}$-types are the standard types for
-intuitionistic linear logic.  We have a constant $[[UnitT]]$, tensor
-product $[[X (*) Y]]$, and linear implication $[[X -o Y]]$, but just
-as in LNL logic we also have a type $[[Gf A]]$ where $[[A]]$ is an
-$\cat{L}$-type; that is, a type from the non-commutative side
-corresponding to the right-adjoint functor between $\cat{L}$ and
-$\cat{C}$. This functor can be used to import types and terms from the
-non-commutative side into the commutative side.  Now $\cat{C}$-typing
-judgments are denoted by $[[P |-c t : X]]$ where $[[P]]$ is a sequence
-of pairs of variables and their types, denoted by $[[x : X]]$, $[[t]]$
-is a $\cat{C}$-term, and $[[X]]$ is a $\cat{C}$-type.  The
-$\cat{C}$-terms are all standard, but $[[Gf s]]$ corresponds to the
-morphism part of the right-adjoint of the adjunction between both
-logics, and $[[ex t1 , t2 with x1 , x2 in t3]]$ is the introduction
-form for the structural rule exchange.
+Now $\cat{C}$-typing judgments are denoted by $[[P |-c t : X]]$ where
+$[[P]]$ is a sequence of pairs of variables and their types, denoted by
+$[[x : X]]$, $[[t]]$ is a $\cat{C}$-term, and $[[X]]$ is a $\cat{C}$-type.  
+The $\cat{C}$-terms are all standard, but $[[Gf s]]$ corresponds to the
+morphism part of the right-adjoint of the adjunction between both logics,
+and $[[ex t1 , t2 with x1 , x2 in t3]]$ is the introduction form for the
+structural rule exchange.
 
-The non-commutative side is a bit more interesting than the
-commutative side just introduced.  The $\cat{L}$-typing judgment has
-the form $[[G |-l s : A]]$ where $[[G]]$ is now a $\cat{L}$-context,
-denoted by $[[G]]$ or $[[D]]$. These contexts are ordered sequences of
-pairs of free variables with their types from \emph{both} sides
-denoted by $[[x : B]]$ and $[[x : X]]$ respectively. Finally, the term
-$[[s]]$ is a $\cat{L}$-term, and $[[A]]$ is a $\cat{L}$-type.  Given
-two typing contexts $[[G]]$ and $[[D]]$ we denote their concatenation
-by $[[G;D]]$; we use a semicolon here to emphasize the fact that the
-contexts are ordered.
-
-The context consisting of hypotheses from both sides goes back to
-Benton~\cite{Benton:1994} and is a property unique to adjoint logics
-such as Benton's LNL logic and CNC logic.  This is also a very useful
-property because it allows one to make use of both sides within the
-Lambek calculus without the need to annotate every formula with a
-modality.
-
-The reader familiar with LNL logic will notice that our typing
-judgment, $[[G |-l s : A]]$, differs from Benton's. His is of the form
-$\Gamma;\Delta \vdash t : A$, where $\Gamma$ contains non-linear
-formulas, and $\Delta$ contains linear formulas.  Just as Benton
-remarks, the splitting of his contexts was a presentational device.
-One should view his contexts as merged, and hence, linear formulas
-were fully mixed with non-linear formulas.  Now why did we not use
-this presentational device?  Because, when contexts from LNL logic
-become out of order Benton could use the exchange rule to put them
-back in order again, but we no longer have general exchange. Thus, we
-are not able to keep the context organized in this way.
-
-The syntax for $\cat{L}$-types are of the typical form for the Lambek
-Calculus.  We have an unit type $[[UnitS]]$, a non-commutative tensor
-product $[[A (>) B]]$, right implication $[[A -> B]]$, and left
-implication $[[B <- A]]$.  $\cat{L}$-terms correspond to introduction
-and elimination forms for each of the previous types.  For example,
-$[[s1 (>) s2]]$ introduces a tensor, and $[[let s1 : A (>) B be x (>)
-    y in s2]]$ eliminates a tensor.
+The $\cat{L}$-typing judgment has the form $[[G |-l s : A]]$ where $[[G]]$
+is now a $\cat{L}$-context, denoted by $[[G]]$ or $[[D]]$. These contexts
+are ordered sequences of pairs of free variables with their types from
+\emph{both} sides denoted by $[[x : B]]$ and $[[x : X]]$ respectively.
+Finally, the term $[[s]]$ is a $\cat{L}$-term, and $[[A]]$ is a
+$\cat{L}$-type.  Given two typing contexts $[[G]]$ and $[[D]]$ we denote
+their concatenation by $[[G;D]]$; we use a semicolon here to emphasize the
+fact that the contexts are ordered. $\cat{L}$-terms correspond to
+introduction and elimination forms for each of the previous types. For
+example, $[[s1 (>) s2]]$ introduces a tensor, and
+$[[let s1 : A (>) B be x (>) y in s2]]$ eliminates a tensor.
 
@@
 are the rules for the mixed commutative/non-commutative Lambek
-calculus whose judgment is the $\mathcal{L}$-judgment denoted by $[[G
-    |-l s : A]]$, but the two halves are connected via the functor
+calculus whose judgment is the $\mathcal{L}$-judgment denoted by
+$[[G |-l s : A]]$, and the two halves are connected via the rules 
 rules $\NDdruleTXXGIName{}$, $\NDdruleSXXGEName{}$,
-$\NDdruleSXXFIName{}$, and $\NDdruleSXXFEName{}$.  Just as in LNL
-logic, the fact that the context $[[G]]$ on the $\mathcal{L}$ side of
-the logic is mixed results in this side having additional elimination
-rules, because the type being eliminated is constructed on the
-$\mathcal{C}$ side of the logic; for example, the rules
+$\NDdruleSXXFIName{}$, and $\NDdruleSXXFEName{}$,
 $\NDdruleSXXunitEOneName{}$, $\NDdruleSXXtenEOneName{}$, and
-$\NDdruleSXXcutOneName{}$ are additional mixed rules.
+$\NDdruleSXXcutOneName{}$.
 

### 2018-09-22 post-linearity-2018/sequent.tex
Fixed compilation.  You needed to include:
\input{ElleType-inc}

in main.tex
Added sequent calculus and cut elimination theorem.

@@
-Section for sequent calculus
+We now introduce Commutative/Non-commutative (CNC) logic in the form of a
+sequent calculus. One should view this logic as cmposed of two logics; one
+sitting to the left of the other. On the left, there is intuitionistic
+linear logic, denoted by $\cat{C}$ and on the right is the Lambek calculus
+denoted by $\cat{L}$. Then we connect these two systems by a pair of
+monoidal adjoint functors $\cat{C} : \func{F} \dashv \func{G} : \cat{L}$.
+Keeping this intuition in mind we now define the syntax for CNC logic.
 
+\begin{definition}
+  \label{def:Lambek-syntax}
+  The following grammar describes the syntax of the sequent calculus of
+  CNC logic:
+  \begin{center}\vspace{-3px}\small
+    \begin{math}
+      \begin{array}{lll}
+        \text{($\cat{C}$-Types)} & [[W]],[[X]],[[Y]],[[Z]] ::= [[UnitT]] \mid [[X (*) Y]] \mid [[X -o Y]] \mid [[Gf A]]\\
+        \text{($\cat{L}$-Types)} & [[A]],[[B]],[[C]],[[DT]] ::= [[UnitS]] \mid [[A (>) B]] \mid [[A -> B]] \mid [[B <- A]] \mid [[F X]]\\
+        \text{($\cat{C}$-Contexts)} & [[I]],[[P]] ::= [[.]] \mid [[X]] \mid [[I,P]]\\
+        \text{($\cat{L}$-Contexts)} & [[G]],[[D]] ::= [[.]] \mid [[A]] \mid [[X]] \mid [[G;D]]\\
+      \end{array}
+    \end{math}
+  \end{center}
+\end{definition}
+
+The syntax for $\cat{C}$-types are the standard types for intuitionistic
+linear logic. We have a constant $[[UnitT]]$, tensor product $[[X (*) Y]]$,
+and linear implication $[[X -o Y]]$, but just as in LNL logic we also have a
+type $[[Gf A]]$ where $[[A]]$ is an $\cat{L}$-type; that is, a type from the
+non-commutative side corresponding to the right-adjoint functor between
+$\cat{L}$ and $\cat{C}$. This functor can be used to import types from the
+non-commutative side into the commutative side. Now a sequent in the the
+commutative side is denoted by $[[I |-c X]]$ where $[[I]]$ is a
+$\cat{C}$-context, which is a sequence of types $[[X]]$.
+
+The non-commutative side is a bit more interesting than the commutative side
+just introduced. Sequents in the non-commutative side are denoted by
+$[[G |-l A]]$ where $[[G]]$ is now a $\cat{L}$-context. These contexts are
+ordered sequences of types from \emph{both} sides denoted by $[[B]]$ and
+$[[X]]$ respectively. Given two contexts $[[G]]$ and $[[D]]$ we denote their
+concatenation by $[[G;D]]$; we use a semicolon here to emphasize the fact
+that the contexts are ordered.
+
+The context consisting of hypotheses from both sides goes back to
+Benton~\cite{Benton:1994} and is a property unique to adjoint logics such as
+Benton's LNL logic and CNC logic. This is also a very useful property
+because it allows one to make use of both sides within the Lambek calculus
+without the need to annotate every formula with a modality.
+
+The reader familiar with LNL logic will notice that our sequent,
+$[[G |-l A]]$, differs from Benton's. His is of the form $[[G; D |-l A]]$,
+where $[[G]]$ contains non-linear types, and $[[D]]$ contains linear
+formulas. Just as Benton remarks, the splitting of his contexts was a
+presentational device. One should view his contexts as merged, and hence,
+linear formulas were fully mixed with non-linear formulas. Now why did we
+not use this presentational device? Because, when contexts from LNL logic
+become out of order Benton could use the exchange rule to put them back in
+order again, but we no longer have general exchange. Thus, we are not able
+to keep the context organized in this way.
+
+The syntax for $\cat{L}$-types are of the typical form for the Lambek
+Calculus. We have a unit type $[[UnitS]]$, a non-commutative tensor product
+$[[A (>) B]]$, right implication $[[A -> B]]$, and left implication
+$[[B <- A]]$.
+
+The sequenct calculus for CNC logic can be found in
+Figure~\ref{fig:CNC-sequent-calculus}.
+\begin{figure}[!h]
+  \footnotesize
+  \begin{tabular}{|c|}
+    \hline\\
     \begin{mathpar}
-\end{mathpar}
+    \SCdruleTXXax{} \and
+    \SCdruleTXXunitL{} \and
+    \SCdruleTXXunitR{} \and
+    \SCdruleTXXtenL{} \and
+    \SCdruleTXXtenR{} \and
+    \SCdruleTXXimpL{} \and
+    \SCdruleTXXimpR{} \and
+    \SCdruleTXXGr{} \and
+    \SCdruleTXXex{} \and
+    \SCdruleTXXcut{}
+    \end{mathpar}\\\\
+    \hline
+    \\[5px]
+    \begin{mathpar}
+    \SCdruleSXXax{} \and
+    \SCdruleSXXunitLOne{} \and
+    \SCdruleSXXunitLTwo{} \and
+    \SCdruleSXXunitR{} \and
+    \SCdruleSXXex{} \and
+    \SCdruleSXXtenLOne{} \and
+    \SCdruleSXXtenLTwo{} \and
+    \SCdruleSXXtenR{} \and
+    \SCdruleSXXimpL{} \and
+    \SCdruleSXXimprL{} \and
+    \SCdruleSXXimprR{} \and
+    \SCdruleSXXimplL{} \and
+    \SCdruleSXXimplR{} \and
+    \SCdruleSXXFl{} \and
+    \SCdruleSXXFr{} \and
+    \SCdruleSXXGl{} \and
+    \SCdruleSXXcutOne{} \and
+    \SCdruleSXXcutTwo{} \and
+    \end{mathpar}\\\\
+    \hline
+  \end{tabular}
+  \caption{Sequent Calculus for CNC Logic}
+  \label{fig:CNC-sequent-calculus}
+\end{figure}
+We split the figure in two: the top of the figure are the rules of
+intuitionistic linear logic whose sequents are the $\mathcal{C}$-sequents
+denoted by $[[P |-c X]]$, and the bottom of the figure are the rules for the
+mixed commutative/non-commutative Lambek calculus whose sequents are the
+$\mathcal{L}$-sequents denoted by $[[G |-l A]]$, but the two halves are
+connected via the functor rules $\SCdruleTXXGrName{}$,
+$\SCdruleSXXGlName{}$, $\SCdruleSXXFlName{}$, and $\SCdruleSXXFrName{}$, and
+the rules $\SCdruleSXXunitLOneName{}$, $\SCdruleSXXexName{}$,
+$\SCdruleSXXtenLOneName{}$, $\SCdruleSXXimpLName{}$,
+$\NDdruleSXXcutOneName{}$.
+
+We prove cut elimination for the sequent calculus. We define the
+\textit{degree} $|X|$ (resp. $|A|$) of a commutative (resp. non-commutative)
+formula to be the number of logical connectives in the proposition. For
+instance, $|[[X (*) Y]]| = |[[X]]| + |[[Y]]| + 1$. The \textit{cut rank}
+$c(\Pi)$ of a proof $\Pi$ is one more than the maximum of the ranks of all
+the cut formulae in $\Pi$, and $0$ if $\Pi$ is cut-free. Then the
+\textit{depth} $d(\Pi)$ of a proof $\Pi$ is the length of the longest path
+in the proof tree (so the depth of an axiom is $0$). The key to the proof
+of cut elimination is the following lemma, which shows how to transform a
+single cut, either by removing it or by replacing it with one or more
+simpler cuts.
+
+\begin{lemma}[Cut Reduction]
+  \label{lem:cut-reduction}
+  \begin{enumerate}
+  \item If $\Pi_1$ is a proof of $[[I |-c X]]$ and $\Pi_2$ is a proof of
+  $[[P1,X,P2 |-c Y]]$ with $c(\Pi_1)$, $c(\Pi_2)\leq |X|$, then there exists
+  a proof $\Pi$ of $[[P1, I, P2 |-c Y]]$ with $c(\Pi)\leq |X|$.
+  \item If $\Pi_1$ is a proof of $[[I |-c X]]$ and $\Pi_2$ is a proof of
+  $[[G1; X; G2 |-l A]]$ with $c(\Pi_1)$, $c(\Pi_2)\leq |X|$, then there
+  exists a proof $\Pi$ of $[[G1; I; G2 |-l A]]$ with $c(\Pi)\leq |X|$.
+  \item If $\Pi_1$ is a proof of $[[G |-l A]]$ and $\Pi_2$ is a proof of
+  $[[D1; A; D2 |-l B]]$ with $c(\Pi_1)$, $c(\Pi_2)\leq |A|$, then there
+  exists a proof $\Pi$ of $[[D1; G; D2 |-l B]]$ with $c(\Pi)\leq |A|$.
+  \end{enumerate}
+\end{lemma}
+\begin{proof}
+  The proof is done case by case similar as in \cite{Mellies:2009}.
+\end{proof}
+
+\begin{lemma}
+  \label{lem:less-cut-rank}
+  Let $\Pi$ be a proof of a sequent $[[I |-c X]]$ or $[[G |-l A]]$ s.t.
+  $c(\Pi)>0$. Then there is a proof $\Pi'$ of the same sequent with
+  $c(\Pi')<c(\Pi)$.
+\end{lemma}
+\begin{proof}
+  We prove the lemma by induction on $d(\Pi)$. We denote the proof $\Pi$ by 
+  $\pi+r$, where $r$ is the last inference of $\Pi$ and $\pi$ denotes the
+  rest of the proof. If $r$ is not a cut, then by induction hypothesis on
+  $\pi$, there is a proof $\pi'$ s.t. $c(\pi')>c(\pi)$ and $\Pi'=\pi'+r$.
+  Otherwise, we assume $r$ is a cut on a formula $X$. If $c(\Pi)>|X|+1$,
+  then there is a cut on $|Y|$ in $\pi$ with $|Y|>|X|$. So we can apply
+  the induction hypothesis on $\pi$ to get $\Pi'$ with $c(\Pi')<c(\Pi)$. The
+  last case to consider is when $c(\Pi)=|X|+1$ (note that $c(\Pi)$ cannot be
+  less than $|X|+1$). In this case, $\Pi$ is in the form of
+  \begin{center}
+    \scriptsize
+    \begin{math}
+      $$\mprset{flushleft}
+      \inferrule* [right={\tiny cut}] {
+        {
+          \begin{array}{cc}
+            \Pi_1 & \Pi_2 \\
+            {[[I |-c X]]} & {[[P1, X, P2 |-c Y]]}
+          \end{array}
+        }
+      }{[[P1, I, P2 |-c Y]]}
+    \end{math}
+    \qquad\qquad
+    or,
+    \begin{math}
+      $$\mprset{flushleft}
+      \inferrule* [right={\tiny cut1}] {
+        {
+          \begin{array}{cc}
+            \Pi_1 & \Pi_2 \\
+            {[[I |-c X]]} & {[[G1; X; G2 |-l A]]}
+          \end{array}
+        }
+      }{[[G1; I; G2 |-l A]]}
+    \end{math}
+  \end{center}
+  By assumption, $c(\Pi_1),c(\Pi_2)\leq |X|+1$. By induction, we can
+  construct $c(\Pi_1')$ proving $[[I |-c X]]$ and $c(\Pi_2')$ proving
+  $[[P1, X, P2 |-c Y]]$ (or $<[[G1; X; G2 |-l A]]$) with
+  $c(\Pi_1'), c(\Pi_2')\leq |X|$. Then by Lemma~\ref{lem:cut-reduction}, we 
+  can construct $\Pi'$ proving $[[P1, I, P2 |-c Y]]$ (or
+  $[[G1; I; G2 |-l A]]$) with $c(\Pi')\leq |X|$. \\
+  The case where the last inference is a cut on a formula $A$ is similar as 
+  when it is a cut on $X$.
+\end{proof}
+
+\begin{theorem}[Cut Elimination]
+  Let $\Pi$ be a proof of a sequent $[[I |-c X]]$ or $[[G |-l A]]$ s.t.
+  $c(\Pi)>0$. Then there is an algorithm which yields a cut-free proof
+  $\Pi'$ of the same sequent.
+\end{theorem}
+\begin{proof}
+  This follows immediately by induction on $c(\Pi)$ and
+  Lemma~\ref{lem:less-cut-rank}.
+\end{proof}

### 2018-10-01 post-linearity-2018/sequent.tex
Proof for cut-elimination in the appendix

@@
 The syntax for $\cat{L}$-types are of the typical form for the Lambek
-Calculus. We have a unit type $[[UnitS]]$, a non-commutative tensor product
-$[[A (>) B]]$, right implication $[[A -> B]]$, and left implication
-$[[B <- A]]$.
+Calculus. We have two unit types $[[UnitS]]$ (one for each side), a
+non-commutative tensor product $[[A (>) B]]$, right implication
+$[[A -> B]]$, and left implication $[[B <- A]]$.
 
 The sequenct calculus for CNC logic can be found in
-Figure~\ref{fig:CNC-sequent-calculus}.
+Figure~\ref{fig:CNC-sequent-calculus}. We split the figure in two: the top
+of the figure are the rules of intuitionistic linear logic whose sequents
+are the $\mathcal{C}$-sequents denoted by $[[P |-c X]]$, and the bottom of
+the figure are the rules for the mixed commutative/non-commutative Lambek
+calculus whose sequents are the $\mathcal{L}$-sequents denoted by
+$[[G |-l A]]$, but the two halves are connected via the functor rules
+$\SCdruleTXXGrName{}$, $\SCdruleSXXGlName{}$, $\SCdruleSXXFlName{}$, and
+$\SCdruleSXXFrName{}$, and the rules $\SCdruleSXXunitLOneName{}$,
+$\SCdruleSXXexName{}$, $\SCdruleSXXtenLOneName{}$, $\SCdruleSXXimpLName{}$,
+$\NDdruleSXXcutOneName{}$.
 \begin{figure}[!h]
@@
 \end{figure}
-We split the figure in two: the top of the figure are the rules of
-intuitionistic linear logic whose sequents are the $\mathcal{C}$-sequents
-denoted by $[[P |-c X]]$, and the bottom of the figure are the rules for the
-mixed commutative/non-commutative Lambek calculus whose sequents are the
-$\mathcal{L}$-sequents denoted by $[[G |-l A]]$, but the two halves are
-connected via the functor rules $\SCdruleTXXGrName{}$,
-$\SCdruleSXXGlName{}$, $\SCdruleSXXFlName{}$, and $\SCdruleSXXFrName{}$, and
-the rules $\SCdruleSXXunitLOneName{}$, $\SCdruleSXXexName{}$,
-$\SCdruleSXXtenLOneName{}$, $\SCdruleSXXimpLName{}$,
-$\NDdruleSXXcutOneName{}$.
 
@@
 simpler cuts.
-
 \begin{lemma}[Cut Reduction]
@@
 \end{lemma}
-\begin{proof}
-  The proof is done case by case similar as in \cite{Mellies:2009}.
-\end{proof}
+The proof for Lemma~\ref{lem:cut-reduction} is done case by case on the last
+step of $\Pi_1$ and $\Pi_2$ and by induction on $d(\Pi_1)$ and $d(\Pi_2)$,
+following \cite{Mellies:2009}. For instance, suppose $\Pi_1$ is a proof of
+$[[I1, X2, X1, I2 |-c Y]]$ and $\Pi_2$ is a proof of $[[P1, Y, P2 |-c Z]]$. 
+Consider the case where the last step in $\Pi_1$ uses the rule
+$\NDdruleTXXbetaName{}$. $\Pi_1$ can be depicted as follows, where the
+previous steps is denoted by $\pi$:
+\begin{center}
+  \scriptsize
+  $\Pi_1$:
+  \begin{math}
+    $$\mprset{flushleft}
+    \inferrule* [right={\tiny ex}] {
+      {
+        \begin{array}{c}
+          \pi \\
+          {[[I1, X1, X2, I2 |-c Y]]}
+        \end{array}
+      }
+    }{[[I1, X2, X1, I2 |-c Y]]}
+  \end{math}
+\end{center}
+By assumption, $c(\Pi_1),c(\Pi_2)\leq |Y|$. By induction on $\pi$ and
+$\Pi_2$, there is a proof $\Pi'$ for the sequent \\
+$[[P1, I1, X1, X2, I2, P2 |-c Z]]$ s.t. $c(\Pi')\leq|Y|$. Therefore, the
+proof $\Pi$ can be constructed as follows, and $c(\Pi)=c(\Pi')\leq|Y|$.
+\begin{center}
+  \scriptsize
+  \begin{math}
+    $$\mprset{flushleft}
+    \inferrule* [right={\tiny ex}] {
+      {
+        \begin{array}{c}
+          \Pi' \\
+          {[[P1, I1, X1, X2, I2, P2 |-c Z]]}
+        \end{array}
+      }
+    }{[[P1, I1, X2, X1, I2, P2 |-c Z]]}
+  \end{math}
+\end{center}
+The full proof of Lemma~\ref{lem:cut-reduction} is in the Appendix. Then we
+have the following lemma.
 
@@
 
+By induction on $c(\Pi)$ and Lemma~\ref{lem:less-cut-rank}, the cut
+elimination theorem follows immediately.
 \begin{theorem}[Cut Elimination]
@@
 \end{theorem}
-\begin{proof}
-  This follows immediately by induction on $c(\Pi)$ and
-  Lemma~\ref{lem:less-cut-rank}.
-\end{proof}

### 2018-10-09 post-linearity-2018/LAM.tex
Added all proofs in appendix. Added equivalence between sequence calculus and natural deduction. Changed some notations for rule names.

@@
 
-\textbf{Additional Results.} The following subsection shows the
-reduction rules for CNC Logic. In addition to the results given in this
-paper we also have defined a sequent calculus for CNC logic, proved
-cut elimination, and proved the the sequent calculus formalization is
-equivalent to the natural deduction formalization given here.
-Furthermore, we proved strong normalization of CNC logic via a
-translation to LNL logic.  We omit these results due to space.
+\textbf{Additional Results.} In addition to the results given so far, we
+also proved that the sequent calculus formalization is equivalent to the
+natural deduction formalization given here
+(Appendix~\ref{app:seq-nat-equiv}). Furthermore, we proved strong
+normalization of CNC logic via a translation to LNL logic
+(Appendix~\ref{app:strong-normalization}).
 

### 2018-10-09 post-linearity-2018/adjoint-models.tex
Added all proofs in appendix. Added equivalence between sequence calculus and natural deduction. Changed some notations for rule names.

@@
 F(X\otimes Y)$ and $\m{I}:I'\rightarrow FI$ as:
-\vspace{-20px}
 \begin{mathpar}
@@
 \begin{theorem}
+\label{thm:m-natural-iso}
   $\m{X,Y}$ are components of a natural isomorphism and their inverses are $\p{X,Y}$. 
@@
   This proof follows by a diagram chase using the adjunction in the
-  definition of a LAM and naturality.
+  definition of a LAM and naturality. The detail of the proof is in
+  Appendix~\ref{app:m-natural-iso}.
+\end{proof}
+
+\begin{theorem}
+\label{thm:m-iso}
+  $\m{I}$ is an isomorphism and its inverse is $\p{I}$.
+\end{theorem}
+\begin{proof}
+  This is equivalent to equations $\m{I}\circ\p{I}=id_{FI}$ and
+  $\p{I}\circ\m{I}=id_{I'}$, equivalent to the following diagrams, which
+  commute because $\varepsilon$ is a monoidal natural transformation.
+  \begin{mathpar}
+  \bfig
+    \square/->`=`->`<-/<400,400>[FI`FGI'`FI`I';F\n{I'}``\varepsilon_{I'}`\m{I}]
+  \efig
+  \and
+  \bfig
+    \square/->`=`->`<-/<400,400>[I'`FI`I'`FGI';\m{I}``F\n{I'}`\varepsilon_{I'}]
+  \efig
+  \end{mathpar}
 \end{proof}
@@
 \end{lemma}
+\begin{proof}
+  The proof is done by checking the conditions for a functor being monoidal.
+  The detail of the proof is in Appendix~\ref{app:monoidal-monad}.
+\end{proof}
 \noindent
@@
 \end{lemma}
+\begin{proof}
+The proof is done by frist defining a natural transformation $\tau$, called
+the \textbf{tensorial strength}, with components
+$\tau_{A,B}:A\tri TB\rightarrow T(A\tri B)$, and then proving the
+commutativity of several diagrams through diagram chasing. The formal
+definition for a strong monad and the full proof are in
+Appendix~\ref{app:strong-monad}.
+\end{proof}
 \noindent
@@
   \efig$$
-  in which $\e{}$ is the exchange for $\cat{C}$.  The remainder of the
-  proof is fairly straightforward, and shows that the typical diagrams
-  for any symmetric monoidal category hold.
+  in which $\e{}$ is the exchange for $\cat{C}$. Then $\e{}^{FG}$ is a
+  natural transformation because the following diagrams commute for
+  morphisms $f:A\rightarrow A'$ and $g:B\rightarrow B'$:
+  \begin{mathpar}
+  \bfig
+    \square|almb|<700,400>[
+      A\tri B`FGA\tri FGB`A'\tri B'`FGA'\tri FGB';
+      h_A\tri h_B`f\tri g`FGf\tri FGg`h_{A'}\tri h_{B'}]
+    \square(700,0)|ammb|/->``->`->/<800,400>[
+      FGA\tri FGB`F(GA\otimes GB)`FGA'\tri FGB'`F(GA'\otimes GB');
+      \m{GA,GB}``F(Gf\otimes Gg)`\m{GA',GB'}]
+    \square(1500,0)|ammb|/->``->`->/<800,400>[
+      F(GA\otimes GB)`F(GB\otimes GA)`F(GA'\otimes GB')`F(GB'\otimes GA');
+      F\e{A,B}``F(Gg\otimes Gf)`F\e{A',B'}]
+    \square(2300,0)|ammb|/->``->`->/<800,400>[
+      F(GB\otimes GA)`FG(B\tri A)`F(GB'\otimes GA')`FG(B'\tri A');
+      F\n{B,A}``FG(g\tri f)`F\n{B',A'}]
+    \square(3100,0)|amrb|/->``->`->/<600,400>[
+      FG(B\tri A)`B\tri A`FG(B'\tri A')`B'\tri A';
+      \varepsilon_{B\tri A}``g\tri f`\varepsilon_{B'\tri A'}]
+  \efig
+  \end{mathpar}
 \end{proof}

### 2018-10-09 post-linearity-2018/sequent.tex
Added all proofs in appendix. Added equivalence between sequence calculus and natural deduction. Changed some notations for rule names.
Some small format changes.

@@
   \label{lem:cut-reduction}
+  The cut-reduction steps are as follows:
   \begin{enumerate}
@@
 \end{lemma}
-The proof for Lemma~\ref{lem:cut-reduction} is done case by case on the last
-step of $\Pi_1$ and $\Pi_2$ and by induction on $d(\Pi_1)$ and $d(\Pi_2)$,
-following \cite{Mellies:2009}. For instance, suppose $\Pi_1$ is a proof of
-$[[I1, X2, X1, I2 |-c Y]]$ and $\Pi_2$ is a proof of $[[P1, Y, P2 |-c Z]]$. 
-Consider the case where the last step in $\Pi_1$ uses the rule
-$\NDdruleTXXbetaName{}$. $\Pi_1$ can be depicted as follows, where the
-previous steps is denoted by $\pi$:
+\begin{proof}
+  This proof is done case by case on the last step of $\Pi_1$ and
+  $\Pi_2$ and by induction on $d(\Pi_1)$ and $d(\Pi_2)$, following
+  \cite{Mellies:2009}. For instance, suppose $\Pi_1$ is a proof of
+  $[[I1, X2, X1, I2 |-c Y]]$ and $\Pi_2$ is a proof of $[[P1, Y, P2
+      |-c Z]]$.  Consider the case where the last step in $\Pi_1$ uses
+  the rule $\NDdruleTXXbetaName{}$. $\Pi_1$ can be depicted as
+  follows, where the previous steps is denoted by $\pi$:
   \begin{center}
@@
   \end{center}
-The full proof of Lemma~\ref{lem:cut-reduction} is in the Appendix. Then we
-have the following lemma.
+  The full proof of Lemma~\ref{lem:cut-reduction} is in
+  Appendix~\ref{app:cut-reduction}. 
+\end{proof}
+\noindent
+Then we have the following lemma.
 
@@
 \end{proof}
-
+\noindent
 By induction on $c(\Pi)$ and Lemma~\ref{lem:less-cut-rank}, the cut

### 2018-10-09 post-linearity-2018/LAM.tex
Strong normalization.

@@
 
-\textbf{Additional Results.} In addition to the results given so far, we
-also proved that the sequent calculus formalization is equivalent to the
-natural deduction formalization given here
-(Appendix~\ref{app:seq-nat-equiv}). Furthermore, we proved strong
-normalization of CNC logic via a translation to LNL logic
-(Appendix~\ref{app:strong-normalization}).
+We also proved that the sequent calculus formalization given in
+Figure~\ref{fig:CNC-sequent-calculus} is equivalent to the typing rules (or
+else called the natural deduction formalization) given in
+Figure~\ref{fig:CNC-typing-rules} are equivalent, as stated in the following
+theorem.
+\begin{theorem}
+  \label{thm:sc-nd-equiv}
+  The sequent calculus ($\mathit{SC}$) and natural deduction ($\mathit{ND}$)
+  formalizations for CNC logic are equivalent in the sense that there are
+  two mappins $N:\mathit{SC}\rightarrow\mathit{ND}$ and
+  $S:\mathit{ND}\rightarrow\mathit{SC}$ that map each rule in $\mathit{SC}$
+  to a proof in $\mathit{ND}$, and each rule in $\mathit{ND}$ to a proof
+  in $\mathit{SC}$, respectively.
+\end{theorem}
+\begin{proof}
+  The proof is done case by case on each rule in the sequence calculus and
+  natural deduction formalizations. It is obvious that the axioms in one
+  formalization can be mapped to the axioms in the other. The introduction
+  rules in $\mathit{ND}$ are mapped to the right rules in $\mathit{SC}$, and
+  vice versa. The elimination rules and lefts rules are mapped to each other
+  with some fiddling. For instance, the elimination rule for the
+  non-commutative tensor is mapped to the following proof in $\mathit{SC}$:
+  \begin{center}
+    \scriptsize
+    \begin{math}
+      $$\mprset{flushleft}
+      \inferrule* [right={\scriptsize $\ElledruleTXXcutName$}] {
+        {[[I |-c t1 : X (*) Y]]} \\
+        $$\mprset{flushleft}
+        \inferrule* [right={\scriptsize $\ElledruleTXXtenLName$}] {
+          {[[P1, x : X, y : Y, P2 |-c t2 : Z]]}
+        }{[[P1, z : X (*) Y, P2 |-c let z : X (*) Y be x (*) y in t2 : Z]]}
+      }{[[P1, I, P2 |-c [t1 / z](let z : X (*) Y be x (*) y in t2) : Z]]}
+    \end{math}
+  \end{center}
+  The full proof is in Appendix~\ref{app:sc-nd-equiv}.
+\end{proof}
+
+Finally, we proved strong normalization of CNC logic via a translation to
+LNL logic. The proof is in Appendix~\ref{app:strong-normalization}. We first
+define a function $CL$ that maps our term assignment for natural deduction
+to Benton's term assignment, and then shows that if there is reduction
+$[[t1 ~> t2]]$ (resp. $[[s1 ~> s2]]$) in CNC, then there is a reduction
+$CL(t_1)\leadsto CL(t_2)$ (resp. $CL(s_1)\leadsto CL(s_2)$) in LNL. Recall
+that a LNL model consists of an adjunction $F:\cat{C}\dashv\cat{L}:G$ in
+which $\cat{C}$ is a cartesian closed category and $\cat{L}$ is a SMCC.
+The basic idea of mapping a LAM model to a LNL model is mapping the SMCC in
+LAM to the cartesian closed category in LNL, and the Lambek category in LAM
+to the SMCC in LNL. For instance, $s_1\triangleright s_2$ in CNC, where
+$[[s1]]$ and $[[s2]]$ are atomic terms, maps to $s_1\otimes s_2$ in LNL.
 

### 2018-10-09 post-linearity-2018/adjoint-models.tex
Strong normalization.

@@
 F(X\otimes Y)$ and $\m{I}:I'\rightarrow FI$ as:
+\vspace{-1em}
 \begin{mathpar}
+\footnotesize
 \bfig
@@
 \efig
-\and
+\end{mathpar}
+\vspace{-1.6em}
+\begin{mathpar}
+\footnotesize
 \bfig
@@
 \end{mathpar}
-We can now see that this straightforwardly follows from Benton's proof.
-
-\begin{theorem}
-\label{thm:m-natural-iso}
-  $\m{X,Y}$ are components of a natural isomorphism and their inverses are $\p{X,Y}$. 
-\end{theorem}
-\begin{proof}
-  This proof follows by a diagram chase using the adjunction in the
-  definition of a LAM and naturality. The detail of the proof is in
-  Appendix~\ref{app:m-natural-iso}.
-\end{proof}
-
 \begin{theorem}
@@
   \begin{mathpar}
+  \footnotesize
   \bfig
@@
     \square/->`=`->`<-/<400,400>[I'`FI`I'`FGI';\m{I}``F\n{I'}`\varepsilon_{I'}]
+  \efig
+  \end{mathpar}
+\end{proof}
+
+\begin{theorem}
+\label{thm:m-natural-iso}
+  $\m{X,Y}$ are components of a natural isomorphism and their inverses are $\p{X,Y}$. 
+\end{theorem}
+\begin{proof}
+  This is equivalent to that the two equations
+  $\m{X,Y}\circ\p{X,Y}=id_{F(X\otimes Y)}$ and
+  $\p{X,Y}\circ\m{X,Y}=id_{FX\tri FX}$ hold, which is proved because the
+  following diagrams commute: (1)-adjunction; (2)-$\eta$ is a monoidal
+  natural transformation; (3)-naturality of $\varepsilon$; (4)-adjunction;
+  (5)-naturality of $\m{}$; (6)-$\varepsilon$ is a monoidal natural
+  transformation.
+  \begin{mathpar}
+  \footnotesize
+  \bfig
+    \square/->`=`->`/<1600,800>[
+      F(X\otimes Y)`F(GFX\otimes GFY)`F(X\otimes Y)`FG(FX\tri FY);
+      F(\eta_X\otimes\eta_Y)``F\n{FX,FY}`]
+    \Atrianglepair|mmmbb|/->``->`<-`<-/<800,400>[
+      FGF(X\otimes Y)`F(X\otimes Y)`FX\tri FY`FG(FX\tri FY);
+      \varepsilon_{F(X\otimes Y)}``FG\m{X,Y}`\m{X,Y}`\varepsilon_{FX\tri FY}]
+    \morphism(0,800)|m|<800,-400>[F(X\otimes Y)`FGF(X\otimes Y);F\eta_{X\otimes Y}]
+    \morphism(300,450)//<0,0>[`;(1)]
+    \morphism(1200,600)//<0,0>[`;(2)]
+    \morphism(800,200)//<0,0>[`;(3)]
+  \efig
+  \end{mathpar}
+  \begin{mathpar}
+  \footnotesize
+  \bfig
+    \square/->`=`->`/<1800,800>[
+      FX\tri FY`F(X\otimes Y)`FX\tri FY`F(GFX\otimes GFY);
+      \m{X,Y}``F(\eta_X\otimes\eta_Y)`]
+    \Atrianglepair|mmmbb|/->``->`<-`<-/<900,400>[
+      FGFX\tri FGFY`FX\tri FY`FG(FX\tri FY)`F(GFX\otimes GFY);
+      \varepsilon_{FX}\tri\varepsilon_{FY}``\m{GFX,GFY}`\varepsilon_{FX\tri FY}`F\n{FX,FY}]
+    \morphism(0,800)|m|<900,-400>[FX\tri FY`FGFX\tri FGFY;F\eta_X\tri F\eta_Y]
+    \morphism(300,450)//<0,0>[`;(4)]
+    \morphism(1300,600)//<0,0>[`;(5)]
+    \morphism(900,200)//<0,0>[`;(6)]
   \efig

### 2018-10-10 post-linearity-2018/LAM.tex
Some small changes.

@@
 
-Finally, we proved strong normalization of CNC logic via a translation to
-LNL logic. The proof is in Appendix~\ref{app:strong-normalization}. We first
-define a function $CL$ that maps our term assignment for natural deduction
-to Benton's term assignment, and then shows that if there is reduction
-$[[t1 ~> t2]]$ (resp. $[[s1 ~> s2]]$) in CNC, then there is a reduction
-$CL(t_1)\leadsto CL(t_2)$ (resp. $CL(s_1)\leadsto CL(s_2)$) in LNL. Recall
-that a LNL model consists of an adjunction $F:\cat{C}\dashv\cat{L}:G$ in
-which $\cat{C}$ is a cartesian closed category and $\cat{L}$ is a SMCC.
-The basic idea of mapping a LAM model to a LNL model is mapping the SMCC in
-LAM to the cartesian closed category in LNL, and the Lambek category in LAM
-to the SMCC in LNL. For instance, $s_1\triangleright s_2$ in CNC, where
-$[[s1]]$ and $[[s2]]$ are atomic terms, maps to $s_1\otimes s_2$ in LNL.
+\noindent
+Finally, we have strong normalization of CNC logic.
+
+\begin{theorem}[Strong Normalization]
+  \label{thm:strong-normalization}
+  CNC logic is strongly normalizing.
+\end{theorem}
+\begin{proof}
+  The proof is via a translation to LNL logic. The proof is in
+  Appendix~\ref{app:strong-normalization}. We first define a function
+  $CL$ that maps our term assignment for natural deduction to Benton's
+  term assignment, and then shows that if there is reduction $[[t1 ~>  t2]]$ (resp. $[[s1 ~> s2]]$) in CNC, then there is a reduction
+  $CL(t_1)\leadsto CL(t_2)$ (resp. $CL(s_1)\leadsto CL(s_2)$) in
+  LNL. Recall that a LNL model consists of an adjunction
+  $F:\cat{C}\dashv\cat{L}:G$ in which $\cat{C}$ is a cartesian closed
+  category and $\cat{L}$ is a SMCC.  The basic idea of mapping a LAM
+  model to a LNL model is mapping the SMCC in LAM to the cartesian
+  closed category in LNL, and the Lambek category in LAM to the SMCC in
+  LNL. For instance, $s_1\triangleright s_2$ in CNC, where $[[s1]]$ and
+  $[[s2]]$ are atomic terms, maps to $CL(s_1)\otimes CL(s_2)$ in LNL.
+\end{proof}
 

### 2018-10-22 post-linearity-2018/sequent.tex
Strong normalization.
Some small changes.
Working on the proof oflemma 29.

@@
 We now introduce Commutative/Non-commutative (CNC) logic in the form of a
-sequent calculus. One should view this logic as cmposed of two logics; one
+sequent calculus. One should view this logic as composed of two logics; one
 sitting to the left of the other. On the left, there is intuitionistic
@@
       $$\mprset{flushleft}
-      \inferrule* [right={\tiny ex}] {
+      \inferrule* [right={\tiny $\SCdruleTXXexName$}] {
         {
@@
   \end{center}
-  The full proof of Lemma~\ref{lem:cut-reduction} is in
-  Appendix~\ref{app:cut-reduction}. 
+  The full proof can be found in Appendix~\ref{app:cut-reduction}.
 \end{proof}
@@
       $$\mprset{flushleft}
-      \inferrule* [right={\tiny cut}] {
+      \inferrule* [right={\tiny $\SCdruleTXXcutName$}] {
         {
@@
     or,
+    \qquad\qquad
     \begin{math}
       $$\mprset{flushleft}
-      \inferrule* [right={\tiny cut1}] {
+      \inferrule* [right={\tiny $\SCdruleSXXcutOneName$}] {
         {

### 2018-10-22 post-linearity-2018/introduction.tex
Couple of changes.

--- 2018-05-22 linearity-2018/introduction.tex
@@
 modality now occurs on both operands being exchanged. That is, one can
-show that $eA \otimes eB \multimap eB \otimes eA$ holds.  We give a
-LNL natural deduction formalization for the Lambek calculus with this
-new modality, and two categorical models: a LNL model and a concrete
-model in dialectica spaces.  Thus giving a second solution to the
+show that $eA \otimes eB \multimap eB \otimes eA$ holds.  We give a sequent
+calculus and a LNL natural deduction formalization for the Lambek calculus
+with this new modality, and two categorical models: a LNL model and a
+concrete model in dialectica spaces. Thus giving a second solution to the
 problem proposed above.
@@
 \textbf{Acknowledgments.}  The first two authors were supported by NSF
-award \#1565557.
+award \#1565557.  We thank the anonymous reviewers for their helpful
+feedback that made this a better paper.
 

### 2018-12-23 post-linearity-2018/adjoint-models.tex
Revised based on the reviews.

--- 2018-10-09 post-linearity-2018/adjoint-models.tex
@@
 \end{definition}
+\noindent
+Lambek categories are also known as monoidal bi-closed categories.
 
@@
 \end{mathpar}
-We can now see that this straightforwardly follows from Benton's proof.
-
-\begin{theorem}
-\label{thm:m-natural-iso}
-  $\m{X,Y}$ are components of a natural isomorphism and their inverses are $\p{X,Y}$. 
-\end{theorem}
-\begin{proof}
-  This proof follows by a diagram chase using the adjunction in the
-  definition of a LAM and naturality. The detail of the proof is in
-  Appendix~\ref{app:m-natural-iso}.
-\end{proof}
-
-\begin{theorem}
-\label{thm:m-iso}
-  $\m{I}$ is an isomorphism and its inverse is $\p{I}$.
-\end{theorem}
-\begin{proof}
-  This is equivalent to equations $\m{I}\circ\p{I}=id_{FI}$ and
-  $\p{I}\circ\m{I}=id_{I'}$, equivalent to the following diagrams, which
-  commute because $\varepsilon$ is a monoidal natural transformation.
-  \begin{mathpar}
-  \bfig
-    \square/->`=`->`<-/<400,400>[FI`FGI'`FI`I';F\n{I'}``\varepsilon_{I'}`\m{I}]
-  \efig
-  \and
-  \bfig
-    \square/->`=`->`<-/<400,400>[I'`FI`I'`FGI';\m{I}``F\n{I'}`\varepsilon_{I'}]
-  \efig
-  \end{mathpar}
-\end{proof}
+Due to \cite{kelly1974doctrinal}, it can be easily shown that $\m{I}$ is an
+isomorphism with inverse, and that $\m{X,Y}$ are components of a natural
+isomorphism with inverses $\p{X,Y}$.
 
@@
 non-commutative monads using adjoint models similar to LNL models? The
-following answers their question in the positive.
+following answers their question in the positive w.r.t. the monoidal monads.
 \begin{lemma}
@@
 \noindent
-Finally, we obtain the non-communativity of the monad induced by any
+Finally, we obtain the non-communativity of the monad induced by some 
 LAM as follows.
@@
 \begin{theorem}
-  The monad, $GF : \cat{C} \mto \cat{C}$, on the SMCC in LAM is strong
-  but non-commutative.
+  There exists a LAM whose monad, $GF : \cat{C} \mto \cat{C}$, on the SMCC
+  in the LAM is strong but non-commutative.
 \end{theorem}
@@
 \textbf{Comonad for exchange}.  We conclude this section by showing
-that the comonad induced by any LAM is monoidal and extends $\cat{L}$
-with exchange.  The latter is shown by proving that its corresponding
-co-Eilenberg-Moore category is symmetric monoidal closed.
-
-\begin{lemma}
-  The comonad, $FG : \cat{L} \mto \cat{L}$, on the Lambek category in any LAM is monoidal.
-\end{lemma}
-\begin{proof}
-  This proof follows by several diagram chases, but really does not
-  depart much from Benton's proof \cite{Benton:1994}.
-\end{proof}
+that the comonad induced by some LAM is monoidal and extends $\cat{L}$
+with exchange. The former is proved in \cite{kelly1974doctrinal}. The
+latter is shown by proving that its corresponding co-Eilenberg-Moore
+category is symmetric monoidal closed.
 
@@
   $\cat{L}^{FG}$ has an exchange natural transformation $\e{A,B}^{FG}:A\tri
-  B\rightarrow B\tri A$.
+  B\rightarrow B\tri A$, and $\e{A,B}^{FG}$ is a symmetry, i.e.,
+  $\e{A,B}^{FG} \circ \e{A,B}^{FG} = id_A$.
 \end{theorem}
@@
   \end{mathpar}
+  $\e{A,B}^{FG}$ is a symmetry because the following diagrams commute:
+  \begin{mathpar}
+  \bfig
+    \ptriangle|amm|/->`=`->/<600,600>[
+      A\tri B`FGA\tri FGB`A\tri B;h_A\tri h_B``\varepsilon_A\tri\varepsilon_B]
+    \morphism(600,0)|b|<-600,0>[FG(A\tri B)`A\tri B;\varepsilon_{A\tri B}]
+    \morphism(600,600)<700,0>[FGA\tri FGB`F(GA\otimes GB);\m{GA,GB}]
+    \morphism(1300,0)|b|<-700,0>[F(GA\otimes GB)`FG(A\tri B);F\n{A,B}]
+    \square(1300,0)/->`=`=`<-/<800,600>[
+      F(GA\otimes GB)`F(GB\otimes GA)`F(GA\otimes GB)`F(GB\otimes GA);F\e{A,B}```F\e{B,A}]
+    \qtriangle(2100,0)|amr|/->``->/<1400,600>[F(GB\otimes GA)`FG(B\tri A)`B\tri A;F\n{B,A}``\varepsilon_{B\tri A}]
+    \morphism(2900,0)|b|<-800,0>[FGB\tri FGA`F(GB\otimes GA);\m{GB,GA}]
+    \btriangle(2900,0)|mmb|/<-`=`<-/<600,400>[
+      B\tri A`FGB\tri FGA`B\tri A;
+      \varepsilon_B\tri\varepsilon_A``h_A\tri h_A])
+  \efig
+  \end{mathpar}
 \end{proof}

### 2018-12-23 post-linearity-2018/sequent.tex
Couple of changes.
Revised based on the reviews.

@@
 non-commutative tensor product $[[A (>) B]]$, right implication
-$[[A -> B]]$, and left implication $[[B <- A]]$.
+$[[A -> B]]$, and left implication $[[B <- A]]$. In standard Lambek
+Calculus, $[[A -> B]]$ is written as $B / A$ and $[[B <- A]]$ as
+$A \backslash B$. We use $\rightharpoonup$ and $\leftharpoonup$ here
+instead to indicate they are two directions of the linear implication
+$\multimap$.
 
@@
 We prove cut elimination for the sequent calculus. We define the
-\textit{degree} $|X|$ (resp. $|A|$) of a commutative (resp. non-commutative)
+\textit{rank} $|X|$ (resp. $|A|$) of a commutative (resp. non-commutative)
 formula to be the number of logical connectives in the proposition. For
@@
   the rule $\NDdruleTXXbetaName{}$. $\Pi_1$ can be depicted as
-  follows, where the previous steps is denoted by $\pi$:
+  follows, where the previous steps are denoted by $\pi$:
   \begin{center}
@@
   rest of the proof. If $r$ is not a cut, then by induction hypothesis on
-  $\pi$, there is a proof $\pi'$ s.t. $c(\pi')>c(\pi)$ and $\Pi'=\pi'+r$.
-  Otherwise, we assume $r$ is a cut on a formula $X$. If $c(\Pi)>|X|+1$,
+  $\pi$, there is a proof $\pi'$ s.t. $c(\pi')<c(\pi)$ and $\Pi'=\pi'+r$.
+  Otherwise, we assume $r$ is a cut on a formula $Y$. If $c(\Pi)>|X|+1$,
   then there is a cut on $|Y|$ in $\pi$ with $|Y|>|X|$. So we can apply

### 2019-02-20 post-linearity-2018/LAM.tex
Working on the proof oflemma 29.
Removed SN, because we lack a citation that proves SN for LNL.

--- 2018-10-09 post-linearity-2018/LAM.tex
@@
-Similar as the sequent calculus, the term assignment for CNC logic is also
-composed of two logics; intuitionistic linear logic on the left, denoted by
-$\cat{C}$, and the Lambek calculus on the right, denoted by $\cat{L}$. The
-two systems by a pair of monoidal adjoint functors
-$\cat{C}:\func{F} \dashv \func{G}:\cat{L}$. The syntax for types and
-contexts we use in the term assignment is the same as in the sequent
-calculus. The rest of the syntax for the term assignment is defined as
-follows.
+Similar as the sequent calculus, the term assignment for CNC logic is
+also composed of two logics; intuitionistic linear logic on the left,
+denoted by $\cat{C}$, and the Lambek calculus on the right, denoted by
+$\cat{L}$. The syntax for types and contexts we use in the term
+assignment is the same as in the sequent calculus. The rest of the
+syntax for the term assignment is defined as follows.
 \begin{definition}
@@
   formalizations for CNC logic are equivalent in the sense that there are
-  two mappins $N:\mathit{SC}\rightarrow\mathit{ND}$ and
+  two mappings $N:\mathit{SC}\rightarrow\mathit{ND}$ and
   $S:\mathit{ND}\rightarrow\mathit{SC}$ that map each rule in $\mathit{SC}$
@@
 
-Finally, we proved strong normalization of CNC logic via a translation to
-LNL logic. The proof is in Appendix~\ref{app:strong-normalization}. We first
-define a function $CL$ that maps our term assignment for natural deduction
-to Benton's term assignment, and then shows that if there is reduction
-$[[t1 ~> t2]]$ (resp. $[[s1 ~> s2]]$) in CNC, then there is a reduction
-$CL(t_1)\leadsto CL(t_2)$ (resp. $CL(s_1)\leadsto CL(s_2)$) in LNL. Recall
-that a LNL model consists of an adjunction $F:\cat{C}\dashv\cat{L}:G$ in
-which $\cat{C}$ is a cartesian closed category and $\cat{L}$ is a SMCC.
-The basic idea of mapping a LAM model to a LNL model is mapping the SMCC in
-LAM to the cartesian closed category in LNL, and the Lambek category in LAM
-to the SMCC in LNL. For instance, $s_1\triangleright s_2$ in CNC, where
-$[[s1]]$ and $[[s2]]$ are atomic terms, maps to $s_1\otimes s_2$ in LNL.
+%% \noindent
+%% Finally, we have strong normalization of CNC logic.
+%% 
+%% \begin{theorem}[Strong Normalization]
+%%   \label{thm:strong-normalization}
+%%   CNC logic is strongly normalizing.
+%% \end{theorem}
+%% \begin{proof}
+%%   The proof is via a translation to LNL logic, which has been proved to be
+%%   strongly normalizing \cite{Mellies:2009}. The proof is in
+%%   Appendix~\ref{app:strong-normalization}. We first define a function
+%%   $CL$ that maps our term assignment for natural deduction to Benton's
+%%   term assignment, and then shows that if there is reduction $[[t1 ~>  t2]]$ (resp. $[[s1 ~> s2]]$) in CNC, then there is a reduction
+%%   $CL(t_1)\leadsto CL(t_2)$ (resp. $CL(s_1)\leadsto CL(s_2)$) in
+%%   LNL. Recall that a LNL model consists of an adjunction
+%%   $F:\cat{C}\dashv\cat{L}:G$ in which $\cat{C}$ is a Cartesian closed
+%%   category and $\cat{L}$ is a SMCC.  The basic idea of mapping a LAM
+%%   model to a LNL model is mapping the SMCC in LAM to the Cartesian
+%%   closed category in LNL, and the Lambek category in LAM to the SMCC in
+%%   LNL. For instance, $s_1\triangleright s_2$ in CNC, where $[[s1]]$ and
+%%   $[[s2]]$ are atomic terms, maps to $CL(s_1)\otimes CL(s_2)$ in LNL.
+%% \end{proof}
 

### 2019-02-20 post-linearity-2018/final-submission/Elle-ND-inc.tex
Final version sources.

% generated by Ott 0.25 from: Elle-ND/Elle-ND.ott
\newcommand{\NDdrule}[4][]{{\displaystyle\frac{\begin{array}{l}#2\end{array}}{#3}\quad\NDdrulename{#4}}}
\newcommand{\NDusedrule}[1]{\[#1\]}
\newcommand{\NDpremise}[1]{ #1 \\}
\newenvironment{NDdefnblock}[3][]{ \framebox{\mbox{#2}} \quad #3 \\[0pt]}{}
\newenvironment{NDfundefnblock}[3][]{ \framebox{\mbox{#2}} \quad #3 \\[0pt]\begin{displaymath}\begin{array}{l}}{\end{array}\end{displaymath}}
\newcommand{\NDfunclause}[2]{ #1 \equiv #2 \\}
\newcommand{\NDnt}[1]{\mathit{#1}}
\newcommand{\NDmv}[1]{\mathit{#1}}
\newcommand{\NDkw}[1]{\mathbf{#1}}
\newcommand{\NDsym}[1]{#1}
\newcommand{\NDcom}[1]{\text{#1}}
\newcommand{\NDdrulename}[1]{\textsc{#1}}
\newcommand{\NDcomplu}[5]{\overline{#1}^{\,#2\in #3 #4 #5}}
\newcommand{\NDcompu}[3]{\overline{#1}^{\,#2<#3}}
\newcommand{\NDcomp}[2]{\overline{#1}^{\,#2}}
\newcommand{\NDgrammartabular}[1]{\begin{supertabular}{llcllllll}#1\end{supertabular}}
\newcommand{\NDmetavartabular}[1]{\begin{supertabular}{ll}#1\end{supertabular}}
\newcommand{\NDrulehead}[3]{$#1$ & & $#2$ & & & \multicolumn{2}{l}{#3}}
\newcommand{\NDprodline}[6]{& & $#1$ & $#2$ & $#3 #4$ & $#5$ & $#6$}
\newcommand{\NDfirstprodline}[6]{\NDprodline{#1}{#2}{#3}{#4}{#5}{#6}}
\newcommand{\NDlongprodline}[2]{& & $#1$ & \multicolumn{4}{l}{$#2$}}
\newcommand{\NDfirstlongprodline}[2]{\NDlongprodline{#1}{#2}}
\newcommand{\NDbindspecprodline}[6]{\NDprodline{#1}{#2}{#3}{#4}{#5}{#6}}
\newcommand{\NDprodnewline}{\\}
\newcommand{\NDinterrule}{\\[5.0mm]}
\newcommand{\NDafterlastrule}{\\}
\newcommand{\NDmetavars}{
\NDmetavartabular{
 $ \NDmv{vars} ,\, \NDmv{n} ,\, \NDmv{a} ,\, \NDmv{x} ,\, \NDmv{y} ,\, \NDmv{z} ,\, \NDmv{w} ,\, \NDmv{m} ,\, \NDmv{o} $ &  \\
 $ \NDmv{ivar} ,\, \NDmv{i} ,\, \NDmv{k} ,\, \NDmv{j} ,\, \NDmv{l} $ &  \\
 $ \NDmv{const} ,\, \NDmv{b} $ &  \\
}}

\newcommand{\NDA}{
\NDrulehead{\NDnt{A}  ,\ \NDnt{B}  ,\ \NDnt{C}  ,\ D}{::=}{}\NDprodnewline
\NDfirstprodline{|}{ \mathsf{B} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{Unit} }{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{A}  \triangleright  \NDnt{B}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{A}  \rightharpoonup  \NDnt{B}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{A}  \leftharpoonup  \NDnt{B}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDsym{(}  \NDnt{A}  \NDsym{)}} {\textsf{M}}{}{}{}\NDprodnewline
\NDprodline{|}{ \NDnt{A} } {\textsf{M}}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{F} \NDnt{X} }{}{}{}{}}

\newcommand{\NDW}{
\NDrulehead{\NDnt{W}  ,\ \NDnt{X}  ,\ \NDnt{Y}  ,\ \NDnt{Z}}{::=}{}\NDprodnewline
\NDfirstprodline{|}{ \mathsf{B} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{Unit} }{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{X}  \otimes  \NDnt{Y}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{X}  \multimap  \NDnt{Y}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDsym{(}  \NDnt{X}  \NDsym{)}} {\textsf{M}}{}{}{}\NDprodnewline
\NDprodline{|}{ \NDnt{X} } {\textsf{M}}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{G} \NDnt{A} }{}{}{}{}}

\newcommand{\NDT}{
\NDrulehead{\NDnt{T}}{::=}{}\NDprodnewline
\NDfirstprodline{|}{\NDnt{A}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{X}}{}{}{}{}}

\newcommand{\NDp}{
\NDrulehead{\NDnt{p}  ,\ \NDnt{q}}{::=}{}\NDprodnewline
\NDfirstprodline{|}{ \star }{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDmv{x}}{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{triv} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{triv} }{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{p}  \otimes  \NDnt{p'}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{p}  \triangleright  \NDnt{p'}}{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{F}\, \NDnt{p} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{G}\, \NDnt{p} }{}{}{}{}}

\newcommand{\NDs}{
\NDrulehead{\NDnt{s}}{::=}{}\NDprodnewline
\NDfirstprodline{|}{\NDmv{x}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDmv{b}}{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{triv} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :  \NDnt{A} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{let}\, \NDnt{t}  :  \NDnt{X} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDnt{s} }{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{s_{{\mathrm{1}}}}  \triangleright  \NDnt{s_{{\mathrm{2}}}}}{}{}{}{}\NDprodnewline
\NDprodline{|}{ \lambda_l  \NDmv{x}  :  \NDnt{A} . \NDnt{s} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \lambda_r  \NDmv{x}  :  \NDnt{A} . \NDnt{s} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{app}_l\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{app}_r\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{derelict}\, \NDnt{t} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{ex}\, \NDnt{s_{{\mathrm{1}}}} , \NDnt{s_{{\mathrm{2}}}} \,\mathsf{with}\, \NDmv{x_{{\mathrm{1}}}} , \NDmv{x_{{\mathrm{2}}}} \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}} }{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDsym{[}  \NDnt{s_{{\mathrm{1}}}}  \NDsym{/}  \NDmv{x}  \NDsym{]}  \NDnt{s_{{\mathrm{2}}}}} {\textsf{M}}{}{}{}\NDprodnewline
\NDprodline{|}{\NDsym{[}  \NDnt{t}  \NDsym{/}  \NDmv{x}  \NDsym{]}  \NDnt{s}} {\textsf{M}}{}{}{}\NDprodnewline
\NDprodline{|}{\NDsym{(}  \NDnt{s}  \NDsym{)}} {\textsf{S}}{}{}{}\NDprodnewline
\NDprodline{|}{ \NDnt{s} } {\textsf{M}}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{F} \NDnt{t} }{}{}{}{}}

\newcommand{\NDt}{
\NDrulehead{\NDnt{t}}{::=}{}\NDprodnewline
\NDfirstprodline{|}{\NDmv{x}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDmv{b}}{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{triv} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{let}\, \NDnt{t_{{\mathrm{1}}}}  :  \NDnt{X} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDnt{t_{{\mathrm{2}}}} }{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{t_{{\mathrm{1}}}}  \otimes  \NDnt{t_{{\mathrm{2}}}}}{}{}{}{}\NDprodnewline
\NDprodline{|}{ \lambda  \NDmv{x}  :  \NDnt{X} . \NDnt{t} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \NDnt{t_{{\mathrm{1}}}}   \NDnt{t_{{\mathrm{2}}}} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{ex}\, \NDnt{t_{{\mathrm{1}}}} , \NDnt{t_{{\mathrm{2}}}} \,\mathsf{with}\, \NDmv{x_{{\mathrm{1}}}} , \NDmv{x_{{\mathrm{2}}}} \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}} }{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDsym{[}  \NDnt{t_{{\mathrm{1}}}}  \NDsym{/}  \NDmv{x}  \NDsym{]}  \NDnt{t_{{\mathrm{2}}}}} {\textsf{M}}{}{}{}\NDprodnewline
\NDprodline{|}{\NDsym{(}  \NDnt{t}  \NDsym{)}} {\textsf{S}}{}{}{}\NDprodnewline
\NDprodline{|}{\NDsym{h(}  \NDnt{t}  \NDsym{)}} {\textsf{M}}{}{}{}\NDprodnewline
\NDprodline{|}{ \mathsf{G}\, \NDnt{s} }{}{}{}{}}

\newcommand{\NDI}{
\NDrulehead{\Phi  ,\ \Psi}{::=}{}\NDprodnewline
\NDfirstprodline{|}{ \cdot }{}{}{}{}\NDprodnewline
\NDprodline{|}{\Phi_{{\mathrm{1}}}  \NDsym{,}  \Phi_{{\mathrm{2}}}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDmv{x}  \NDsym{:}  \NDnt{X}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDsym{(}  \Phi  \NDsym{)}} {\textsf{S}}{}{}{}}

\newcommand{\NDG}{
\NDrulehead{\Gamma  ,\ \Delta}{::=}{}\NDprodnewline
\NDfirstprodline{|}{ \cdot }{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDmv{x}  \NDsym{:}  \NDnt{A}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\Phi}{}{}{}{}\NDprodnewline
\NDprodline{|}{\Gamma_{{\mathrm{1}}}  \NDsym{;}  \Gamma_{{\mathrm{2}}}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDsym{(}  \Gamma  \NDsym{)}} {\textsf{S}}{}{}{}}

\newcommand{\NDformula}{
\NDrulehead{\NDnt{formula}}{::=}{}\NDprodnewline
\NDfirstprodline{|}{\NDnt{judgement}}{}{}{}{}\NDprodnewline
\NDprodline{|}{ \NDnt{formula_{{\mathrm{1}}}}  \quad  \NDnt{formula_{{\mathrm{2}}}} } {\textsf{M}}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{formula_{{\mathrm{1}}}} \, ... \, \NDnt{formula_{\NDmv{i}}}} {\textsf{M}}{}{}{}\NDprodnewline
\NDprodline{|}{ \NDnt{formula} } {\textsf{S}}{}{}{}\NDprodnewline
\NDprodline{|}{ \NDmv{x}  \not\in \mathsf{FV}( \NDnt{s} ) }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \NDmv{x}  \not\in |  \Gamma ,  \Delta ,  \Psi  | }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \NDmv{x}  \not\in |  \Gamma ,  \Delta  | }{}{}{}{}}

\newcommand{\NDterminals}{
\NDrulehead{\NDnt{terminals}}{::=}{}\NDprodnewline
\NDfirstprodline{|}{ \otimes }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \triangleright }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \circop{e} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \circop{w} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \circop{c} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \rightharpoonup }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \leftharpoonup }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \multimap }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \vdash_\mathcal{C} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \vdash_\mathcal{L} }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \leadsto_\beta }{}{}{}{}\NDprodnewline
\NDprodline{|}{ \leadsto_\mathsf{c} }{}{}{}{}}

\newcommand{\NDJtype}{
\NDrulehead{\NDnt{Jtype}}{::=}{}\NDprodnewline
\NDfirstprodline{|}{\Phi  \vdash_\mathcal{C}  \NDnt{t}  \NDsym{:}  \NDnt{X}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\Gamma  \vdash_\mathcal{L}  \NDnt{s}  \NDsym{:}  \NDnt{A}}{}{}{}{}}

\newcommand{\NDReduction}{
\NDrulehead{\NDnt{Reduction}}{::=}{}\NDprodnewline
\NDfirstprodline{|}{\NDnt{t_{{\mathrm{1}}}}  \leadsto_\beta  \NDnt{t_{{\mathrm{2}}}}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{s_{{\mathrm{1}}}}  \leadsto_\beta  \NDnt{s_{{\mathrm{2}}}}}{}{}{}{}}

\newcommand{\NDCommuting}{
\NDrulehead{\NDnt{Commuting}}{::=}{}\NDprodnewline
\NDfirstprodline{|}{\NDnt{t_{{\mathrm{1}}}}  \leadsto_\mathsf{c}  \NDnt{t_{{\mathrm{2}}}}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{s_{{\mathrm{1}}}}  \leadsto_\mathsf{c}  \NDnt{s_{{\mathrm{2}}}}}{}{}{}{}}

\newcommand{\NDjudgement}{
\NDrulehead{\NDnt{judgement}}{::=}{}\NDprodnewline
\NDfirstprodline{|}{\NDnt{Jtype}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{Reduction}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{Commuting}}{}{}{}{}}

\newcommand{\NDuserXXsyntax}{
\NDrulehead{\NDnt{user\_syntax}}{::=}{}\NDprodnewline
\NDfirstprodline{|}{\NDmv{vars}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDmv{ivar}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDmv{const}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{A}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{W}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{T}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{p}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{s}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{t}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\Phi}{}{}{}{}\NDprodnewline
\NDprodline{|}{\Gamma}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{formula}}{}{}{}{}\NDprodnewline
\NDprodline{|}{\NDnt{terminals}}{}{}{}{}}

\newcommand{\NDgrammar}{\NDgrammartabular{
\NDA\NDinterrule
\NDW\NDinterrule
\NDT\NDinterrule
\NDp\NDinterrule
\NDs\NDinterrule
\NDt\NDinterrule
\NDI\NDinterrule
\NDG\NDinterrule
\NDformula\NDinterrule
\NDterminals\NDinterrule
\NDJtype\NDinterrule
\NDReduction\NDinterrule
\NDCommuting\NDinterrule
\NDjudgement\NDinterrule
\NDuserXXsyntax\NDafterlastrule
}}

% defnss
% defns Jtype
%% defn tty
\newcommand{\NDdruleTXXidName}[0]{\NDdrulename{T\_id}}
\newcommand{\NDdruleTXXid}[1]{\NDdrule[#1]{%
}{
\NDmv{x}  \NDsym{:}  \NDnt{X}  \vdash_\mathcal{C}  \NDmv{x}  \NDsym{:}  \NDnt{X}}{%
{\NDdruleTXXidName}{}%
}}

\newcommand{\NDdruleTXXunitIName}[0]{\NDdrulename{T\_unitI}}
\newcommand{\NDdruleTXXunitI}[1]{\NDdrule[#1]{%
}{
 \cdot   \vdash_\mathcal{C}   \mathsf{triv}   \NDsym{:}   \mathsf{Unit} }{%
{\NDdruleTXXunitIName}{}%
}}

\newcommand{\NDdruleTXXunitEName}[0]{\NDdrulename{T\_unitE}}
\newcommand{\NDdruleTXXunitE}[1]{\NDdrule[#1]{%
\NDpremise{ \Phi  \vdash_\mathcal{C}  \NDnt{t_{{\mathrm{1}}}}  \NDsym{:}   \mathsf{Unit}   \quad  \Psi  \vdash_\mathcal{C}  \NDnt{t_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{Y} }%
}{
\Phi  \NDsym{,}  \Psi  \vdash_\mathcal{C}   \mathsf{let}\, \NDnt{t_{{\mathrm{1}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{t_{{\mathrm{2}}}}   \NDsym{:}  \NDnt{Y}}{%
{\NDdruleTXXunitEName}{}%
}}

\newcommand{\NDdruleTXXtenIName}[0]{\NDdrulename{T\_tenI}}
\newcommand{\NDdruleTXXtenI}[1]{\NDdrule[#1]{%
\NDpremise{ \Phi  \vdash_\mathcal{C}  \NDnt{t_{{\mathrm{1}}}}  \NDsym{:}  \NDnt{X}  \quad  \Psi  \vdash_\mathcal{C}  \NDnt{t_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{Y} }%
}{
\Phi  \NDsym{,}  \Psi  \vdash_\mathcal{C}  \NDnt{t_{{\mathrm{1}}}}  \otimes  \NDnt{t_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{X}  \otimes  \NDnt{Y}}{%
{\NDdruleTXXtenIName}{}%
}}

\newcommand{\NDdruleTXXtenEName}[0]{\NDdrulename{T\_tenE}}
\newcommand{\NDdruleTXXtenE}[1]{\NDdrule[#1]{%
\NDpremise{ \Phi  \vdash_\mathcal{C}  \NDnt{t_{{\mathrm{1}}}}  \NDsym{:}  \NDnt{X}  \otimes  \NDnt{Y}  \quad  \Psi_{{\mathrm{1}}}  \NDsym{,}  \NDmv{x}  \NDsym{:}  \NDnt{X}  \NDsym{,}  \NDmv{y}  \NDsym{:}  \NDnt{Y}  \NDsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \NDnt{t_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{Z} }%
}{
\Psi_{{\mathrm{1}}}  \NDsym{,}  \Phi  \NDsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}   \mathsf{let}\, \NDnt{t_{{\mathrm{1}}}}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{t_{{\mathrm{2}}}}   \NDsym{:}  \NDnt{Z}}{%
{\NDdruleTXXtenEName}{}%
}}

\newcommand{\NDdruleTXXimpIName}[0]{\NDdrulename{T\_impI}}
\newcommand{\NDdruleTXXimpI}[1]{\NDdrule[#1]{%
\NDpremise{\Phi  \NDsym{,}  \NDmv{x}  \NDsym{:}  \NDnt{X}  \vdash_\mathcal{C}  \NDnt{t}  \NDsym{:}  \NDnt{Y}}%
}{
\Phi  \vdash_\mathcal{C}   \lambda  \NDmv{x}  :  \NDnt{X} . \NDnt{t}   \NDsym{:}  \NDnt{X}  \multimap  \NDnt{Y}}{%
{\NDdruleTXXimpIName}{}%
}}

\newcommand{\NDdruleTXXimpEName}[0]{\NDdrulename{T\_impE}}
\newcommand{\NDdruleTXXimpE}[1]{\NDdrule[#1]{%
\NDpremise{ \Phi  \vdash_\mathcal{C}  \NDnt{t_{{\mathrm{1}}}}  \NDsym{:}  \NDnt{X}  \multimap  \NDnt{Y}  \quad  \Psi  \vdash_\mathcal{C}  \NDnt{t_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{X} }%
}{
\Phi  \NDsym{,}  \Psi  \vdash_\mathcal{C}   \NDnt{t_{{\mathrm{1}}}}   \NDnt{t_{{\mathrm{2}}}}   \NDsym{:}  \NDnt{Y}}{%
{\NDdruleTXXimpEName}{}%
}}

\newcommand{\NDdruleTXXGIName}[0]{\NDdrulename{T\_GI}}
\newcommand{\NDdruleTXXGI}[1]{\NDdrule[#1]{%
\NDpremise{\Phi  \vdash_\mathcal{L}  \NDnt{s}  \NDsym{:}  \NDnt{A}}%
}{
\Phi  \vdash_\mathcal{C}   \mathsf{G}\, \NDnt{s}   \NDsym{:}   \mathsf{G} \NDnt{A} }{%
{\NDdruleTXXGIName}{}%
}}

\newcommand{\NDdruleTXXbetaName}[0]{\NDdrulename{T\_beta}}
\newcommand{\NDdruleTXXbeta}[1]{\NDdrule[#1]{%
\NDpremise{\Phi  \NDsym{,}  \NDmv{x}  \NDsym{:}  \NDnt{X}  \NDsym{,}  \NDmv{y}  \NDsym{:}  \NDnt{Y}  \NDsym{,}  \Psi  \vdash_\mathcal{C}  \NDnt{t}  \NDsym{:}  \NDnt{Z}}%
}{
\Phi  \NDsym{,}  \NDmv{z}  \NDsym{:}  \NDnt{Y}  \NDsym{,}  \NDmv{w}  \NDsym{:}  \NDnt{X}  \NDsym{,}  \Psi  \vdash_\mathcal{C}   \mathsf{ex}\, \NDmv{w} , \NDmv{z} \,\mathsf{with}\, \NDmv{x} , \NDmv{y} \,\mathsf{in}\, \NDnt{t}   \NDsym{:}  \NDnt{Z}}{%
{\NDdruleTXXbetaName}{}%
}}

\newcommand{\NDdruleTXXcutName}[0]{\NDdrulename{T\_cut}}
\newcommand{\NDdruleTXXcut}[1]{\NDdrule[#1]{%
\NDpremise{ \Phi  \vdash_\mathcal{C}  \NDnt{t_{{\mathrm{1}}}}  \NDsym{:}  \NDnt{X}  \quad  \Psi_{{\mathrm{1}}}  \NDsym{,}  \NDmv{x}  \NDsym{:}  \NDnt{X}  \NDsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \NDnt{t_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{Y} }%
}{
\Psi_{{\mathrm{1}}}  \NDsym{,}  \Phi  \NDsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \NDsym{[}  \NDnt{t_{{\mathrm{1}}}}  \NDsym{/}  \NDmv{x}  \NDsym{]}  \NDnt{t_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{Y}}{%
{\NDdruleTXXcutName}{}%
}}

\newcommand{\NDdefntty}[1]{\begin{NDdefnblock}[#1]{$\Phi  \vdash_\mathcal{C}  \NDnt{t}  \NDsym{:}  \NDnt{X}$}{}
\NDusedrule{\NDdruleTXXid{}}
\NDusedrule{\NDdruleTXXunitI{}}
\NDusedrule{\NDdruleTXXunitE{}}
\NDusedrule{\NDdruleTXXtenI{}}
\NDusedrule{\NDdruleTXXtenE{}}
\NDusedrule{\NDdruleTXXimpI{}}
\NDusedrule{\NDdruleTXXimpE{}}
\NDusedrule{\NDdruleTXXGI{}}
\NDusedrule{\NDdruleTXXbeta{}}
\NDusedrule{\NDdruleTXXcut{}}
\end{NDdefnblock}}

%% defn sty
\newcommand{\NDdruleSXXidName}[0]{\NDdrulename{S\_id}}
\newcommand{\NDdruleSXXid}[1]{\NDdrule[#1]{%
}{
\NDmv{x}  \NDsym{:}  \NDnt{A}  \vdash_\mathcal{L}  \NDmv{x}  \NDsym{:}  \NDnt{A}}{%
{\NDdruleSXXidName}{}%
}}

\newcommand{\NDdruleSXXunitIName}[0]{\NDdrulename{S\_unitI}}
\newcommand{\NDdruleSXXunitI}[1]{\NDdrule[#1]{%
}{
 \cdot   \vdash_\mathcal{L}   \mathsf{triv}   \NDsym{:}   \mathsf{Unit} }{%
{\NDdruleSXXunitIName}{}%
}}

\newcommand{\NDdruleSXXunitEOneName}[0]{\NDdrulename{S\_unitE1}}
\newcommand{\NDdruleSXXunitEOne}[1]{\NDdrule[#1]{%
\NDpremise{ \Phi  \vdash_\mathcal{C}  \NDnt{t}  \NDsym{:}   \mathsf{Unit}   \quad  \Gamma  \vdash_\mathcal{L}  \NDnt{s}  \NDsym{:}  \NDnt{A} }%
}{
\Phi  \NDsym{;}  \Gamma  \vdash_\mathcal{L}   \mathsf{let}\, \NDnt{t}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s}   \NDsym{:}  \NDnt{A}}{%
{\NDdruleSXXunitEOneName}{}%
}}

\newcommand{\NDdruleSXXunitETwoName}[0]{\NDdrulename{S\_unitE2}}
\newcommand{\NDdruleSXXunitETwo}[1]{\NDdrule[#1]{%
\NDpremise{ \Gamma  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{1}}}}  \NDsym{:}   \mathsf{Unit}   \quad  \Delta  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{A} }%
}{
\Gamma  \NDsym{;}  \Delta  \vdash_\mathcal{L}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}   \NDsym{:}  \NDnt{A}}{%
{\NDdruleSXXunitETwoName}{}%
}}

\newcommand{\NDdruleSXXtenIName}[0]{\NDdrulename{S\_tenI}}
\newcommand{\NDdruleSXXtenI}[1]{\NDdrule[#1]{%
\NDpremise{ \Gamma  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{1}}}}  \NDsym{:}  \NDnt{A}  \quad  \Delta  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{B} }%
}{
\Gamma  \NDsym{;}  \Delta  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{1}}}}  \triangleright  \NDnt{s_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{A}  \triangleright  \NDnt{B}}{%
{\NDdruleSXXtenIName}{}%
}}

\newcommand{\NDdruleSXXtenEOneName}[0]{\NDdrulename{S\_tenE1}}
\newcommand{\NDdruleSXXtenEOne}[1]{\NDdrule[#1]{%
\NDpremise{ \Phi  \vdash_\mathcal{C}  \NDnt{t}  \NDsym{:}  \NDnt{X}  \otimes  \NDnt{Y}  \quad  \Gamma_{{\mathrm{1}}}  \NDsym{;}  \NDmv{x}  \NDsym{:}  \NDnt{X}  \NDsym{;}  \NDmv{y}  \NDsym{:}  \NDnt{Y}  \NDsym{;}  \Gamma_{{\mathrm{2}}}  \vdash_\mathcal{L}  \NDnt{s}  \NDsym{:}  \NDnt{A} }%
}{
\Gamma_{{\mathrm{1}}}  \NDsym{;}  \Phi  \NDsym{;}  \Gamma_{{\mathrm{2}}}  \vdash_\mathcal{L}   \mathsf{let}\, \NDnt{t}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{s}   \NDsym{:}  \NDnt{A}}{%
{\NDdruleSXXtenEOneName}{}%
}}

\newcommand{\NDdruleSXXtenETwoName}[0]{\NDdrulename{S\_tenE2}}
\newcommand{\NDdruleSXXtenETwo}[1]{\NDdrule[#1]{%
\NDpremise{ \Gamma  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{1}}}}  \NDsym{:}  \NDnt{A}  \triangleright  \NDnt{B}  \quad  \Delta_{{\mathrm{1}}}  \NDsym{;}  \NDmv{x}  \NDsym{:}  \NDnt{A}  \NDsym{;}  \NDmv{y}  \NDsym{:}  \NDnt{B}  \NDsym{;}  \Delta_{{\mathrm{2}}}  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{C} }%
}{
\Delta_{{\mathrm{1}}}  \NDsym{;}  \Gamma  \NDsym{;}  \Delta_{{\mathrm{2}}}  \vdash_\mathcal{L}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :  \NDnt{A}  \triangleright  \NDnt{B} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}   \NDsym{:}  \NDnt{C}}{%
{\NDdruleSXXtenETwoName}{}%
}}

\newcommand{\NDdruleSXXimprIName}[0]{\NDdrulename{S\_imprI}}
\newcommand{\NDdruleSXXimprI}[1]{\NDdrule[#1]{%
\NDpremise{\Gamma  \NDsym{;}  \NDmv{x}  \NDsym{:}  \NDnt{A}  \vdash_\mathcal{L}  \NDnt{s}  \NDsym{:}  \NDnt{B}}%
}{
\Gamma  \vdash_\mathcal{L}   \lambda_r  \NDmv{x}  :  \NDnt{A} . \NDnt{s}   \NDsym{:}  \NDnt{A}  \rightharpoonup  \NDnt{B}}{%
{\NDdruleSXXimprIName}{}%
}}

\newcommand{\NDdruleSXXimprEName}[0]{\NDdrulename{S\_imprE}}
\newcommand{\NDdruleSXXimprE}[1]{\NDdrule[#1]{%
\NDpremise{ \Gamma  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{1}}}}  \NDsym{:}  \NDnt{A}  \rightharpoonup  \NDnt{B}  \quad  \Delta  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{A} }%
}{
\Gamma  \NDsym{;}  \Delta  \vdash_\mathcal{L}   \mathsf{app}_r\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}   \NDsym{:}  \NDnt{B}}{%
{\NDdruleSXXimprEName}{}%
}}

\newcommand{\NDdruleSXXimplIName}[0]{\NDdrulename{S\_implI}}
\newcommand{\NDdruleSXXimplI}[1]{\NDdrule[#1]{%
\NDpremise{\NDmv{x}  \NDsym{:}  \NDnt{A}  \NDsym{;}  \Gamma  \vdash_\mathcal{L}  \NDnt{s}  \NDsym{:}  \NDnt{B}}%
}{
\Gamma  \vdash_\mathcal{L}   \lambda_l  \NDmv{x}  :  \NDnt{A} . \NDnt{s}   \NDsym{:}  \NDnt{B}  \leftharpoonup  \NDnt{A}}{%
{\NDdruleSXXimplIName}{}%
}}

\newcommand{\NDdruleSXXimplEName}[0]{\NDdrulename{S\_implE}}
\newcommand{\NDdruleSXXimplE}[1]{\NDdrule[#1]{%
\NDpremise{ \Gamma  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{1}}}}  \NDsym{:}  \NDnt{B}  \leftharpoonup  \NDnt{A}  \quad  \Delta  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{A} }%
}{
\Delta  \NDsym{;}  \Gamma  \vdash_\mathcal{L}   \mathsf{app}_l\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}   \NDsym{:}  \NDnt{B}}{%
{\NDdruleSXXimplEName}{}%
}}

\newcommand{\NDdruleSXXFIName}[0]{\NDdrulename{S\_FI}}
\newcommand{\NDdruleSXXFI}[1]{\NDdrule[#1]{%
\NDpremise{\Phi  \vdash_\mathcal{C}  \NDnt{t}  \NDsym{:}  \NDnt{X}}%
}{
\Phi  \vdash_\mathcal{L}   \mathsf{F} \NDnt{t}   \NDsym{:}   \mathsf{F} \NDnt{X} }{%
{\NDdruleSXXFIName}{}%
}}

\newcommand{\NDdruleSXXFEName}[0]{\NDdrulename{S\_FE}}
\newcommand{\NDdruleSXXFE}[1]{\NDdrule[#1]{%
\NDpremise{ \Gamma  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{1}}}}  \NDsym{:}   \mathsf{F} \NDnt{X}   \quad  \Delta_{{\mathrm{1}}}  \NDsym{;}  \NDmv{x}  \NDsym{:}  \NDnt{X}  \NDsym{;}  \Delta_{{\mathrm{2}}}  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{A} }%
}{
\Delta_{{\mathrm{1}}}  \NDsym{;}  \Gamma  \NDsym{;}  \Delta_{{\mathrm{2}}}  \vdash_\mathcal{L}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}   \NDsym{:}  \NDnt{A}}{%
{\NDdruleSXXFEName}{}%
}}

\newcommand{\NDdruleSXXGEName}[0]{\NDdrulename{S\_GE}}
\newcommand{\NDdruleSXXGE}[1]{\NDdrule[#1]{%
\NDpremise{\Phi  \vdash_\mathcal{C}  \NDnt{t}  \NDsym{:}   \mathsf{G} \NDnt{A} }%
}{
\Phi  \vdash_\mathcal{L}   \mathsf{derelict}\, \NDnt{t}   \NDsym{:}  \NDnt{A}}{%
{\NDdruleSXXGEName}{}%
}}

\newcommand{\NDdruleSXXbetaName}[0]{\NDdrulename{S\_beta}}
\newcommand{\NDdruleSXXbeta}[1]{\NDdrule[#1]{%
\NDpremise{\Gamma  \NDsym{;}  \NDmv{x}  \NDsym{:}  \NDnt{X}  \NDsym{;}  \NDmv{y}  \NDsym{:}  \NDnt{Y}  \NDsym{;}  \Delta  \vdash_\mathcal{L}  \NDnt{s}  \NDsym{:}  \NDnt{A}}%
}{
\Gamma  \NDsym{;}  \NDmv{z}  \NDsym{:}  \NDnt{Y}  \NDsym{;}  \NDmv{w}  \NDsym{:}  \NDnt{X}  \NDsym{;}  \Delta  \vdash_\mathcal{L}   \mathsf{ex}\, \NDmv{w} , \NDmv{z} \,\mathsf{with}\, \NDmv{x} , \NDmv{y} \,\mathsf{in}\, \NDnt{s}   \NDsym{:}  \NDnt{A}}{%
{\NDdruleSXXbetaName}{}%
}}

\newcommand{\NDdruleSXXcutOneName}[0]{\NDdrulename{S\_cut1}}
\newcommand{\NDdruleSXXcutOne}[1]{\NDdrule[#1]{%
\NDpremise{ \Phi  \vdash_\mathcal{C}  \NDnt{t}  \NDsym{:}  \NDnt{X}  \quad  \Gamma_{{\mathrm{1}}}  \NDsym{;}  \NDmv{x}  \NDsym{:}  \NDnt{X}  \NDsym{;}  \Gamma_{{\mathrm{2}}}  \vdash_\mathcal{L}  \NDnt{s}  \NDsym{:}  \NDnt{A} }%
}{
\Gamma_{{\mathrm{1}}}  \NDsym{;}  \Phi  \NDsym{;}  \Gamma_{{\mathrm{1}}}  \vdash_\mathcal{L}  \NDsym{[}  \NDnt{t}  \NDsym{/}  \NDmv{x}  \NDsym{]}  \NDnt{s}  \NDsym{:}  \NDnt{A}}{%
{\NDdruleSXXcutOneName}{}%
}}

\newcommand{\NDdruleSXXcutTwoName}[0]{\NDdrulename{S\_cut2}}
\newcommand{\NDdruleSXXcutTwo}[1]{\NDdrule[#1]{%
\NDpremise{ \Gamma  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{1}}}}  \NDsym{:}  \NDnt{A}  \quad  \Delta_{{\mathrm{1}}}  \NDsym{;}  \NDmv{x}  \NDsym{:}  \NDnt{A}  \NDsym{;}  \Delta_{{\mathrm{2}}}  \vdash_\mathcal{L}  \NDnt{s_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{B} }%
}{
\Delta_{{\mathrm{1}}}  \NDsym{;}  \Gamma  \NDsym{;}  \Delta_{{\mathrm{2}}}  \vdash_\mathcal{L}  \NDsym{[}  \NDnt{s_{{\mathrm{1}}}}  \NDsym{/}  \NDmv{x}  \NDsym{]}  \NDnt{s_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{B}}{%
{\NDdruleSXXcutTwoName}{}%
}}

\newcommand{\NDdefnsty}[1]{\begin{NDdefnblock}[#1]{$\Gamma  \vdash_\mathcal{L}  \NDnt{s}  \NDsym{:}  \NDnt{A}$}{}
\NDusedrule{\NDdruleSXXid{}}
\NDusedrule{\NDdruleSXXunitI{}}
\NDusedrule{\NDdruleSXXunitEOne{}}
\NDusedrule{\NDdruleSXXunitETwo{}}
\NDusedrule{\NDdruleSXXtenI{}}
\NDusedrule{\NDdruleSXXtenEOne{}}
\NDusedrule{\NDdruleSXXtenETwo{}}
\NDusedrule{\NDdruleSXXimprI{}}
\NDusedrule{\NDdruleSXXimprE{}}
\NDusedrule{\NDdruleSXXimplI{}}
\NDusedrule{\NDdruleSXXimplE{}}
\NDusedrule{\NDdruleSXXFI{}}
\NDusedrule{\NDdruleSXXFE{}}
\NDusedrule{\NDdruleSXXGE{}}
\NDusedrule{\NDdruleSXXbeta{}}
\NDusedrule{\NDdruleSXXcutOne{}}
\NDusedrule{\NDdruleSXXcutTwo{}}
\end{NDdefnblock}}

\newcommand{\NDdefnsJtype}{
\NDdefntty{}\NDdefnsty{}}

% defns Reduction
%% defn tred
\newcommand{\NDdruleTbetaXXletUName}[0]{\NDdrulename{Tbeta\_letU}}
\newcommand{\NDdruleTbetaXXletU}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\,  \mathsf{triv}   :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{t}   \leadsto_\beta  \NDnt{t}}{%
{\NDdruleTbetaXXletUName}{}%
}}

\newcommand{\NDdruleTbetaXXletTName}[0]{\NDdrulename{Tbeta\_letT}}
\newcommand{\NDdruleTbetaXXletT}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDnt{t_{{\mathrm{1}}}}  \otimes  \NDnt{t_{{\mathrm{2}}}}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}}   \leadsto_\beta  \NDsym{[}  \NDnt{t_{{\mathrm{1}}}}  \NDsym{/}  \NDmv{x}  \NDsym{]}  \NDsym{[}  \NDnt{t_{{\mathrm{2}}}}  \NDsym{/}  \NDmv{y}  \NDsym{]}  \NDnt{t_{{\mathrm{3}}}}}{%
{\NDdruleTbetaXXletTName}{}%
}}

\newcommand{\NDdruleTbetaXXlamName}[0]{\NDdrulename{Tbeta\_lam}}
\newcommand{\NDdruleTbetaXXlam}[1]{\NDdrule[#1]{%
}{
 \NDsym{(}   \lambda  \NDmv{x}  :  \NDnt{X} . \NDnt{t_{{\mathrm{1}}}}   \NDsym{)}   \NDnt{t_{{\mathrm{2}}}}   \leadsto_\beta  \NDsym{[}  \NDnt{t_{{\mathrm{2}}}}  \NDsym{/}  \NDmv{x}  \NDsym{]}  \NDnt{t_{{\mathrm{1}}}}}{%
{\NDdruleTbetaXXlamName}{}%
}}

\newcommand{\NDdruleTbetaXXappOneName}[0]{\NDdrulename{Tbeta\_app1}}
\newcommand{\NDdruleTbetaXXappOne}[1]{\NDdrule[#1]{%
\NDpremise{\NDnt{t_{{\mathrm{1}}}}  \leadsto_\beta  \NDnt{t'_{{\mathrm{1}}}}}%
}{
 \NDnt{t_{{\mathrm{1}}}}   \NDnt{t_{{\mathrm{2}}}}   \leadsto_\beta   \NDnt{t'_{{\mathrm{1}}}}   \NDnt{t_{{\mathrm{2}}}} }{%
{\NDdruleTbetaXXappOneName}{}%
}}

\newcommand{\NDdruleTbetaXXappTwoName}[0]{\NDdrulename{Tbeta\_app2}}
\newcommand{\NDdruleTbetaXXappTwo}[1]{\NDdrule[#1]{%
\NDpremise{\NDnt{t_{{\mathrm{2}}}}  \leadsto_\beta  \NDnt{t'_{{\mathrm{2}}}}}%
}{
 \NDnt{t_{{\mathrm{1}}}}   \NDnt{t_{{\mathrm{2}}}}   \leadsto_\beta   \NDnt{t_{{\mathrm{1}}}}   \NDnt{t'_{{\mathrm{2}}}} }{%
{\NDdruleTbetaXXappTwoName}{}%
}}

\newcommand{\NDdruleTbetaXXappLetName}[0]{\NDdrulename{Tbeta\_appLet}}
\newcommand{\NDdruleTbetaXXappLet}[1]{\NDdrule[#1]{%
}{
 \NDsym{(}   \mathsf{let}\, \NDnt{t}  :  \NDnt{X} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDnt{t_{{\mathrm{1}}}}   \NDsym{)}   \NDnt{t_{{\mathrm{2}}}}   \leadsto_\beta   \mathsf{let}\, \NDnt{t}  :  \NDnt{X} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDsym{(}   \NDnt{t_{{\mathrm{1}}}}   \NDnt{t_{{\mathrm{2}}}}   \NDsym{)} }{%
{\NDdruleTbetaXXappLetName}{}%
}}

\newcommand{\NDdruleTbetaXXletLetName}[0]{\NDdrulename{Tbeta\_letLet}}
\newcommand{\NDdruleTbetaXXletLet}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :  \NDnt{X} \,\mathsf{be}\, \NDnt{p_{{\mathrm{1}}}} \,\mathsf{in}\, \NDnt{t_{{\mathrm{1}}}}   \NDsym{)}  :  \NDnt{Y} \,\mathsf{be}\, \NDnt{p_{{\mathrm{2}}}} \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}}   \leadsto_\beta   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :  \NDnt{X} \,\mathsf{be}\, \NDnt{p_{{\mathrm{1}}}} \,\mathsf{in}\,  \mathsf{let}\, \NDnt{t_{{\mathrm{1}}}}  :  \NDnt{Y} \,\mathsf{be}\, \NDnt{p_{{\mathrm{2}}}} \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}}  }{%
{\NDdruleTbetaXXletLetName}{}%
}}

\newcommand{\NDdruleTbetaXXletAppName}[0]{\NDdrulename{Tbeta\_letApp}}
\newcommand{\NDdruleTbetaXXletApp}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDnt{t_{{\mathrm{1}}}}  :  \NDnt{X} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDsym{(}   \NDnt{t_{{\mathrm{1}}}}   \NDnt{t_{{\mathrm{2}}}}   \NDsym{)}   \leadsto_\beta   \NDsym{(}   \mathsf{let}\, \NDnt{t_{{\mathrm{1}}}}  :  \NDnt{X} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDnt{t_{{\mathrm{1}}}}   \NDsym{)}   \NDsym{(}   \mathsf{let}\, \NDnt{t_{{\mathrm{1}}}}  :  \NDnt{X} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDnt{t_{{\mathrm{2}}}}   \NDsym{)} }{%
{\NDdruleTbetaXXletAppName}{}%
}}

\newcommand{\NDdefntred}[1]{\begin{NDdefnblock}[#1]{$\NDnt{t_{{\mathrm{1}}}}  \leadsto_\beta  \NDnt{t_{{\mathrm{2}}}}$}{}
\NDusedrule{\NDdruleTbetaXXletU{}}
\NDusedrule{\NDdruleTbetaXXletT{}}
\NDusedrule{\NDdruleTbetaXXlam{}}
\NDusedrule{\NDdruleTbetaXXappOne{}}
\NDusedrule{\NDdruleTbetaXXappTwo{}}
\NDusedrule{\NDdruleTbetaXXappLet{}}
\NDusedrule{\NDdruleTbetaXXletLet{}}
\NDusedrule{\NDdruleTbetaXXletApp{}}
\end{NDdefnblock}}

%% defn sred
\newcommand{\NDdruleSbetaXXletUOneName}[0]{\NDdrulename{Sbeta\_letU1}}
\newcommand{\NDdruleSbetaXXletUOne}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\,  \mathsf{triv}   :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s}   \leadsto_\beta  \NDnt{s}}{%
{\NDdruleSbetaXXletUOneName}{}%
}}

\newcommand{\NDdruleSbetaXXletTOneName}[0]{\NDdrulename{Sbeta\_letT1}}
\newcommand{\NDdruleSbetaXXletTOne}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDnt{t_{{\mathrm{1}}}}  \otimes  \NDnt{t_{{\mathrm{2}}}}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDnt{s}   \leadsto_\beta  \NDsym{[}  \NDnt{t_{{\mathrm{1}}}}  \NDsym{/}  \NDmv{x}  \NDsym{]}  \NDsym{[}  \NDnt{t_{{\mathrm{2}}}}  \NDsym{/}  \NDmv{y}  \NDsym{]}  \NDnt{s}}{%
{\NDdruleSbetaXXletTOneName}{}%
}}

\newcommand{\NDdruleSbetaXXletTTwoName}[0]{\NDdrulename{Sbeta\_letT2}}
\newcommand{\NDdruleSbetaXXletTTwo}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  \triangleright  \NDnt{s_{{\mathrm{2}}}}  :  \NDnt{A}  \triangleright  \NDnt{B} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\beta  \NDsym{[}  \NDnt{s_{{\mathrm{1}}}}  \NDsym{/}  \NDmv{x}  \NDsym{]}  \NDsym{[}  \NDnt{s_{{\mathrm{2}}}}  \NDsym{/}  \NDmv{y}  \NDsym{]}  \NDnt{s_{{\mathrm{3}}}}}{%
{\NDdruleSbetaXXletTTwoName}{}%
}}

\newcommand{\NDdruleSbetaXXletFName}[0]{\NDdrulename{Sbeta\_letF}}
\newcommand{\NDdruleSbetaXXletF}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\,  \mathsf{F} \NDnt{t}   :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDnt{s}   \leadsto_\beta  \NDsym{[}  \NDnt{t}  \NDsym{/}  \NDmv{x}  \NDsym{]}  \NDnt{s}}{%
{\NDdruleSbetaXXletFName}{}%
}}

\newcommand{\NDdruleSbetaXXlamLName}[0]{\NDdrulename{Sbeta\_lamL}}
\newcommand{\NDdruleSbetaXXlamL}[1]{\NDdrule[#1]{%
}{
 \mathsf{app}_l\, \NDsym{(}   \lambda_l  \NDmv{x}  :  \NDnt{A} . \NDnt{s_{{\mathrm{1}}}}   \NDsym{)} \, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\beta  \NDsym{[}  \NDnt{s_{{\mathrm{2}}}}  \NDsym{/}  \NDmv{x}  \NDsym{]}  \NDnt{s_{{\mathrm{1}}}}}{%
{\NDdruleSbetaXXlamLName}{}%
}}

\newcommand{\NDdruleSbetaXXlamRName}[0]{\NDdrulename{Sbeta\_lamR}}
\newcommand{\NDdruleSbetaXXlamR}[1]{\NDdrule[#1]{%
}{
 \mathsf{app}_r\, \NDsym{(}   \lambda_r  \NDmv{x}  :  \NDnt{A} . \NDnt{s_{{\mathrm{1}}}}   \NDsym{)} \, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\beta  \NDsym{[}  \NDnt{s_{{\mathrm{2}}}}  \NDsym{/}  \NDmv{x}  \NDsym{]}  \NDnt{s_{{\mathrm{1}}}}}{%
{\NDdruleSbetaXXlamRName}{}%
}}

\newcommand{\NDdruleSbetaXXapplOneName}[0]{\NDdrulename{Sbeta\_appl1}}
\newcommand{\NDdruleSbetaXXapplOne}[1]{\NDdrule[#1]{%
\NDpremise{\NDnt{s_{{\mathrm{1}}}}  \leadsto_\beta  \NDnt{s'_{{\mathrm{1}}}}}%
}{
 \mathsf{app}_l\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\beta   \mathsf{app}_l\, \NDnt{s'_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}} }{%
{\NDdruleSbetaXXapplOneName}{}%
}}

\newcommand{\NDdruleSbetaXXapplTwoName}[0]{\NDdrulename{Sbeta\_appl2}}
\newcommand{\NDdruleSbetaXXapplTwo}[1]{\NDdrule[#1]{%
\NDpremise{\NDnt{s_{{\mathrm{2}}}}  \leadsto_\beta  \NDnt{s'_{{\mathrm{2}}}}}%
}{
 \mathsf{app}_l\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\beta   \mathsf{app}_l\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s'_{{\mathrm{2}}}} }{%
{\NDdruleSbetaXXapplTwoName}{}%
}}

\newcommand{\NDdruleSbetaXXapprOneName}[0]{\NDdrulename{Sbeta\_appr1}}
\newcommand{\NDdruleSbetaXXapprOne}[1]{\NDdrule[#1]{%
\NDpremise{\NDnt{s_{{\mathrm{1}}}}  \leadsto_\beta  \NDnt{s'_{{\mathrm{1}}}}}%
}{
 \mathsf{app}_r\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\beta   \mathsf{app}_r\, \NDnt{s'_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}} }{%
{\NDdruleSbetaXXapprOneName}{}%
}}

\newcommand{\NDdruleSbetaXXapprTwoName}[0]{\NDdrulename{Sbeta\_appr2}}
\newcommand{\NDdruleSbetaXXapprTwo}[1]{\NDdrule[#1]{%
\NDpremise{\NDnt{s_{{\mathrm{2}}}}  \leadsto_\beta  \NDnt{s'_{{\mathrm{2}}}}}%
}{
 \mathsf{app}_r\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\beta   \mathsf{app}_r\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s'_{{\mathrm{2}}}} }{%
{\NDdruleSbetaXXapprTwoName}{}%
}}

\newcommand{\NDdruleSbetaXXderelictName}[0]{\NDdrulename{Sbeta\_derelict}}
\newcommand{\NDdruleSbetaXXderelict}[1]{\NDdrule[#1]{%
}{
 \mathsf{derelict}\, \NDsym{(}   \mathsf{G}\, \NDnt{s}   \NDsym{)}   \leadsto_\beta  \NDnt{s}}{%
{\NDdruleSbetaXXderelictName}{}%
}}

\newcommand{\NDdruleSbetaXXapplLetName}[0]{\NDdrulename{Sbeta\_applLet}}
\newcommand{\NDdruleSbetaXXapplLet}[1]{\NDdrule[#1]{%
}{
 \mathsf{app}_l\, \NDsym{(}   \mathsf{let}\, \NDnt{s}  :  \NDnt{A} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)} \, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\beta   \mathsf{let}\, \NDnt{s}  :  \NDnt{A} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDsym{(}   \mathsf{app}_l\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}   \NDsym{)} }{%
{\NDdruleSbetaXXapplLetName}{}%
}}

\newcommand{\NDdruleSbetaXXapprLetName}[0]{\NDdrulename{Sbeta\_apprLet}}
\newcommand{\NDdruleSbetaXXapprLet}[1]{\NDdrule[#1]{%
}{
 \mathsf{app}_r\, \NDsym{(}   \mathsf{let}\, \NDnt{s}  :  \NDnt{A} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)} \, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\beta   \mathsf{let}\, \NDnt{s}  :  \NDnt{A} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDsym{(}   \mathsf{app}_r\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}   \NDsym{)} }{%
{\NDdruleSbetaXXapprLetName}{}%
}}

\newcommand{\NDdruleSbetaXXletLetName}[0]{\NDdrulename{Sbeta\_letLet}}
\newcommand{\NDdruleSbetaXXletLet}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :  \NDnt{A} \,\mathsf{be}\, \NDnt{p_{{\mathrm{1}}}} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)}  :  \NDnt{B} \,\mathsf{be}\, \NDnt{p_{{\mathrm{2}}}} \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\beta   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :  \NDnt{A} \,\mathsf{be}\, \NDnt{p_{{\mathrm{1}}}} \,\mathsf{in}\,  \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :  \NDnt{B} \,\mathsf{be}\, \NDnt{p_{{\mathrm{2}}}} \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}  }{%
{\NDdruleSbetaXXletLetName}{}%
}}

\newcommand{\NDdruleSbetaXXletApplName}[0]{\NDdrulename{Sbeta\_letAppl}}
\newcommand{\NDdruleSbetaXXletAppl}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :  \NDnt{A} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDsym{(}   \mathsf{app}_l\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}   \NDsym{)}   \leadsto_\beta   \mathsf{app}_l\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :  \NDnt{A} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)} \, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :  \NDnt{A} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}   \NDsym{)} }{%
{\NDdruleSbetaXXletApplName}{}%
}}

\newcommand{\NDdruleSbetaXXletApprName}[0]{\NDdrulename{Sbeta\_letAppr}}
\newcommand{\NDdruleSbetaXXletAppr}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :  \NDnt{A} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDsym{(}   \mathsf{app}_r\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}   \NDsym{)}   \leadsto_\beta   \mathsf{app}_r\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :  \NDnt{A} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)} \, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :  \NDnt{A} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}   \NDsym{)} }{%
{\NDdruleSbetaXXletApprName}{}%
}}

\newcommand{\NDdefnsred}[1]{\begin{NDdefnblock}[#1]{$\NDnt{s_{{\mathrm{1}}}}  \leadsto_\beta  \NDnt{s_{{\mathrm{2}}}}$}{}
\NDusedrule{\NDdruleSbetaXXletUOne{}}
\NDusedrule{\NDdruleSbetaXXletTOne{}}
\NDusedrule{\NDdruleSbetaXXletTTwo{}}
\NDusedrule{\NDdruleSbetaXXletF{}}
\NDusedrule{\NDdruleSbetaXXlamL{}}
\NDusedrule{\NDdruleSbetaXXlamR{}}
\NDusedrule{\NDdruleSbetaXXapplOne{}}
\NDusedrule{\NDdruleSbetaXXapplTwo{}}
\NDusedrule{\NDdruleSbetaXXapprOne{}}
\NDusedrule{\NDdruleSbetaXXapprTwo{}}
\NDusedrule{\NDdruleSbetaXXderelict{}}
\NDusedrule{\NDdruleSbetaXXapplLet{}}
\NDusedrule{\NDdruleSbetaXXapprLet{}}
\NDusedrule{\NDdruleSbetaXXletLet{}}
\NDusedrule{\NDdruleSbetaXXletAppl{}}
\NDusedrule{\NDdruleSbetaXXletAppr{}}
\end{NDdefnblock}}

\newcommand{\NDdefnsReduction}{
\NDdefntred{}\NDdefnsred{}}

% defns Commuting
%% defn tcom
\newcommand{\NDdruleTcomXXunitEXXunitEName}[0]{\NDdrulename{Tcom\_unitE\_unitE}}
\newcommand{\NDdruleTcomXXunitEXXunitE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{t_{{\mathrm{1}}}}   \NDsym{)}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{t_{{\mathrm{1}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleTcomXXunitEXXunitEName}{}%
}}

\newcommand{\NDdruleTcomXXunitEXXtenEName}[0]{\NDdrulename{Tcom\_unitE\_tenE}}
\newcommand{\NDdruleTcomXXunitEXXtenE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{t_{{\mathrm{1}}}}   \NDsym{)}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{t_{{\mathrm{1}}}}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleTcomXXunitEXXtenEName}{}%
}}

\newcommand{\NDdruleTcomXXunitEXXimpEName}[0]{\NDdrulename{Tcom\_unitE\_impE}}
\newcommand{\NDdruleTcomXXunitEXXimpE}[1]{\NDdrule[#1]{%
}{
 \NDsym{(}   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{t_{{\mathrm{1}}}}   \NDsym{)}   \NDnt{t_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDsym{(}   \NDnt{t_{{\mathrm{1}}}}   \NDnt{t_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleTcomXXunitEXXimpEName}{}%
}}

\newcommand{\NDdruleTcomXXtenEXXunitEName}[0]{\NDdrulename{Tcom\_tenE\_unitE}}
\newcommand{\NDdruleTcomXXtenEXXunitE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{t_{{\mathrm{1}}}}   \NDsym{)}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{t_{{\mathrm{1}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleTcomXXtenEXXunitEName}{}%
}}

\newcommand{\NDdruleTcomXXtenEXXtenEName}[0]{\NDdrulename{Tcom\_tenE\_tenE}}
\newcommand{\NDdruleTcomXXtenEXXtenE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :  \NDnt{X_{{\mathrm{2}}}}  \otimes  \NDnt{Y_{{\mathrm{2}}}} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{t_{{\mathrm{1}}}}   \NDsym{)}  :  \NDnt{X_{{\mathrm{1}}}}  \otimes  \NDnt{Y_{{\mathrm{1}}}} \,\mathsf{be}\, \NDmv{w}  \otimes  \NDmv{z} \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :  \NDnt{X_{{\mathrm{2}}}}  \otimes  \NDnt{Y_{{\mathrm{2}}}} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{t_{{\mathrm{1}}}}  :  \NDnt{X_{{\mathrm{1}}}}  \otimes  \NDnt{Y_{{\mathrm{1}}}} \,\mathsf{be}\, \NDmv{w}  \otimes  \NDmv{z} \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleTcomXXtenEXXtenEName}{}%
}}

\newcommand{\NDdruleTcomXXtenEXXimpEName}[0]{\NDdrulename{Tcom\_tenE\_impE}}
\newcommand{\NDdruleTcomXXtenEXXimpE}[1]{\NDdrule[#1]{%
}{
 \NDsym{(}   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :  \NDnt{X_{{\mathrm{2}}}}  \otimes  \NDnt{Y_{{\mathrm{2}}}} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{t_{{\mathrm{1}}}}   \NDsym{)}   \NDnt{t_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :  \NDnt{X_{{\mathrm{2}}}}  \otimes  \NDnt{Y_{{\mathrm{2}}}} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDsym{(}   \NDnt{t_{{\mathrm{1}}}}   \NDnt{t_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleTcomXXtenEXXimpEName}{}%
}}

\newcommand{\NDdruleTcomXXimpEXXunitEName}[0]{\NDdrulename{Tcom\_impE\_unitE}}
\newcommand{\NDdruleTcomXXimpEXXunitE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \NDnt{t_{{\mathrm{1}}}}   \NDnt{t_{{\mathrm{2}}}}   \NDsym{)}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \NDnt{t_{{\mathrm{1}}}}   \NDsym{(}   \mathsf{let}\, \NDnt{t_{{\mathrm{2}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleTcomXXimpEXXunitEName}{}%
}}

\newcommand{\NDdefntcom}[1]{\begin{NDdefnblock}[#1]{$\NDnt{t_{{\mathrm{1}}}}  \leadsto_\mathsf{c}  \NDnt{t_{{\mathrm{2}}}}$}{}
\NDusedrule{\NDdruleTcomXXunitEXXunitE{}}
\NDusedrule{\NDdruleTcomXXunitEXXtenE{}}
\NDusedrule{\NDdruleTcomXXunitEXXimpE{}}
\NDusedrule{\NDdruleTcomXXtenEXXunitE{}}
\NDusedrule{\NDdruleTcomXXtenEXXtenE{}}
\NDusedrule{\NDdruleTcomXXtenEXXimpE{}}
\NDusedrule{\NDdruleTcomXXimpEXXunitE{}}
\end{NDdefnblock}}

%% defn scom
\newcommand{\NDdruleScomXXunitEXXunitEName}[0]{\NDdrulename{Scom\_unitE\_unitE}}
\newcommand{\NDdruleScomXXunitEXXunitE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleScomXXunitEXXunitEName}{}%
}}

\newcommand{\NDdruleScomXXunitETwoXXunitEName}[0]{\NDdrulename{Scom\_unitE2\_unitE}}
\newcommand{\NDdruleScomXXunitETwoXXunitE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{t}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{t}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}   \NDsym{)} }{%
{\NDdruleScomXXunitETwoXXunitEName}{}%
}}

\newcommand{\NDdruleScomXXunitEXXimprEName}[0]{\NDdrulename{Scom\_unitE\_imprE}}
\newcommand{\NDdruleScomXXunitEXXimprE}[1]{\NDdrule[#1]{%
}{
 \mathsf{app}_r\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)} \, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDsym{(}   \mathsf{app}_r\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleScomXXunitEXXimprEName}{}%
}}

\newcommand{\NDdruleScomXXunitETwoXXimprEName}[0]{\NDdrulename{Scom\_unitE2\_imprE}}
\newcommand{\NDdruleScomXXunitETwoXXimprE}[1]{\NDdrule[#1]{%
}{
 \mathsf{app}_r\, \NDsym{(}   \mathsf{let}\, \NDnt{t}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)} \, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{t}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDsym{(}   \mathsf{app}_r\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}   \NDsym{)} }{%
{\NDdruleScomXXunitETwoXXimprEName}{}%
}}

\newcommand{\NDdruleScomXXunitEXXFEName}[0]{\NDdrulename{Scom\_unitE\_FE}}
\newcommand{\NDdruleScomXXunitEXXFE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleScomXXunitEXXFEName}{}%
}}

\newcommand{\NDdruleScomXXunitETwoXXFEName}[0]{\NDdrulename{Scom\_unitE2\_FE}}
\newcommand{\NDdruleScomXXunitETwoXXFE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{t}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{t}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}   \NDsym{)} }{%
{\NDdruleScomXXunitETwoXXFEName}{}%
}}

\newcommand{\NDdruleScomXXtenEXXunitEName}[0]{\NDdrulename{Scom\_tenE\_unitE}}
\newcommand{\NDdruleScomXXtenEXXunitE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :  \NDnt{A}  \triangleright  \NDnt{B} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :  \NDnt{A}  \triangleright  \NDnt{B} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleScomXXtenEXXunitEName}{}%
}}

\newcommand{\NDdruleScomXXtenETwoXXunitEName}[0]{\NDdrulename{Scom\_tenE2\_unitE}}
\newcommand{\NDdruleScomXXtenETwoXXunitE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{t}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{t}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}   \NDsym{)} }{%
{\NDdruleScomXXtenETwoXXunitEName}{}%
}}

\newcommand{\NDdruleScomXXtenEXXtenEName}[0]{\NDdrulename{Scom\_tenE\_tenE}}
\newcommand{\NDdruleScomXXtenEXXtenE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :  \NDnt{A_{{\mathrm{2}}}}  \triangleright  \NDnt{B_{{\mathrm{2}}}} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)}  :  \NDnt{A_{{\mathrm{1}}}}  \triangleright  \NDnt{B_{{\mathrm{1}}}} \,\mathsf{be}\, \NDmv{w}  \triangleright  \NDmv{z} \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :  \NDnt{A_{{\mathrm{2}}}}  \triangleright  \NDnt{B_{{\mathrm{2}}}} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :  \NDnt{A_{{\mathrm{1}}}}  \triangleright  \NDnt{B_{{\mathrm{1}}}} \,\mathsf{be}\, \NDmv{w}  \triangleright  \NDmv{z} \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleScomXXtenEXXtenEName}{}%
}}

\newcommand{\NDdruleScomXXtenETwoXXtenEName}[0]{\NDdrulename{Scom\_tenE2\_tenE}}
\newcommand{\NDdruleScomXXtenETwoXXtenE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{t}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)}  :  \NDnt{A_{{\mathrm{1}}}}  \triangleright  \NDnt{B_{{\mathrm{1}}}} \,\mathsf{be}\, \NDmv{w}  \triangleright  \NDmv{z} \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{t}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :  \NDnt{A_{{\mathrm{1}}}}  \triangleright  \NDnt{B_{{\mathrm{1}}}} \,\mathsf{be}\, \NDmv{w}  \triangleright  \NDmv{z} \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}   \NDsym{)} }{%
{\NDdruleScomXXtenETwoXXtenEName}{}%
}}

\newcommand{\NDdruleScomXXtenEXXimprEName}[0]{\NDdrulename{Scom\_tenE\_imprE}}
\newcommand{\NDdruleScomXXtenEXXimprE}[1]{\NDdrule[#1]{%
}{
 \mathsf{app}_r\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :  \NDnt{A_{{\mathrm{2}}}}  \triangleright  \NDnt{B_{{\mathrm{2}}}} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)} \, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :  \NDnt{A_{{\mathrm{2}}}}  \triangleright  \NDnt{B_{{\mathrm{2}}}} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDsym{(}   \mathsf{app}_r\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleScomXXtenEXXimprEName}{}%
}}

\newcommand{\NDdruleScomXXtenETwoXXimprEName}[0]{\NDdrulename{Scom\_tenE2\_imprE}}
\newcommand{\NDdruleScomXXtenETwoXXimprE}[1]{\NDdrule[#1]{%
}{
 \mathsf{app}_r\, \NDsym{(}   \mathsf{let}\, \NDnt{t}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)} \, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{t}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDsym{(}   \mathsf{app}_r\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}   \NDsym{)} }{%
{\NDdruleScomXXtenETwoXXimprEName}{}%
}}

\newcommand{\NDdruleScomXXtenEXXimplEName}[0]{\NDdrulename{Scom\_tenE\_implE}}
\newcommand{\NDdruleScomXXtenEXXimplE}[1]{\NDdrule[#1]{%
}{
 \mathsf{app}_l\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :  \NDnt{A_{{\mathrm{2}}}}  \triangleright  \NDnt{B_{{\mathrm{2}}}} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)} \, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :  \NDnt{A_{{\mathrm{2}}}}  \triangleright  \NDnt{B_{{\mathrm{2}}}} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDsym{(}   \mathsf{app}_l\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleScomXXtenEXXimplEName}{}%
}}

\newcommand{\NDdruleScomXXtenETwoXXimplEName}[0]{\NDdrulename{Scom\_tenE2\_implE}}
\newcommand{\NDdruleScomXXtenETwoXXimplE}[1]{\NDdrule[#1]{%
}{
 \mathsf{app}_l\, \NDsym{(}   \mathsf{let}\, \NDnt{t}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)} \, \NDnt{s_{{\mathrm{2}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{t}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDsym{(}   \mathsf{app}_l\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}   \NDsym{)} }{%
{\NDdruleScomXXtenETwoXXimplEName}{}%
}}

\newcommand{\NDdruleScomXXtenEXXFEName}[0]{\NDdrulename{Scom\_tenE\_FE}}
\newcommand{\NDdruleScomXXtenEXXFE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :  \NDnt{A}  \triangleright  \NDnt{B} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{z}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :  \NDnt{A}  \triangleright  \NDnt{B} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{z}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleScomXXtenEXXFEName}{}%
}}

\newcommand{\NDdruleScomXXtenETwoXXFEName}[0]{\NDdrulename{Scom\_tenE2\_FE}}
\newcommand{\NDdruleScomXXtenETwoXXFE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{t}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)}  :   \mathsf{F} \NDnt{Z}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{z}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{t}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :   \mathsf{F} \NDnt{Z}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{z}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleScomXXtenETwoXXFEName}{}%
}}

\newcommand{\NDdruleScomXXFEXXunitEName}[0]{\NDdrulename{Scom\_FE\_unitE}}
\newcommand{\NDdruleScomXXFEXXunitE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :   \mathsf{Unit}  \,\mathsf{be}\,  \mathsf{triv}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}   \NDsym{)} }{%
{\NDdruleScomXXFEXXunitEName}{}%
}}

\newcommand{\NDdruleScomXXFEXXtenEName}[0]{\NDdrulename{Scom\_FE\_tenE}}
\newcommand{\NDdruleScomXXFEXXtenE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)}  :  \NDnt{A}  \triangleright  \NDnt{B} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :  \NDnt{A}  \triangleright  \NDnt{B} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleScomXXFEXXtenEName}{}%
}}

\newcommand{\NDdruleScomXXFEXXimprEName}[0]{\NDdrulename{Scom\_FE\_imprE}}
\newcommand{\NDdruleScomXXFEXXimprE}[1]{\NDdrule[#1]{%
}{
 \mathsf{app}_r\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)} \, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDsym{(}   \mathsf{app}_r\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleScomXXFEXXimprEName}{}%
}}

\newcommand{\NDdruleScomXXFEXXimplEName}[0]{\NDdrulename{Scom\_FE\_implE}}
\newcommand{\NDdruleScomXXFEXXimplE}[1]{\NDdrule[#1]{%
}{
 \mathsf{app}_l\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)} \, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDsym{(}   \mathsf{app}_l\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleScomXXFEXXimplEName}{}%
}}

\newcommand{\NDdruleScomXXFEXXFEName}[0]{\NDdrulename{Scom\_FE\_FE}}
\newcommand{\NDdruleScomXXFEXXFE}[1]{\NDdrule[#1]{%
}{
 \mathsf{let}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{1}}}}   \NDsym{)}  :   \mathsf{F} \NDnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{y}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \leadsto_\mathsf{c}   \mathsf{let}\, \NDnt{s_{{\mathrm{2}}}}  :   \mathsf{F} \NDnt{X}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{x}  \,\mathsf{in}\, \NDsym{(}   \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :   \mathsf{F} \NDnt{Y}  \,\mathsf{be}\,  \mathsf{F}\, \NDmv{y}  \,\mathsf{in}\, \NDnt{s_{{\mathrm{3}}}}   \NDsym{)} }{%
{\NDdruleScomXXFEXXFEName}{}%
}}

\newcommand{\NDdefnscom}[1]{\begin{NDdefnblock}[#1]{$\NDnt{s_{{\mathrm{1}}}}  \leadsto_\mathsf{c}  \NDnt{s_{{\mathrm{2}}}}$}{}
\NDusedrule{\NDdruleScomXXunitEXXunitE{}}
\NDusedrule{\NDdruleScomXXunitETwoXXunitE{}}
\NDusedrule{\NDdruleScomXXunitEXXimprE{}}
\NDusedrule{\NDdruleScomXXunitETwoXXimprE{}}
\NDusedrule{\NDdruleScomXXunitEXXFE{}}
\NDusedrule{\NDdruleScomXXunitETwoXXFE{}}
\NDusedrule{\NDdruleScomXXtenEXXunitE{}}
\NDusedrule{\NDdruleScomXXtenETwoXXunitE{}}
\NDusedrule{\NDdruleScomXXtenEXXtenE{}}
\NDusedrule{\NDdruleScomXXtenETwoXXtenE{}}
\NDusedrule{\NDdruleScomXXtenEXXimprE{}}
\NDusedrule{\NDdruleScomXXtenETwoXXimprE{}}
\NDusedrule{\NDdruleScomXXtenEXXimplE{}}
\NDusedrule{\NDdruleScomXXtenETwoXXimplE{}}
\NDusedrule{\NDdruleScomXXtenEXXFE{}}
\NDusedrule{\NDdruleScomXXtenETwoXXFE{}}
\NDusedrule{\NDdruleScomXXFEXXunitE{}}
\NDusedrule{\NDdruleScomXXFEXXtenE{}}
\NDusedrule{\NDdruleScomXXFEXXimprE{}}
\NDusedrule{\NDdruleScomXXFEXXimplE{}}
\NDusedrule{\NDdruleScomXXFEXXFE{}}
\end{NDdefnblock}}

\newcommand{\NDdefnsCommuting}{
\NDdefntcom{}\NDdefnscom{}}

\newcommand{\NDdefnss}{
\NDdefnsJtype
\NDdefnsReduction
\NDdefnsCommuting
}

\newcommand{\NDall}{\NDmetavars\\[0pt]
\NDgrammar\\[5.0mm]
\NDdefnss}

### 2019-02-20 post-linearity-2018/final-submission/LAM-output.tex
Final version sources.

--- 2019-02-20 post-linearity-2018/LAM.tex
@@
       \begin{array}{lll}        
-        \text{($\cat{C}$-Terms)} & [[t]] ::= [[x]] \mid [[trivT]] \mid [[t1 (*) t2]] \mid [[let t1 : X be q in t2]] \mid [[\x:X.t]] \mid [[t1 t2]] \mid [[ex t1 , t2 with x1 , x2 in t3]] \mid [[Gf s]]\\
-        \text{($\cat{L}$-Terms)} & [[s]] ::= [[x]] \mid [[trivS]] \mid [[s1 (>) s2]] \mid [[let s1 : A be p in s2]] \mid [[let t : X be q in s]] \mid [[\l x : A.s]] \mid [[\r x : A . s]] \\
-        & \,\,\,\,\,\,\,\,\,\mid [[appl s1 s2]] \mid [[appr s1 s2]] \mid [[F t]]\\        
-        \text{($\cat{C}$-Patterns)} & [[q]] ::= [[trivTp]] \mid [[x]] \mid [[q1 (*) q2]] \mid [[Gf p]]\\
-        \text{($\cat{L}$-Patterns)} & [[p]] ::= [[trivSp]] \mid [[x]] \mid [[p1 (>) p2]] \mid [[F q]]\\        
-        \text{($\cat{C}$-Typing Judgment)} & [[I |-c t : X]]\\
-        \text{($\cat{L}$-Typing Judgment)} & [[G |-l s : A]]\\
+        \text{($\cat{C}$-Terms)} & \NDnt{t} ::= \NDmv{x} \mid  \mathsf{triv}  \mid \NDnt{t_{{\mathrm{1}}}}  \otimes  \NDnt{t_{{\mathrm{2}}}} \mid  \mathsf{let}\, \NDnt{t_{{\mathrm{1}}}}  :  \NDnt{X} \,\mathsf{be}\, \NDnt{q} \,\mathsf{in}\, \NDnt{t_{{\mathrm{2}}}}  \mid  \lambda  \NDmv{x}  :  \NDnt{X} .
+\NDnt{t}  \mid  \NDnt{t_{{\mathrm{1}}}}   \NDnt{t_{{\mathrm{2}}}}  \mid  \mathsf{ex}\, \NDnt{t_{{\mathrm{1}}}} , \NDnt{t_{{\mathrm{2}}}} \,\mathsf{with}\, \NDmv{x_{{\mathrm{1}}}} , \NDmv{x_{{\mathrm{2}}}} \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}}  \mid  \mathsf{G}\, \NDnt{s} \\
+        \text{($\cat{L}$-Terms)} & \NDnt{s} ::= \NDmv{x} \mid  \mathsf{triv}  \mid \NDnt{s_{{\mathrm{1}}}}  \triangleright  \NDnt{s_{{\mathrm{2}}}} \mid  \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :  \NDnt{A} \,\mathsf{be}\, \NDnt{p} \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}}  \mid  \mathsf{let}\, \NDnt{t}  :  \NDnt{X} \,\mathsf{be}\, \NDnt{q} \,\mathsf{in}\, \NDnt{s}  \mid  \lambda_l  \NDmv{x}  :  \NDnt{A} .
+\NDnt{s}  \mid  \lambda_r  \NDmv{x}  :  \NDnt{A} .
+\NDnt{s}  \\
+        & \,\,\,\,\,\,\,\,\,\mid  \mathsf{app}_l\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}  \mid  \mathsf{app}_r\, \NDnt{s_{{\mathrm{1}}}} \, \NDnt{s_{{\mathrm{2}}}}  \mid  \mathsf{F} \NDnt{t} \\
+        \text{($\cat{C}$-Patterns)} & \NDnt{q} ::=  \mathsf{triv}  \mid \NDmv{x} \mid \NDnt{q_{{\mathrm{1}}}}  \otimes  \NDnt{q_{{\mathrm{2}}}} \mid  \mathsf{G}\, \NDnt{p} \\
+        \text{($\cat{L}$-Patterns)} & \NDnt{p} ::=  \mathsf{triv}  \mid \NDmv{x} \mid \NDnt{p_{{\mathrm{1}}}}  \triangleright  \NDnt{p_{{\mathrm{2}}}} \mid  \mathsf{F}\, \NDnt{q} \\        
+        \text{($\cat{C}$-Typing Judgment)} & \Phi  \vdash_\mathcal{C}  \NDnt{t}  \NDsym{:}  \NDnt{X}\\
+        \text{($\cat{L}$-Typing Judgment)} & \Gamma  \vdash_\mathcal{L}  \NDnt{s}  \NDsym{:}  \NDnt{A}\\
       \end{array}
@@
 
-Now $\cat{C}$-typing judgments are denoted by $[[P |-c t : X]]$ where
-$[[P]]$ is a sequence of pairs of variables and their types, denoted by
-$[[x : X]]$, $[[t]]$ is a $\cat{C}$-term, and $[[X]]$ is a $\cat{C}$-type.  
-The $\cat{C}$-terms are all standard, but $[[Gf s]]$ corresponds to the
+Now $\cat{C}$-typing judgments are denoted by $\Psi  \vdash_\mathcal{C}  \NDnt{t}  \NDsym{:}  \NDnt{X}$ where
+$\Psi$ is a sequence of pairs of variables and their types, denoted by
+$\NDmv{x}  \NDsym{:}  \NDnt{X}$, $\NDnt{t}$ is a $\cat{C}$-term, and $\NDnt{X}$ is a $\cat{C}$-type.  
+The $\cat{C}$-terms are all standard, but $ \mathsf{G}\, \NDnt{s} $ corresponds to the
 morphism part of the right-adjoint of the adjunction between both logics,
-and $[[ex t1 , t2 with x1 , x2 in t3]]$ is the introduction form for the
+and $ \mathsf{ex}\, \NDnt{t_{{\mathrm{1}}}} , \NDnt{t_{{\mathrm{2}}}} \,\mathsf{with}\, \NDmv{x_{{\mathrm{1}}}} , \NDmv{x_{{\mathrm{2}}}} \,\mathsf{in}\, \NDnt{t_{{\mathrm{3}}}} $ is the introduction form for the
 structural rule exchange.
 
-The $\cat{L}$-typing judgment has the form $[[G |-l s : A]]$ where $[[G]]$
-is now a $\cat{L}$-context, denoted by $[[G]]$ or $[[D]]$. These contexts
+The $\cat{L}$-typing judgment has the form $\Gamma  \vdash_\mathcal{L}  \NDnt{s}  \NDsym{:}  \NDnt{A}$ where $\Gamma$
+is now a $\cat{L}$-context, denoted by $\Gamma$ or $\Delta$. These contexts
 are ordered sequences of pairs of free variables with their types from
-\emph{both} sides denoted by $[[x : B]]$ and $[[x : X]]$ respectively.
-Finally, the term $[[s]]$ is a $\cat{L}$-term, and $[[A]]$ is a
-$\cat{L}$-type.  Given two typing contexts $[[G]]$ and $[[D]]$ we denote
-their concatenation by $[[G;D]]$; we use a semicolon here to emphasize the
+\emph{both} sides denoted by $\NDmv{x}  \NDsym{:}  \NDnt{B}$ and $\NDmv{x}  \NDsym{:}  \NDnt{X}$ respectively.
+Finally, the term $\NDnt{s}$ is a $\cat{L}$-term, and $\NDnt{A}$ is a
+$\cat{L}$-type.  Given two typing contexts $\Gamma$ and $\Delta$ we denote
+their concatenation by $\Gamma  \NDsym{;}  \Delta$; we use a semicolon here to emphasize the
 fact that the contexts are ordered. $\cat{L}$-terms correspond to
 introduction and elimination forms for each of the previous types. For
-example, $[[s1 (>) s2]]$ introduces a tensor, and
-$[[let s1 : A (>) B be x (>) y in s2]]$ eliminates a tensor.
+example, $\NDnt{s_{{\mathrm{1}}}}  \triangleright  \NDnt{s_{{\mathrm{2}}}}$ introduces a tensor, and
+$ \mathsf{let}\, \NDnt{s_{{\mathrm{1}}}}  :  \NDnt{A}  \triangleright  \NDnt{B} \,\mathsf{be}\, \NDmv{x}  \triangleright  \NDmv{y} \,\mathsf{in}\, \NDnt{s_{{\mathrm{2}}}} $ eliminates a tensor.
 
@@
 intuitionistic linear logic whose judgment is the $\mathcal{C}$-typing
-judgment denoted by $[[P |-c t : X]]$, and the bottom of the figure
+judgment denoted by $\Psi  \vdash_\mathcal{C}  \NDnt{t}  \NDsym{:}  \NDnt{X}$, and the bottom of the figure
 are the rules for the mixed commutative/non-commutative Lambek
 calculus whose judgment is the $\mathcal{L}$-judgment denoted by
-$[[G |-l s : A]]$, and the two halves are connected via the rules 
+$\Gamma  \vdash_\mathcal{L}  \NDnt{s}  \NDsym{:}  \NDnt{A}$, and the two halves are connected via the rules 
 rules $\NDdruleTXXGIName{}$, $\NDdruleSXXGEName{}$,
@@
       \inferrule* [right={\scriptsize $\ElledruleTXXcutName$}] {
-        {[[I |-c t1 : X (*) Y]]} \\
+        {\Phi  \vdash_\mathcal{C}  \NDnt{t_{{\mathrm{1}}}}  \NDsym{:}  \NDnt{X}  \otimes  \NDnt{Y}} \\
         $$\mprset{flushleft}
         \inferrule* [right={\scriptsize $\ElledruleTXXtenLName$}] {
-          {[[P1, x : X, y : Y, P2 |-c t2 : Z]]}
-        }{[[P1, z : X (*) Y, P2 |-c let z : X (*) Y be x (*) y in t2 : Z]]}
-      }{[[P1, I, P2 |-c [t1 / z](let z : X (*) Y be x (*) y in t2) : Z]]}
+          {\Psi_{{\mathrm{1}}}  \NDsym{,}  \NDmv{x}  \NDsym{:}  \NDnt{X}  \NDsym{,}  \NDmv{y}  \NDsym{:}  \NDnt{Y}  \NDsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \NDnt{t_{{\mathrm{2}}}}  \NDsym{:}  \NDnt{Z}}
+        }{\Psi_{{\mathrm{1}}}  \NDsym{,}  \NDmv{z}  \NDsym{:}  \NDnt{X}  \otimes  \NDnt{Y}  \NDsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}   \mathsf{let}\, \NDmv{z}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{t_{{\mathrm{2}}}}   \NDsym{:}  \NDnt{Z}}
+      }{\Psi_{{\mathrm{1}}}  \NDsym{,}  \Phi  \NDsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \NDsym{[}  \NDnt{t_{{\mathrm{1}}}}  \NDsym{/}  \NDmv{z}  \NDsym{]}  \NDsym{(}   \mathsf{let}\, \NDmv{z}  :  \NDnt{X}  \otimes  \NDnt{Y} \,\mathsf{be}\, \NDmv{x}  \otimes  \NDmv{y} \,\mathsf{in}\, \NDnt{t_{{\mathrm{2}}}}   \NDsym{)}  \NDsym{:}  \NDnt{Z}}
     \end{math}
@@
 %%   $CL$ that maps our term assignment for natural deduction to Benton's
-%%   term assignment, and then shows that if there is reduction $[[t1 ~>  t2]]$ (resp. $[[s1 ~> s2]]$) in CNC, then there is a reduction
+%%   term assignment, and then shows that if there is reduction $\NDnt{t_{{\mathrm{1}}}}  \leadsto_\beta  \NDnt{t_{{\mathrm{2}}}}$ (resp.
+$\NDnt{s_{{\mathrm{1}}}}  \leadsto_\beta  \NDnt{s_{{\mathrm{2}}}}$) in CNC, then there is a reduction
 %%   $CL(t_1)\leadsto CL(t_2)$ (resp. $CL(s_1)\leadsto CL(s_2)$) in
@@
 %%   closed category in LNL, and the Lambek category in LAM to the SMCC in
-%%   LNL. For instance, $s_1\triangleright s_2$ in CNC, where $[[s1]]$ and
-%%   $[[s2]]$ are atomic terms, maps to $CL(s_1)\otimes CL(s_2)$ in LNL.
+%%   LNL. For instance, $s_1\triangleright s_2$ in CNC, where $\NDnt{s_{{\mathrm{1}}}}$ and
+%%   $\NDnt{s_{{\mathrm{2}}}}$ are atomic terms, maps to $CL(s_1)\otimes CL(s_2)$ in LNL.
 %% \end{proof}

### 2019-02-20 post-linearity-2018/final-submission/adjoint-models.tex
Final version sources.

--- 2018-12-23 post-linearity-2018/adjoint-models.tex
@@
 LNL model consists of a symmetric monoidal adjunction
-$F:\cat{C}\dashv\cat{L}:G$ between a cartesian closed category
+$F:\cat{C}\dashv\cat{L}:G$ between a Cartesian closed category
 $\cat{C}$ and a symmetric monoidal closed category $\cat{L}$. LAM
@@
 $\cat{C}$ in LAM is strong but non-commutative. In Benton's LNL model,
-the monad on the cartesian closed category is commutative, but later
+the monad on the Cartesian closed category is commutative, but later
 Benton and Wadler \cite{Benton:1996} wonder, is it possible to model
 non-commutative monads using adjoint models similar to LNL models? The
-following answers their question in the positive w.r.t. the monoidal monads.
+following shows that LAMs correspond to strong non-commutative
+monoidal monads.
 \begin{lemma}
@@
 \begin{proof}
-The proof is done by frist defining a natural transformation $\tau$, called
+The proof is done by first defining a natural transformation $\tau$, called
 the \textbf{tensorial strength}, with components
@@
 \noindent
-Finally, we obtain the non-communativity of the monad induced by some 
+Finally, we obtain the non-commutativity of the monad induced by some 
 LAM as follows.
@@
 latter is shown by proving that its corresponding co-Eilenberg-Moore
-category is symmetric monoidal closed.
+category is symmetric monoidal.
 
@@
 
-\begin{corollary}
-  The subcategory, $\mathsf{Exp}(\cat{L}^{FG})$, of the
-  co-Eilenberg-Moore category $\cat{L}^{FG}$ consisting of the free
-  exponential coalgebras is symmetric monoidal closed.
-\end{corollary}
-\begin{proof}
-  The proof that $\mathsf{Exp}(\cat{L}^{FG})$ is monoidal closed
-  follows similarly to Benton~\cite{Benton:1994}.
-\end{proof}
+%% \begin{corollary}
+%%   The subcategory, $\mathsf{Exp}(\cat{L}^{FG})$, of the
+%%   co-Eilenberg-Moore category $\cat{L}^{FG}$ consisting of the free
+%%   exponential coalgebras is symmetric monoidal closed.
+%% \end{corollary}
+%% \begin{proof}
+%%   The proof that $\mathsf{Exp}(\cat{L}^{FG})$ is monoidal closed
+%%   follows similarly to Benton~\cite{Benton:1994}.
+%% \end{proof}
 

### 2019-02-20 post-linearity-2018/final-submission/fwork.tex
Final version sources.

--- 2018-05-22 linearity-2018/fwork.tex
@@
 in the future.
+
+Hasegawa~\cite{EPTCS238.6} studies the linear of-course modality,
+$!A$, as a comonad induced by an adjunction between a Cartesian closed
+category a (non-symmetric) monoidal category.  The results here
+generalizes his by generalizing the Cartesian closed category to a
+symmetric monoidal closed category.  However, his approach focuses on
+the comonad rather than the adjunctions.  It would be interesting to
+do the same for LAM as well.

### 2019-02-20 post-linearity-2018/final-submission/introduction.tex
Final version sources.

--- 2018-10-22 post-linearity-2018/introduction.tex
@@
 mathematics of sentence structure, and can be found at the core of
-Categorial Grammar; a term first used in the title of Bar-Hillel,
+Categorical Grammar; a term first used in the title of Bar-Hillel,
 Gaifman and Shamir (1960), but categorical grammar began with
 Ajdukiewicz (1935) quite a few years earlier. At the end of the
-eighties the Lambek calculus and other systems of categorial grammars
+eighties the Lambek calculus and other systems of categorical grammars
 were taken up by computational linguists as exemplified by

### 2019-02-20 post-linearity-2018/final-submission/sequent-output.tex
Final version sources.

We now introduce Commutative/Non-commutative (CNC) logic in the form of a
sequent calculus. One should view this logic as composed of two logics; one
sitting to the left of the other. On the left, there is intuitionistic
linear logic, denoted by $\cat{C}$ and on the right is the Lambek calculus
denoted by $\cat{L}$. Then we connect these two systems by a pair of
monoidal adjoint functors $\cat{C} : \func{F} \dashv \func{G} : \cat{L}$.
Keeping this intuition in mind we now define the syntax for CNC logic.

\begin{definition}
  \label{def:Lambek-syntax}
  The following grammar describes the syntax of the sequent calculus of
  CNC logic:
  \begin{center}\vspace{-3px}\small
    \begin{math}
      \begin{array}{lll}
        \text{($\cat{C}$-Types)} & \SCnt{W},\SCnt{X},\SCnt{Y},\SCnt{Z} ::=  \mathsf{Unit}  \mid \SCnt{X}  \otimes  \SCnt{Y} \mid \SCnt{X}  \multimap  \SCnt{Y} \mid  \mathsf{G} \SCnt{A} \\
        \text{($\cat{L}$-Types)} & \SCnt{A},\SCnt{B},\SCnt{C},D ::=  \mathsf{Unit}  \mid \SCnt{A}  \triangleright  \SCnt{B} \mid \SCnt{A}  \rightharpoonup  \SCnt{B} \mid \SCnt{B}  \leftharpoonup  \SCnt{A} \mid  \mathsf{F} \SCnt{X} \\
        \text{($\cat{C}$-Contexts)} & \Phi,\Psi ::=  \cdot  \mid \SCnt{X} \mid \Phi  \SCsym{,}  \Psi\\
        \text{($\cat{L}$-Contexts)} & \Gamma,\Delta ::=  \cdot  \mid \SCnt{A} \mid \SCnt{X} \mid \Gamma  \SCsym{;}  \Delta\\
      \end{array}
    \end{math}
  \end{center}
\end{definition}

The syntax for $\cat{C}$-types are the standard types for intuitionistic
linear logic. We have a constant $ \mathsf{Unit} $, tensor product $\SCnt{X}  \otimes  \SCnt{Y}$,
and linear implication $\SCnt{X}  \multimap  \SCnt{Y}$, but just as in LNL logic we also have a
type $ \mathsf{G} \SCnt{A} $ where $\SCnt{A}$ is an $\cat{L}$-type; that is, a type from the
non-commutative side corresponding to the right-adjoint functor between
$\cat{L}$ and $\cat{C}$. This functor can be used to import types from the
non-commutative side into the commutative side. Now a sequent in the the
commutative side is denoted by $\Phi  \vdash_\mathcal{C}  \SCnt{X}$ where $\Phi$ is a
$\cat{C}$-context, which is a sequence of types $\SCnt{X}$.

The non-commutative side is a bit more interesting than the commutative side
just introduced. Sequents in the non-commutative side are denoted by
$\Gamma  \vdash_\mathcal{L}  \SCnt{A}$ where $\Gamma$ is now a $\cat{L}$-context. These contexts are
ordered sequences of types from \emph{both} sides denoted by $\SCnt{B}$ and
$\SCnt{X}$ respectively. Given two contexts $\Gamma$ and $\Delta$ we denote their
concatenation by $\Gamma  \SCsym{;}  \Delta$; we use a semicolon here to emphasize the fact
that the contexts are ordered.

The context consisting of hypotheses from both sides goes back to
Benton~\cite{Benton:1994} and is a property unique to adjoint logics such as
Benton's LNL logic and CNC logic. This is also a very useful property
because it allows one to make use of both sides within the Lambek calculus
without the need to annotate every formula with a modality.

The reader familiar with LNL logic will notice that our sequent,
$\Gamma  \vdash_\mathcal{L}  \SCnt{A}$, differs from Benton's. His is of the form $\Gamma  \SCsym{;}  \Delta  \vdash_\mathcal{L}  \SCnt{A}$,
where $\Gamma$ contains non-linear types, and $\Delta$ contains linear
formulas. Just as Benton remarks, the splitting of his contexts was a
presentational device. One should view his contexts as merged, and hence,
linear formulas were fully mixed with non-linear formulas. Now why did we
not use this presentational device? Because, when contexts from LNL logic
become out of order Benton could use the exchange rule to put them back in
order again, but we no longer have general exchange. Thus, we are not able
to keep the context organized in this way.

The syntax for $\cat{L}$-types are of the typical form for the Lambek
Calculus. We have two unit types $ \mathsf{Unit} $ (one for each side), a
non-commutative tensor product $\SCnt{A}  \triangleright  \SCnt{B}$, right implication $\SCnt{A}  \rightharpoonup  \SCnt{B}$, and left implication $\SCnt{B}  \leftharpoonup  \SCnt{A}$. In standard Lambek
Calculus \cite{Pentus1995}, $\SCnt{A}  \rightharpoonup  \SCnt{B}$ is written as $B / A$ and
$\SCnt{B}  \leftharpoonup  \SCnt{A}$ as $A \backslash B$. We use $\rightharpoonup$ and
$\leftharpoonup$ here instead to indicate they are two directions of
the linear implication $\multimap$.

The sequent calculus for CNC logic can be found in
Figure~\ref{fig:CNC-sequent-calculus}. We split the figure in two: the top
of the figure are the rules of intuitionistic linear logic whose sequents
are the $\mathcal{C}$-sequents denoted by $\Psi  \vdash_\mathcal{C}  \SCnt{X}$, and the bottom of
the figure are the rules for the mixed commutative/non-commutative Lambek
calculus whose sequents are the $\mathcal{L}$-sequents denoted by
$\Gamma  \vdash_\mathcal{L}  \SCnt{A}$, but the two halves are connected via the functor rules
$\SCdruleTXXGrName{}$, $\SCdruleSXXGlName{}$, $\SCdruleSXXFlName{}$, and
$\SCdruleSXXFrName{}$, and the rules $\SCdruleSXXunitLOneName{}$,
$\SCdruleSXXexName{}$, $\SCdruleSXXtenLOneName{}$, $\SCdruleSXXimpLName{}$,
$\NDdruleSXXcutOneName{}$.
\begin{figure}[!h]
  \footnotesize
  \begin{tabular}{|c|}
    \hline\\
    \begin{mathpar}
    \SCdruleTXXax{} \and
    \SCdruleTXXunitL{} \and
    \SCdruleTXXunitR{} \and
    \SCdruleTXXtenL{} \and
    \SCdruleTXXtenR{} \and
    \SCdruleTXXimpL{} \and
    \SCdruleTXXimpR{} \and
    \SCdruleTXXGr{} \and
    \SCdruleTXXex{} \and
    \SCdruleTXXcut{}
    \end{mathpar}\\\\
    \hline
    \\[5px]
    \begin{mathpar}
    \SCdruleSXXax{} \and
    \SCdruleSXXunitLOne{} \and
    \SCdruleSXXunitLTwo{} \and
    \SCdruleSXXunitR{} \and
    \SCdruleSXXex{} \and
    \SCdruleSXXtenLOne{} \and
    \SCdruleSXXtenLTwo{} \and
    \SCdruleSXXtenR{} \and
    \SCdruleSXXimpL{} \and
    \SCdruleSXXimprL{} \and
    \SCdruleSXXimprR{} \and
    \SCdruleSXXimplL{} \and
    \SCdruleSXXimplR{} \and
    \SCdruleSXXFl{} \and
    \SCdruleSXXFr{} \and
    \SCdruleSXXGl{} \and
    \SCdruleSXXcutOne{} \and
    \SCdruleSXXcutTwo{} \and
    \end{mathpar}\\\\
    \hline
  \end{tabular}
  \caption{Sequent Calculus for CNC Logic}
  \label{fig:CNC-sequent-calculus}
\end{figure}

We prove cut elimination for the sequent calculus. We define the
\textit{rank} $|X|$ (resp. $|A|$) of a commutative (resp. non-commutative)
formula to be the number of logical connectives in the proposition. For
instance, $|\SCnt{X}  \otimes  \SCnt{Y}| = |\SCnt{X}| + |\SCnt{Y}| + 1$. The \textit{cut rank}
$c(\Pi)$ of a proof $\Pi$ is one more than the maximum of the ranks of all
the cut formulae in $\Pi$, and $0$ if $\Pi$ is cut-free. Then the
\textit{depth} $d(\Pi)$ of a proof $\Pi$ is the length of the longest path
in the proof tree (so the depth of an axiom is $0$). The key to the proof
of cut elimination is the following lemma, which shows how to transform a
single cut, either by removing it or by replacing it with one or more
simpler cuts.
\begin{lemma}[Cut Reduction]
  \label{lem:cut-reduction}
  The cut-reduction steps are as follows:
  \begin{enumerate}
  \item If $\Pi_1$ is a proof of $\Phi  \vdash_\mathcal{C}  \SCnt{X}$ and $\Pi_2$ is a proof of
  $\Psi_{{\mathrm{1}}}  \SCsym{,}  \SCnt{X}  \SCsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \SCnt{Y}$ with $c(\Pi_1)$, $c(\Pi_2)\leq |X|$, then there exists
  a proof $\Pi$ of $\Psi_{{\mathrm{1}}}  \SCsym{,}  \Phi  \SCsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \SCnt{Y}$ with $c(\Pi)\leq |X|$.
  \item If $\Pi_1$ is a proof of $\Phi  \vdash_\mathcal{C}  \SCnt{X}$ and $\Pi_2$ is a proof of
  $\Gamma_{{\mathrm{1}}}  \SCsym{;}  \SCnt{X}  \SCsym{;}  \Gamma_{{\mathrm{2}}}  \vdash_\mathcal{L}  \SCnt{A}$ with $c(\Pi_1)$, $c(\Pi_2)\leq |X|$, then there
  exists a proof $\Pi$ of $\Gamma_{{\mathrm{1}}}  \SCsym{;}  \Phi  \SCsym{;}  \Gamma_{{\mathrm{2}}}  \vdash_\mathcal{L}  \SCnt{A}$ with $c(\Pi)\leq |X|$.
  \item If $\Pi_1$ is a proof of $\Gamma  \vdash_\mathcal{L}  \SCnt{A}$ and $\Pi_2$ is a proof of
  $\Delta_{{\mathrm{1}}}  \SCsym{;}  \SCnt{A}  \SCsym{;}  \Delta_{{\mathrm{2}}}  \vdash_\mathcal{L}  \SCnt{B}$ with $c(\Pi_1)$, $c(\Pi_2)\leq |A|$, then there
  exists a proof $\Pi$ of $\Delta_{{\mathrm{1}}}  \SCsym{;}  \Gamma  \SCsym{;}  \Delta_{{\mathrm{2}}}  \vdash_\mathcal{L}  \SCnt{B}$ with $c(\Pi)\leq |A|$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  This proof is done case by case on the last step of $\Pi_1$ and
  $\Pi_2$ and by induction on $d(\Pi_1)$ and $d(\Pi_2)$, following
  \cite{Mellies:2009}. For instance, suppose $\Pi_1$ is a proof of
  $\Phi_{{\mathrm{1}}}  \SCsym{,}  \SCnt{X_{{\mathrm{2}}}}  \SCsym{,}  \SCnt{X_{{\mathrm{1}}}}  \SCsym{,}  \Phi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \SCnt{Y}$ and $\Pi_2$ is a proof of $\Psi_{{\mathrm{1}}}  \SCsym{,}  \SCnt{Y}  \SCsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \SCnt{Z}$.  Consider the case where the last step in $\Pi_1$ uses
  the rule $\NDdruleTXXbetaName{}$. $\Pi_1$ can be depicted as
  follows, where the previous steps are denoted by $\pi$:
  \begin{center}
    \scriptsize
    $\Pi_1$:
    \begin{math}
      $$\mprset{flushleft}
      \inferrule* [right={\tiny $\SCdruleTXXexName$}] {
        {
          \begin{array}{c}
            \pi \\
                {\Phi_{{\mathrm{1}}}  \SCsym{,}  \SCnt{X_{{\mathrm{1}}}}  \SCsym{,}  \SCnt{X_{{\mathrm{2}}}}  \SCsym{,}  \Phi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \SCnt{Y}}
          \end{array}
        }
      }{\Phi_{{\mathrm{1}}}  \SCsym{,}  \SCnt{X_{{\mathrm{2}}}}  \SCsym{,}  \SCnt{X_{{\mathrm{1}}}}  \SCsym{,}  \Phi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \SCnt{Y}}
    \end{math}
  \end{center}
  By assumption, $c(\Pi_1),c(\Pi_2)\leq |Y|$. By induction on $\pi$ and
  $\Pi_2$, there is a proof $\Pi'$ for the sequent \\
  $\Psi_{{\mathrm{1}}}  \SCsym{,}  \Phi_{{\mathrm{1}}}  \SCsym{,}  \SCnt{X_{{\mathrm{1}}}}  \SCsym{,}  \SCnt{X_{{\mathrm{2}}}}  \SCsym{,}  \Phi_{{\mathrm{2}}}  \SCsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \SCnt{Z}$ s.t. $c(\Pi')\leq|Y|$. Therefore, the
  proof $\Pi$ can be constructed as follows, and $c(\Pi)=c(\Pi')\leq|Y|$.
  \begin{center}
    \scriptsize
    \begin{math}
      $$\mprset{flushleft}
      \inferrule* [right={\tiny $\SCdruleTXXexName$}] {
        {
          \begin{array}{c}
            \Pi' \\
                 {\Psi_{{\mathrm{1}}}  \SCsym{,}  \Phi_{{\mathrm{1}}}  \SCsym{,}  \SCnt{X_{{\mathrm{1}}}}  \SCsym{,}  \SCnt{X_{{\mathrm{2}}}}  \SCsym{,}  \Phi_{{\mathrm{2}}}  \SCsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \SCnt{Z}}
          \end{array}
        }
      }{\Psi_{{\mathrm{1}}}  \SCsym{,}  \Phi_{{\mathrm{1}}}  \SCsym{,}  \SCnt{X_{{\mathrm{2}}}}  \SCsym{,}  \SCnt{X_{{\mathrm{1}}}}  \SCsym{,}  \Phi_{{\mathrm{2}}}  \SCsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \SCnt{Z}}
    \end{math}
  \end{center}
  The full proof can be found in Appendix~\ref{app:cut-reduction}.
\end{proof}
\noindent
Then we have the following lemma.

\begin{lemma}
  \label{lem:less-cut-rank}
  Let $\Pi$ be a proof of a sequent $\Phi  \vdash_\mathcal{C}  \SCnt{X}$ or $\Gamma  \vdash_\mathcal{L}  \SCnt{A}$ s.t.
  $c(\Pi)>0$. Then there is a proof $\Pi'$ of the same sequent with
  $c(\Pi')<c(\Pi)$.
\end{lemma}
\begin{proof}
  We prove the lemma by induction on $d(\Pi)$. We denote the proof $\Pi$ by 
  $\pi+r$, where $r$ is the last inference of $\Pi$ and $\pi$ denotes the
  rest of the proof. If $r$ is not a cut, then by induction hypothesis on
  $\pi$, there is a proof $\pi'$ s.t. $c(\pi')<c(\pi)$ and $\Pi'=\pi'+r$.
  Otherwise, we assume $r$ is a cut on a formula $Y$. If $c(\Pi)>|X|+1$,
  then there is a cut on $|Y|$ in $\pi$ with $|Y|>|X|$. So we can apply
  the induction hypothesis on $\pi$ to get $\Pi'$ with $c(\Pi')<c(\Pi)$. The
  last case to consider is when $c(\Pi)=|X|+1$ (note that $c(\Pi)$ cannot be
  less than $|X|+1$). In this case, $\Pi$ is in the form of
  \begin{center}
    \scriptsize
    \begin{math}
      $$\mprset{flushleft}
      \inferrule* [right={\tiny $\SCdruleTXXcutName$}] {
        {
          \begin{array}{cc}
            \Pi_1 & \Pi_2 \\
            {\Phi  \vdash_\mathcal{C}  \SCnt{X}} & {\Psi_{{\mathrm{1}}}  \SCsym{,}  \SCnt{X}  \SCsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \SCnt{Y}}
          \end{array}
        }
      }{\Psi_{{\mathrm{1}}}  \SCsym{,}  \Phi  \SCsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \SCnt{Y}}
    \end{math}
    \qquad\qquad
    or,
    \qquad\qquad
    \begin{math}
      $$\mprset{flushleft}
      \inferrule* [right={\tiny $\SCdruleSXXcutOneName$}] {
        {
          \begin{array}{cc}
            \Pi_1 & \Pi_2 \\
            {\Phi  \vdash_\mathcal{C}  \SCnt{X}} & {\Gamma_{{\mathrm{1}}}  \SCsym{;}  \SCnt{X}  \SCsym{;}  \Gamma_{{\mathrm{2}}}  \vdash_\mathcal{L}  \SCnt{A}}
          \end{array}
        }
      }{\Gamma_{{\mathrm{1}}}  \SCsym{;}  \Phi  \SCsym{;}  \Gamma_{{\mathrm{2}}}  \vdash_\mathcal{L}  \SCnt{A}}
    \end{math}
  \end{center}
  By assumption, $c(\Pi_1),c(\Pi_2)\leq |X|+1$. By induction, we can
  construct $c(\Pi_1')$ proving $\Phi  \vdash_\mathcal{C}  \SCnt{X}$ and $c(\Pi_2')$ proving
  $\Psi_{{\mathrm{1}}}  \SCsym{,}  \SCnt{X}  \SCsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \SCnt{Y}$ (or $<\Gamma_{{\mathrm{1}}}  \SCsym{;}  \SCnt{X}  \SCsym{;}  \Gamma_{{\mathrm{2}}}  \vdash_\mathcal{L}  \SCnt{A}$) with
  $c(\Pi_1'), c(\Pi_2')\leq |X|$. Then by Lemma~\ref{lem:cut-reduction}, we
  can construct $\Pi'$ proving $\Psi_{{\mathrm{1}}}  \SCsym{,}  \Phi  \SCsym{,}  \Psi_{{\mathrm{2}}}  \vdash_\mathcal{C}  \SCnt{Y}$ (or
  $\Gamma_{{\mathrm{1}}}  \SCsym{;}  \Phi  \SCsym{;}  \Gamma_{{\mathrm{2}}}  \vdash_\mathcal{L}  \SCnt{A}$) with $c(\Pi')\leq |X|$. \\
  The case where the last inference is a cut on a formula $A$ is similar as
  when it is a cut on $X$.
\end{proof}
\noindent
By induction on $c(\Pi)$ and Lemma~\ref{lem:less-cut-rank}, the cut
elimination theorem follows immediately.
\begin{theorem}[Cut Elimination]
  Let $\Pi$ be a proof of a sequent $\Phi  \vdash_\mathcal{C}  \SCnt{X}$ or $\Gamma  \vdash_\mathcal{L}  \SCnt{A}$ s.t.
  $c(\Pi)>0$. Then there is an algorithm which yields a cut-free proof
  $\Pi'$ of the same sequent.
\end{theorem}

### 2019-02-28 post-linearity-2018/dialectica-spaces.tex
Fixed the overflows.

--- 2018-04-13 linearity-2018/dialectica-spaces.tex
@@
   complete formalization can be found online at
-  \url{https://github.com/MonoidalAttackTrees/non-comm-monads-adjoint-models/tree/master/dialectica-formalization}.}
+  \href{https://github.com/MonoidalAttackTrees/non-comm-monads-adjoint-models/tree/master/dialectica-formalization}{our Github repository}.}
 this section in the proof assistant Agda~\cite{bove2009}.
@@
   \item[-] objects, or dialectica Lambek spaces, are triples $(U, X,
-    \alpha)$ where $U$ and $X$ are sets, and $\alpha : U \times X \mto
-    M$ is a generalized relation over $M$, and
-
+    \alpha)$ where $U$ and $X$ are sets, and \\
+    $\alpha : U \times X \mto M$ is a generalized relation over $M$, and
   \item[-] maps that are pairs $(f, F) : (U , X, \alpha) \mto (V , Y ,
@@
   \rhd \beta)((u, v), (f, g)) = \alpha(u, f(v)) \circ \beta(g(u), v)$.
+
+  \ \\
+  \noindent
+  The unit of the above tensor product is defined as follows:
+  \[ \small
+  I = (\top , \top , \iota)
+  \]
+  where $\top$ is the initial object in $\Set$, and $\iota(*,*) = e$.
 \end{definition}
@@
   \textbf{exchange} modalities can be defined as 
-  $! (U, X, \alpha) = (U, U \to X^*, !\alpha)$ and
+  $! (U, X, \alpha) = (U, U \to X^*, !\alpha)$ and \\
   $\xi (U, X, \alpha) = (U, X, \xi \alpha)$
@@
   Suppose $M$ is a biclosed poset with exchange.  Then
-  $\Dial{M}{\Set}$ is a sound and complete model for CNC logic.
+  $\Dial{M}{\Set}$ is a sound model for CNC logic.
 \end{theorem}

### 2019-02-28 post-linearity-2018/sequent.tex
Fixed the overflows.

@@
 Calculus. We have two unit types $[[UnitS]]$ (one for each side), a
-non-commutative tensor product $[[A (>) B]]$, right implication
-$[[A -> B]]$, and left implication $[[B <- A]]$. In standard Lambek
-Calculus, $[[A -> B]]$ is written as $B / A$ and $[[B <- A]]$ as
-$A \backslash B$. We use $\rightharpoonup$ and $\leftharpoonup$ here
-instead to indicate they are two directions of the linear implication
-$\multimap$.
+non-commutative tensor product $[[A (>) B]]$, right implication $[[A
+    -> B]]$, and left implication $[[B <- A]]$. In standard Lambek
+Calculus \cite{Pentus1995}, $[[A -> B]]$ is written as $B / A$ and
+$[[B <- A]]$ as $A \backslash B$. We use $\rightharpoonup$ and
+$\leftharpoonup$ here instead to indicate they are two directions of
+the linear implication $\multimap$.
 
-The sequenct calculus for CNC logic can be found in
+The sequent calculus for CNC logic can be found in
 Figure~\ref{fig:CNC-sequent-calculus}. We split the figure in two: the top
@@
   \footnotesize
+  \resizebox{\columnwidth}{!}{%
   \begin{tabular}{|c|}
@@
     \SCdruleTXXimpL{} \and
-    \SCdruleTXXimpR{} \and
+    \SCdruleTXXimpR{} \\
     \SCdruleTXXGr{} \and
@@
   \end{tabular}
+  }
   \caption{Sequent Calculus for CNC Logic}
